---
title: "width_beach"
author: "Edgar"
date: "2024-07-17"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r }
library(ggplot2)
library(tidyr)
library(forcats)
library(dplyr)
library(readxl) 
library(readr)
library(RColorBrewer)
library(tidyverse)
library(binom)
library(lubridate)
library(ade4)
library(ggrepel)
library(broom)
library(ggpubr)
library(rstatix)
library(wesanderson)
library(car)
library(multcompView)
library(rcompanion)
library(writexl)
library(gmodels)
library(tools)
library(fmsb)
```

```{r import data}
surval_modif <- read_excel("Datasheets/surval_modif.xlsx") %>% 
  separate(coeff, into = c("coeff1", "coeff2"), sep = "/") %>% 
  mutate(across(c(coeff1, coeff2), as.numeric)) %>% 
  rowwise() %>%
  mutate(coeff_mean = mean(c(coeff1, coeff2), na.rm = TRUE),
         surface_m2 = width_high_tide_mark*100) %>%
  ungroup() %>% 
  rename(width_beach = width_high_tide_mark) 
surval_modif

```

```{r regression width vs. coeff}

surval_low <- surval_modif %>% 
  filter(tide == "low"| tide == "middle")
surval_low

surval_high <- surval_modif %>% 
  filter(tide == "high")
surval_high

CrossTable(surval_modif$site)

G_reg <- surval_low%>% 
  ggplot(aes(x = coeff_mean, y = width_beach, color = tide)) +
  geom_point() +
  geom_smooth(method = "lm", se = T, color = "black") +
  facet_wrap(~site, scales = "free") 
G_reg
```

Correlation results are so weird. I recommend to do a mean width of the low and middle tides for each site.

```{r}
avg_width_low <- surval_low %>% 
  group_by(Country, North_South, site) %>% 
  summarise(n_L = n(),
            avg_width_L = mean(width_beach, na.rm = TRUE),
            sd_width_L = sd(width_beach, na.rm = TRUE),
            avg_surface_L = mean(surface_m2, na.rm = TRUE),
            sd_surface_L = sd(surface_m2, na.rm = TRUE))
avg_width_low

avg_width_high <- surval_high %>% 
  group_by(Country, North_South, site) %>% 
  summarise(n_H = n(),
            avg_width_H = mean(width_beach, na.rm = TRUE),
            sd_width_H = sd(width_beach, na.rm = TRUE),
            avg_surface_H = mean(surface_m2, na.rm = TRUE),
            sd_surface_H = sd(surface_m2, na.rm = TRUE))
avg_width_high

avg_joined <- left_join(avg_width_low, avg_width_high, by = c("site", "Country", "North_South")) %>% 
filter(site != "Le Teich") %>% mutate(cov_rate_S = 100-(avg_surface_H*100/avg_surface_L)) %>% 
  rename(Site_long = site,
         Site = North_South)
avg_joined

avg_for_join <- avg_joined %>% 
  ungroup() %>% 
  dplyr::select(Site, avg_surface_L)

#write_xlsx(avg_for_join, "Datasheets/avg_for_join.xlsx")

#Mean beach coverage at high tide
avg_cv_HT <- avg_joined %>% 
  group_by(Country) %>% 
  summarise(avg_cov_rate_S = mean(cov_rate_S, na.rm = TRUE),
            sd_cov_rate_S = sd(cov_rate_S, na.rm = TRUE))
avg_cv_HT

```

cov_rate_S is the percentage of surface of the beach covered by the high tide

At low tide French beaches are 1.7 to 6.2 time widerthan Basque country ones. 
At high tide, French beaches are 1.8 to 24.5 times wider than Basque country ones. 
The percentage of surface covered by the high tide is 1.6 to 2.5 times higher in Basque country than in France.
In average at high tide French beaches are recovered at 31.5±15.7% by the sea while the Spanish ones are covered at 58.7±20.3%. 

```{r stat coverage}
df_stat <- avg_joined %>% 
  dplyr::select(Country, cov_rate_S)
df_stat

france_data <- df_stat$cov_rate_S[df_stat$Country == "France"]
shapiro.test(france_data)
spain_data <- df_stat$cov_rate_S[df_stat$Country == "Spain"]
shapiro.test(spain_data)

par(mfrow=c(1,2))
qqnorm(france_data, main="Q-Q Plot France")
qqline(france_data)
qqnorm(spain_data, main="Q-Q Plot Espagne")
qqline(spain_data)

#Statistical test for the coverage rate
##t-test
t_test <- t.test(france_data, spain_data)
t_test

##MWU
wilcox.test(cov_rate_S ~ Country, data = df_stat)

```


















