---
title: "Fish behavior"
author: "Edgar Dusacre"
date: "13/06/2023"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r Insertion package, include=FALSE}
library(ggplot2) 
library(tidyr)
library(purrr)
library(tidyverse)
library(ggrepel)
library(ggpubr)
library(knitr)
library(yaml)
library(dplyr) 
library(matrixStats)
library(EnvStats)
library(stringr)
library(gtable)
library(grid)
library(FSA)
library(scales)
library(wbstats)
library(ggh4x)
library(multcompView)
library(report)
library(ecotox)
library(wesanderson)
library(RColorBrewer)
library(readr)
library(readxl)
library(gmodels)
library(ggpattern)
library(zoo)
library(forcats)
library(car)
library(dunn.test)



library(forcats)
library(binom)
library(lubridate)
library(ade4)
library(broom)
library(rstatix)
library(rcompanion)
library(chron)
library(devtools)
library(PMCMRplus)
library(grDevices)
```

```{r Charger les palettes de couleurs, include=FALSE}
Plasfito_C <- c("#80CAD0", "#36A7A7", "#276573", "#054959","#E3CCC0", "#F7EAE1", "#A48A7B", "#C6AF8D", "#49BED3", "#256CB4", "#008163", "#44B494", "#7BC6B9")

Plasfito_color <- c("GreenP4" = "#80CAD0", "GreenP3" = "#36A7A7", "GreenP2" = "#276573", "GreenP1" = "#054959","Brown1" = "#E3CCC0", "Brown2" = "#F7EAE1", "Brown3" = "#A48A7B", "Brown4" = "#C6AF8D", "Turquoise1" = "#49BED3", "Blue1" = "#256CB4", "Green1" = "#008163", "Green2" = "#44B494", "Green3" = "#7BC6B9")

List_color_Fr <- c("Mimizan" = "#008163" , "Bayonne" = "#44B494", "Hendaye" = "#7BC6B9", 
                   "Capbretons"  = "#80CAD0", "Arcachon" = "#36A7A7", "St_Jean" = "#276573")

List_color <- c("Mimizan" = "#008163" , "Bayonne" = "#44B494", "Hendaye" = "#7BC6B9", 
                 "Capbretons"  = "#80CAD0", "Arcachon" = "#36A7A7", "St_Jean" = "#276573",
                 "Euskadi" = "#054959")

Plasfito_Tps <- c("5" = "#80CAD0", "15" = "#36A7A7", "30" = "#276573")


#A part si vous souhaitez changer les couleurs do not touch.
Ech_K2CR2O7<- c("K2CR2O7" = "#80CAD0")

Tps_color <- c("5" = "#80CAD0" , "15" = "#36A7A7", "30" = "#276573")

Dilu_color <- c("0.0125" = "#80CAD0" , "0.025" = "#36A7A7", "0.05" = "#276573", "0.1" = "#008163")

Conc_color <- c("0.4125" = "#80CAD0" , "0.825" = "#36A7A7", "1.65" = "#276573", "3.3" = "#008163")
Conc_color3 <- c("0.825" = "aquamarine", "1.65" = "#36A7A7", "3.3" = "#276573")

Color_biolu_Pasaia <- c("Ech1" = "aquamarine", "Ech2" = "#36A7A7" , "DMSO" = "#A48A7B")

Color_real_FN <- c("dmso" = "#A48A7B", "CTL" = "#256CB4", "PA_a35" = "#4fd355", "PA_b33" = "#ca98d3", "PA_b95" = "#6e217c", "PA_g33" = "#92b78f", "PA_g60" = "#bbb3bc", "PBS_d35" = "#d3ad4f","PBS_d60" = "#c68640", "HPPE_e425" = "#36A7A7")
```


Pour l'analyse poisson, tout run n'est pas forcément utile, mieux vaut faire analyse par analyse car on retrouve parfois les mêmes noms.

# BLA LOFF 
```{r data import new}
# Mettre le bon trajet dossier adapté :

BLA_OFF_all <- rbind(BLA_OFF_n, BLA_OFF_u) 
BLA_OFF_all
```


```{r Outliers 25 100%}
#Boxplot by replicates to see if there are outliers

Outliers <- BLA_OFF_all %>% 
  ggplot(aes(FN, Dist_tot1, fill = state)) + 
  geom_violin(fill = NA, aes(color = FN), width = 1) +
  geom_boxplot(width = 0.3) 

Outliers
```


```{r Average tibble}

#Average and boxplot by replicates to see if there is outliers
BLA_OFF_avg_Rep <- BLA_OFF_all %>% group_by(FN, Rep, state) %>%  summarise(n = n(), 
                                                          Vel_avg = mean(Vel_avg1, na.rm=T),
                                                          Vel_sd = sd(Vel_avg1, na.rm=T), 
                                                          Vel_se = Vel_sd / sqrt(n),
                                                          Dist_avg = mean(Dist_avg1, na.rm=T),
                                                          Dist_sd = sd(Dist_avg1, na.rm=T), 
                                                          Dist_se = Dist_sd / sqrt(n),
                                                          Dtot_avg = mean(Dist_tot1, na.rm=T),
                                                          Dtot_sd = sd(Dist_tot1, na.rm=T), 
                                                          Dtot_se = Dtot_sd / sqrt(n)) %>% dplyr::select(-Vel_sd, -Dist_sd, -Dtot_sd) %>% mutate(ID = "LOFF")

BLA_OFF_avg_Rep

BLA_OFF_avg <- BLA_OFF_all %>% group_by(FN, state) %>%  summarise(n = n(), 
                                                          Vel_avg = mean(Vel_avg1, na.rm=T),
                                                          Vel_sd = sd(Vel_avg1, na.rm=T), 
                                                          Vel_se = Vel_sd / sqrt(n),
                                                          Dist_avg = mean(Dist_avg1, na.rm=T),
                                                          Dist_sd = sd(Dist_avg1, na.rm=T), 
                                                          Dist_se = Dist_sd / sqrt(n),
                                                          Dtot_med = median(Dist_tot1, na.rm=T),
                                                          Dtot_avg = mean(Dist_tot1, na.rm=T),
                                                          Dtot_sd = sd(Dist_tot1, na.rm=T), 
                                                          Dtot_se = Dtot_sd / sqrt(n),
                                                          Dtot_low = quantile(Dist_tot1, probs = 0.025, na.rm= T), 
                                                          Dtot_up = quantile(Dist_tot1, probs = 0.975, na.rm= T)) #%>% select(-Vel_sd, -Dist_sd, -Dtot_sd) %>% mutate(ID = "LOFF")
  

BLA_OFF_avg 

```

```{r Graph}

BLA_OFF_avg %>% 
  arrange(desc(state)) %>% 
  ggplot(aes(x= FN, y = Dtot_med, fill = state)) + 
  geom_col(width =0.5, position = position_dodge()) +
  geom_errorbar(aes(ymin= ifelse(Dtot_med-Dtot_se < 0, 0, Dtot_med-Dtot_se), ymax=Dtot_med+Dtot_se), width=0.08, size = 1, position=position_dodge(width=0.5)) +
  scale_fill_brewer(palette = "Paired") +
  theme_bw()

```

```{r Ctl Avg et stat}

BLA_OFF_avg_ctl <- BLA_OFF_all %>% filter(FN == "dmso") %>% 
  #filter(!Dist_tot1 >= 2900) %>% 
  group_by(FN, state) %>%  
  summarise(n = n(), 
            Vel_avg = mean(Vel_avg1, na.rm=T),
            Vel_sd = sd(Vel_avg1, na.rm=T), 
            Vel_se = Vel_sd / sqrt(n),
            Dist_avg = mean(Dist_avg1, na.rm=T),
            Dist_sd = sd(Dist_avg1, na.rm=T), 
            Dist_se = Dist_sd / sqrt(n),
            Dtot_med = median(Dist_tot1, na.rm=T),
            Dtot_avg = mean(Dist_tot1, na.rm=T),
            Dtot_sd = sd(Dist_tot1, na.rm=T), 
            Dtot_se = Dtot_sd / sqrt(n),
            Dtot_low = quantile(Dist_tot1, probs = 0.025, na.rm= T), 
            Dtot_up = quantile(Dist_tot1, probs = 0.975, na.rm= T)) #%>% select(-Vel_sd, -Dist_sd, -Dtot_sd) %>% mutate(ID = "LOFF")
  

BLA_OFF_avg_ctl

BLA_OFF_ctl_n <- BLA_OFF_avg_ctl %>% filter(state == "n")
BLA_OFF_ctl_u <- BLA_OFF_avg_ctl %>% filter(state == "u")

```

```{r Normalisation des données autour du CTL}

#Adjusted with the blank median
Dist_tot_aju <- BLA_OFF_all %>% 
  mutate(aju_Dtot = if_else(state == "n", (Dist_tot1 * 100) / BLA_OFF_ctl_n$Dtot_med,
                            if_else(state == "u", (Dist_tot1 * 100) / BLA_OFF_ctl_u$Dtot_med,  NA)))
Dist_tot_aju

#raw data ready for IBR analysis
IBR_BLA_OFF <- Dist_tot_aju %>% 
  mutate(endpt = "BLA_OFF") %>% 
  select(Arena, FN, Rep, state, endpt, aju_Dtot) %>% filter(FN != "benzo") %>% 
  rename(value = aju_Dtot)
IBR_BLA_OFF

#Adjusted with the blank average
Dist_tot_aju_avg <- BLA_OFF_all %>% 
  mutate(aju_Dtot = if_else(state == "n", (Dist_tot1 * 100) / BLA_OFF_ctl_n$Dtot_avg,
                            if_else(state == "u", (Dist_tot1 * 100) / BLA_OFF_ctl_u$Dtot_avg,  NA))) 
Dist_tot_aju_avg

df_avg_BLA_avg <- Dist_tot_aju_avg %>% 
  group_by(FN, state) %>% 
  summarise(n = n(),
            avg_val_adj = mean(aju_Dtot), 
            sd_val_adj = sd(aju_Dtot),
            se_val_adj = sd_val_adj/sqrt(n)) %>% 
  mutate(endpt = as.factor("BLA_OFF"))
  
df_avg_BLA_avg

df_avg_BLA <- Dist_tot_aju %>% 
  group_by(FN, state) %>% 
  summarise(n = n(),
            med_Dtot_adj = median(aju_Dtot), 
            sd_Dtot_adj = sd(aju_Dtot),
            se_Dtot_adj = sd_Dtot_adj/sqrt(n)) %>% 
  mutate(endpt = as.factor("BLA_OFF"))

df_avg_BLA$endpt_UV <- paste(df_avg_BLA$endpt, df_avg_BLA$state, sep = "_")  
  
df_avg_BLA

```

```{r Visualisation}
BoxDtot <- Dist_tot_aju %>% 
  ggplot(aes(x = FN, y = aju_Dtot, fill = state)) +
  geom_boxplot(width = 0.2, position = position_dodge(width = 0.6)) +
  stat_summary(fun = mean, 
               geom = "point", 
               size = 2, 
               color = "red3", 
               position = position_dodge(width = 0.6)) +
  geom_hline(yintercept = 100, colour = "black", linetype = "dashed") +
  scale_y_continuous(limits = c(0, 1250)) +
  theme_minimal() +
  labs(x = "Fishing nets",
       y = "Heart bate (% of the control)",
       title = expression(paste("Effect of aa leachates on the cardiac rhythm of ", italic("Oryzias latipes"))),
       subtitle = "Concentration plastic eq.= 0.33 mg/ml",
       fill = "Treatment" ) +
  theme(axis.title.x = element_text(size = 14, face = "bold", vjust = 0.5, margin = margin(t = 10, r = 20, b = 0, l = 0)),
        axis.title.y = element_text(size = 14, face = "bold", vjust = 3, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.text.x = element_text(size = 14, face = 'bold'),
        axis.text.y = element_text(size = 12, face = 'bold'),
        title = element_text(size = 12, face = "bold"),
        strip.text = element_text(face = "bold", size = rel(1)),
        legend.position = "top",
        legend.spacing.x = unit(0.5, 'cm'),
        legend.text = element_text(size = 12, face = 'bold'),
        legend.key.size = unit(1.5, "cm"),
        legend.key.width = unit(0.5, "cm"),
        plot.margin = unit(c(1, 1, 1, 1), "cm"))
BoxDtot
```

```{r Statistics}
Dunn_all_BLA <- rbind(MWU_n_Lett_BLAOFF_new %>% mutate(state = "n"), MWU_u_Lett_BLAOFF_used %>% mutate(state = "u")) 
Dunn_all_BLA
```

```{r final table}
Dunn_all_BLA_s <- Dunn_all_BLA %>%  dplyr::select(-max_value)
Dunn_all_BLA_s

BLA_OFF_all_f <- df_avg_BLA %>% left_join(Dunn_all_BLA_s) %>% arrange(state) %>% mutate(diff = if_else(diff == "ns", NA, diff))
BLA_OFF_all_f
```

```{r Heatmap BLA}

max_Dtot_BLA <- max(BLA_OFF_all_f$med_Dtot_adj)
max_Dtot_BLA

min_Dtot_BLA <- 100-(max_Dtot_BLA-100)+1
min_Dtot_BLA


HM_BLA <- BLA_OFF_all_f %>% filter(FN != "dmso", FN != "benzo") %>% 
  ggplot(aes(x = FN, y = factor(endpt_UV, levels = rev(unique(endpt_UV))), fill = med_Dtot_adj)) +
  geom_tile(height = 1, width = 1) +
  scale_fill_gradient2(low = "#36A7A7", high = "#b751ca", mid = "white", 
   midpoint = 100, limit = c(min_Dtot_BLA-1, max_Dtot_BLA), 
   breaks = round(c(0, 100, max_Dtot_BLA), digits = 0), 
   guide = "colourbar") +
  scale_x_discrete(labels = c("PA6 \u03B1 35 \nn = 48",
                              "PA6 \u03B2 33 \nn = 48",
                              "PA6 \u03B2 95 \nn = 48",
                              "PBS-PBAT \n\u03B4 35\nn = 48",
                              "PBS-PBAT \n\u03B4 60\nn = 48",
                              "HPPE-PP \n\u03B5 4.25\nn = 48",
                              "PA6 \u03B3 33\nn = 48",
                              "PA6 \u03B3 60\nn = 48")) +
  labs(#title = "Effect of the fishing nets leachates on medaka fish",
       x = "Fishing nets",
       fill = "Blank H2O = 100",
       legend.box.just = "center") +
  theme_classic() +
  theme(axis.title.x = element_text(size = 14, face = "bold", vjust = 0.5, margin = margin(t = 10, r = 20, b = 0, l = 0)),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 14, face = 'bold'),
        axis.text.y = element_text(size = 12, face = 'bold'),
        title = element_text(size = 12, face = "bold"),
        strip.text = element_text(face = "bold", size = rel(1)),
        legend.position = "top",
        legend.spacing.x = unit(0.5, 'cm'),
        legend.text = element_text(size = 12, face = 'bold', color = "black"),
        legend.key = element_rect(color = "black"),
        legend.key.size = unit(0.85, "cm"),
        legend.key.width = unit(1, "cm"),
        legend.title.align = 0.5,
        plot.margin = unit(c(1, 1, 1, 1), "cm"),
        aspect.ratio = 3/8) +
  guides(fill = guide_colourbar(title.position="top", 
                                title.vjust = 2, 
                                ticks.colour = "black", 
                                barheight = unit( 0.3 , "in" ),))

HM_BLA + geom_text(aes(FN, endpt_UV, label = round(med_Dtot_adj, digits = 1)), color = "black", size = 3.5, fontface = "bold") +
  geom_text(aes(FN, endpt_UV, label = diff), size = 5, vjust = 2, color = "black", fontface = "bold")


```

# BLA LON
```{r data import new}
# Mettre le bon trajet dossier adapté :

BLA_LON_all <- rbind(BLA_ON_n, BLA_ON_u) 
BLA_LON_all
```


```{r Outliers 25 100%}
#Boxplot by replicates to see if there are outliers

Outliers <- BLA_LON_all %>% 
  ggplot(aes(FN, Dist_tot1, fill = state)) + 
  geom_violin(fill = NA, aes(color = FN), width = 1) +
  geom_boxplot(width = 0.3) 

Outliers
```


```{r Average tibble}

#Average and boxplot by replicates to see if there is outliers
BLA_LON_avg_Rep <- BLA_LON_all %>% group_by(FN, Rep, state) %>%  summarise(n = n(), 
                                                          Vel_avg = mean(Vel_avg1, na.rm=T),
                                                          Vel_sd = sd(Vel_avg1, na.rm=T), 
                                                          Vel_se = Vel_sd / sqrt(n),
                                                          Dist_avg = mean(Dist_avg1, na.rm=T),
                                                          Dist_sd = sd(Dist_avg1, na.rm=T), 
                                                          Dist_se = Dist_sd / sqrt(n),
                                                          Dtot_avg = mean(Dist_tot1, na.rm=T),
                                                          Dtot_sd = sd(Dist_tot1, na.rm=T), 
                                                          Dtot_se = Dtot_sd / sqrt(n)) %>% dplyr::select(-Vel_sd, -Dist_sd, -Dtot_sd) %>% mutate(ID = "LOFF")

BLA_LON_avg_Rep

BLA_LON_avg <- BLA_LON_all %>% group_by(FN, state) %>%  summarise(n = n(), 
                                                          Vel_avg = mean(Vel_avg1, na.rm=T),
                                                          Vel_sd = sd(Vel_avg1, na.rm=T), 
                                                          Vel_se = Vel_sd / sqrt(n),
                                                          Dist_avg = mean(Dist_avg1, na.rm=T),
                                                          Dist_sd = sd(Dist_avg1, na.rm=T), 
                                                          Dist_se = Dist_sd / sqrt(n),
                                                          Dtot_med = median(Dist_tot1, na.rm=T),
                                                          Dtot_avg = mean(Dist_tot1, na.rm=T),
                                                          Dtot_sd = sd(Dist_tot1, na.rm=T), 
                                                          Dtot_se = Dtot_sd / sqrt(n),
                                                          Dtot_low = quantile(Dist_tot1, probs = 0.025, na.rm= T), 
                                                          Dtot_up = quantile(Dist_tot1, probs = 0.975, na.rm= T)) #%>% select(-Vel_sd, -Dist_sd, -Dtot_sd) %>% mutate(ID = "LOFF")
  

BLA_LON_avg 

```

```{r Graph}

BLA_LON_avg %>% 
  arrange(desc(state)) %>% 
  ggplot(aes(x= FN, y = Dtot_med, fill = state)) + 
  geom_col(width =0.5, position = position_dodge()) +
  geom_errorbar(aes(ymin= ifelse(Dtot_med-Dtot_se < 0, 0, Dtot_med-Dtot_se), ymax=Dtot_med+Dtot_se), width=0.08, size = 1, position=position_dodge(width=0.5)) +
  scale_fill_brewer(palette = "Paired") +
  theme_bw()

```

```{r Ctl Avg et stat}

BLA_LON_avg_ctl <- BLA_LON_all %>% filter(FN == "dmso") %>% 
  #filter(!Dist_tot1 >= 2900) %>% 
  group_by(FN, state) %>%  
  summarise(n = n(), 
            Vel_avg = mean(Vel_avg1, na.rm=T),
            Vel_sd = sd(Vel_avg1, na.rm=T), 
            Vel_se = Vel_sd / sqrt(n),
            Dist_avg = mean(Dist_avg1, na.rm=T),
            Dist_sd = sd(Dist_avg1, na.rm=T), 
            Dist_se = Dist_sd / sqrt(n),
            Dtot_med = median(Dist_tot1, na.rm=T),
            Dtot_avg = mean(Dist_tot1, na.rm=T),
            Dtot_sd = sd(Dist_tot1, na.rm=T), 
            Dtot_se = Dtot_sd / sqrt(n),
            Dtot_low = quantile(Dist_tot1, probs = 0.025, na.rm= T), 
            Dtot_up = quantile(Dist_tot1, probs = 0.975, na.rm= T)) #%>% select(-Vel_sd, -Dist_sd, -Dtot_sd) %>% mutate(ID = "LOFF")
  

BLA_LON_avg_ctl

BLA_LON_ctl_n <- BLA_LON_avg_ctl %>% filter(state == "n")
BLA_LON_ctl_u <- BLA_LON_avg_ctl %>% filter(state == "u")

```

```{r Normalisation des données autour du CTL}

Dist_tot_aju <- BLA_LON_all %>% 
  mutate(aju_Dtot = if_else(state == "n", (Dist_tot1 * 100) / BLA_LON_ctl_n$Dtot_med,
                            if_else(state == "u", (Dist_tot1 * 100) / BLA_LON_ctl_u$Dtot_med,  NA)))
Dist_tot_aju

#raw data ready for IBR analysis
IBR_BLA_ON <- Dist_tot_aju %>% 
  mutate(endpt = "BLA_ON") %>% 
  select(Arena, FN, Rep, state, endpt, aju_Dtot) %>% filter(FN != "benzo") %>% 
  rename(value = aju_Dtot)
IBR_BLA_ON

Dist_tot_aju_avg <- BLA_LON_all %>% 
  mutate(aju_Dtot = if_else(state == "n", (Dist_tot1 * 100) / BLA_LON_ctl_n$Dtot_avg,
                            if_else(state == "u", (Dist_tot1 * 100) / BLA_LON_ctl_u$Dtot_avg,  NA)))
Dist_tot_aju_avg

df_avg_BLAON_avg <- Dist_tot_aju_avg %>% 
  group_by(FN, state) %>% 
  summarise(n = n(),
            avg_val_adj = mean(aju_Dtot), 
            sd_val_adj = sd(aju_Dtot),
            se_val_adj = sd_val_adj/sqrt(n)) %>% 
  mutate(endpt = as.factor("BLA_LON"))
  
df_avg_BLAON_avg

df_avg_BLAON <- Dist_tot_aju %>% 
  group_by(FN, state) %>% 
  summarise(n = n(),
            med_Dtot_adj = median(aju_Dtot), 
            sd_Dtot_adj = sd(aju_Dtot),
            se_Dtot_adj = sd_Dtot_adj/sqrt(n)) %>% 
  mutate(endpt = as.factor("BLA_LON"))

df_avg_BLAON$endpt_UV <- paste(df_avg_BLAON$endpt, df_avg_BLAON$state, sep = "_")  
  
df_avg_BLAON

```

```{r Visualisation}
BoxDtot <- Dist_tot_aju %>% 
  ggplot(aes(x = FN, y = aju_Dtot, fill = state)) +
  geom_boxplot(width = 0.2, position = position_dodge(width = 0.6)) +
  stat_summary(fun = mean, 
               geom = "point", 
               size = 2, 
               color = "red3", 
               position = position_dodge(width = 0.6)) +
  geom_hline(yintercept = 100, colour = "black", linetype = "dashed") +
  scale_y_continuous(limits = c(0, 400)) +
  theme_minimal() +
  labs(x = "Fishing nets",
       y = "Heart bate (% of the control)",
       title = expression(paste("Effect of aa leachates on the cardiac rhythm of ", italic("Oryzias latipes"))),
       subtitle = "Concentration plastic eq.= 0.33 mg/ml",
       fill = "Treatment" ) +
  theme(axis.title.x = element_text(size = 14, face = "bold", vjust = 0.5, margin = margin(t = 10, r = 20, b = 0, l = 0)),
        axis.title.y = element_text(size = 14, face = "bold", vjust = 3, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.text.x = element_text(size = 14, face = 'bold'),
        axis.text.y = element_text(size = 12, face = 'bold'),
        title = element_text(size = 12, face = "bold"),
        strip.text = element_text(face = "bold", size = rel(1)),
        legend.position = "top",
        legend.spacing.x = unit(0.5, 'cm'),
        legend.text = element_text(size = 12, face = 'bold'),
        legend.key.size = unit(1.5, "cm"),
        legend.key.width = unit(0.5, "cm"),
        plot.margin = unit(c(1, 1, 1, 1), "cm"))
BoxDtot
```

```{r Statistics}
Dunn_all_BLA_ON <- rbind(MWU_n_Lett_BLAON_new %>% mutate(state = "n"), MWU_u_Lett_BLAON_used %>% mutate(state = "u")) 
Dunn_all_BLA_ON
```

```{r final table}
Dunn_all_BLAON_s <- Dunn_all_BLA_ON %>%  dplyr::select(-max_value)
Dunn_all_BLAON_s

BLA_LON_all_f <- df_avg_BLAON %>% left_join(Dunn_all_BLAON_s) %>% arrange(state) %>% mutate(diff = if_else(diff == "ns", NA, diff))
BLA_LON_all_f

```

```{r Heatmap BLA_ON}

max_Dtot_BLA_ON <- max(BLA_LON_all_f$med_Dtot_adj)
max_Dtot_BLA_ON

min_Dtot_BLA_ON <- 100-(max_Dtot_BLA_ON-100)+1
min_Dtot_BLA_ON


HM_BLA_ON <- BLA_LON_all_f %>% filter(FN != "dmso", FN != "benzo") %>% 
  ggplot(aes(x = FN, y = factor(endpt_UV, levels = rev(unique(endpt_UV))), fill = med_Dtot_adj)) +
  geom_tile(height = 1, width = 1) +
  scale_fill_gradient2(low = "#36A7A7", high = "#b751ca", mid = "white", 
   midpoint = 100, limit = c(min_Dtot_BLA_ON-1, max_Dtot_BLA_ON), 
   breaks = round(c(0, 100, max_Dtot_BLA_ON), digits = 0), 
   guide = "colourbar") +
  scale_x_discrete(labels = c("PA6 \u03B1 35 \nn = 48",
                              "PA6 \u03B2 33 \nn = 48",
                              "PA6 \u03B2 95 \nn = 48",
                              "PBS-PBAT \n\u03B4 60\nn = 48",
                              "PBS-PBAT \n\u03B4 35\nn = 48",
                              "HPPE-PP \n\u03B5 4.25\nn = 48",
                              "PA6 \u03B3 33\nn = 48",
                              "PA6 \u03B3 60\nn = 48")) +
  labs(#title = "Effect of the fishing nets leachates on medaka fish",
       x = "Fishing nets",
       fill = "Blank H2O = 100",
       legend.box.just = "center") +
  theme_classic() +
  theme(axis.title.x = element_text(size = 14, face = "bold", vjust = 0.5, margin = margin(t = 10, r = 20, b = 0, l = 0)),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 14, face = 'bold'),
        axis.text.y = element_text(size = 12, face = 'bold'),
        title = element_text(size = 12, face = "bold"),
        strip.text = element_text(face = "bold", size = rel(1)),
        legend.position = "top",
        legend.spacing.x = unit(0.5, 'cm'),
        legend.text = element_text(size = 12, face = 'bold', color = "black"),
        legend.key = element_rect(color = "black"),
        legend.key.size = unit(0.85, "cm"),
        legend.key.width = unit(1, "cm"),
        legend.title.align = 0.5,
        plot.margin = unit(c(1, 1, 1, 1), "cm"),
        aspect.ratio = 3/8) +
  guides(fill = guide_colourbar(title.position="top", 
                                title.vjust = 2, 
                                ticks.colour = "black", 
                                barheight = unit( 0.3 , "in" ),))

HM_BLA_ON + geom_text(aes(FN, endpt_UV, label = round(med_Dtot_adj, digits = 1)), color = "black", size = 3.5, fontface = "bold") +
  geom_text(aes(FN, endpt_UV, label = diff), size = 5, vjust = 2, color = "black", fontface = "bold")


```

# VLSR
```{r data import new}
# Mettre le bon trajet dossier adapté :

VLSR_all <- rbind(VLSR_stimu_n, VLSR_stimu_u) 
VLSR_all
```


```{r Outliers 25 100%}
#Boxplot by replicates to see if there are outliers

Outliers <- VLSR_all %>% 
  ggplot(aes(FN, Dist_tot1, fill = state)) + 
  geom_violin(fill = NA, aes(color = FN), width = 1) +
  geom_boxplot(width = 0.3) 

Outliers
```


```{r Average tibble}

#Average and boxplot by replicates to see if there is outliers
VLSR_avg_Rep <- VLSR_all %>% group_by(FN, Rep, state) %>%  summarise(n = n(), 
                                                          Dtot_avg = mean(Dist_tot1, na.rm=T),
                                                          Dtot_sd = sd(Dist_tot1, na.rm=T), 
                                                          Dtot_se = Dtot_sd / sqrt(n)) %>% dplyr::select(-Dtot_sd) %>% mutate(ID = "LOFF")

VLSR_avg_Rep

VLSR_avg <- VLSR_all %>% group_by(FN, state) %>%  summarise(n = n(), 
                                                          Dtot_med = median(Dist_tot1, na.rm=T),
                                                          Dtot_avg = mean(Dist_tot1, na.rm=T),
                                                          Dtot_sd = sd(Dist_tot1, na.rm=T), 
                                                          Dtot_se = Dtot_sd / sqrt(n),
                                                          Dtot_low = quantile(Dist_tot1, probs = 0.025, na.rm= T), 
                                                          Dtot_up = quantile(Dist_tot1, probs = 0.975, na.rm= T)) #%>% select(-Vel_sd, -Dist_sd, -Dtot_sd) %>% mutate(ID = "LOFF")
  

VLSR_avg 

```

```{r Graph}

VLSR_avg %>% 
  arrange(desc(state)) %>% 
  ggplot(aes(x= FN, y = Dtot_med, fill = state)) + 
  geom_col(width =0.5, position = position_dodge()) +
  geom_errorbar(aes(ymin= ifelse(Dtot_med-Dtot_se < 0, 0, Dtot_med-Dtot_se), ymax=Dtot_med+Dtot_se), width=0.08, size = 1, position=position_dodge(width=0.5)) +
  scale_fill_brewer(palette = "Paired") +
  theme_bw()

```

```{r Ctl Avg et stat}

VLSR_avg_ctl <- VLSR_all %>% filter(FN == "dmso") %>% 
  #filter(!Dist_tot1 >= 2900) %>% 
  group_by(FN, state) %>%  
  summarise(n = n(), 
            Dtot_med = median(Dist_tot1, na.rm=T),
            Dtot_avg = mean(Dist_tot1, na.rm=T),
            Dtot_sd = sd(Dist_tot1, na.rm=T), 
            Dtot_se = Dtot_sd / sqrt(n),
            Dtot_low = quantile(Dist_tot1, probs = 0.025, na.rm= T), 
            Dtot_up = quantile(Dist_tot1, probs = 0.975, na.rm= T)) #%>% select(-Vel_sd, -Dist_sd, -Dtot_sd) %>% mutate(ID = "LOFF")
  

VLSR_avg_ctl

VLSR_ctl_n <- VLSR_avg_ctl %>% filter(state == "n")
VLSR_ctl_u <- VLSR_avg_ctl %>% filter(state == "u")

```

```{r Normalisation des données autour du CTL}

Dist_tot_aju <- VLSR_all %>% 
  mutate(aju_Dtot = if_else(state == "n", (Dist_tot1 * 100) / VLSR_ctl_n$Dtot_med,
                            if_else(state == "u", (Dist_tot1 * 100) / VLSR_ctl_u$Dtot_med,  NA)))
Dist_tot_aju

#raw data ready for IBR analysis
IBR_VLSR <- Dist_tot_aju %>% 
  mutate(endpt = "VLSR") %>% 
  select(Arena, FN, Rep, state, endpt, aju_Dtot) %>% filter(FN != "benzo") %>% 
  rename(value = aju_Dtot)
IBR_VLSR

Dist_tot_aju_avg <- VLSR_all %>% 
  mutate(aju_Dtot = if_else(state == "n", (Dist_tot1 * 100) / VLSR_ctl_n$Dtot_avg,
                            if_else(state == "u", (Dist_tot1 * 100) / VLSR_ctl_u$Dtot_avg,  NA)))
Dist_tot_aju_avg

df_avg_VLSR_avg <- Dist_tot_aju_avg %>% 
  group_by(FN, state) %>% 
  summarise(n = n(),
            avg_val_adj = mean(aju_Dtot, na.rm = T), 
            sd_val_adj = sd(aju_Dtot, na.rm = T),
            se_val_adj = sd_val_adj/sqrt(n)) %>% 
  mutate(endpt = as.factor("VLSR"))
  
df_avg_VLSR_avg

df_avg_VLSR <- Dist_tot_aju %>% 
  group_by(FN, state) %>% 
  summarise(n = n(),
            med_Dtot_adj = median(aju_Dtot, na.rm = T), 
            sd_Dtot_adj = sd(aju_Dtot, na.rm = T),
            se_Dtot_adj = sd_Dtot_adj/sqrt(n)) %>% 
  mutate(endpt = as.factor("VLSR"))

df_avg_VLSR$endpt_UV <- paste(df_avg_VLSR$endpt, df_avg_VLSR$state, sep = "_")  
  
df_avg_VLSR

```

```{r Visualisation}
BoxDtot <- Dist_tot_aju %>% 
  ggplot(aes(x = FN, y = aju_Dtot, fill = state)) +
  geom_boxplot(width = 0.2, position = position_dodge(width = 0.6)) +
  stat_summary(fun = mean, 
               geom = "point", 
               size = 2, 
               color = "red3", 
               position = position_dodge(width = 0.6)) +
  geom_hline(yintercept = 100, colour = "black", linetype = "dashed") +
  scale_y_continuous(limits = c(0, 400)) +
  theme_minimal() +
  labs(x = "Fishing nets",
       y = "Heart bate (% of the control)",
       title = expression(paste("Effect of aa leachates on the cardiac rhythm of ", italic("Oryzias latipes"))),
       subtitle = "Concentration plastic eq.= 0.33 mg/ml",
       fill = "Treatment" ) +
  theme(axis.title.x = element_text(size = 14, face = "bold", vjust = 0.5, margin = margin(t = 10, r = 20, b = 0, l = 0)),
        axis.title.y = element_text(size = 14, face = "bold", vjust = 3, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.text.x = element_text(size = 14, face = 'bold'),
        axis.text.y = element_text(size = 12, face = 'bold'),
        title = element_text(size = 12, face = "bold"),
        strip.text = element_text(face = "bold", size = rel(1)),
        legend.position = "top",
        legend.spacing.x = unit(0.5, 'cm'),
        legend.text = element_text(size = 12, face = 'bold'),
        legend.key.size = unit(1.5, "cm"),
        legend.key.width = unit(0.5, "cm"),
        plot.margin = unit(c(1, 1, 1, 1), "cm"))
BoxDtot
```

```{r Statistics}
Dunn_all_VLSR <- rbind(MWU_n_Lett_VLSR_new %>% mutate(state = "n"), MWU_u_Lett_VLSR_used %>% mutate(state = "u")) 
Dunn_all_VLSR
```

```{r final table}
Dunn_all_VLSR_s <- Dunn_all_VLSR %>%  dplyr::select(-max_value)
Dunn_all_VLSR_s

VLSR_all_f <- df_avg_VLSR %>% left_join(Dunn_all_VLSR_s) %>% arrange(state) %>% mutate(diff = if_else(diff == "ns", NA, diff))
VLSR_all_f

```

```{r Heatmap VLSR}

max_Dtot_VLSR <- max(VLSR_all_f$med_Dtot_adj)
max_Dtot_VLSR

min_Dtot_VLSR <- 100-(max_Dtot_VLSR-100)+1
min_Dtot_VLSR


HM_VLSR <- VLSR_all_f %>% filter(FN != "dmso", FN != "benzo") %>% 
  ggplot(aes(x = FN, y = factor(endpt_UV, levels = rev(unique(endpt_UV))), fill = med_Dtot_adj)) +
  geom_tile(height = 1, width = 1) +
  scale_fill_gradient2(low = "#36A7A7", high = "#b751ca", mid = "white", 
   midpoint = 100, limit = c(20, 180), 
   breaks = round(c(20, 100, 180), digits = 0), 
   guide = "colourbar") +
  scale_x_discrete(labels = c("PA6 \u03B1 35 \nn = 48",
                              "PA6 \u03B2 33 \nn = 48",
                              "PA6 \u03B2 95 \nn = 48",
                              "PBS-PBAT \n\u03B4 60\nn = 48",
                              "PBS-PBAT \n\u03B4 35\nn = 48",
                              "HPPE-PP \n\u03B5 4.25\nn = 48",
                              "PA6 \u03B3 33\nn = 48",
                              "PA6 \u03B3 60\nn = 48")) +
  labs(#title = "Effect of the fishing nets leachates on medaka fish",
       x = "Fishing nets",
       fill = "Blank H2O = 100",
       legend.box.just = "center") +
  theme_classic() +
  theme(axis.title.x = element_text(size = 14, face = "bold", vjust = 0.5, margin = margin(t = 10, r = 20, b = 0, l = 0)),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 14, face = 'bold'),
        axis.text.y = element_text(size = 12, face = 'bold'),
        title = element_text(size = 12, face = "bold"),
        strip.text = element_text(face = "bold", size = rel(1)),
        legend.position = "top",
        legend.spacing.x = unit(0.5, 'cm'),
        legend.text = element_text(size = 12, face = 'bold', color = "black"),
        legend.key = element_rect(color = "black"),
        legend.key.size = unit(0.85, "cm"),
        legend.key.width = unit(1, "cm"),
        legend.title.align = 0.5,
        plot.margin = unit(c(1, 1, 1, 1), "cm"),
        aspect.ratio = 3/8) +
  guides(fill = guide_colourbar(title.position="top", 
                                title.vjust = 2, 
                                ticks.colour = "black", 
                                barheight = unit( 0.3 , "in" ),))

HM_VLSR + geom_text(aes(FN, endpt_UV, label = round(med_Dtot_adj, digits = 1)), color = "black", size = 3.5, fontface = "bold") +
  geom_text(aes(FN, endpt_UV, label = diff), size = 5, vjust = 2, color = "black", fontface = "bold")


```


# VLMR
```{r data import new}
# Mettre le bon trajet dossier adapté :

VLMR_all <- rbind(VLMR_n, VLMR_u) 
VLMR_all
```


```{r Outliers 25 100%}
#Boxplot by replicates to see if there are outliers

Outliers <- VLMR_all %>% 
  ggplot(aes(FN, Dist_tot1, fill = state)) + 
  geom_violin(fill = NA, aes(color = FN), width = 1) +
  geom_boxplot(width = 0.3) 

Outliers
```


```{r Average tibble}

#Average and boxplot by replicates to see if there is outliers
VLMR_avg_Rep <- VLMR_all %>% group_by(FN, Rep, state) %>%  summarise(n = n(), 
                                                          Dtot_avg = mean(Dist_tot1, na.rm=T),
                                                          Dtot_sd = sd(Dist_tot1, na.rm=T), 
                                                          Dtot_se = Dtot_sd / sqrt(n)) %>% dplyr::select(-Dtot_sd) %>% mutate(ID = "LOFF")

VLMR_avg_Rep

VLMR_avg <- VLMR_all %>% group_by(FN, state) %>%  summarise(n = n(), 
                                                          Dtot_med = median(Dist_tot1, na.rm=T),
                                                          Dtot_avg = mean(Dist_tot1, na.rm=T),
                                                          Dtot_sd = sd(Dist_tot1, na.rm=T), 
                                                          Dtot_se = Dtot_sd / sqrt(n),
                                                          Dtot_low = quantile(Dist_tot1, probs = 0.025, na.rm= T), 
                                                          Dtot_up = quantile(Dist_tot1, probs = 0.975, na.rm= T)) #%>% select(-Vel_sd, -Dist_sd, -Dtot_sd) %>% mutate(ID = "LOFF")
  

VLMR_avg 

```

```{r Graph}

VLMR_avg %>% 
  arrange(desc(state)) %>% 
  ggplot(aes(x= FN, y = Dtot_med, fill = state)) + 
  geom_col(width =0.5, position = position_dodge()) +
  geom_errorbar(aes(ymin= ifelse(Dtot_med-Dtot_se < 0, 0, Dtot_med-Dtot_se), ymax=Dtot_med+Dtot_se), width=0.08, size = 1, position=position_dodge(width=0.5)) +
  scale_fill_brewer(palette = "Paired") +
  theme_bw()

```

```{r Ctl Avg et stat}

VLMR_avg_ctl <- VLMR_all %>% filter(FN == "dmso") %>% 
  #filter(!Dist_tot1 >= 2900) %>% 
  group_by(FN, state) %>%  
  summarise(n = n(), 
            Dtot_med = median(Dist_tot1, na.rm=T),
            Dtot_avg = mean(Dist_tot1, na.rm=T),
            Dtot_sd = sd(Dist_tot1, na.rm=T), 
            Dtot_se = Dtot_sd / sqrt(n),
            Dtot_low = quantile(Dist_tot1, probs = 0.025, na.rm= T), 
            Dtot_up = quantile(Dist_tot1, probs = 0.975, na.rm= T)) #%>% select(-Vel_sd, -Dist_sd, -Dtot_sd) %>% mutate(ID = "LOFF")
  

VLMR_avg_ctl

VLMR_ctl_n <- VLMR_avg_ctl %>% filter(state == "n")
VLMR_ctl_u <- VLMR_avg_ctl %>% filter(state == "u")

```

```{r Normalisation des données autour du CTL}

Dist_tot_aju <- VLMR_all %>% 
  mutate(aju_Dtot = if_else(state == "n", (Dist_tot1 * 100) / VLMR_ctl_n$Dtot_med,
                            if_else(state == "u", (Dist_tot1 * 100) / VLMR_ctl_u$Dtot_med,  NA)))
Dist_tot_aju

#raw data ready for IBR analysis
IBR_VLMR <- Dist_tot_aju %>% 
  mutate(endpt = "VLMR") %>% 
  select(Arena, FN, Rep, state, endpt, aju_Dtot) %>% filter(FN != "benzo") %>% 
  rename(value = aju_Dtot)
IBR_VLMR

Dist_tot_aju_avg <- VLMR_all %>% 
  mutate(aju_Dtot = if_else(state == "n", (Dist_tot1 * 100) / VLMR_ctl_n$Dtot_avg,
                            if_else(state == "u", (Dist_tot1 * 100) / VLMR_ctl_u$Dtot_avg,  NA)))
Dist_tot_aju_avg

df_avg_VLMR_avg <- Dist_tot_aju_avg %>% 
  group_by(FN, state) %>% 
  summarise(n = n(),
            avg_val_adj = mean(aju_Dtot, na.rm = T), 
            sd_val_adj = sd(aju_Dtot, na.rm = T),
            se_val_adj = sd_val_adj/sqrt(n)) %>% 
  mutate(endpt = as.factor("VLMR"))
  
df_avg_VLMR_avg

df_avg_VLMR <- Dist_tot_aju %>% 
  group_by(FN, state) %>% 
  summarise(n = n(),
            med_Dtot_adj = median(aju_Dtot, na.rm = T), 
            sd_Dtot_adj = sd(aju_Dtot, na.rm = T),
            se_Dtot_adj = sd_Dtot_adj/sqrt(n)) %>% 
  mutate(endpt = as.factor("VLMR"))

df_avg_VLMR$endpt_UV <- paste(df_avg_VLMR$endpt, df_avg_VLMR$state, sep = "_")  
  
df_avg_VLMR

```

```{r Visualisation}
BoxDtot <- Dist_tot_aju %>% 
  ggplot(aes(x = FN, y = aju_Dtot, fill = state)) +
  geom_boxplot(width = 0.2, position = position_dodge(width = 0.6)) +
  stat_summary(fun = mean, 
               geom = "point", 
               size = 2, 
               color = "red3", 
               position = position_dodge(width = 0.6)) +
  geom_hline(yintercept = 100, colour = "black", linetype = "dashed") +
  scale_y_continuous(limits = c(0, 400)) +
  theme_minimal() +
  labs(x = "Fishing nets",
       y = "Heart bate (% of the control)",
       title = expression(paste("Effect of aa leachates on the cardiac rhythm of ", italic("Oryzias latipes"))),
       subtitle = "Concentration plastic eq.= 0.33 mg/ml",
       fill = "Treatment" ) +
  theme(axis.title.x = element_text(size = 14, face = "bold", vjust = 0.5, margin = margin(t = 10, r = 20, b = 0, l = 0)),
        axis.title.y = element_text(size = 14, face = "bold", vjust = 3, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.text.x = element_text(size = 14, face = 'bold'),
        axis.text.y = element_text(size = 12, face = 'bold'),
        title = element_text(size = 12, face = "bold"),
        strip.text = element_text(face = "bold", size = rel(1)),
        legend.position = "top",
        legend.spacing.x = unit(0.5, 'cm'),
        legend.text = element_text(size = 12, face = 'bold'),
        legend.key.size = unit(1.5, "cm"),
        legend.key.width = unit(0.5, "cm"),
        plot.margin = unit(c(1, 1, 1, 1), "cm"))
BoxDtot
```

```{r Statistics}
Dunn_all_VLMR <- rbind(MWU_n_Lett_VLMR_new %>% mutate(state = "n"), MWU_u_Lett_VLMR_used %>% mutate(state = "u")) 
Dunn_all_VLMR
```

```{r final table}
Dunn_all_VLMR_s <- Dunn_all_VLMR %>%  dplyr::select(-max_value)
Dunn_all_VLMR_s

VLMR_all_f <- df_avg_VLMR %>% left_join(Dunn_all_VLMR_s) %>% arrange(state) %>% mutate(diff = if_else(diff == "ns", NA, diff))
VLMR_all_f

```

```{r Heatmap VLMR}

max_Dtot_VLMR <- max(VLMR_all_f$med_Dtot_adj)
max_Dtot_VLMR

min_Dtot_VLMR <- 100-(max_Dtot_VLMR-100)+1
min_Dtot_VLMR


HM_VLMR <- VLMR_all_f %>% filter(FN != "dmso", FN != "benzo") %>% 
  ggplot(aes(x = FN, y = factor(endpt_UV, levels = rev(unique(endpt_UV))), fill = med_Dtot_adj)) +
  geom_tile(height = 1, width = 1) +
  scale_fill_gradient2(low = "#36A7A7", high = "#b751ca", mid = "white", 
   midpoint = 100, limit = c(20, 180), 
   breaks = round(c(20, 100, 180), digits = 0), 
   guide = "colourbar") +
  scale_x_discrete(labels = c("PA6 \u03B1 35 \nn = 48",
                              "PA6 \u03B2 33 \nn = 48",
                              "PA6 \u03B2 95 \nn = 48",
                              "PBS-PBAT \n\u03B4 60\nn = 48",
                              "PBS-PBAT \n\u03B4 35\nn = 48",
                              "HPPE-PP \n\u03B5 4.25\nn = 48",
                              "PA6 \u03B3 33\nn = 48",
                              "PA6 \u03B3 60\nn = 48")) +
  labs(#title = "Effect of the fishing nets leachates on medaka fish",
       x = "Fishing nets",
       fill = "Blank H2O = 100",
       legend.box.just = "center") +
  theme_classic() +
  theme(axis.title.x = element_text(size = 14, face = "bold", vjust = 0.5, margin = margin(t = 10, r = 20, b = 0, l = 0)),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 14, face = 'bold'),
        axis.text.y = element_text(size = 12, face = 'bold'),
        title = element_text(size = 12, face = "bold"),
        strip.text = element_text(face = "bold", size = rel(1)),
        legend.position = "top",
        legend.spacing.x = unit(0.5, 'cm'),
        legend.text = element_text(size = 12, face = 'bold', color = "black"),
        legend.key = element_rect(color = "black"),
        legend.key.size = unit(0.85, "cm"),
        legend.key.width = unit(1, "cm"),
        legend.title.align = 0.5,
        plot.margin = unit(c(1, 1, 1, 1), "cm"),
        aspect.ratio = 3/8) +
  guides(fill = guide_colourbar(title.position="top", 
                                title.vjust = 2, 
                                ticks.colour = "black", 
                                barheight = unit( 0.3 , "in" ),))

HM_VLMR + geom_text(aes(FN, endpt_UV, label = round(med_Dtot_adj, digits = 1)), color = "black", size = 3.5, fontface = "bold") +
  geom_text(aes(FN, endpt_UV, label = diff), size = 5, vjust = 2, color = "black", fontface = "bold")


```



# AUC_OFF2
```{r data import new}
# Mettre le bon trajet dossier adapté :

AUC_OFF2_all <- rbind(AUC_results_used %>% mutate(state = "u"), AUC_results_new %>% mutate(state = "n")) 
AUC_OFF2_all
```


```{r Outliers 25 100%}
#Boxplot by replicates to see if there are outliers

Outliers <- AUC_OFF2_all %>% 
  ggplot(aes(FN, AUC, fill = state)) + 
  geom_violin(fill = NA, aes(color = FN), width = 1) +
  geom_boxplot(width = 0.3) +
  geom_jitter(width = 0.18, alpha = 0.5, color = "red3") 

Outliers
```


```{r Average tibble}

#Average and boxplot by replicates to see if there is outliers
AUC_OFF2_avg_Rep <- AUC_OFF2_all %>% group_by(FN, Rep, state) %>%  summarise(n = n(), 
                                                          AUC_OFF2_avg = mean(AUC, na.rm=T),
                                                          AUC_OFF2_sd = sd(AUC, na.rm=T), 
                                                          AUC_OFF2_se = AUC_OFF2_sd / sqrt(n)) 
AUC_OFF2_avg_Rep

AUC_OFF2_avg <- AUC_OFF2_all %>% group_by(FN, state) %>%  summarise(n = n(), 
                                                          AUC_OFF2_med = median(AUC, na.rm=T),
                                                          AUC_OFF2_avg = mean(AUC, na.rm=T),
                                                          AUC_OFF2_sd = sd(AUC, na.rm=T), 
                                                          AUC_OFF2_se = AUC_OFF2_sd / sqrt(n),
                                                          AUC_OFF2_low = quantile(AUC, probs = 0.025, na.rm= T), 
                                                          AUC_OFF2_up = quantile(AUC, probs = 0.975, na.rm= T)) 

AUC_OFF2_avg 

```

```{r Graph}

AUC_OFF2_avg %>% 
  arrange(desc(state)) %>% 
  ggplot(aes(x= FN, y = AUC_OFF2_med, fill = state)) + 
  geom_col(width =0.5, position = position_dodge()) +
  geom_errorbar(aes(ymin= ifelse(AUC_OFF2_med-AUC_OFF2_se < 0, 0, AUC_OFF2_med-AUC_OFF2_se), ymax=AUC_OFF2_med+AUC_OFF2_se), width=0.08, size = 1, position=position_dodge(width=0.5)) +
  scale_fill_brewer(palette = "Paired") +
  theme_bw()

```

```{r Ctl Avg et stat}

AUC_OFF2_avg_ctl <- AUC_OFF2_all %>% filter(FN == "dmso") %>% 
  group_by(FN, state) %>%  
  summarise(n = n(), 
            AUC_OFF2_med = median(AUC, na.rm=T),
            AUC_OFF2_avg = mean(AUC, na.rm=T),
            AUC_OFF2_sd = sd(AUC, na.rm=T), 
            AUC_OFF2_se = AUC_OFF2_sd / sqrt(n),
            AUC_OFF2_low = quantile(AUC, probs = 0.025, na.rm= T), 
            AUC_OFF2_up = quantile(AUC, probs = 0.975, na.rm= T)) 

AUC_OFF2_avg_ctl

AUC_OFF2_ctl_n <- AUC_OFF2_avg_ctl %>% filter(state == "n")
AUC_OFF2_ctl_u <- AUC_OFF2_avg_ctl %>% filter(state == "u")

# #test_t
# #HO = les deux groupes ont la meme moyenne
# #H1 = les deux groupes ont des moyennes differentes 
# stat_ctl <- AUC_OFF2_all %>% filter(FN == "CTL")
# test <- t.test(AUC~ state, stat_ctl, var.equal=TRUE)
# test
# #p-value = 0.55 > 0.05, on ne rejette pas H0 
# 
# #Normalité 
# #H0 = distribution normale 
# #H1 = pas de distribution normale
# stat_ctl %>% 
#   group_by(state) %>% 
#   summarise(shapiro_test(AUC), groups= "drop")
# 
# MWU_res_10 <- wilcox.test(AUC ~ state, stat_ctl)
# MWU_res_10

```

```{r Normalisation des données autour du CTL}

AUC_OFF2_aju <- AUC_OFF2_all %>% 
  mutate(aju_AUC_OFF2 = if_else(state == "n", (AUC * 100) / AUC_OFF2_ctl_n$AUC_OFF2_med, 
                              if_else(state == "u", (AUC * 100) / AUC_OFF2_ctl_u$AUC_OFF2_med, NA)))
AUC_OFF2_aju

#raw data ready for IBR analysis
IBR_ASD <- AUC_OFF2_aju %>% 
  mutate(endpt = "ASD") %>% 
  select(Arena, FN, Rep, state, endpt, aju_AUC_OFF2) %>% filter(FN != "benzo") %>% 
  rename(value = aju_AUC_OFF2)
IBR_ASD

AUC_OFF2_aju_avg <- AUC_OFF2_all %>% 
  mutate(aju_AUC_OFF2 = if_else(state == "n", (AUC * 100) / AUC_OFF2_ctl_n$AUC_OFF2_avg, 
                              if_else(state == "u", (AUC * 100) / AUC_OFF2_ctl_u$AUC_OFF2_avg, NA)))
AUC_OFF2_aju_avg

df_avg_AUC_OFF2_avg <- AUC_OFF2_aju_avg %>% filter(aju_AUC_OFF2 != 0) %>% 
  group_by(FN, state) %>% 
  summarise(n = n(),
            avg_val_adj = mean(aju_AUC_OFF2), 
            sd_val_adj = sd(aju_AUC_OFF2),
            se_val_adj = sd_val_adj/sqrt(n)) %>% 
  mutate(endpt = as.factor("ASD_LOFF2"))
  
df_avg_AUC_OFF2_avg


df_avg_AUC_OFF2_rep <- AUC_OFF2_aju %>% filter(aju_AUC_OFF2 != 0) %>% 
  group_by(FN, state, Rep) %>% 
  summarise(n = n(),
            med_val_adj = median(aju_AUC_OFF2), 
            sd_val_adj = sd(aju_AUC_OFF2),
            se_val_adj = sd_val_adj/sqrt(n)) %>% 
  mutate(endpt = as.factor("ASD_LOFF2"))
  
df_avg_AUC_OFF2_rep

df_avg_AUC_OFF2 <- AUC_OFF2_aju %>% filter(aju_AUC_OFF2 != 0) %>% 
  group_by(FN, state) %>% 
  summarise(n = n(),
            med_AUC_OFF2_adj = median(aju_AUC_OFF2), 
            sd_AUC_OFF2_adj = sd(aju_AUC_OFF2),
            se_AUC_OFF2_adj = sd_AUC_OFF2_adj/sqrt(n)) %>% 
  mutate(endpt = as.factor("ASD_LOFF2"))

df_avg_AUC_OFF2$endpt_UV <- paste(df_avg_AUC_OFF2$endpt, df_avg_AUC_OFF2$state, sep = "_")  
  
df_avg_AUC_OFF2

```

```{r Visualisation}
BoxAUC_OFF2 <- AUC_OFF2_aju %>% 
  ggplot(aes(x = FN, y = aju_AUC_OFF2, fill = state)) +
  geom_boxplot(width = 0.2, position = position_dodge(width = 0.6)) +
  stat_summary(fun = mean, 
               geom = "point", 
               size = 2, 
               color = "red3", 
               position = position_dodge(width = 0.6)) +
  geom_hline(yintercept = 100, colour = "black", linetype = "dashed") +
  theme_minimal() +
  labs(x = "Fishing nets",
       y = "Heart bate (% of the control)",
       title = expression(paste("Effect of aa leachates on the cardiac rhythm of ", italic("Oryzias latipes"))),
       subtitle = "Concentration plastic eq.= 0.33 mg/ml",
       fill = "Treatment" ) +
  theme(axis.title.x = element_text(size = 14, face = "bold", vjust = 0.5, margin = margin(t = 10, r = 20, b = 0, l = 0)),
        axis.title.y = element_text(size = 14, face = "bold", vjust = 3, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.text.x = element_text(size = 14, face = 'bold'),
        axis.text.y = element_text(size = 12, face = 'bold'),
        title = element_text(size = 12, face = "bold"),
        strip.text = element_text(face = "bold", size = rel(1)),
        legend.position = "top",
        legend.spacing.x = unit(0.5, 'cm'),
        legend.text = element_text(size = 12, face = 'bold'),
        legend.key.size = unit(1.5, "cm"),
        legend.key.width = unit(0.5, "cm"),
        plot.margin = unit(c(1, 1, 1, 1), "cm"))
BoxAUC_OFF2
```


```{r Statistics}
Dunn_all_AUC_OFF2 <- rbind(MWU_n_Lett_AUC_new %>% mutate(state = "n"), MWU_u_Lett_AUC_used %>% mutate(state = "u"))
Dunn_all_AUC_OFF2
```

```{r final table}
Dunn_all_AUC_OFF2_s <- Dunn_all_AUC_OFF2 %>%  dplyr::select(-max_value)
Dunn_all_AUC_OFF2_s

AUC_OFF2_all_f <- df_avg_AUC_OFF2 %>% left_join(Dunn_all_AUC_OFF2_s) %>% arrange(state) %>% mutate(diff = if_else(diff == "ns", NA, diff)) 
AUC_OFF2_all_f

```

```{r Heatmap AUC_OFF2}

max_AUC_OFF2_AUC_OFF2 <- max(AUC_OFF2_all_f$med_AUC_OFF2_adj)
max_AUC_OFF2_AUC_OFF2
min_AUC_OFF2_AUC_OFF2 <- 100-(max_AUC_OFF2_AUC_OFF2-100)+1
min_AUC_OFF2_AUC_OFF2

HM_AUC_OFF2 <- AUC_OFF2_all_f %>% filter(FN != "dmso", FN != "benzo") %>% 
  ggplot(aes(x = FN, y = factor(endpt_UV, levels = rev(unique(endpt_UV))), fill = med_AUC_OFF2_adj)) +
  geom_tile(height = 1, width = 1) +
  scale_fill_gradient2(low = "#36A7A7", high = "#b751ca", mid = "white", 
   midpoint = 100, limit = c(20, 180), 
   breaks = round(c(20, 100, 180), digits = 0), 
   guide = "colourbar") +
  scale_x_discrete(labels = c("PA6 \u03B1 35 \nn = 48",
                              "PA6 \u03B2 33 \nn = 48",
                              "PA6 \u03B2 95 \nn = 48",
                              "PBS-PBAT \n\u03B4 60\nn = 48",
                              "HPPE-PP \n\u03B5 4.25\nn = 48",
                              "PA6 \u03B3 33\nn = 48",
                              "PA6 \u03B3 60\nn = 48",
                              "PBS-PBAT \n\u03B4 35\nn = 48")) +
  labs(#title = "Effect of the fishing nets leachates on medaka fish",
       x = "Fishing nets",
       fill = "blank H2O = 100",
       legend.box.just = "center") +
  theme_classic() +
  theme(axis.title.x = element_text(size = 14, face = "bold", vjust = 0.5, margin = margin(t = 10, r = 20, b = 0, l = 0)),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 14, face = 'bold'),
        axis.text.y = element_text(size = 12, face = 'bold'),
        title = element_text(size = 12, face = "bold"),
        strip.text = element_text(face = "bold", size = rel(1)),
        legend.position = "top",
        legend.spacing.x = unit(0.5, 'cm'),
        legend.text = element_text(size = 12, face = 'bold', color = "black"),
        legend.key = element_rect(color = "black"),
        legend.key.size = unit(0.85, "cm"),
        legend.key.width = unit(1, "cm"),
        legend.title.align = 0.5,
        plot.margin = unit(c(1, 1, 1, 1), "cm"),
        aspect.ratio = 3/8) +
  guides(fill = guide_colourbar(title.position="top", 
                                title.vjust = 2, 
                                ticks.colour = "black", 
                                barheight = unit( 0.3 , "in" ),))

HM_AUC_OFF2 + geom_text(aes(FN, endpt_UV, label = round(med_AUC_OFF2_adj, digits = 1)), color = "black", size = 3.5, fontface = "bold") +
  geom_text(aes(FN, endpt_UV, label = diff), size = 5, vjust = 2, color = "black", fontface = "bold")


```


# TPZ LOFF1 
```{r data import new}
# Mettre le bon trajet dossier adapté :

TPZ_OFF_all <- rbind(DDIZ_u_LOFF1, DDIZ_n_LOFF1) 
TPZ_OFF_all
```


```{r Outliers 25 100%}
#Boxplot by replicates to see if there are outliers

Outliers <- TPZ_OFF_all %>% 
  ggplot(aes(FN, Dura_s, fill = state)) + 
  geom_violin(fill = NA, aes(color = FN), width = 1) +
  geom_boxplot(width = 0.3) +
  geom_jitter(width = 0.18, alpha = 0.5, color = "red3") 

Outliers
```


```{r Average tibble}

#Average and boxplot by replicates to see if there is outliers
TPZ_OFF_avg_Rep <- TPZ_OFF_all %>% group_by(FN, Rep, state) %>%  summarise(n = n(), 
                                                          Dura_avg = mean(Dura_s, na.rm=T),
                                                          Dura_sd = sd(Dura_s, na.rm=T), 
                                                          Dura_se = Dura_sd / sqrt(n)) 
TPZ_OFF_avg_Rep

TPZ_OFF_avg <- TPZ_OFF_all %>% group_by(FN, state) %>%  summarise(n = n(), 
                                                          Dura_med = median(Dura_s, na.rm=T),
                                                          Dura_avg = mean(Dura_s, na.rm=T),
                                                          Dura_sd = sd(Dura_s, na.rm=T), 
                                                          Dura_se = Dura_sd / sqrt(n),
                                                          Dura_low = quantile(Dura_s, probs = 0.025, na.rm= T), 
                                                          Dura_up = quantile(Dura_s, probs = 0.975, na.rm= T)) 

TPZ_OFF_avg 

```

```{r Graph}

TPZ_OFF_avg %>% 
  arrange(desc(state)) %>% 
  ggplot(aes(x= FN, y = Dura_med, fill = state)) + 
  geom_col(width =0.5, position = position_dodge()) +
  geom_errorbar(aes(ymin= ifelse(Dura_med-Dura_se < 0, 0, Dura_med-Dura_se), ymax=Dura_med+Dura_se), width=0.08, size = 1, position=position_dodge(width=0.5)) +
  scale_fill_brewer(palette = "Paired") +
  theme_bw()

```

```{r Ctl Avg et stat}

TPZ_OFF_avg_ctl <- TPZ_OFF_all %>% filter(FN == "dmso") %>% 
  #filter(!Dura_s >= 2000) %>% 
  group_by(FN, state) %>%  
  summarise(n = n(), 
            Dura_med = median(Dura_s, na.rm=T),
            Dura_avg = mean(Dura_s, na.rm=T),
            Dura_sd = sd(Dura_s, na.rm=T), 
            Dura_se = Dura_sd / sqrt(n),
            Dura_low = quantile(Dura_s, probs = 0.025, na.rm= T), 
            Dura_up = quantile(Dura_s, probs = 0.975, na.rm= T)) 

TPZ_OFF_avg_ctl

TPZ_OFF_ctl_n <- TPZ_OFF_avg_ctl %>% filter(state == "n")
TPZ_OFF_ctl_u <- TPZ_OFF_avg_ctl %>% filter(state == "u")

# #test_t
# #HO = les deux groupes ont la meme moyenne
# #H1 = les deux groupes ont des moyennes differentes 
# stat_ctl <- TPZ_OFF_all %>% filter(FN == "CTL")
# test <- t.test(Border~ state, stat_ctl, var.equal=TRUE)
# test
# #p-value = 0.55 > 0.05, on ne rejette pas H0 
# 
# #Normalité 
# #H0 = distribution normale 
# #H1 = pas de distribution normale
# stat_ctl %>% 
#   group_by(state) %>% 
#   summarise(shapiro_test(Border), groups= "drop")
# 
# MWU_res_10 <- wilcox.test(Border ~ state, stat_ctl)
# MWU_res_10

```

```{r Normalisation des données autour du CTL}

Dura_s_aju <- TPZ_OFF_all %>% 
  mutate(aju_Dura = if_else(state == "n", (Dura_s * 100) / TPZ_OFF_ctl_n$Dura_med, 
                              if_else(state == "u", (Dura_s * 100) / TPZ_OFF_ctl_u$Dura_med, NA)))
Dura_s_aju

#raw data ready for IBR analysis
IBR_TPZ_LOFF1 <- Dura_s_aju %>% 
  mutate(endpt = "TPZ_LOFF1") %>% 
  ungroup() %>% 
  select(Arena, FN, Rep, state, endpt, aju_Dura) %>% filter(FN != "benzo") %>% 
  rename(value = aju_Dura)
IBR_TPZ_LOFF1

Dura_s_aju_avg <- TPZ_OFF_all %>% 
  mutate(aju_Dura = if_else(state == "n", (Dura_s * 100) / TPZ_OFF_ctl_n$Dura_avg, 
                              if_else(state == "u", (Dura_s * 100) / TPZ_OFF_ctl_u$Dura_avg, NA)))
Dura_s_aju_avg

df_avg_TPZ_avg <- Dura_s_aju_avg %>% 
  group_by(FN, state) %>% 
  summarise(n = n(),
            avg_val_adj = mean(aju_Dura, na.rm = T), 
            sd_val_adj = sd(aju_Dura, na.rm = T),
            se_val_adj = sd_val_adj/sqrt(n)) %>% 
  mutate(endpt = as.factor("TPZ_LOFF1"))
  
df_avg_TPZ_avg

df_avg_TPZ <- Dura_s_aju %>% 
  group_by(FN, state) %>% 
  summarise(n = n(),
            med_Dura_adj = median(aju_Dura, na.rm = T), 
            sd_Dura_adj = sd(aju_Dura, na.rm = T),
            se_Dura_adj = sd_Dura_adj/sqrt(n)) %>% 
  mutate(endpt = as.factor("TPZ_LOFF1"))

df_avg_TPZ$endpt_UV <- paste(df_avg_TPZ$endpt, df_avg_TPZ$state, sep = "_")  
  
df_avg_TPZ

```

```{r Visualisation}
BoxDura <- Dura_s_aju %>% 
  ggplot(aes(x = FN, y = aju_Dura, fill = state)) +
  geom_boxplot(width = 0.2, position = position_dodge(width = 0.6)) +
  stat_summary(fun = mean, 
               geom = "point", 
               size = 2, 
               color = "red3", 
               position = position_dodge(width = 0.6)) +
  geom_hline(yintercept = 100, colour = "black", linetype = "dashed") +
  theme_minimal() +
  labs(x = "Fishing nets",
       y = "Heart bate (% of the control)",
       title = expression(paste("Effect of aa leachates on the cardiac rhythm of ", italic("Oryzias latipes"))),
       subtitle = "Concentration plastic eq.= 0.33 mg/ml",
       fill = "Treatment" ) +
  theme(axis.title.x = element_text(size = 14, face = "bold", vjust = 0.5, margin = margin(t = 10, r = 20, b = 0, l = 0)),
        axis.title.y = element_text(size = 14, face = "bold", vjust = 3, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.text.x = element_text(size = 14, face = 'bold'),
        axis.text.y = element_text(size = 12, face = 'bold'),
        title = element_text(size = 12, face = "bold"),
        strip.text = element_text(face = "bold", size = rel(1)),
        legend.position = "top",
        legend.spacing.x = unit(0.5, 'cm'),
        legend.text = element_text(size = 12, face = 'bold'),
        legend.key.size = unit(1.5, "cm"),
        legend.key.width = unit(0.5, "cm"),
        plot.margin = unit(c(1, 1, 1, 1), "cm"))
BoxDura
```

```{r Statistics}
Dunn_all_TPZ <- rbind(MWU_u_Lett_LOFF1_used %>% mutate(state = "u"), MWU_n_Lett_LOFF1_new %>% mutate(state = "n"))
Dunn_all_TPZ
```

```{r final table}
Dunn_all_TPZ_s <- Dunn_all_TPZ %>%  dplyr::select(-max_value)
Dunn_all_TPZ_s

TPZ_all_f <- df_avg_TPZ %>% left_join(Dunn_all_TPZ_s) %>% arrange(state) %>% mutate(diff = if_else(diff == "ns", NA, diff))
TPZ_all_f

```

```{r Heatmap TPZ LOFF1}

max_Dura_TPZ <- max(TPZ_all_f$med_Dura_adj)
max_Dura_TPZ
min_Dura_TPZ <- 100-(max_Dura_TPZ-100)+1
min_Dura_TPZ

HM_TPZ <- TPZ_all_f %>% filter(FN != "dmso") %>% 
  ggplot(aes(x = FN, y = factor(endpt_UV, levels = rev(unique(endpt_UV))), fill = med_Dura_adj)) +
  geom_tile(height = 1, width = 1) +
  scale_fill_gradient2(low = "#36A7A7", high = "#b751ca", mid = "white", 
   midpoint = 100, limit = c(65, 135), 
   breaks = round(c(65, 100, 135), digits = 0), 
   guide = "colourbar") +
  scale_x_discrete(labels = c("PA6 \u03B1 35 \nn = 48",
                              "PA6 \u03B2 33 \nn = 48",
                              "PA6 \u03B2 95 \nn = 48",
                              "PBS-PBAT \n\u03B4 35\nn = 48",
                              "PBS-PBAT \n\u03B4 60\nn = 48",
                              "HPPE-PP \n\u03B5 4.25\nn = 48",
                              "PA6 \u03B3 33\nn = 48",
                              "PA6 \u03B3 60\nn = 48")) +
  labs(#title = "Effect of the fishing nets leachates on medaka fish",
       x = "Fishing nets",
       fill = "blank H2O = 100",
       legend.box.just = "center") +
  theme_classic() +
  theme(axis.title.x = element_text(size = 14, face = "bold", vjust = 0.5, margin = margin(t = 10, r = 20, b = 0, l = 0)),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 14, face = 'bold'),
        axis.text.y = element_text(size = 12, face = 'bold'),
        title = element_text(size = 12, face = "bold"),
        strip.text = element_text(face = "bold", size = rel(1)),
        legend.position = "top",
        legend.spacing.x = unit(0.5, 'cm'),
        legend.text = element_text(size = 12, face = 'bold', color = "black"),
        legend.key = element_rect(color = "black"),
        legend.key.size = unit(0.85, "cm"),
        legend.key.width = unit(1, "cm"),
        legend.title.align = 0.5,
        plot.margin = unit(c(1, 1, 1, 1), "cm"),
        aspect.ratio = 3/8) +
  guides(fill = guide_colourbar(title.position="top", 
                                title.vjust = 2, 
                                ticks.colour = "black", 
                                barheight = unit( 0.3 , "in" ),))

HM_TPZ + geom_text(aes(FN, endpt_UV, label = round(med_Dura_adj, digits = 1)), color = "black", size = 3.5, fontface = "bold") +
  geom_text(aes(FN, endpt_UV, label = diff), size = 5, vjust = 2, color = "black", fontface = "bold")


```



# TPZ LON 
```{r data import new}
# Mettre le bon trajet dossier adapté :

TPZ_ON_all <- rbind(DDIZ_u_LON, DDIZ_n_LON) 
TPZ_ON_all
```


```{r Outliers 25 100%}
#Boxplot by replicates to see if there are outliers

Outliers <- TPZ_ON_all %>% 
  ggplot(aes(FN, Dura_s, fill = state)) + 
  geom_violin(fill = NA, aes(color = FN), width = 1) +
  geom_boxplot(width = 0.3) +
  geom_jitter(width = 0.18, alpha = 0.5, color = "red3") 

Outliers
```


```{r Average tibble}

#Average and boxplot by replicates to see if there is outliers
TPZ_ON_avg_Rep <- TPZ_ON_all %>% group_by(FN, Rep, state) %>%  summarise(n = n(), 
                                                          Dura_avg = mean(Dura_s, na.rm=T),
                                                          Dura_sd = sd(Dura_s, na.rm=T), 
                                                          Dura_se = Dura_sd / sqrt(n)) 
TPZ_ON_avg_Rep

TPZ_ON_avg <- TPZ_ON_all %>% group_by(FN, state) %>%  summarise(n = n(), 
                                                          Dura_med = median(Dura_s, na.rm=T),
                                                          Dura_avg = mean(Dura_s, na.rm=T),
                                                          Dura_sd = sd(Dura_s, na.rm=T), 
                                                          Dura_se = Dura_sd / sqrt(n),
                                                          Dura_low = quantile(Dura_s, probs = 0.025, na.rm= T), 
                                                          Dura_up = quantile(Dura_s, probs = 0.975, na.rm= T)) 

TPZ_ON_avg 

```

```{r Graph}

TPZ_ON_avg %>% 
  arrange(desc(state)) %>% 
  ggplot(aes(x= FN, y = Dura_med, fill = state)) + 
  geom_col(width =0.5, position = position_dodge()) +
  geom_errorbar(aes(ymin= ifelse(Dura_med-Dura_se < 0, 0, Dura_med-Dura_se), ymax=Dura_med+Dura_se), width=0.08, size = 1, position=position_dodge(width=0.5)) +
  scale_fill_brewer(palette = "Paired") +
  theme_bw()

```

```{r Ctl Avg et stat}

TPZ_ON_avg_ctl <- TPZ_ON_all %>% filter(FN == "dmso") %>% 
  #filter(!Dura_s >= 2000) %>% 
  group_by(FN, state) %>%  
  summarise(n = n(), 
            Dura_med = median(Dura_s, na.rm=T),
            Dura_avg = mean(Dura_s, na.rm=T),
            Dura_sd = sd(Dura_s, na.rm=T), 
            Dura_se = Dura_sd / sqrt(n),
            Dura_low = quantile(Dura_s, probs = 0.025, na.rm= T), 
            Dura_up = quantile(Dura_s, probs = 0.975, na.rm= T)) 

TPZ_ON_avg_ctl

TPZ_ON_ctl_n <- TPZ_ON_avg_ctl %>% filter(state == "n")
TPZ_ON_ctl_u <- TPZ_ON_avg_ctl %>% filter(state == "u")

# #test_t
# #HO = les deux groupes ont la meme moyenne
# #H1 = les deux groupes ont des moyennes differentes 
# stat_ctl <- TPZ_ON_all %>% filter(FN == "CTL")
# test <- t.test(Border~ state, stat_ctl, var.equal=TRUE)
# test
# #p-value = 0.55 > 0.05, on ne rejette pas H0 
# 
# #Normalité 
# #H0 = distribution normale 
# #H1 = pas de distribution normale
# stat_ctl %>% 
#   group_by(state) %>% 
#   summarise(shapiro_test(Border), groups= "drop")
# 
# MWU_res_10 <- wilcox.test(Border ~ state, stat_ctl)
# MWU_res_10

```

```{r Normalisation des données autour du CTL}

Dura_s_aju <- TPZ_ON_all %>% 
  mutate(aju_Dura = if_else(state == "n", (Dura_s * 100) / TPZ_ON_ctl_n$Dura_med, 
                              if_else(state == "u", (Dura_s * 100) / TPZ_ON_ctl_u$Dura_med, NA)))
Dura_s_aju

#raw data ready for IBR analysis
IBR_TPZ_LON <- Dura_s_aju %>% 
  mutate(endpt = "TPZ_LON") %>% 
  ungroup() %>% 
  select(Arena, FN, Rep, state, endpt, aju_Dura) %>% filter(FN != "benzo") %>% 
  rename(value = aju_Dura)
IBR_TPZ_LON

Dura_s_aju_avg <- TPZ_ON_all %>% 
  mutate(aju_Dura = if_else(state == "n", (Dura_s * 100) / TPZ_ON_ctl_n$Dura_avg, 
                              if_else(state == "u", (Dura_s * 100) / TPZ_ON_ctl_u$Dura_avg, NA)))
Dura_s_aju_avg

df_avg_TPZON_avg <- Dura_s_aju_avg %>% 
  group_by(FN, state) %>% 
  summarise(n = n(),
            avg_val_adj = mean(aju_Dura, na.rm = T), 
            sd_val_adj = sd(aju_Dura, na.rm = T),
            se_val_adj = sd_val_adj/sqrt(n)) %>% 
  mutate(endpt = as.factor("TPZ_LON"))
  
df_avg_TPZON_avg

df_avg_TPZON <- Dura_s_aju %>% 
  group_by(FN, state) %>% 
  summarise(n = n(),
            med_Dura_adj = median(aju_Dura, na.rm = T), 
            sd_Dura_adj = sd(aju_Dura, na.rm = T),
            se_Dura_adj = sd_Dura_adj/sqrt(n)) %>% 
  mutate(endpt = as.factor("TPZ_LON"))

df_avg_TPZON$endpt_UV <- paste(df_avg_TPZON$endpt, df_avg_TPZON$state, sep = "_")  
  
df_avg_TPZON

```

```{r Visualisation}
BoxDura <- Dura_s_aju %>% 
  ggplot(aes(x = FN, y = aju_Dura, fill = state)) +
  geom_boxplot(width = 0.2, position = position_dodge(width = 0.6)) +
  stat_summary(fun = mean, 
               geom = "point", 
               size = 2, 
               color = "red3", 
               position = position_dodge(width = 0.6)) +
  geom_hline(yintercept = 100, colour = "black", linetype = "dashed") +
  theme_minimal() +
  labs(x = "Fishing nets",
       y = "Heart bate (% of the control)",
       title = expression(paste("Effect of aa leachates on the cardiac rhythm of ", italic("Oryzias latipes"))),
       subtitle = "Concentration plastic eq.= 0.33 mg/ml",
       fill = "Treatment" ) +
  theme(axis.title.x = element_text(size = 14, face = "bold", vjust = 0.5, margin = margin(t = 10, r = 20, b = 0, l = 0)),
        axis.title.y = element_text(size = 14, face = "bold", vjust = 3, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.text.x = element_text(size = 14, face = 'bold'),
        axis.text.y = element_text(size = 12, face = 'bold'),
        title = element_text(size = 12, face = "bold"),
        strip.text = element_text(face = "bold", size = rel(1)),
        legend.position = "top",
        legend.spacing.x = unit(0.5, 'cm'),
        legend.text = element_text(size = 12, face = 'bold'),
        legend.key.size = unit(1.5, "cm"),
        legend.key.width = unit(0.5, "cm"),
        plot.margin = unit(c(1, 1, 1, 1), "cm"))
BoxDura
```

```{r Statistics}
Dunn_all_TPZON <- rbind(MWU_u_Lett_LON_used %>% mutate(state = "u"), MWU_n_Lett_LON_new %>% mutate(state = "n"))
Dunn_all_TPZON
```

```{r final table}
Dunn_all_TPZON_s <- Dunn_all_TPZON %>%  dplyr::select(-max_value)
Dunn_all_TPZON_s

TPZON_all_f <- df_avg_TPZON %>% left_join(Dunn_all_TPZON_s) %>% arrange(state) %>% mutate(diff = if_else(diff == "ns", NA, diff))
TPZON_all_f

```

```{r Heatmap TPZON LON}

max_Dura_TPZON <- max(TPZON_all_f$med_Dura_adj)
max_Dura_TPZON
min_Dura_TPZON <- 100-(max_Dura_TPZON-100)+1
min_Dura_TPZON

HM_TPZON <- TPZON_all_f %>% filter(FN != "dmso") %>% 
  ggplot(aes(x = FN, y = factor(endpt_UV, levels = rev(unique(endpt_UV))), fill = med_Dura_adj)) +
  geom_tile(height = 1, width = 1) +
  scale_fill_gradient2(low = "#36A7A7", high = "#b751ca", mid = "white", 
   midpoint = 100, limit = c(65, 135), 
   breaks = round(c(65, 100, 135), digits = 0), 
   guide = "colourbar") +
  scale_x_discrete(labels = c("PA6 \u03B1 35 \nn = 48",
                              "PA6 \u03B2 33 \nn = 48",
                              "PA6 \u03B2 95 \nn = 48",
                              "PBS-PBAT \n\u03B4 35\nn = 48",
                              "PBS-PBAT \n\u03B4 60\nn = 48",
                              "HPPE-PP \n\u03B5 4.25\nn = 48",
                              "PA6 \u03B3 33\nn = 48",
                              "PA6 \u03B3 60\nn = 48")) +
  labs(#title = "Effect of the fishing nets leachates on medaka fish",
       x = "Fishing nets",
       fill = "blank H2O = 100",
       legend.box.just = "center") +
  theme_classic() +
  theme(axis.title.x = element_text(size = 14, face = "bold", vjust = 0.5, margin = margin(t = 10, r = 20, b = 0, l = 0)),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 14, face = 'bold'),
        axis.text.y = element_text(size = 12, face = 'bold'),
        title = element_text(size = 12, face = "bold"),
        strip.text = element_text(face = "bold", size = rel(1)),
        legend.position = "top",
        legend.spacing.x = unit(0.5, 'cm'),
        legend.text = element_text(size = 12, face = 'bold', color = "black"),
        legend.key = element_rect(color = "black"),
        legend.key.size = unit(0.85, "cm"),
        legend.key.width = unit(1, "cm"),
        legend.title.align = 0.5,
        plot.margin = unit(c(1, 1, 1, 1), "cm"),
        aspect.ratio = 3/8) +
  guides(fill = guide_colourbar(title.position="top", 
                                title.vjust = 2, 
                                ticks.colour = "black", 
                                barheight = unit( 0.3 , "in" ),))

HM_TPZON + geom_text(aes(FN, endpt_UV, label = round(med_Dura_adj, digits = 1)), color = "black", size = 3.5, fontface = "bold") +
  geom_text(aes(FN, endpt_UV, label = diff), size = 5, vjust = 2, color = "black", fontface = "bold")


```


# TPZ LOFF2
```{r data import new}
# Mettre le bon trajet dossier adapté :

TPZ_LOFF2_all <- rbind(DDIZ_u_LOFF2 %>% mutate(state = "u"), DDIZ_n_LOFF2 %>% mutate(state = "n")) 
TPZ_LOFF2_all
```


```{r Outliers 25 100%}
#Boxplot by replicates to see if there are outliers

Outliers <- TPZ_LOFF2_all %>% 
  ggplot(aes(FN, Dura_s, fill = state)) + 
  geom_violin(fill = NA, aes(color = FN), width = 1) +
  geom_boxplot(width = 0.3) +
  geom_jitter(width = 0.18, alpha = 0.5, color = "red3") 

Outliers
```


```{r Average tibble}

#Average and boxplot by replicates to see if there is outliers
TPZ_LOFF2_avg_Rep <- TPZ_LOFF2_all %>% group_by(FN, Rep, state) %>%  summarise(n = n(), 
                                                          Dura_avg = mean(Dura_s, na.rm=T),
                                                          Dura_sd = sd(Dura_s, na.rm=T), 
                                                          Dura_se = Dura_sd / sqrt(n)) 
TPZ_LOFF2_avg_Rep

TPZ_LOFF2_avg <- TPZ_LOFF2_all %>% group_by(FN, state) %>%  summarise(n = n(), 
                                                          Dura_med = median(Dura_s, na.rm=T),
                                                          Dura_avg = mean(Dura_s, na.rm=T),
                                                          Dura_sd = sd(Dura_s, na.rm=T), 
                                                          Dura_se = Dura_sd / sqrt(n),
                                                          Dura_low = quantile(Dura_s, probs = 0.025, na.rm= T), 
                                                          Dura_up = quantile(Dura_s, probs = 0.975, na.rm= T)) 

TPZ_LOFF2_avg 

```

```{r Graph}

TPZ_LOFF2_avg %>% 
  arrange(desc(state)) %>% 
  ggplot(aes(x= FN, y = Dura_med, fill = state)) + 
  geom_col(width =0.5, position = position_dodge()) +
  geom_errorbar(aes(ymin= ifelse(Dura_med-Dura_se < 0, 0, Dura_med-Dura_se), ymax=Dura_med+Dura_se), width=0.08, size = 1, position=position_dodge(width=0.5)) +
  scale_fill_brewer(palette = "Paired") +
  theme_bw()

```

```{r Ctl Avg et stat}

TPZ_LOFF2_avg_ctl <- TPZ_LOFF2_all %>% filter(FN == "dmso") %>% 
  #filter(!Dura_s >= 2000) %>% 
  group_by(FN, state) %>%  
  summarise(n = n(), 
            Dura_med = median(Dura_s, na.rm=T),
            Dura_avg = mean(Dura_s, na.rm=T),
            Dura_sd = sd(Dura_s, na.rm=T), 
            Dura_se = Dura_sd / sqrt(n),
            Dura_low = quantile(Dura_s, probs = 0.025, na.rm= T), 
            Dura_up = quantile(Dura_s, probs = 0.975, na.rm= T)) 

TPZ_LOFF2_avg_ctl

TPZ_LOFF2_ctl_n <- TPZ_LOFF2_avg_ctl %>% filter(state == "n")
TPZ_LOFF2_ctl_u <- TPZ_LOFF2_avg_ctl %>% filter(state == "u")

# #test_t
# #HO = les deux groupes ont la meme moyenne
# #H1 = les deux groupes ont des moyennes differentes 
# stat_ctl <- TPZ_LOFF2_all %>% filter(FN == "CTL")
# test <- t.test(Border~ state, stat_ctl, var.equal=TRUE)
# test
# #p-value = 0.55 > 0.05, on ne rejette pas H0 
# 
# #Normalité 
# #H0 = distribution normale 
# #H1 = pas de distribution normale
# stat_ctl %>% 
#   group_by(state) %>% 
#   summarise(shapiro_test(Border), groups= "drop")
# 
# MWU_res_10 <- wilcox.test(Border ~ state, stat_ctl)
# MWU_res_10

```

```{r Normalisation des données autour du CTL}

Dura_s_aju <- TPZ_LOFF2_all %>% 
  mutate(aju_Dura = if_else(state == "n", (Dura_s * 100) / TPZ_LOFF2_ctl_n$Dura_med, 
                              if_else(state == "u", (Dura_s * 100) / TPZ_LOFF2_ctl_u$Dura_med, NA)))
Dura_s_aju

#raw data ready for IBR analysis
IBR_TPZ_LOFF2 <- Dura_s_aju %>% 
  mutate(endpt = "TPZ_LOFF2") %>% 
  ungroup() %>% 
  select(Arena, FN, Rep, state, endpt, aju_Dura) %>% filter(FN != "benzo") %>% 
  rename(value = aju_Dura)
IBR_TPZ_LOFF2

Dura_s_aju_avg <- TPZ_LOFF2_all %>% 
  mutate(aju_Dura = if_else(state == "n", (Dura_s * 100) / TPZ_LOFF2_ctl_n$Dura_avg, 
                              if_else(state == "u", (Dura_s * 100) / TPZ_LOFF2_ctl_u$Dura_avg, NA)))
Dura_s_aju_avg

df_avg_TPZ_LOFF2_avg <- Dura_s_aju_avg %>% 
  group_by(FN, state) %>% 
  summarise(n = n(),
            avg_val_adj = mean(aju_Dura, na.rm = T), 
            sd_val_adj = sd(aju_Dura, na.rm = T),
            se_val_adj = sd_val_adj/sqrt(n)) %>% 
  mutate(endpt = as.factor("TPZ_LOFF2"))
  
df_avg_TPZ_LOFF2_avg

df_avg_TPZ_LOFF2 <- Dura_s_aju %>% 
  group_by(FN, state) %>% 
  summarise(n = n(),
            med_Dura_adj = median(aju_Dura, na.rm = T), 
            sd_Dura_adj = sd(aju_Dura, na.rm = T),
            se_Dura_adj = sd_Dura_adj/sqrt(n)) %>% 
  mutate(endpt = as.factor("TPZ_LOFF2"))

df_avg_TPZ_LOFF2$endpt_UV <- paste(df_avg_TPZ_LOFF2$endpt, df_avg_TPZ_LOFF2$state, sep = "_")  
  
df_avg_TPZ_LOFF2

```

```{r Visualisation}
BoxDura <- Dura_s_aju %>% 
  ggplot(aes(x = FN, y = aju_Dura, fill = state)) +
  geom_boxplot(width = 0.2, position = position_dodge(width = 0.6)) +
  stat_summary(fun = mean, 
               geom = "point", 
               size = 2, 
               color = "red3", 
               position = position_dodge(width = 0.6)) +
  geom_hline(yintercept = 100, colour = "black", linetype = "dashed") +
  theme_minimal() +
  labs(x = "Fishing nets",
       y = "Heart bate (% of the control)",
       title = expression(paste("Effect of aa leachates on the cardiac rhythm of ", italic("Oryzias latipes"))),
       subtitle = "Concentration plastic eq.= 0.33 mg/ml",
       fill = "Treatment" ) +
  theme(axis.title.x = element_text(size = 14, face = "bold", vjust = 0.5, margin = margin(t = 10, r = 20, b = 0, l = 0)),
        axis.title.y = element_text(size = 14, face = "bold", vjust = 3, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.text.x = element_text(size = 14, face = 'bold'),
        axis.text.y = element_text(size = 12, face = 'bold'),
        title = element_text(size = 12, face = "bold"),
        strip.text = element_text(face = "bold", size = rel(1)),
        legend.position = "top",
        legend.spacing.x = unit(0.5, 'cm'),
        legend.text = element_text(size = 12, face = 'bold'),
        legend.key.size = unit(1.5, "cm"),
        legend.key.width = unit(0.5, "cm"),
        plot.margin = unit(c(1, 1, 1, 1), "cm"))
BoxDura
```

```{r Statistics}
Dunn_all_TPZ_LOFF2 <- rbind(MWU_u_Lett_LOFF2_used %>% mutate(state = "u"), MWU_n_Lett_LOFF2_new %>% mutate(state = "n"))
Dunn_all_TPZ_LOFF2
```

```{r final table}
Dunn_all_TPZ_LOFF2_s <- Dunn_all_TPZ_LOFF2 %>%  dplyr::select(-max_value)
Dunn_all_TPZ_LOFF2_s

TPZ_LOFF2_all_f <- df_avg_TPZ_LOFF2 %>% left_join(Dunn_all_TPZ_LOFF2_s) %>% arrange(state) %>% mutate(diff = if_else(diff == "ns", NA, diff))
TPZ_LOFF2_all_f

```

```{r Heatmap TPZ_LOFF2}

max_Dura_TPZ_LOFF2 <- max(TPZ_LOFF2_all_f$med_Dura_adj)
max_Dura_TPZ_LOFF2
min_Dura_TPZ_LOFF2 <- 100-(max_Dura_TPZ_LOFF2-100)+1
min_Dura_TPZ_LOFF2

HM_TPZ_LOFF2 <- TPZ_LOFF2_all_f %>% filter(FN != "dmso") %>% 
  ggplot(aes(x = FN, y = factor(endpt_UV, levels = rev(unique(endpt_UV))), fill = med_Dura_adj)) +
  geom_tile(height = 1, width = 1) +
  scale_fill_gradient2(low = "#36A7A7", high = "#b751ca", mid = "white", 
   midpoint = 100, limit = c(75, 125), 
   breaks = round(c(75, 100, 125), digits = 0), 
   guide = "colourbar") +
  scale_x_discrete(labels = c("PA6 \u03B1 35 \nn = 48",
                              "PA6 \u03B2 33 \nn = 48",
                              "PA6 \u03B2 95 \nn = 48",
                              "PBS-PBAT \n\u03B4 35\nn = 48",
                              "PBS-PBAT \n\u03B4 60\nn = 48",
                              "HPPE-PP \n\u03B5 4.25\nn = 48",
                              "PA6 \u03B3 33\nn = 48",
                              "PA6 \u03B3 60\nn = 48")) +
  labs(#title = "Effect of the fishing nets leachates on medaka fish",
       x = "Fishing nets",
       fill = "blank H2O = 100",
       legend.box.just = "center") +
  theme_classic() +
  theme(axis.title.x = element_text(size = 14, face = "bold", vjust = 0.5, margin = margin(t = 10, r = 20, b = 0, l = 0)),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 14, face = 'bold'),
        axis.text.y = element_text(size = 12, face = 'bold'),
        title = element_text(size = 12, face = "bold"),
        strip.text = element_text(face = "bold", size = rel(1)),
        legend.position = "top",
        legend.spacing.x = unit(0.5, 'cm'),
        legend.text = element_text(size = 12, face = 'bold', color = "black"),
        legend.key = element_rect(color = "black"),
        legend.key.size = unit(0.85, "cm"),
        legend.key.width = unit(1, "cm"),
        legend.title.align = 0.5,
        plot.margin = unit(c(1, 1, 1, 1), "cm"),
        aspect.ratio = 3/8) +
  guides(fill = guide_colourbar(title.position="top", 
                                title.vjust = 2, 
                                ticks.colour = "black", 
                                barheight = unit( 0.3 , "in" ),))

HM_TPZ_LOFF2 + geom_text(aes(FN, endpt_UV, label = round(med_Dura_adj, digits = 1)), color = "black", size = 3.5, fontface = "bold") +
  geom_text(aes(FN, endpt_UV, label = diff), size = 5, vjust = 2, color = "black", fontface = "bold")


```


#----------------------------------------------

#All END POINTS
```{r General dataframe}
#modify variable AUC et Dura en Dtot pour avoir qu'une colonne en joignant

AUC_OFF2_all_f_Dtot <- AUC_OFF2_all_f %>% rename(med_Dtot_adj = med_AUC_OFF2_adj,
                                       sd_Dtot_adj = sd_AUC_OFF2_adj,
                                       se_Dtot_adj = se_AUC_OFF2_adj)

TPZ_all_f_Dtot <- TPZ_all_f %>% rename(med_Dtot_adj = med_Dura_adj,
                                       sd_Dtot_adj = sd_Dura_adj,
                                       se_Dtot_adj = se_Dura_adj)

TPZ_on_all_f_Dtot <- TPZON_all_f %>% rename(med_Dtot_adj = med_Dura_adj,
                                       sd_Dtot_adj = sd_Dura_adj,
                                       se_Dtot_adj = se_Dura_adj)

TPZ_loff2_all_f_Dtot <- TPZ_LOFF2_all_f %>% rename(med_Dtot_adj = med_Dura_adj,
                                       sd_Dtot_adj = sd_Dura_adj,
                                       se_Dtot_adj = se_Dura_adj)


General1 <- rbind(BLA_OFF_all_f, 
                 BLA_LON_all_f,
                 TPZ_all_f_Dtot, 
                 TPZ_on_all_f_Dtot,
                 VLSR_all_f, 
                 AUC_OFF2_all_f_Dtot,
                 VLMR_all_f, 
                 TPZ_loff2_all_f_Dtot) %>% 
  mutate(ctl_0 = round(med_Dtot_adj/100, digits = 2),
         Bioassay = "Behavior",
         Organism = "medaka") %>% 
  filter(FN != "benzo") %>% 
  mutate(endpt_UV = factor(endpt_UV)) %>% 
  mutate(endpt_IBR = if_else(grepl("BLA", endpt), "BLA",
                             if_else(grepl("TPZ", endpt), "TPZ", endpt)))

General1


# Tri du data frame en fonction de la variable endpt_UV
ordre_specifique <- c("BLA_OFF", "TPZ_LOFF1", "BLA_LON", "TPZ_LON", "VLSR", "VLMR", "ASD_LOFF2", "TPZ_LOFF2")

General <- General1 %>%
  mutate(endpt = factor(endpt, levels = ordre_specifique)) %>%
  filter(FN != "dmso")
General

library(writexl)
write_xlsx(General, "Behav_corr_matrix_dmso.xlsx")
```

```{r toxicity score}

Tox_sco_behav <- General %>% 
  mutate(m_effect = if_else(!(is.na(diff)), abs(100-med_Dtot_adj), 0),
         score = m_effect/0.33*0.4) %>% 
  #filter(!is.na(diff))
  group_by(FN, state) %>%
  summarise(tot_score = sum(score, na.rm = T),
            n = n())
Tox_sco_behav

#export as csv
#write.csv(Tox_sco_behav, "dmso_tox_score/Tox_sco_behav.csv")


```

```{r IBR data}
#final df with all the raw data ready for IBR analysis
df_IBR1 <- bind_rows(IBR_BLA_OFF, IBR_BLA_ON, IBR_VLSR, IBR_VLMR, IBR_ASD, IBR_TPZ_LOFF1, IBR_TPZ_LON, IBR_TPZ_LOFF2)
df_IBR1

#export as csv
#write.csv(df_IBR1, "dmso_tox_score/IBR_behav.csv")

```


```{r Heatmap General raw data}

General2 <- General %>% mutate(diff = if_else(diff == "*", "   *",
                                                  if_else(diff == "**", "  **",
                                                          if_else(diff == "***", " ***",
                                                                  if_else(diff == "****", "****", NA)))))
General2

max_Dtot_G <- max(General2$med_Dtot_adj)
max_Dtot_G
min_Dtot_G <- 100-(max_Dtot_G-100)+1
min_Dtot_G

General2$endpt_UV <- gsub("ASD_LOFF2", "ASD", General2$endpt_UV)

HM_TPZ <- General2 %>% filter(FN != "dmso") %>% 
  ggplot(aes(x = FN, y = factor(endpt_UV, levels = rev(unique(endpt_UV))), fill = med_Dtot_adj)) +
  geom_tile(height = 1, width = 1) +
  scale_fill_gradient2(low = "#36A7A7", high = "#c68640", mid = "grey100", 
   midpoint = 100, limit = c(20, 180), 
   breaks = round(c(20, 100, 180), digits = 0), 
   guide = "colourbar") +
  facet_grid(endpt~., scales = "free_y") +
  scale_x_discrete(labels = c("PA \u03B135",
                              "PA \u03B233",
                              "PA \u03B295",
                              "PBS \u03B435",
                              "PBS \u03B460",
                              "HPPE \u03B54.25",
                              "PA \u03B333",
                              "PA \u03B360")) +
  labs(title = expression(paste("Effect of FN extracts on ", italic("Oryzias latipes"), " larvae")),
       subtitle = "Exposure time = 48h",
       x = "Fishing nets",
       fill = "Solvent control = 100",
       legend.box.just = "center") +
  theme_classic() +
  theme(axis.title.x = element_text(size = 18, face = "bold", vjust = 0.5, margin = margin(t = 10, r = 20, b = 0, l = 0)),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 16, face = 'bold'),
        axis.text.y = element_text(size = 16, face = 'bold'),
        title = element_text(size = 22, face = "bold"),
        strip.text = element_text(face = "bold", size = rel(1)),
        legend.position = "top",
        legend.spacing.x = unit(0.5, 'cm'),
        legend.text = element_text(size = 12, face = 'bold', color = "black"),
        legend.key = element_rect(color = "black"),
        legend.key.size = unit(0.85, "cm"),
        legend.key.width = unit(1, "cm"),
        legend.title.align = 0.5,
        legend.title = element_text(size = 18, face = "bold"),
        plot.margin = unit(c(1, 1, -2, 1), "cm"),
        strip.background = element_blank(),
        strip.text.y = element_blank(),
        aspect.ratio = 3/60) +
  guides(fill = guide_colourbar(title.position="top", 
                                title.vjust = 2, 
                                ticks.colour = "black", 
                                barheight = unit( 0.3 , "in" ),))
         
HM_TPZ + geom_text(aes(FN, endpt_UV, label = round(med_Dtot_adj, digits = 1)), color = "black", size = 5, fontface = "bold", vjust = 0.6) +
  geom_text(aes(FN, endpt_UV, label = diff), size = 6, vjust = 0.7, hjust = -0.7, color = "black", fontface = "bold") +
  labs(caption = "Statistics:\nMann-Whitney U-test\n FN vs Solvent control\n* = p-value < 0.05\n** = p-value < 0.01\n*** = p-value < 0.001\n**** = p-value < 0.0001\nn = 48") + 
  theme(plot.caption = element_text(family = "serif", 
               face = "bold", 
               color = 1, 
               size = 12, 
               hjust = 0.99, 
               vjust = 265, 
               angle = 0, 
               lineheight = 1))


```


```{r Heatmap General % difference with the control, eval=FALSE, include=FALSE}

max_Dtot_G <- max(General$ctl_0)
max_Dtot_G
min_Dtot_G <- min(General$ctl_0)
min_Dtot_G

#rename FN with the final name
General3 <- General %>% 
  mutate(FN = if_else(FN == "epsi", "HPPE \u03B54.25",
                      if_else(FN == "alpha", "PA \u03B135",
                              if_else(FN == "beta33", "PA \u03B233",
                                      if_else(FN == "beta95", "PA \u03B295",
                                              if_else(FN == "gamma33", "PA \u03B333",
                                                      if_else(FN == "gamma60", "PA \u03B360",
                                                              if_else(FN == "delta35", "PBS \u03B435",
                                                                      if_else(FN == "delta60", "PBS \u03B460", NA))))))))) %>% 
  #change BLA_OFF in BLA_LOFF1
  mutate(endpt_UV = if_else(endpt_UV == "BLA_OFF_n", "BLA_LOFF1_n", 
                            if_else(endpt_UV == "BLA_OFF_u", "BLA_LOFF1_u", endpt_UV))) 
  
General3

#Order x-axis with FN variable
General3$FN <- factor(General3$FN, levels = c("HPPE ε4.25", "PA α35", "PA β33", "PA β95", "PA γ33", "PA γ60", "PBS δ35", "PBS δ60"))

HM_TPZ <- General3 %>% filter(FN != "CTL") %>% 
  ggplot(aes(x = FN, y = factor(endpt_UV, levels = rev(unique(endpt_UV))), fill = ctl_0)) +
  geom_tile(height = 1, width = 1) +
  scale_fill_gradient2(low = "#ef6565", high = "#256CB4", mid = "grey100", 
   midpoint = 1, limit = c(0, 2), 
   breaks = round(c(0, 1, 2), digits = 0), 
   guide = "colourbar") +
  facet_grid(endpt~., scales = "free_y") +
  labs(#title = "Effect of the fishing nets leachates on medaka fish",
       x = "Fishing nets",
       y = "Endpoints_FN state",
       fill = "",
       legend.box.just = "center") +
  theme_classic() +
  theme(axis.title.x = element_text(size = 20, face = "bold", vjust = 0.5, margin = margin(t = 10, r = 20, b = 0, l = 0)),
        axis.title.y = element_text(size = 20, face = "bold", vjust = 0.5, margin = margin(t = 10, r = 20, b = 0, l = 0)),
        axis.text.x = element_text(size = 19, face = 'bold'),
        axis.text.y = element_text(size = 19, face = 'bold'),
        title = element_text(size = 22, face = "bold"),
        strip.text = element_text(face = "bold", size = rel(1)),
        legend.position = "right",
        legend.spacing.x = unit(0.5, 'cm'),
        legend.text = element_text(size = 20, face = 'bold', color = "black"),
        legend.key = element_rect(color = "black"),
        legend.key.size = unit(0.85, "cm"),
        legend.key.width = unit(1, "cm"),
        legend.title.align = 0.5,
        plot.margin = unit(c(1, 1, 1, 1), "cm"),
        strip.background = element_blank(),
        strip.text.y = element_blank(),
        #aspect.ratio = 3/45
        ) +
  guides(fill = guide_colourbar(title.vjust = 2, 
                                ticks.colour = "black", 
                                barheight = unit( 2 , "in" ),))

HM_TPZ + geom_text(aes(FN, endpt_UV, label = round(ctl_0, digits = 2)), color = "black", size = 5, fontface = "bold", vjust = -0.02) +
  geom_text(aes(FN, endpt_UV, label = diff), size = 7, vjust = 1.3, color = "black", fontface = "bold")


```


Analyses results :
- The BLA tends to increase for nets irradiated for 12.54 days. The distance covered by fishes was significantly higher for 4 of the 5 FN tested. At the contrary the general trend of the BLA was at the decrease when increasing the UV irradiation time. However any significant difference as been shown. 
The time spent in peripheral zone during the BLA significantly increased for all the FN and for 6 on 8 at 12.54 days and 25.08 days respectively. However, for PA g33 and PBS d60 at 25.08 days of UV irradiation the increase were no more significant. 
For the startle response any significant difference according to the control has been observed and no general trend can be identified. 
A longer but not significant habituation to vibration stimuli has been induced by the FN irradiated for 12.54 days. After 25.08 days of Uv irradiation 5 fishing net induce a increase and three are significant (HPPE e4.25, PA b0.95 and PA y33). Whereas PA y33 and PBS d35 show a non significant quicker habituation.
During this vibration stimuli for the fishes exposed th the FN irradiated for 12.54 days the time in peripheral zone increase significantly for the HPPE e4.25 and the PBS d60 as during the BLA. The other show also an increase but not significant. After 25.08 days of irradiation 5 on 8 FN induce a significant increase of the TPZ, while the PA b33 induce a significant decrease. 
For VMR to lights out the FN irradiated for 12.54 days induced a slight increase, only significant for the PA y33 and the PBS d35. At the contrary for those irradiated for 25.08 days the general trend is towards shorter distances travelled and significantly for the PA b33 and PA y60. Using the same stimuli but taking the time needed to acclimatize the result is similar. 
Finally, for all the FN and for both irradiation time the difference of TPZ is higly significant, inducing a increase for all, except for the PA b33. 
Finally, we can conclude that, apart for the VSR that is not significant, the irradiation of 12.54 days induce a general increase of the endpoints, whereas some decrease has been caused by a longer irradiation. This is particularly true for the PA b33, which, apart from the TPZ during the BLA, induced a decrease of all endpoints compared with the control.
 














