---
title: "PCA_kinetics"
author: "Edgar Dusacre"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r Insertion package, include=FALSE}
library(ggnewscale)
library(ggplot2) 
library(tidyr)
library(purrr)
library(tidyverse)
library(ggrepel)
library(ggpubr)
library(knitr)
library(yaml)
library(dplyr) 
library(matrixStats)
library(EnvStats)
library(stringr)
library(gtable)
library(grid)
library(FSA)
library(scales)
#library(wbstats)
library(ggh4x)
library(multcompView)
library(report)
library(ecotox)
library(wesanderson)
library(RColorBrewer)
library(readr)
library(readxl)
library(gmodels)
library(ggpattern)
library(zoo)
library(forcats)
library(car)
library(dunn.test)
library(gridExtra)


library(forcats)
library(binom)
library(lubridate)
library(ade4)
library(broom)
library(rstatix)
library(rcompanion)
library(chron)
library(PMCMRplus)

library(factoextra)
library(gclus)
library(ape)
library(corrplot)
library(RVAideMemoire)
library(vegan)
library(cowplot)
library(magick)
```


```{r Charger les palettes de couleurs, include=FALSE}

Plasfito_C <- c("#80CAD0", "#36A7A7", "#276573", "#054959","#E3CCC0", "#F7EAE1", "#A48A7B", "#C6AF8D", "#49BED3", "#256CB4", "#008163", "#44B494", "#7BC6B9")

Plasfito_color <- c("GreenP4" = "#80CAD0", "GreenP3" = "#36A7A7", "GreenP2" = "#276573", "GreenP1" = "#054959","Brown1" = "#E3CCC0", "Brown2" = "#F7EAE1", "Brown3" = "#A48A7B", "Brown4" = "#C6AF8D", "Turquoise1" = "#49BED3", "Blue1" = "#256CB4", "Green1" = "#008163", "Green2" = "#44B494", "Green3" = "#7BC6B9")

List_color_Fr <- c("Mimizan" = "#008163" , "Bayonne" = "#44B494", "Hendaye" = "#7BC6B9", 
                   "Capbretons"  = "#80CAD0", "Arcachon" = "#36A7A7", "St_Jean" = "#276573")

List_color <- c("Mimizan" = "#008163" , "Bayonne" = "#44B494", "Hendaye" = "#7BC6B9", 
                 "Capbretons"  = "#80CAD0", "Arcachon" = "#36A7A7", "St_Jean" = "#276573",
                 "Euskadi" = "#054959")

Plasfito_Tps <- c("5" = "#80CAD0", "15" = "#36A7A7", "30" = "#276573")


#A part si vous souhaitez changer les couleurs do not touch.
Ech_K2CR2O7<- c("K2CR2O7" = "#80CAD0")

Tps_color <- c("5" = "#80CAD0" , "15" = "#36A7A7", "30" = "#276573")

Dilu_color <- c("0.0125" = "#80CAD0" , "0.025" = "#36A7A7", "0.05" = "#276573", "0.1" = "#008163")

Conc_color <- c("0.4125" = "#80CAD0" , "0.825" = "#36A7A7", "1.65" = "#276573", "3.3" = "#008163")
Conc_color3 <- c("0.825" = "aquamarine", "1.65" = "#36A7A7", "3.3" = "#276573")

Color_biolu_Pasaia <- c("Ech1" = "aquamarine", "Ech2" = "#36A7A7" , "DMSO" = "#A48A7B")

Color_real_FN <- c("dmso" = "#A48A7B", "CTL" = "#256CB4", "PA_a35" = "#4fd355", "PA_b33" = "#ca98d3", "PA_b95" = "#6e217c", "PA_g33" = "#92b78f", "PA_g60" = "#bbb3bc", "PBS_d35" = "#d3ad4f","PBS_d60" = "#c68640", "HPPE_e425" = "#36A7A7")

my_palette <- rev(brewer.pal(name="BrBG", n=11))[c(1, 3, 4, 5, 7, 8, 9, 11)]
my_palette

```

```{r import datasets}

metal_conc <-  read_csv("Tox/PCA_tables_dmso/Avg_metals.csv", 
    na = "NA") %>% 
  dplyr::select(-"...1") %>% 
  filter(FN != "dmso") %>%   
  arrange(state)
metal_conc

#Diviser metal_conc
df_metals <- split(metal_conc, metal_conc$Metals)
df_metals
# Créer des dataframes individuels dans l'environnement global
names_df <- paste0("", names(df_metals)) 
for (i in seq_along(df_metals)) {
  assign(names_df[i], df_metals[[i]])
}

orga_conc_cat <-  read_xlsx("Tox/PCA_tables_dmso/orga_dmso_avg_cat.xlsx", 
    na = "NA") %>%   
  mutate(state = if_else(state == "EOL", "used", state)) %>% 
  #filter(compounds != "AKP") %>% 
  mutate(FN = case_when(
    FN %in% c("alpha", "PA α ø.35", "pa_a33", "α35") ~ "pa_a35",
    FN %in% c("beta33", "PA β ø.33", "pa_b33", "β33") ~ "pa_b33", 
    FN %in% c("beta95", "PA β ø.95", "pa_b95", "β95") ~ "pa_b95",
    FN %in% c("gamma33", "PA γ ø.33", "pa_g33", "γ33") ~ "pa_g33",
    FN %in% c("gamma60", "PA γ ø.60", "pa_g60", "γ60") ~ "pa_g60",
    FN %in% c("delta35", "PBS δ ø.35", "pbs_d35", "δ35") ~ "pbs_d35",
    FN %in% c("delta60", "PBS δ ø.60", "pbs_d60", "δ60") ~ "pbs_d60",
    FN %in% c("epsi", "HPPE ε ø4.25", "pe_e4.25", "ε4,25") ~ "hppe_e425",
    TRUE ~ FN  # Garde les autres valeurs inchangées
  )) %>% 
  arrange(state)
orga_conc_cat

#Diviser orga_conc_cat
df_orga_cat <- split(orga_conc_cat, orga_conc_cat$compounds)
df_orga_cat
# Créer des dataframes individuels dans l'environnement global
names_df <- paste0("", names(df_orga_cat)) 
for (i in seq_along(df_orga_cat)) {
  assign(names_df[i], df_orga_cat[[i]])
}

orga_conc <-  read_xlsx("Tox/PCA_tables_dmso/orga_dmso_avg.xlsx", 
    na = "NA") %>% 
  mutate(state = if_else(state == "EOL", "used", state)) %>%
  #filter(compounds != "Nonylphénols") %>%
  mutate(FN = case_when(
    FN %in% c("alpha", "PA α ø.35", "pa_a33", "α35") ~ "pa_a35",
    FN %in% c("beta33", "PA β ø.33", "pa_b33", "β33") ~ "pa_b33", 
    FN %in% c("beta95", "PA β ø.95", "pa_b95", "β95") ~ "pa_b95",
    FN %in% c("gamma33", "PA γ ø.33", "pa_g33", "γ33") ~ "pa_g33",
    FN %in% c("gamma60", "PA γ ø.60", "pa_g60", "γ60") ~ "pa_g60",
    FN %in% c("delta35", "PBS δ ø.35", "pbs_d35", "δ35") ~ "pbs_d35",
    FN %in% c("delta60", "PBS δ ø.60", "pbs_d60", "δ60") ~ "pbs_d60",
    FN %in% c("epsi", "HPPE ε ø4.25", "pe_e4.25", "ε4,25") ~ "hppe_e425",
    TRUE ~ FN  # Garde les autres valeurs inchangées
  )) %>% 
  mutate(compounds = case_when(
    compounds == "Nonylphénols" ~ "Nonylphenols",
    TRUE ~ compounds  # Garde les autres valeurs inchangées
  )) %>%
  filter(FN != "blank") %>% 
  arrange(state)
orga_conc

#CrossTable(orga_conc$compounds)

#Diviser orga_conc
df_orga <- split(orga_conc, orga_conc$compounds)
df_orga
# Créer des dataframes individuels dans l'environnement global
names_df <- paste0("", names(df_orga)) 
for (i in seq_along(df_orga)) {
  assign(names_df[i], df_orga[[i]])
}
  

Biolu_inhi <- read_csv("Tox/PCA_tables_dmso/Avg_microtox.csv", 
    na = "NA") %>% 
  dplyr::select(-"...1") %>% 
  filter(FN != "dmso", state != "used+") %>%   
  arrange(state)
Biolu_inhi

Behav_BSI <- read_csv("Tox/PCA_tables_dmso/BSI.csv", 
    na = "NA") %>%  
  mutate(FN = case_when(
    FN %in% c("alpha", "PA α ø.35", "pa_a33") ~ "pa_a35",
    FN %in% c("beta33", "PA β ø.33", "pa_b33") ~ "pa_b33", 
    FN %in% c("beta95", "PA β ø.95", "pa_b95") ~ "pa_b95",
    FN %in% c("gamma33", "PA γ ø.33", "pa_g33") ~ "pa_g33",
    FN %in% c("gamma60", "PA γ ø.60", "pa_g60") ~ "pa_g60",
    FN %in% c("delta35", "PBS δ ø.35", "pbs_d35") ~ "pbs_d35",
    FN %in% c("delta60", "PBS δ ø.60", "pbs_d60") ~ "pbs_d60",
    FN %in% c("epsi", "HPPE ε ø4.25", "pe_e4.25") ~ "hppe_e425",
    TRUE ~ FN  # Garde les autres valeurs inchangées
  ),
  state = case_when(
    state %in% c("u") ~ "used",
    state %in% c("n") ~ "new",
    TRUE ~ state  # Garde les autres valeurs inchangées
  )) %>% 
  dplyr::select(-"...1", -diff, -ctl_0) %>% 
  # mutate(endpt = if_else(endpt == "TPZ LOFF1", "TPZ_LOFF1",
  #                        if_else(endpt == "TPZ LOFF3", "TPZ_LOFF3",
  #                                if_else(endpt == "TPZ Tapping", "TPZ_Tapping", endpt)))
  #        ) %>%  
  arrange(state) %>% 
  mutate(score = if_else(is.na(score), 0, score))
Behav_BSI

#Diviser Behav_BSI 
df_enpts <- split(Behav_BSI, Behav_BSI$endpt)
df_enpts
#Attribuer des noms spécifiques aux df
names_df <- paste0("", names(df_enpts)) 
# Créer des dataframes individuels dans l'environnement global
for (i in seq_along(df_enpts)) {
  assign(names_df[i], df_enpts[[i]])
}



#Behavior based on control value at 1 
Behav_raw <- read_excel("Tox/Ethovision/Behav_corr_matrix_dmso.xlsx") %>% 
  dplyr::select(FN, state, endpt, ctl_0) %>% 
  mutate(FN = case_when(
    FN %in% c("alpha", "PA α ø.35", "pa_a33") ~ "pa_a35",
    FN %in% c("beta33", "PA β ø.33", "pa_b33") ~ "pa_b33", 
    FN %in% c("beta95", "PA β ø.95", "pa_b95") ~ "pa_b95",
    FN %in% c("gamma33", "PA γ ø.33", "pa_g33") ~ "pa_g33",
    FN %in% c("gamma60", "PA γ ø.60", "pa_g60") ~ "pa_g60",
    FN %in% c("delta35", "PBS δ ø.35", "pbs_d35") ~ "pbs_d35",
    FN %in% c("delta60", "PBS δ ø.60", "pbs_d60") ~ "pbs_d60",
    FN %in% c("epsi", "HPPE ε ø4.25", "pe_e4.25") ~ "hppe_e425",
    TRUE ~ FN  # Garde les autres valeurs inchangées
  ),
  state = case_when(
    state %in% c("u") ~ "used",
    state %in% c("n") ~ "new",
    TRUE ~ state  # Garde les autres valeurs inchangées
  )) %>% 
  #make a mean of score by FN and state for the different BLA and the different TPZ
  # group_by(FN, state, endpt_IBR) %>%
  # reframe(avg_ctl0 = mean(ctl_0, na.rm = TRUE)) %>%
  rename(endpt = endpt,
         score = ctl_0) #%>% 
  #filter enpt based on significant diff --> if any diff then useless
  #filter(endpt %in% c("BLA_ON", "VLMR", "VLSR", "ASD_LOFF2", "TPZ_LON", "TPZ_LOFF2"))
Behav_raw

#Diviser Behav raw 
df_enpts <- split(Behav_raw, Behav_raw$endpt)
df_enpts
#Attribuer des noms spécifiques aux df
names_df <- paste0("", names(df_enpts)) 
# Créer des dataframes individuels dans l'environnement global
for (i in seq_along(df_enpts)) {
  assign(names_df[i], df_enpts[[i]])
}

HR <- read_csv("Tox/PCA_tables_dmso/Avg_HR.csv", 
    na = "NA") %>% 
  dplyr::select(-"...1") %>% 
  mutate(FN = case_when(
    FN %in% c("epsi", "HPPE ε ø4.25", "pe_e4.25") ~ "hppe_e425",
    TRUE ~ FN  # Garde les autres valeurs inchangées
  )) %>% 
  filter(FN != "dmso") %>%  
  mutate(avg_HR_adj_eff = abs(100-avg_HR_adj)) %>%
  arrange(state)
HR

Survival <- read_csv("Tox/PCA_tables_dmso/Avg_survival.csv", 
    na = "NA") %>% 
  dplyr::select(-"...1") %>% 
  mutate(FN = case_when(
    FN %in% c("alpha", "PA α ø.35", "pa_a33") ~ "pa_a35",
    FN %in% c("beta33", "PA β ø.33", "pa_b33") ~ "pa_b33", 
    FN %in% c("beta95", "PA β ø.95", "pa_b95") ~ "pa_b95",
    FN %in% c("gamma33", "PA γ ø.33", "pa_g33") ~ "pa_g33",
    FN %in% c("gamma60", "PA γ ø.60", "pa_g60") ~ "pa_g60",
    FN %in% c("delta35", "PBS δ ø.35", "pbs_d35") ~ "pbs_d35",
    FN %in% c("delta60", "PBS δ ø.60", "pbs_d60") ~ "pbs_d60",
    FN %in% c("epsi", "HPPE ε ø4.25", "pe_e4.25") ~ "hppe_e425",
    TRUE ~ FN  # Garde les autres valeurs inchangées
  ),
  state = case_when(
    state %in% c("u") ~ "used",
    state %in% c("n") ~ "new",
    TRUE ~ state  # Garde les autres valeurs inchangées
  )) %>%
  filter(FN != "Solvent control") %>%   
  arrange(state)
Survival

Viability <- read_csv("Tox/PCA_tables_dmso/Avg_viabillity.csv", 
    na = "NA") %>% 
  dplyr::select(-"...1") %>% 
  filter(FN != "ControlP", FN != "ControlN", FN != "dmso") %>% 
  mutate(avg_eff = abs(100-avg)) %>% 
  arrange(state)
Viability

ROS <- read_csv("Tox/PCA_tables_dmso/Avg_ROS.csv", 
    na = "NA") %>% 
  dplyr::select(-"...1") %>% 
  filter(FN != "ControlP", FN != "ControlN", FN != "dmso") %>%   
  arrange(state)
ROS

Op_time <- ROS %>% 
  dplyr::select(FN, state) %>%
  mutate(op_time_h = c(0, 0, 0, 0, 0, 0, 0, 0,
                     12700, 650, 2700, 2700, 624, 624, 624, 624))
Op_time

```

### Data Preparation
```{r }

df_PCA1 <- tibble(FN = BLA_OFF$FN, 
                 state = BLA_OFF$state,
                 Op_time = Op_time$op_time_h,
                 
                 Ag=Ag$Avg,
                 Al=Al$Avg,
                 As=As$Avg,
                 Cu=Cu$Avg,
                 Fe=Fe$Avg,
                 Mn=Mn$Avg,
                 Zn=Zn$Avg,
                 
                 # HAP = HAP$avg_corr,
                 # PBDE = PBDE$avg_corr,
                 # Phtalates = Phtalates$avg_corr,
                 # AKP_NP = AKP_NP$avg_corr,
                 tOP = `4-tOP`$avg_corr,
                 acenaphtene = acenaphtene$avg_corr,
                 acenaphtylene = acenaphtylene$avg_corr,
                 anthracene = anthracene$avg_corr,
                 ATBC = ATBC$avg_corr,
                 BBP = BBP$avg_corr,
                 BDE_100 = `BDE 100`$avg_corr,
                 BDE_153 = `BDE 153`$avg_corr,
                 BDE_28 = `BDE 28`$avg_corr,
                 BDE_47 = `BDE 47`$avg_corr,
                 BDE_154 = `BDE 154`$avg_corr,
                 BDE_183 = `BDE 183`$avg_corr,
                 BDE_99 = `BDE 99`$avg_corr,
                 benzoghiperylee = `benzo(ghi)péryléne`$avg_corr,
                 benzofluoranthene = `benzo[b+k]fluoranthene`$avg_corr,
                 benzoaanthracene = benzoaanthracene$avg_corr,
                 benzoepyrene = benzoepyrene$avg_corr,
                 benzothiophene = benzothiophene$avg_corr,
                 biphenyl = biphenyl$avg_corr,
                 chrysene = chrysene$avg_corr,
                 DBP = DBP$avg_corr,
                 DEHA = DEHA$avg_corr,
                 DEP = DEP$avg_corr,
                 DEHP = DEHP$avg_corr,
                 DMP = DMP$avg_corr,
                 dibenzoahanthracene = dibenzoahanthracene$avg_corr,
                 Dibenzothiophene = Dibenzothiophene$avg_corr,
                 fluoranthene = fluoranthene$avg_corr,
                 fluorene = fluorene$avg_corr,
                 indeno123cdpyrene = indeno123cdpyrene$avg_corr,
                 naphtalene = naphtalene$avg_corr,
                 nonylphenols = Nonylphenols$avg_corr,
                 Phenanthrene = Phenanthrene$avg_corr,
                 pyrene = pyrene$avg_corr,
                 
                 Biolu_inhi = Biolu_inhi$mean,
                 # BLA_LOFF1 = BLA_OFF$score, 
                 # BLA_LON = BLA_LON$score,
                 BLA_OFF = BLA_OFF$score, 
                 BLA_LON = BLA_LON$score, 
                 VLMR = VLMR$score,
                 VLSR = VLSR$score,
                 ASD_LOFF2 = ASD_LOFF2$score,
                 TPZ_LOFF1 = TPZ_LOFF1$score,
                 TPZ_LON = TPZ_LON$score,
                 TPZ_LOFF2 = TPZ_LOFF2$score,
                 Survival = Survival$Dead_avg,
                 HR = HR$avg_HR_adj,
                 ROS = ROS$avg,
                 Viability = Viability$avg
                 ) %>% 
  mutate(state = as.factor(state)) %>% 
  mutate_all(~ replace(., is.na(.), 0))
df_PCA1

df_PCA <- df_PCA1 
df_PCA

```


#Correlation matrix
##All FN
```{r corr test without corr}
df_PCA2 <- df_PCA %>% 
  mutate(FN_state = paste(FN, state, sep = "_")) %>% 
  dplyr::select(-FN, -state, -FN_state) #%>% 
#   dplyr::select(
#     "Op_time",
#     "Ag", "Al", "Cu", "Fe", "Mn", "Zn",
# "benzoghiperylee", "dibenzoahanthracene", "anthracene","benzoepyrene", "acenaphtene", "fluorene", "pyrene", "Phenanthrene", "benzofluoranthene",
# "BDE_100", "BDE_47", "BDE_153",
# "ATBC", "DEHA", "DEP",
# "tOP", "nonylphenols",
# "Biolu_inhi",
#                 "BLA", "VLMR", "VLSR",
#                 "ASD_LOFF2", "TPZ", "Survival", "HR", "ROS", "Viability")
df_PCA2

df_PCA2 <- as.data.frame(df_PCA2)
rownames(df_PCA2) <- c("pa_a35_new", "pa_b33_new", "pa_b95_new", 
                       "pbs_d35_new", "pbs_d60_new",    "hppe_e425_new","pa_g33_new", "pa_g60_new",
                       "pa_a35_used", "pa_b33_used", "pa_b95_used", "pbs_d35_used", "pbs_d60_used",
                       "hppe_e425_used", "pa_g33_used", "pa_g60_used")
df_PCA2

## PCA quantitative variables
#Obtaining the final matrix with values
data <- df_PCA2 %>% 
  cor(method = "spearman", use = "pairwise.complete.obs") %>% 
  round(2)
data

summary(data)

#pairs(data)

#Statistic of correlation
# mat : is a matrix of data
# ... : further arguments to pass to the native R cor.test function
cor.mtest <- function(mat, ...) {
    mat <- as.matrix(mat)
    n <- ncol(mat)
    p.mat<- matrix(NA, n, n)
    diag(p.mat) <- 0
    for (i in 1:(n - 1)) {
        for (j in (i + 1):n) {
            tmp <- cor.test(method = "spearman", mat[, i], mat[, j], ...)
            p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
        }
    }
  colnames(p.mat) <- rownames(p.mat) <- colnames(mat)
  p.mat
}
# matrix of the p-value of the correlation
p.mat <- cor.mtest(df_PCA2)
p.mat

#In p.mat transform all the value > 0.05 to NA
p.mat2 <- ifelse(p.mat > 0.05, NA, p.mat)

p_clean <- p.mat2

# 1) Ignore diagonal when deciding what to keep
diag(p_clean) <- NA_real_  # sets diagonal to NA [web:31]

# 2) Identify variables having at least one significant p-value with another variable
keep <- rowSums(!is.na(p_clean)) > 0  # rows that are not all NA [web:23]

# 3) Subset rows and columns consistently (keeps a square matrix)
p_mat_signif <- p.mat[keep, keep, drop = FALSE]
p_mat_signif 

#A vector with the different variables included in the matrix p_mat_signif 
variables_to_keep <- rownames(p_mat_signif)
variables_to_keep

Plasfito_C <- c("#80CAD0", "#36A7A7", "#276573", "#054959","#E3CCC0", "#F7EAE1", "#A48A7B", "#C6AF8D", "#49BED3", "#256CB4", "#008163", "#44B494", "#7BC6B9")



col <- colorRampPalette(c("#c68640", "#E3CCC0", "grey100",  "#80CAD0", "#36A7A7"))
col <- colorRampPalette(c('#ef6565', '#F7B0B0', 'white', '#90B0D9', '#256CB4'))

#To get the * below the corr coef. 
  #trace(corrplot, edit=TRUE)
  #line 443 replace place_point fct by 
  # adjust text(X,Y ...) according to your needs, here +0.25 is added to the Y-position    
# place_points = function(sig.locs, point) {
#       text(pos.pNew[, 1][sig.locs], (pos.pNew[, 2][sig.locs])+0.25, 
#            labels = point, col = pch.col, cex = pch.cex, 
#            lwd = 2)


corrplot(data, 
         method="circle", 
         #col=col(10), 
         type="lower",
         # tl.col=c("#256CB4","#256CB4","#256CB4", "#256CB4", "#256CB4", "#256CB4", "#256CB4", 
         #          "purple3", 
         #          "green4", "green4", "green4", "#ef6565", "#ef6565", "#ef6565",
         #          "firebrick", "firebrick",
         #          "orange2", "orange2"),
         tl.col="black",
         tl.srt=60,
         p.mat = p.mat, 
         sig.level = c(.001, .01, .05), 
         insig = "label_sig",  # Ceci remplace les astérisques par des espaces vides
         pch.cex = 1.5,
         pch.col = "white",
         diag=T,
         #addCoef.col = "black",
         number.cex = 1,  # Ajuste la taille des nombres
         number.digits = 2,
         mar=c(0,0,0,0),
         addgrid.col = "grey90",
         #col=colorRampPalette(c("#f8e83c", "#368e8c","#430f56"))(200)
         col=colorRampPalette(c("#ed6468", "white","#2b6db2"))(200)
)

```

Correlation between explanatory variable and toxicity variables
Ag, Cu, Fe, Mn, Zn,
benzog

Including all the data:
Both BLA_OFF and BLA_LON are correlated to different explenatory variables
TPZ_LON is not correlated to any explenatory variable
TPZ_LOFF1 and TPZ_LOFF2 are correlated to very similar explenatory variables --> A choice will be needed

```{r corr test with BH correction}
df_PCA2 <- df_PCA %>% 
  mutate(FN_state = paste(FN, state, sep = "_")) %>% 
  dplyr::select(-FN, -state, -FN_state) 
df_PCA2

df_PCA2 <- as.data.frame(df_PCA2)
rownames(df_PCA2) <- c("pa_a35_new", "pa_b33_new", "pa_b95_new", 
                       "pbs_d35_new", "pbs_d60_new",    "hppe_e425_new","pa_g33_new", "pa_g60_new",
                       "pa_a35_used", "pa_b33_used", "pa_b95_used", "pbs_d35_used", "pbs_d60_used",
                       "hppe_e425_used", "pa_g33_used", "pa_g60_used")
df_PCA2


##Correlation coeeficient estimation
#Obtaining the final matrix with values
data <- df_PCA2 %>% 
  cor(method = "spearman", use = "pairwise.complete.obs") %>% 
  round(2)
data

summary(data)

#pairs(data)

##Correlation statistics estimation --> p-value
# mat : is a matrix of data
# ... : further arguments to pass to the native R cor.test function
cor.mtest <- function(mat, ...) {
  mat <- as.matrix(mat)
  n   <- ncol(mat)

  # raw p-value matrix
  p.mat <- matrix(NA_real_, n, n)
  diag(p.mat) <- 0

  for (i in 1:(n - 1)) {
    for (j in (i + 1):n) {
      tmp <- cor.test(mat[, i], mat[, j],
                      method = "spearman", ...)
      p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
    }
  }
  colnames(p.mat) <- rownames(p.mat) <- colnames(mat)

  # Benjamini–Hochberg adjustment on upper triangle
  up.idx   <- upper.tri(p.mat)
  p.vec    <- p.mat[up.idx]
  p.adjvec <- p.adjust(p.vec, method = "BH")  # same as method = "fdr"
  p.adj    <- matrix(NA_real_, n, n)
  diag(p.adj) <- 0
  p.adj[up.idx] <- p.adjvec
  p.adj[lower.tri(p.adj)] <- t(p.adj)[lower.tri(p.adj)]
  colnames(p.adj) <- rownames(p.adj) <- colnames(mat)

  # return both matrices as a list
  list(p.raw = p.mat,
       p.BH  = p.adj)
}

# use:
p.mat   <- cor.mtest(df_PCA2)
p.raw   <- p.mat$p.raw
p.BH    <- p.mat$p.BH

#In p.mat transform all the value > 0.05 to NA
p.mat2 <- ifelse(p.BH > 0.05, NA, p.BH)

p_clean <- p.mat2

# 1) Ignore diagonal when deciding what to keep
diag(p_clean) <- NA_real_  # sets diagonal to NA [web:31]

# 2) Identify variables having at least one significant p-value with another variable
keep <- rowSums(!is.na(p_clean)) > 0  # rows that are not all NA 

# 3) Subset rows and columns consistently (keeps a square matrix)
p_mat_signif <- p.BH[keep, keep, drop = FALSE]
p_mat_signif 

#A vector with the different variables included in the matrix p_mat_signif 
variables_to_keep <- rownames(p_mat_signif)
variables_to_keep

Plasfito_C <- c("#80CAD0", "#36A7A7", "#276573", "#054959","#E3CCC0", "#F7EAE1", "#A48A7B", "#C6AF8D", "#49BED3", "#256CB4", "#008163", "#44B494", "#7BC6B9")



col <- colorRampPalette(c("#c68640", "#E3CCC0", "grey100",  "#80CAD0", "#36A7A7"))
col <- colorRampPalette(c('#ef6565', '#F7B0B0', 'white', '#90B0D9', '#256CB4'))

#To get the * below the corr coef. 
  #trace(corrplot, edit=TRUE)
  #line 443 replace place_point fct by 
  # adjust text(X,Y ...) according to your needs, here +0.25 is added to the Y-position    
# place_points = function(sig.locs, point) {
#       text(pos.pNew[, 1][sig.locs], (pos.pNew[, 2][sig.locs])+0.25, 
#            labels = point, col = pch.col, cex = pch.cex, 
#            lwd = 2)


corrplot(data, 
         method="circle", 
         #col=col(10), 
         type="lower",
         # tl.col=c("#256CB4","#256CB4","#256CB4", "#256CB4", "#256CB4", "#256CB4", "#256CB4", 
         #          "purple3", 
         #          "green4", "green4", "green4", "#ef6565", "#ef6565", "#ef6565",
         #          "firebrick", "firebrick",
         #          "orange2", "orange2"),
         tl.col="black",
         tl.srt=60,
         p.mat = p.BH, 
         sig.level = c(.001, .01, .05), 
         insig = "label_sig",  # Ceci remplace les astérisques par des espaces vides
         pch.cex = 1.5,
         pch.col = "white",
         diag=T,
         #addCoef.col = "black",
         number.cex = 1,  # Ajuste la taille des nombres
         number.digits = 2,
         mar=c(0,0,0,0),
         addgrid.col = "grey90",
         #col=colorRampPalette(c("#f8e83c", "#368e8c","#430f56"))(200)
         col=colorRampPalette(c("#ed6468", "white","#2b6db2"))(200)
)

```


```{r final matrix all}
library(tidyverse)
library(ggplot2)

# Step 1: Convert the correlation matrix to a tidy tibble
cor_tibble <- data %>%
  as.data.frame() %>%
  rownames_to_column("Var1") %>%
  pivot_longer(-Var1, names_to = "Var2", values_to = "cor") %>%
  mutate(Var1 = factor(Var1, levels = colnames(data)),
         Var2 = factor(Var2, levels = colnames(data)))

# Step 2: Convert the p-value matrix to a tidy tibble
pval_tibble <- p.BH %>%
  as.data.frame() %>%
  rownames_to_column("Var1") %>%
  pivot_longer(-Var1, names_to = "Var2", values_to = "p") %>%
  mutate(Var1 = factor(Var1, levels = colnames(p.BH)),
         Var2 = factor(Var2, levels = colnames(p.BH)))

# Step 3: Merge correlation and p-value tibbles
plot_df <- left_join(cor_tibble, pval_tibble, by = c("Var1", "Var2")) %>%
  # Step 4: Set correlation to NA if not significant
  mutate(cor_sig = if_else(p < 0.05, cor, NA_real_)) %>% 
  mutate(
    stars = case_when(
      p < 0.001 ~ "***",
      p < 0.01  ~ "**",
      p < 0.05  ~ "*",
      TRUE      ~ ""
    )
  ) %>% 
  #use the vector variables_to_keep to filter the plot_df
  filter(Var1 %in% variables_to_keep & Var2 %in% variables_to_keep) #%>% 
  # filter(!Var1 %in% c("BDE_154", "BDE_28", "BBP", "DEHP", "indeno123cdpyrene", "naphtalene", "Phenanthrene", "pyrene", "benzoepyrene", 
  #                     "benzoaanthracene", "ATBC", "anthracene", "tOP", "acenapthtene", "fluoranthene", "Dibenzothiophene") & 
  #          !Var2 %in% c("BDE_154", "BDE_28", "BBP", "DEHP", "indeno123cdpyrene", "naphtalene", "Phenanthrene", "pyrene", "benzoepyrene", 
  #                     "benzoaanthracene", "ATBC", "anthracene", "tOP", "acenapthtene", "fluoranthene", "Dibenzothiophene")) 
plot_df

CrossTable(plot_df$Var1)

plot_df_lower <- plot_df %>%
  mutate(
  Var1 = case_when(
    Var1 == "Op_time" ~ "Duration of use (FN)",
      Var1 == "acenaphtene" ~ "Acenaphtene",
      #Var1 == "anthracene" ~ "Anthracene",
      Var1 == "acenaphtylene" ~ "Acenaphtylene",
      Var1 == "benzofluoranthene" ~ "Benzo[b+k]fluoranthene",
      Var1 == "benzoghiperylee" ~ "Benzo(ghi)perylene",
      Var1 == "benzoepyrene" ~ "Benzo[e]pyrene",
    Var1 == "benzoaanthracene" ~ "Benzo[a]anthracene",
      #Var1 == "benzothiophene" ~ "Benzothiophene",
      Var1 == "biphenyl" ~ "Biphenyl", 
      Var1 == "chrysene" ~ "Chrysene",
      Var1 == "dibenzoahanthracene" ~ "Dibenzo[a,h]anthracene",
      Var1 == "fluorene" ~ "Fluorene",
    Var1 == "fluoranthene" ~ "Fluoranthene",
      Var1 == "pyrene" ~ "Pyrene",
      Var1 == "BDE_153" ~ "BDE 153",
    Var1 == "BDE_154" ~ "BDE 154",
    Var1 == "BDE_28" ~ "BDE 28",
      Var1 == "BDE_100" ~ "BDE 100",
      Var1 == "BDE_47" ~ "BDE 47",
      Var1 == "BDE_183" ~ "BDE 183",
      Var1 == "BDE_99" ~ "BDE 99",
      #Var1 == "tOP" ~ "4-tOP",
      Var1 == "nonylphenols" ~ "Nonylphenols",
      Var1 == "Biolu_inhi" ~ "Bacteria Biolu. Inhi.",
      Var1 == "BLA_OFF" ~ "Fish BLA_LOFF",
      Var1 == "BLA_LON" ~ "Fish BLA_LON",
      Var1 == "VLMR" ~ "Fish VLMR",
      Var1 == "VLSR" ~ "Fish VLSR",  
      Var1 == "ASD_LOFF2" ~ "Fish ASD",
      Var1 == "TPZ_LON" ~ "Fish TPZ",
      Var1 == "HR" ~ "Fish heart rate",
      Var1 == "ROS" ~ "Cell ROS",
      Var1 == "Viability" ~ "Cell viability",
      TRUE ~ Var1  # keeps original if no match
    ),
    Var2 = case_when(
    Var2 == "Op_time" ~ "Duration of use (FN)",
      Var2 == "acenaphtene" ~ "Acenaphtene",
      #Var2 == "anthracene" ~ "Anthracene",
      Var2 == "acenaphtylene" ~ "Acenaphtylene",
      Var2 == "benzofluoranthene" ~ "Benzo[b+k]fluoranthene",
      Var2 == "benzoghiperylee" ~ "Benzo(ghi)perylene",
      Var2 == "benzoepyrene" ~ "Benzo[e]pyrene",
    Var2 == "benzoaanthracene" ~ "Benzo[a]anthracene",
      #Var2 == "benzothiophene" ~ "Benzothiophene",
      Var2 == "biphenyl" ~ "Biphenyl", 
      Var2 == "chrysene" ~ "Chrysene",
      Var2 == "dibenzoahanthracene" ~ "Dibenzo[a,h]anthracene",
      Var2 == "fluorene" ~ "Fluorene",
    Var2 == "fluoranthene" ~ "Fluoranthene",
      Var2 == "pyrene" ~ "Pyrene",
    Var2 == "BDE_154" ~ "BDE 154",
    Var2 == "BDE_28" ~ "BDE 28",
      Var2 == "BDE_153" ~ "BDE 153",
      Var2 == "BDE_100" ~ "BDE 100",
      Var2 == "BDE_47" ~ "BDE 47",
      Var2 == "BDE_183" ~ "BDE 183",
      Var2 == "BDE_99" ~ "BDE 99",
      #Var2 == "tOP" ~ "4-tOP",
      Var2 == "nonylphenols" ~ "Nonylphenols",
      Var2 == "Biolu_inhi" ~ "Bacteria Biolu. Inhi.",
      Var2 == "BLA_OFF" ~ "Fish BLA_LOFF",
      Var2 == "BLA_LON" ~ "Fish BLA_LON",
      Var2 == "VLMR" ~ "Fish VLMR",
      Var2 == "VLSR" ~ "Fish VLSR",  
      Var2 == "ASD_LOFF2" ~ "Fish ASD",
      Var2 == "TPZ_LON" ~ "Fish TPZ",
      Var2 == "HR" ~ "Fish heart rate",
      Var2 == "ROS" ~ "Cell ROS",
      Var2 == "Viability" ~ "Cell viability",
      TRUE ~ Var2  # keeps original if no match
    )) %>%
  mutate(
  # Define the order of variables by group
    Var1 = factor(Var1, levels = c(
      "Duration of use (FN)",
      "Al", "Ag", "As", "Cu", "Fe", "Mn", "Zn",
      "Acenaphtene", "Acenaphtylene", "Benzo[a]anthracene", "Benzo[b+k]fluoranthene", "Benzo[e]pyrene", "Benzo(ghi)perylene", "Benzothiophene", "Biphenyl", 
      "Chrysene", "Dibenzo[a,h]anthracene", "Dibenzothiophene", "Fluoranthene", "Fluorene", "Phenanthrene", "Pyrene",
          
      "BDE 47", "BDE 99","BDE 100", "BDE 153", "BDE 183", "BDE 154", "BDE 28",
      "ATBC", "DEHA", "BBPy", "DBP", "DEP", "DMP", 
      "Nonylphenols",
      "Bacteria Biolu. Inhi.", "Fish BLA_LOFF", "Fish BLA_LON", "Fish VLMR", "Fish VLSR", "Fish ASD", "Fish TPZ", 
      "Fish heart rate", "Cell ROS", "Cell viability" 
    )),
    Var2 = factor(Var2, levels = c(
      "Duration of use (FN)",
      "Al", "Ag", "As", "Cu", "Fe", "Mn", "Zn",
      "Acenaphtene", "Acenaphtylene", "Benzo[a]anthracene", "Benzo[b+k]fluoranthene", "Benzo[e]pyrene", "Benzo(ghi)perylene", "Benzothiophene", "Biphenyl", 
      "Chrysene", "Dibenzo[a,h]anthracene", "Dibenzothiophene", "Fluoranthene", "Fluorene", "Phenanthrene", "Pyrene",
          
      "BDE 47", "BDE 99","BDE 100", "BDE 153", "BDE 183", "BDE 154", "BDE 28",
      "ATBC", "DEHA", "BBP", "DBP", "DEP", "DMP", 
      "Nonylphenols",
      "Bacteria Biolu. Inhi.", "Fish BLA_LOFF", "Fish BLA_LON", "Fish VLMR", "Fish VLSR", "Fish ASD", "Fish TPZ", 
      "Fish heart rate", "Cell ROS", "Cell viability" 
    ))
  ) %>%
  filter(as.integer(Var1) > as.integer(Var2)) 

# if not already installed
library(ggtext)

color_mapping <- c(
  # Operating time (black)
  "Duration of use (FN)" = "black",
  # Metals (brown)
  "Al" = "black", "Zn" = "black", "Mn" = "black", "Fe" = "black", "Cu" = "black", "Ag" = "black", "As" = "black",
  # PAHs (grey)
  "Acenaphtene"= "black", "Acenaphtylene"= "black", "Benzo[a]anthracene" = "black", "Benzo[b+k]fluoranthene"= "black", "Benzo[e]pyrene"= "black", "Benzo(ghi)perylene"= "black", "Benzothiophene"= "black", "Biphenyl"= "black", "Chrysene"= "black", "Dibenzo[a,h]anthracene"= "black", "Dibenzothiophene" = "black", "Fluorene"= "black", "Fluoranthene"= "black", "Phenanthrene"= "black", "Pyrene"= "black",
  # PBDE (blue)
  "BDE 47" = "black", "BDE 99" = "black", "BDE 100" = "black", "BDE 153" = "black", "BDE 183" = "black", "BDE 154" = "black", "BDE 28" = "black",
  # Phthalate (sky blue)
  "DEHA" = "black", "BBP" = "black", "DBP" = "black", "DMP" = "black", "DEP" = "black", "ATBC" = "black",
  # Alkylphenol (orange)
  "Nonylphenols" = "black",
  # Toxicity variables (red)
  "Fish BLA_LOFF" = "#256CB4", "Fish BLA_LON" = "#256CB4", "Fish VLMR" = "#256CB4", "Fish VLSR" = "#256CB4", "Fish ASD" = "#256CB4", "Fish TPZ" = "#256CB4", 
  "Fish Mortality" = "#256CB4", "Fish heart rate" = "#256CB4",
  "Cell ROS" = "#256CB4", "Cell viability" = "#256CB4", "Bacteria Biolu. Inhi." = "#256CB4"
)

labeller_fun <- function(lbls) {
  sapply(lbls, function(x) paste0("<span style='color:", color_mapping[x], ";'>", x, "</span>"))
}

ggplot(plot_df_lower, aes(x = Var1, y = Var2, fill = cor_sig)) +
  geom_tile(color = "grey90", na.rm = TRUE) +
  geom_text(aes(label = if_else(is.na(cor_sig), "", sprintf("%.2f", cor_sig))),
            size = 3.3, fontface = "bold", color = "white", vjust = 0.1) +
  geom_text(aes(label = stars), vjust = 1.1, color = "white", size = 5.5) +
  scale_fill_gradient2(low = "#f52a3f", mid = "white", high = "#1848b3", 
                       midpoint = 0, limits = c(-1, 1), na.value = "white") +
  scale_x_discrete(labels = labeller_fun) +
  scale_y_discrete(labels = labeller_fun) +
  labs(
    #title = "Correlations between chemical compounds in the extracts\nand ecotoxicological effects caused by the extracts",
    #subtitle = "Including extracts of new and EOL fishing nets",
    x = NULL,
    y = NULL,
    fill = "Spearman's Correlation with Benjamini–Hochberg's corrrection"
  ) +
  theme_classic() +
  theme(
    axis.text.x = ggtext::element_markdown(size = 16, face = 'bold', angle = 35, hjust = 1),
    axis.text.y = ggtext::element_markdown(size = 16, face = 'bold'),
    axis.title.x = element_text(size = 16, face = "bold"),
    axis.title.y = element_text(size = 16, face = "bold"),
    title = element_text(size = 19, face = "bold"),
    strip.text = element_text(face = "bold", size = rel(2)),
    legend.position = "top",
    legend.spacing.y = unit(1, 'cm'),
    legend.text = element_text(size = 12, face = 'bold', color = "black"),
    legend.key.size = unit(0.85, "cm"),
    legend.key.width = unit(1, "cm"),
    legend.title.align = 0,
    legend.title = element_text(size = 15, face = "bold"),
    plot.margin = unit(c(1, 1, 1, 1), "cm"),
    legend.key.spacing.y = unit(1, "cm")
  ) +
  guides(fill = guide_colorbar(barwidth = 15, barheight = 1,
                title.position = "top", title.hjust = 0.5))

```


##New FN
```{r}
df_PCA2 <- df_PCA %>% 
  filter(state == "new") %>%
  mutate(FN_state = paste(FN, state, sep = "_")) %>% 
  dplyr::select(-FN, -state, -FN_state) #%>% 
  # dplyr::select("Zn", "Mn",
  # 
  #               "acenaphtylene","anthracene", "benzoaanthracene", "benzofluoranthene", "fluorene", "chrysene", "pyrene",
  #               "BDE_99",
  #               "ATBC","BBP","tOP","DBP","DEHA",
  # 
  #               "Biolu_inhi",
  #               "BLA",
  #               "ASD_LOFF2", "TPZ", "Survival", "HR", "ROS", "Viability")
  #dplyr::select(-Op_time, -benzoghiperylee, -dibenzoahanthracene, -BDE_183)
df_PCA2

df_PCA2 <- as.data.frame(df_PCA2)
rownames(df_PCA2) <- c("pa_a35_new", "pa_b33_new", "pa_b95_new", 
                       "pbs_d35_new", "pbs_d60_new",    "hppe_e425_new","pa_g33_new", "pa_g60_new")
df_PCA2

## PCA quantitative variables
#Obtaining the final matrix with values
data <- df_PCA2 %>% 
  cor(method = "spearman") %>% 
  round(2)
data

summary(data)

# p.mat <- cor_pmat(df_PCA2, method = "spearman") %>% 
#   round(3)
# p.mat

#pairs(data)

##Correlation statistics estimation --> p-value
# mat : is a matrix of data
# ... : further arguments to pass to the native R cor.test function
cor.mtest <- function(mat, ...) {
  mat <- as.matrix(mat)
  n   <- ncol(mat)

  # raw p-value matrix
  p.mat <- matrix(NA_real_, n, n)
  diag(p.mat) <- 0

  for (i in 1:(n - 1)) {
    for (j in (i + 1):n) {
      tmp <- cor.test(mat[, i], mat[, j],
                      method = "spearman", ...)
      p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
    }
  }
  colnames(p.mat) <- rownames(p.mat) <- colnames(mat)

  # Benjamini–Hochberg adjustment on upper triangle
  up.idx   <- upper.tri(p.mat)
  p.vec    <- p.mat[up.idx]
  p.adjvec <- p.adjust(p.vec, method = "BH")  # same as method = "fdr"
  p.adj    <- matrix(NA_real_, n, n)
  diag(p.adj) <- 0
  p.adj[up.idx] <- p.adjvec
  p.adj[lower.tri(p.adj)] <- t(p.adj)[lower.tri(p.adj)]
  colnames(p.adj) <- rownames(p.adj) <- colnames(mat)

  # return both matrices as a list
  list(p.raw = p.mat,
       p.BH  = p.adj)
}

# use:
p.mat   <- cor.mtest(df_PCA2)
p.raw   <- p.mat$p.raw
p.BH    <- p.mat$p.BH

#In p.mat transform all the value > 0.05 to NA
p.mat2 <- ifelse(p.BH > 0.05, NA, p.BH)

p_clean <- p.mat2

# 1) Ignore diagonal when deciding what to keep
diag(p_clean) <- NA_real_  # sets diagonal to NA [web:31]

# 2) Identify variables having at least one significant p-value with another variable
keep <- rowSums(!is.na(p_clean)) > 0  # rows that are not all NA 

# 3) Subset rows and columns consistently (keeps a square matrix)
p_mat_signif <- p.BH[keep, keep, drop = FALSE]
p_mat_signif 

#A vector with the different variables included in the matrix p_mat_signif 
variables_to_keep <- rownames(p_mat_signif)
variables_to_keep

Plasfito_C <- c("#80CAD0", "#36A7A7", "#276573", "#054959","#E3CCC0", "#F7EAE1", "#A48A7B", "#C6AF8D", "#49BED3", "#256CB4", "#008163", "#44B494", "#7BC6B9")


col <- colorRampPalette(c("#c68640", "#E3CCC0", "grey100",  "#80CAD0", "#36A7A7"))
col <- colorRampPalette(c('#ef6565', '#F7B0B0', 'white', '#90B0D9', '#256CB4'))

#To get the * below the corr coef. 
  #trace(corrplot, edit=TRUE)
  #line 443 replace place_point fct by 
  # adjust text(X,Y ...) according to your needs, here +0.25 is added to the Y-position    
# place_points = function(sig.locs, point) {
#       text(pos.pNew[, 1][sig.locs], (pos.pNew[, 2][sig.locs])+0.25, 
#            labels = point, col = pch.col, cex = pch.cex, 
#            lwd = 2)


corrplot(data, 
         method="color", 
         #col=col(10), 
         type="upper",
         # tl.col=c("#256CB4","#256CB4","#256CB4", "#256CB4", "#256CB4", "#256CB4", "#256CB4", 
         #          "purple3", 
         #          "green4", "green4", "green4", "#ef6565", "#ef6565", "#ef6565",
         #          "firebrick", "firebrick",
         #          "orange2", "orange2"),
         tl.col="black",
         tl.srt=90,
         p.mat = p.BH, 
         sig.level = c(.001, .01, .05), 
         insig = "label_sig",  # Ceci remplace les astérisques par des espaces vides
         pch.cex = 1.5,
         pch.col = "white",
         diag=T,
         #addCoef.col = "black",
         number.cex = 1,  # Ajuste la taille des nombres
         number.digits = 2,
         mar=c(0,0,1,0),
         addgrid.col = "grey90",
         #col=colorRampPalette(c("#f8e83c", "#368e8c","#430f56"))(200)
         col=colorRampPalette(c("firebrick", "white","blue4"))(200)
)

```

In the matrix with only the new FNs:
BLA_OFF and BLA_LON are correlated to different explenatory variables
TPZ_LON is not correlated to any explenatory variable
TPZ_LOFF1 & TPZ_LOFF2 are correlated to different explenatory variables --> TPZ_LOFF1 no correlation while TPZ_LOFF2 interesting correlations



```{r final matrix new}
library(tidyverse)
library(ggplot2)

# Step 1: Convert the correlation matrix to a tidy tibble
cor_tibble <- data %>%
  as.data.frame() %>%
  rownames_to_column("Var1") %>%
  pivot_longer(-Var1, names_to = "Var2", values_to = "cor") %>%
  mutate(Var1 = factor(Var1, levels = colnames(data)),
         Var2 = factor(Var2, levels = colnames(data)))

# Step 2: Convert the p-value matrix to a tidy tibble
pval_tibble <- p.BH %>%
  as.data.frame() %>%
  rownames_to_column("Var1") %>%
  pivot_longer(-Var1, names_to = "Var2", values_to = "p") %>%
  mutate(Var1 = factor(Var1, levels = colnames(p.BH)),
         Var2 = factor(Var2, levels = colnames(p.BH)))

# Step 3: Merge correlation and p-value tibbles
plot_df <- left_join(cor_tibble, pval_tibble, by = c("Var1", "Var2")) %>%
  # Step 4: Set correlation to NA if not significant
  mutate(cor_sig = if_else(p < 0.05, cor, NA_real_)) %>% 
  mutate(
    stars = case_when(
      p < 0.001 ~ "***",
      p < 0.01  ~ "**",
      p < 0.05  ~ "*",
      TRUE      ~ ""
    )
  ) %>% 
  #use the vector variables_to_keep to filter the plot_df
  filter(Var1 %in% variables_to_keep & Var2 %in% variables_to_keep) %>% 
  filter(!Var1 %in% c("BDE_100", "BDE_153", "BDE_154", "BMP", "DMP", "Phenanthrene", "pyrene", "benzoepyrene",
                      "benzoaanthracene", "acenapthtene", "fluoranthene", "Dibenzothiophene", "benzofluoranthene",
                      "benzothiophene", "chrysene", "DEP", "nonylphenols", "acenaphtene") &
           !Var2 %in% c("BDE_100", "BDE_153", "BDE_154", "BMP", "DMP", "Phenanthrene", "pyrene", "benzoepyrene",
                      "benzoaanthracene", "acenapthtene", "fluoranthene", "Dibenzothiophene", "benzofluoranthene",
                      "benzothiophene", "chrysene", "DEP", "nonylphenols", "acenaphtene"))
plot_df

CrossTable(plot_df$Var1)


plot_df_lower <- plot_df %>%
  mutate(
  Var1 = case_when(
      Var1 == "acenaphtylene" ~ "Acenaphtylene",
      Var1 == "anthracene" ~ "Anthracene",
      #Var1 == "benzoaanthracene" ~ "Benzo[a]anthracene",
      #Var1 == "benzofluoranthene" ~ "Benzo[b+k]fluoranthene",
      Var1 == "fluorene" ~ "Fluorene",
      Var1 == "biphenyl" ~ "Biphenyl",
      Var1 == "naphtalene" ~ "Naphtalene",
      #Var1 == "pyrene" ~ "Pyrene",
      Var1 == "BDE_28" ~ "BDE 28",
      Var1 == "BDE_47" ~ "BDE 47",
      Var1 == "BDE_99" ~ "BDE 99",
      Var1 == "tOP" ~ "4-tOP",
      Var1 == "Biolu_inhi" ~ "Bacteria biolu. inhi.",
      Var1 == "BLA_OFF" ~ "Fish BLA_LOFF",
      Var1 == "BLA_LON" ~ "Fish BLA_LON",
      Var1 == "VLSR" ~ "Fish VLSR",
      Var1 == "VLMR" ~ "Fish VLMR",
      Var1 == "ASD_LOFF2" ~ "Fish ASD",
      Var1 == "TPZ_OFF2" ~ "Fish TPZ",
      Var1 == "Survival" ~ "Fish Mortality",
      Var1 == "HR" ~ "Fish heart rate",
      Var1 == "ROS" ~ "Cell ROS",
      Var1 == "Viability" ~ "Cell viability",
      TRUE ~ Var1  # keeps original if no match
    ),
    Var2 = case_when(
      Var2 == "acenaphtylene" ~ "Acenaphtylene",
      Var2 == "anthracene" ~ "Anthracene",
      #Var2 == "benzoaanthracene" ~ "Benzo[a]anthracene",
      #Var2 == "benzofluoranthene" ~ "Benzo[b+k]fluoranthene",
      Var2 == "fluorene" ~ "Fluorene",
      Var2 == "biphenyl" ~ "Biphenyl",
      Var2 == "naphtalene" ~ "Naphtalene",
      #Var2 == "pyrene" ~ "Pyrene",
      Var2 == "BDE_28" ~ "BDE 28",
      Var2 == "BDE_47" ~ "BDE 47",
      Var2 == "BDE_99" ~ "BDE 99",
      Var2 == "tOP" ~ "4-tOP",
      Var2 == "Biolu_inhi" ~ "Bacteria biolu. inhi.",
      Var2 == "BLA_OFF" ~ "Fish BLA_LOFF",
      Var2 == "BLA_LON" ~ "Fish BLA_LON",
      Var2 == "VLSR" ~ "Fish VLSR",
      Var2 == "VLMR" ~ "Fish VLMR",
      Var2 == "ASD_LOFF2" ~ "Fish ASD",
      Var2 == "TPZ_OFF2" ~ "Fish TPZ",
      Var2 == "Survival" ~ "Fish Mortality",
      Var2 == "HR" ~ "Fish heart rate",
      Var2 == "ROS" ~ "Cell ROS",
      Var2 == "Viability" ~ "Cell viability",
      TRUE ~ Var2  # keeps original if no match
    )) %>%
  mutate(
  # Define the order of variables by group
    Var1 = factor(Var1, levels = c(
      "Ag", "Al", "As", "Mn", "Zn",
      "Acenaphtylene", "Anthracene", "Biphenyl", "Fluorene", "Naphtalene", 
      "BDE 28", "BDE 47", "BDE 99",
      "ATBC", "DEHA", "DEHP", "DBP",
      "4-tOP",
      "Bacteria biolu. inhi.", "Fish BLA_LOFF", "Fish BLA_LON", "Fish VLSR", "Fish VLMR", "Fish ASD", "Fish TPZ", "Fish Mortality",
      "Fish heart rate", "Cell ROS", "Cell viability"
    )),
    Var2 = factor(Var2, levels = c(
      "Ag", "Al", "As", "Mn", "Zn",
      "Acenaphtylene", "Anthracene", "Biphenyl", "Fluorene", "Naphtalene", 
      "BDE 28", "BDE 47", "BDE 99",
      "ATBC", "DEHA", "DEHP", "DBP",
      "4-tOP",
      "Bacteria biolu. inhi.", "Fish BLA_LOFF", "Fish BLA_LON", "Fish VLSR", "Fish VLMR", "Fish ASD", "Fish TPZ", "Fish Mortality",
      "Fish heart rate", "Cell ROS", "Cell viability"
    ))
  ) %>%
  filter(as.integer(Var1) > as.integer(Var2)) 

# if not already installed
library(ggtext)

color_mapping <- c(
  # Metals (brown)
  "Ag"= "black", "Al"= "black", "As"= "black", "Mn" = "black", "Zn" = "black",
  # PAHs (grey)
  "Acenaphtylene"="black", "Anthracene"="black", "Biphenyl"="black", "Fluorene"="black", "Naphtalene"="black", 
  # PBDE (blue)
  "BDE 28"="black", "BDE 47"="black","BDE 99" = "black",
  # Phthalate (sky blue)
  "ATBC" = "black", "DEHA" = "black", "DEHP" = "black", "DBP" = "black",
  # Alkylphenol (orange)
  "4-tOP" = "black",
  # Toxicity variables (red)
  "Fish BLA_LOFF" = "#256CB4", "Fish BLA_LON" = "#256CB4", "Fish VLSR" = "#256CB4","Fish VLMR" = "#256CB4","Fish ASD" = "#256CB4", "Fish TPZ" = "#256CB4", 
  "Fish Mortality" = "#256CB4", "Fish heart rate" = "#256CB4",
  "Cell ROS" = "#256CB4", "Cell viability" = "#256CB4", "Bacteria biolu. inhi." = "#256CB4"
)

labeller_fun <- function(lbls) {
  sapply(lbls, function(x) paste0("<span style='color:", color_mapping[x], ";'>", x, "</span>"))
}

ggplot(plot_df_lower, aes(x = Var1, y = Var2, fill = cor_sig)) +
  geom_tile(color = "grey90", na.rm = TRUE) +
  geom_text(aes(label = if_else(is.na(cor_sig), "", sprintf("%.2f", cor_sig))),
            size = 3.5, fontface = "bold", color = "white", vjust = 0.1) +
  geom_text(aes(label = stars), vjust = 1.2, color = "white", size = 5.5) +
  scale_fill_gradient2(low = "#f52a3f", mid = "white", high = "#1848b3", 
                       midpoint = 0, limits = c(-1, 1), na.value = "white") +
  scale_x_discrete(labels = labeller_fun) +
  scale_y_discrete(labels = labeller_fun) +
  labs(
    title = "Correlations between chemical compounds in the extracts of new FNs\nand ecotoxicological effects caused by the extracts on new FNs",
    x = NULL,
    y = NULL,
    fill = "Spearman Correlation"
  ) +
  theme_classic() +
  theme(
    axis.text.x = ggtext::element_markdown(size = 16, face = 'bold', angle = 45, hjust = 1),
    axis.text.y = ggtext::element_markdown(size = 16, face = 'bold'),
    axis.title.x = element_text(size = 18, face = "bold"),
    axis.title.y = element_text(size = 18, face = "bold"),
    title = element_text(size = 19, face = "bold"),
    strip.text = element_text(face = "bold", size = rel(2)),
    legend.position = "top",
    legend.spacing.y = unit(1, 'cm'),
    legend.text = element_text(size = 12, face = 'bold', color = "black"),
    legend.key.size = unit(0.85, "cm"),
    legend.key.width = unit(1, "cm"),
    legend.title.align = 0,
    legend.title = element_text(size = 16, face = "bold"),
    plot.margin = unit(c(1, 1, 1, 1), "cm"),
    legend.key.spacing.y = unit(1, "cm")
  ) +
  guides(fill = guide_colorbar(barwidth = 15, barheight = 1.1,
                title.position = "top", title.hjust = 0.5))

```

```{r new metals and orga separated, eval=FALSE, include=FALSE}
df_PCA2_metals <- df_PCA %>% 
  filter(state == "new") %>%
  dplyr::select("FN", "state", "Ag", "Al", "As", "Cu", "Fe", "Mn", "Zn",
                "Biolu_inhi", 
                #"BLA_LOFF1", "VLMR",
                "BLA", 
                "ASD_LOFF2", "TPZ", "Survival", "HR", "ROS", "Viability") %>% 
  mutate(FN_state = paste(FN, state, sep = "_")) %>% 
  dplyr::select(-FN, -state, -FN_state) 
df_PCA2_metals

df_PCA2_metals <- as.data.frame(df_PCA2_metals)
rownames(df_PCA2_metals) <- c("pa_a35_new", "pa_b33_new", "pa_b95_new", 
                       "pbs_d35_new", "pbs_d60_new",    "hppe_e425_new","pa_g33_new", "pa_g60_new")
df_PCA2_metals

## PCA quantitative variables
#Obtaining the final matrix with values
data_metals <- df_PCA2_metals %>% 
  cor(method = "spearman") %>% 
  round(2)
data_metals

summary(data_metals)

#Statistic of correlation
# mat : is a matrix of data
# ... : further arguments to pass to the native R cor.test function
cor.mtest <- function(mat, ...) {
    mat <- as.matrix(mat)
    n <- ncol(mat)
    p.mat<- matrix(NA, n, n)
    diag(p.mat) <- 0
    for (i in 1:(n - 1)) {
        for (j in (i + 1):n) {
            tmp <- cor.test(method = "spearman", mat[, i], mat[, j], ...)
            p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
        }
    }
  colnames(p.mat) <- rownames(p.mat) <- colnames(mat)
  p.mat
}
# matrix of the p-value of the correlation
p.mat <- cor.mtest(df_PCA2_metals)
p.mat

# Step 1: Convert the correlation matrix to a tidy tibble
cor_tibble <- data_metals %>%
  as.data.frame() %>%
  rownames_to_column("Var1") %>%
  pivot_longer(-Var1, names_to = "Var2", values_to = "cor") %>%
  mutate(Var1 = factor(Var1, levels = colnames(data_metals)),
         Var2 = factor(Var2, levels = colnames(data_metals)))

# Step 2: Convert the p-value matrix to a tidy tibble
pval_tibble <- p.mat %>%
  as.data.frame() %>%
  rownames_to_column("Var1") %>%
  pivot_longer(-Var1, names_to = "Var2", values_to = "p") %>%
  mutate(Var1 = factor(Var1, levels = colnames(p.mat)),
         Var2 = factor(Var2, levels = colnames(p.mat)))

# Step 3: Merge correlation and p-value tibbles
plot_df <- left_join(cor_tibble, pval_tibble, by = c("Var1", "Var2")) %>%
  # Step 4: Set correlation to NA if not significant
  mutate(cor_sig = if_else(p < 0.05, cor, NA_real_)) %>% 
  mutate(
    stars = case_when(
      p < 0.001 ~ "***",
      p < 0.01  ~ "**",
      p < 0.05  ~ "*",
      TRUE      ~ ""
    )
  )

# Generate ggplot2 heatmap
ggplot(plot_df, aes(x = Var1, y = Var2, fill = cor_sig)) +
  geom_tile(color = "grey90", na.rm = TRUE) +
  geom_text(aes(label = if_else(is.na(cor_sig), "", sprintf("%.2f", cor_sig))),
            size = 4, fontface = "bold", color = "white", vjust = 0.1) +
  # Add the stars slightly higher in the cell (adjust vjust as you need)
  geom_text(aes(label = stars), vjust = 1.3, color = "white", size = 6) +
  scale_fill_gradient2(low = "firebrick", mid = "white", high = "blue4", 
                       midpoint = 0, limits = c(-1, 1), na.value = "white") +
  labs(
    x = NULL,
    y = NULL,
    fill = "Spearman\nCorrelation",
    #title = "Significant Correlations Only (p < 0.05)"
  ) +
  theme_bw() +
  theme(legend.position = "none") +
  theme(axis.title.x = element_text(size = 18, face = "bold", vjust = 0, margin = margin(t = 0, r = 0, b = 0, l = 0)),
        axis.title.y = element_text(size = 18, face = "bold", vjust = 0, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.text.x = element_text(size = 16, face = 'bold', angle = 45, hjust = 1),
        axis.text.y = element_text(size = 16, face = 'bold'),
        title = element_text(size = 22, face = "bold"),
        strip.text = element_text(face = "bold", size = rel(2)),
        legend.position = "right",
        legend.spacing.y = unit(0.3, 'cm'),
        legend.text = element_text(size = 12, face = 'bold', color = "black"),
        legend.key.size = unit(0.85, "cm"),
        legend.key.width = unit(1, "cm"),
        legend.title.align = 0,
        legend.title = element_text(size = 16, face = "bold", margin = margin(t = 0, r = 0, b = 10, l = 0)),
        plot.margin = unit(c(1, 1, 1, 1), "cm"),
        legend.key.spacing.y = unit(0.3, "cm"))

#organic compounds----------
df_PCA2_orga <- df_PCA %>% 
  filter(state == "new") %>%
  dplyr::select("FN", "state", 
                
                # "tOP",  "acenaphtene",  "acenaphtylene",  "anthracene",  "ATBC",  "BBP",      "BDE_28",  "BDE_47",  "BDE_154",  
                # #"BDE_183",  "BDE_153", "BDE_100", "benzofluoranthene",  "dibenzoahanthracene", 
                # "BDE_99",  "benzoghiperylee",  "benzoaanthracene",  "Dibenzothiophene", "fluoranthene", "benzoepyrene",  "benzothiophene",  "biphenyl",  "chrysene",  "DBP",  "DEHA",  "DEP",  "DEHP",  "DMP", ,    "fluorene",  "indeno123cdpyrene",  "naphtalene", "Phenanthrene",  "pyrene",
                
                "acenaphtylene","anthracene", "benzoaanthracene", "fluorene", "chrysene", "pyrene", 
                "BDE_99",
                "ATBC","BBP","tOP","DBP","DEHA",
                
                "Biolu_inhi", 
                #"BLA_LOFF1", "VLMR",
                "BLA", 
                "ASD_LOFF2", "TPZ", "Survival", "HR", "ROS", "Viability") %>% 
  mutate(FN_state = paste(FN, state, sep = "_")) %>% 
  dplyr::select(-FN, -state, -FN_state) 
df_PCA2_orga

df_PCA2_orga <- as.data.frame(df_PCA2_orga)
rownames(df_PCA2_orga) <- c("pa_a35_new", "pa_b33_new", "pa_b95_new", 
                       "pbs_d35_new", "pbs_d60_new",    "hppe_e425_new","pa_g33_new", "pa_g60_new")
df_PCA2_orga

## PCA quantitative variables
#Obtaining the final matrix with values
data_orga <- df_PCA2_orga %>% 
  cor(method = "spearman") %>% 
  round(2)
data_orga

summary(data_orga)

#Statistic of correlation
# mat : is a matrix of data
# ... : further arguments to pass to the native R cor.test function
cor.mtest <- function(mat, ...) {
    mat <- as.matrix(mat)
    n <- ncol(mat)
    p.mat<- matrix(NA, n, n)
    diag(p.mat) <- 0
    for (i in 1:(n - 1)) {
        for (j in (i + 1):n) {
            tmp <- cor.test(method = "spearman", mat[, i], mat[, j], ...)
            p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
        }
    }
  colnames(p.mat) <- rownames(p.mat) <- colnames(mat)
  p.mat
}
# matrix of the p-value of the correlation
p.mat <- cor.mtest(df_PCA2_orga)
p.mat

# Step 1: Convert the correlation matrix to a tidy tibble
cor_tibble <- data_orga %>%
  as.data.frame() %>%
  rownames_to_column("Var1") %>%
  pivot_longer(-Var1, names_to = "Var2", values_to = "cor") %>%
  mutate(Var1 = factor(Var1, levels = colnames(data_orga)),
         Var2 = factor(Var2, levels = colnames(data_orga)))

# Step 2: Convert the p-value matrix to a tidy tibble
pval_tibble <- p.mat %>%
  as.data.frame() %>%
  rownames_to_column("Var1") %>%
  pivot_longer(-Var1, names_to = "Var2", values_to = "p") %>%
  mutate(Var1 = factor(Var1, levels = colnames(p.mat)),
         Var2 = factor(Var2, levels = colnames(p.mat)))

# Step 3: Merge correlation and p-value tibbles
plot_df <- left_join(cor_tibble, pval_tibble, by = c("Var1", "Var2")) %>%
  # Step 4: Set correlation to NA if not significant
  mutate(cor_sig = if_else(p < 0.05, cor, NA_real_)) %>% 
  mutate(
    stars = case_when(
      p < 0.001 ~ "***",
      p < 0.01  ~ "**",
      p < 0.05  ~ "*",
      TRUE      ~ ""
    )
  )

# Generate ggplot2 heatmap
ggplot(plot_df, aes(x = Var1, y = Var2, fill = cor_sig)) +
  geom_tile(color = "grey90", na.rm = TRUE) +
  geom_text(aes(label = if_else(is.na(cor_sig), "", sprintf("%.2f", cor_sig))),
            size = 4, fontface = "bold", color = "white", vjust = 0.1) +
  # Add the stars slightly higher in the cell (adjust vjust as you need)
  geom_text(aes(label = stars), vjust = 1.3, color = "white", size = 6) +
  scale_fill_gradient2(low = "#f52a3f", mid = "white", high = "#1848b3", 
                       midpoint = 0, limits = c(-1, 1), na.value = "white") +
  labs(
    x = NULL,
    y = NULL,
    fill = "Spearman\nCorrelation",
    #title = "Significant Correlations Only (p < 0.05)"
  ) +
  theme_bw() +
  theme(legend.position = "none") +
  theme(axis.title.x = element_text(size = 18, face = "bold", vjust = 0, margin = margin(t = 0, r = 0, b = 0, l = 0)),
        axis.title.y = element_text(size = 18, face = "bold", vjust = 0, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.text.x = element_text(size = 16, face = 'bold', angle = 45, hjust = 1),
        axis.text.y = element_text(size = 16, face = 'bold'),
        title = element_text(size = 22, face = "bold"),
        strip.text = element_text(face = "bold", size = rel(2)),
        legend.position = "right",
        legend.spacing.y = unit(0.3, 'cm'),
        legend.text = element_text(size = 12, face = 'bold', color = "black"),
        legend.key.size = unit(0.85, "cm"),
        legend.key.width = unit(1, "cm"),
        legend.title.align = 0,
        legend.title = element_text(size = 16, face = "bold", margin = margin(t = 0, r = 0, b = 10, l = 0)),
        plot.margin = unit(c(1, 1, 1, 1), "cm"),
        legend.key.spacing.y = unit(0.3, "cm"))
  

```

orga compounds with significant correlations:
acenaphtylene
anthracene
ATBC
BBP
tOP
DBP
DEHA
fluorene
BDE_99
benzoaanthracene
chysene
pyrene

##Used FN
```{r}
df_PCA2 <- df_PCA %>% 
  filter(state == "used") %>%
  mutate(FN_state = paste(FN, state, sep = "_")) %>% 
  dplyr::select(-FN, -state, -FN_state) #%>%
  # dplyr::select("Op_time",
  #               "Ag",
  # 
  #               "benzothiophene", "benzofluoranthene", "benzoaanthracene", "benzothiophene", "pyrene", "Phenanthrene",
  #               "BDE_100", "BDE_153",
  #               "ATBC", "DEHA",
  # 
  #               "Biolu_inhi",
  #               "BLA", "VLSR", "VLMR",
  #               "ASD_LOFF2", "TPZ", "Survival", "HR", "ROS", "Viability")
  #dplyr::select(-Op_time)
df_PCA2

df_PCA2 <- as.data.frame(df_PCA2)
rownames(df_PCA2) <- c("pa_a35_used", "pa_b33_used", "pa_b95_used", "pbs_d35_used", "pbs_d60_used",
                       "hppe_e425_used", "pa_g33_used", "pa_g60_used")
df_PCA2

## PCA quantitative variables
#Obtaining the final matrix with values
data <- df_PCA2 %>% 
  cor(method = "spearman") %>% 
  round(2)
data

summary(data)

# p.mat <- cor_pmat(df_PCA2, method = "spearman") %>% 
#   round(3)
# p.mat

#pairs(data)

##Correlation statistics estimation --> p-value
# mat : is a matrix of data
# ... : further arguments to pass to the native R cor.test function
cor.mtest <- function(mat, ...) {
  mat <- as.matrix(mat)
  n   <- ncol(mat)

  # raw p-value matrix
  p.mat <- matrix(NA_real_, n, n)
  diag(p.mat) <- 0

  for (i in 1:(n - 1)) {
    for (j in (i + 1):n) {
      tmp <- cor.test(mat[, i], mat[, j],
                      method = "spearman", ...)
      p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
    }
  }
  colnames(p.mat) <- rownames(p.mat) <- colnames(mat)

  # Benjamini–Hochberg adjustment on upper triangle
  up.idx   <- upper.tri(p.mat)
  p.vec    <- p.mat[up.idx]
  p.adjvec <- p.adjust(p.vec, method = "BH")  # same as method = "fdr"
  p.adj    <- matrix(NA_real_, n, n)
  diag(p.adj) <- 0
  p.adj[up.idx] <- p.adjvec
  p.adj[lower.tri(p.adj)] <- t(p.adj)[lower.tri(p.adj)]
  colnames(p.adj) <- rownames(p.adj) <- colnames(mat)

  # return both matrices as a list
  list(p.raw = p.mat,
       p.BH  = p.adj)
}

# use:
p.mat   <- cor.mtest(df_PCA2)
p.raw   <- p.mat$p.raw
p.BH    <- p.mat$p.BH

#In p.mat transform all the value > 0.05 to NA
p.mat2 <- ifelse(p.BH > 0.05, NA, p.BH)

p_clean <- p.mat2

# 1) Ignore diagonal when deciding what to keep
diag(p_clean) <- NA_real_  # sets diagonal to NA [web:31]

# 2) Identify variables having at least one significant p-value with another variable
keep <- rowSums(!is.na(p_clean)) > 0  # rows that are not all NA 

# 3) Subset rows and columns consistently (keeps a square matrix)
p_mat_signif <- p.BH[keep, keep, drop = FALSE]
p_mat_signif 

#A vector with the different variables included in the matrix p_mat_signif 
variables_to_keep <- rownames(p_mat_signif)
variables_to_keep


Plasfito_C <- c("#80CAD0", "#36A7A7", "#276573", "#054959","#E3CCC0", "#F7EAE1", "#A48A7B", "#C6AF8D", "#49BED3", "#256CB4", "#008163", "#44B494", "#7BC6B9")


col <- colorRampPalette(c("#c68640", "#E3CCC0", "grey100",  "#80CAD0", "#36A7A7"))
col <- colorRampPalette(c('#ef6565', '#F7B0B0', 'white', '#90B0D9', '#256CB4'))

#To get the * below the corr coef. 
  #trace(corrplot, edit=TRUE)
  #line 443 replace place_point fct by 
  # adjust text(X,Y ...) according to your needs, here +0.25 is added to the Y-position    
# place_points = function(sig.locs, point) {
#       text(pos.pNew[, 1][sig.locs], (pos.pNew[, 2][sig.locs])+0.25, 
#            labels = point, col = pch.col, cex = pch.cex, 
#            lwd = 2)


corrplot(data, 
         method="circle", 
         #col=col(10), 
         type="lower",
         # tl.col=c("#256CB4","#256CB4","#256CB4", "#256CB4", "#256CB4", "#256CB4", "#256CB4", 
         #          "purple3", 
         #          "green4", "green4", "green4", "#ef6565", "#ef6565", "#ef6565",
         #          "firebrick", "firebrick",
         #          "orange2", "orange2"),
         tl.col="black",
         tl.srt=30,
         p.mat = p.BH, 
         sig.level = c(.001, .01, .05), 
         insig = "label_sig",  # Ceci remplace les astérisques par des espaces vides
         pch.cex = 1.5,
         pch.col = "white",
         diag=T,
         #addCoef.col = "black",
         number.cex = 1,  # Ajuste la taille des nombres
         number.digits = 2,
         mar=c(0,0,1,0),
         addgrid.col = "grey90",
         #col=colorRampPalette(c("#f8e83c", "#368e8c","#430f56"))(200)
         col=colorRampPalette(c("firebrick", "white","blue4"))(200)
)

```


```{r final matrix used}
library(tidyverse)
library(ggplot2)

# Step 1: Convert the correlation matrix to a tidy tibble
cor_tibble <- data %>%
  as.data.frame() %>%
  rownames_to_column("Var1") %>%
  pivot_longer(-Var1, names_to = "Var2", values_to = "cor") %>%
  mutate(Var1 = factor(Var1, levels = colnames(data)),
         Var2 = factor(Var2, levels = colnames(data)))

# Step 2: Convert the p-value matrix to a tidy tibble
pval_tibble <- p.BH %>%
  as.data.frame() %>%
  rownames_to_column("Var1") %>%
  pivot_longer(-Var1, names_to = "Var2", values_to = "p") %>%
  mutate(Var1 = factor(Var1, levels = colnames(p.BH)),
         Var2 = factor(Var2, levels = colnames(p.BH)))

# Step 3: Merge correlation and p-value tibbles
plot_df <- left_join(cor_tibble, pval_tibble, by = c("Var1", "Var2")) %>%
  # Step 4: Set correlation to NA if not significant
  mutate(cor_sig = if_else(p < 0.05, cor, NA_real_)) %>% 
  mutate(
    stars = case_when(
      p < 0.001 ~ "***",
      p < 0.01  ~ "**",
      p < 0.05  ~ "*",
      TRUE      ~ ""
    )
  ) #%>% 
  #use the vector variables_to_keep to filter the plot_df
  #filter(Var1 %in% variables_to_keep & Var2 %in% variables_to_keep) 


plot_df_lower <- plot_df %>%
  mutate(
  Var1 = case_when(
    Var1 == "Op_time" ~ "Operation time",
    Var1 == "acenaphthylene" ~ "Acenaphtylene",
      Var1 == "benzofluoranthene" ~ "Benzofluoranthene",
    Var1 == "benzothiophene" ~ "Benzothiophene",
    Var1 == "biphenyl" ~ "Biphenyl",
      Var1 == "indeno123cdpyrene" ~ "Indeno[1,2,3-cd]pyrene",
      Var1 == "BDE_28" ~ "BDE 28",
    Var1 == "BDE_47" ~ "BDE 47",
      Var1 == "BDE_99" ~ "BDE 99",
      Var1 == "BDE_183" ~ "BDE 183",
      Var1 == "BDE_154" ~ "BDE 154",
      Var1 == "Biolu_inhi" ~ "Bacteria biolu. inhi.",
      Var1 == "BLA_OFF" ~ "Fish BLA_LOFF",
      Var1 == "BLA_LON" ~ "Fish BLA_LON",
      Var1 == "VLSR" ~ "Fish VLSR",
      Var1 == "VLMR" ~ "Fish VLMR",
      Var1 == "ASD_LOFF2" ~ "Fish ASD",
      Var1 == "TPZ_OFF2" ~ "Fish TPZ",
      Var1 == "Survival" ~ "Fish Mortality",
      Var1 == "HR" ~ "Fish heart rate",
      Var1 == "ROS" ~ "Cell ROS",
      Var1 == "Viability" ~ "Cell viability",
      TRUE ~ Var1  # keeps original if no match
    ),
    Var2 = case_when(
      Var2 == "Op_time" ~ "Operation time",
    Var2 == "acenaphthylene" ~ "Acenaphtylene",
      Var2 == "benzofluoranthene" ~ "Benzofluoranthene",
    Var2 == "benzothiophene" ~ "Benzothiophene",
    Var2 == "biphenyl" ~ "Biphenyl",
      Var2 == "BDE_28" ~ "BDE 28",
    Var2 == "BDE_47" ~ "BDE 47",
      Var2 == "BDE_99" ~ "BDE 99",
      Var2 == "BDE_183" ~ "BDE 183",
      Var2 == "BDE_154" ~ "BDE 154",
      Var2 == "Biolu_inhi" ~ "Bacteria biolu. inhi.",
      Var2 == "BLA_OFF" ~ "Fish BLA_LOFF",
      Var2 == "BLA_LON" ~ "Fish BLA_LON",
      Var2 == "VLSR" ~ "Fish VLSR",
      Var2 == "VLMR" ~ "Fish VLMR",
      Var2 == "ASD_LOFF2" ~ "Fish ASD",
      Var2 == "TPZ_OFF2" ~ "Fish TPZ",
      Var2 == "Survival" ~ "Fish Mortality",
      Var2 == "HR" ~ "Fish heart rate",
      Var2 == "ROS" ~ "Cell ROS",
      Var2 == "Viability" ~ "Cell viability",
      TRUE ~ Var2  # keeps original if no match
    )) %>%
  mutate(
  # Define the order of variables by group
    Var1 = factor(Var1, levels = c(
      "Operation time",
      "Ag", "Al", "Zn", "Fe", "Mn",
      "Acenaphtylene", "Benzofluoranthene",  "Benzothiophene", "Biphenyl", "Indeno[1,2,3-cd]pyrene", 
      "BDE 28", "BDE 47","BDE 99","BDE 183","BDE 154", 
      "DEHA", "BBP", "DMP",
      "Bacteria biolu. inhi.", "Fish BLA_LOFF", "Fish BLA_LON", "Fish VLSR", "Fish VLMR", "Fish ASD", "Fish TPZ", "Fish Mortality",
      "Fish heart rate", "Cell ROS", "Cell viability"
    )),
    Var2 = factor(Var2, levels = c(
      "Operation time",
      "Ag", "Al", "Zn", "Fe", "Mn",
      "Acenaphtylene", "Benzofluoranthene",  "Benzothiophene", "Biphenyl", "Indeno[1,2,3-cd]pyrene", 
      "BDE 28", "BDE 47","BDE 99","BDE 183","BDE 154", 
      "DEHA", "BBP", "DMP",
      "Bacteria biolu. inhi.", "Fish BLA_LOFF", "Fish BLA_LON", "Fish VLSR", "Fish VLMR", "Fish ASD", "Fish TPZ", "Fish Mortality",
      "Fish heart rate", "Cell ROS", "Cell viability"
    ))
  ) %>%
  filter(as.integer(Var1) > as.integer(Var2)) %>% 
  mutate(cor_sig = if_else(cor_sig == 1 & stars == "***" & p == 0, NA_real_, cor_sig)) %>%
  mutate(stars = if_else(cor_sig == 1 & stars == "***" & p == 0, "", stars)) 

# if not already installed
library(ggtext)

color_mapping <- c(
  "Operation time" = "black",
  "Ag" = "black", "Al" = "black", "Zn" = "black", "Fe" = "black", "Mn" = "black",
  "Benzofluoranthene" = "black", "Indeno[1,2,3-cd]pyrene" = "black", "Acenaphtylene" = "black", "Benzothiophene" = "black", "Biphenyl" = "black",
  "BDE 28" = "black", "BDE 47" = "black", "BDE 99" = "black", "BDE 183" = "black", "BDE 154" = "black", 
  "DEHA" = "black", "BBP" = "black", "DMP" = "black", 
  # Toxicity variables (red)
  "Bacteria biolu. inhi." = "#256CB4", "Fish BLA_LOFF" = "#256CB4", "Fish BLA_LON" = "#256CB4","Fish VLSR" = "#256CB4", "Fish VLMR" = "#256CB4", "Fish ASD" = "#256CB4", "Fish TPZ" = "#256CB4", 
  "Fish Mortality" = "#256CB4", "Fish heart rate" = "#256CB4",
  "Cell ROS" = "#256CB4", "Cell viability" = "#256CB4"
)

labeller_fun <- function(lbls) {
  sapply(lbls, function(x) paste0("<span style='color:", color_mapping[x], ";'>", x, "</span>"))
}

ggplot(plot_df_lower, aes(x = Var1, y = Var2, fill = cor_sig)) +
  geom_tile(color = "grey90", na.rm = TRUE) +
  geom_text(aes(label = if_else(is.na(cor_sig), "", sprintf("%.2f", cor_sig))),
            size = 3.5, fontface = "bold", color = "white", vjust = 0.1) +
  geom_text(aes(label = stars), vjust = 1.2, color = "white", size = 5.5) +
  scale_fill_gradient2(low = "#f52a3f", mid = "white", high = "#1848b3", 
                       midpoint = 0, limits = c(-1, 1), na.value = "white") +
  scale_x_discrete(labels = labeller_fun) +
  scale_y_discrete(labels = labeller_fun) +
  labs(
    title = "Correlations between chemical compounds in the extracts of EOL FNs\nand ecotoxicological effects caused by the extracts on EOL FNs",
    x = NULL,
    y = NULL,
    fill = "Spearman Correlation"
  ) +
  theme_classic() +
  theme(
    axis.text.x = ggtext::element_markdown(size = 16, face = 'bold', angle = 45, hjust = 1),
    axis.text.y = ggtext::element_markdown(size = 16, face = 'bold'),
    axis.title.x = element_text(size = 18, face = "bold"),
    axis.title.y = element_text(size = 18, face = "bold"),
    title = element_text(size = 19, face = "bold"),
    strip.text = element_text(face = "bold", size = rel(2)),
    legend.position = "top",
    legend.spacing.y = unit(1, 'cm'),
    legend.text = element_text(size = 12, face = 'bold', color = "black"),
    legend.key.size = unit(0.85, "cm"),
    legend.key.width = unit(1, "cm"),
    legend.title.align = 0,
    legend.title = element_text(size = 16, face = "bold"),
    plot.margin = unit(c(1, 1, 1, 1), "cm"),
    legend.key.spacing.y = unit(1, "cm")
  ) +
  guides(fill = guide_colorbar(barwidth = 15, barheight = 1.1,
                title.position = "top", title.hjust = 0.5))
```

```{r new metals and orga separated, eval=FALSE, include=FALSE}
df_PCA2_metals <- df_PCA %>% 
  filter(state == "used") %>%
  dplyr::select("FN", "state", "Ag", "Al", "As", "Cu", "Fe", "Mn", "Zn",
                "Biolu_inhi", 
                "VLMR",
                "BLA", 
                "ASD_LOFF2", "TPZ", "Survival", "HR", "ROS", "Viability") %>% 
  mutate(FN_state = paste(FN, state, sep = "_")) %>% 
  dplyr::select(-FN, -state, -FN_state) 
df_PCA2_metals

df_PCA2_metals <- as.data.frame(df_PCA2_metals)
rownames(df_PCA2_metals) <- c("pa_a35_new", "pa_b33_new", "pa_b95_new", 
                       "pbs_d35_new", "pbs_d60_new",    "hppe_e425_new","pa_g33_new", "pa_g60_new")
df_PCA2_metals

## PCA quantitative variables
#Obtaining the final matrix with values
data_metals <- df_PCA2_metals %>% 
  cor(method = "spearman") %>% 
  round(2)
data_metals

summary(data_metals)

#Statistic of correlation
# mat : is a matrix of data
# ... : further arguments to pass to the native R cor.test function
cor.mtest <- function(mat, ...) {
    mat <- as.matrix(mat)
    n <- ncol(mat)
    p.mat<- matrix(NA, n, n)
    diag(p.mat) <- 0
    for (i in 1:(n - 1)) {
        for (j in (i + 1):n) {
            tmp <- cor.test(method = "spearman", mat[, i], mat[, j], ...)
            p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
        }
    }
  colnames(p.mat) <- rownames(p.mat) <- colnames(mat)
  p.mat
}
# matrix of the p-value of the correlation
p.mat <- cor.mtest(df_PCA2_metals)
p.mat

# Step 1: Convert the correlation matrix to a tidy tibble
cor_tibble <- data_metals %>%
  as.data.frame() %>%
  rownames_to_column("Var1") %>%
  pivot_longer(-Var1, names_to = "Var2", values_to = "cor") %>%
  mutate(Var1 = factor(Var1, levels = colnames(data_metals)),
         Var2 = factor(Var2, levels = colnames(data_metals)))

# Step 2: Convert the p-value matrix to a tidy tibble
pval_tibble <- p.mat %>%
  as.data.frame() %>%
  rownames_to_column("Var1") %>%
  pivot_longer(-Var1, names_to = "Var2", values_to = "p") %>%
  mutate(Var1 = factor(Var1, levels = colnames(p.mat)),
         Var2 = factor(Var2, levels = colnames(p.mat)))

# Step 3: Merge correlation and p-value tibbles
plot_df <- left_join(cor_tibble, pval_tibble, by = c("Var1", "Var2")) %>%
  # Step 4: Set correlation to NA if not significant
  mutate(cor_sig = if_else(p < 0.05, cor, NA_real_)) %>% 
  mutate(
    stars = case_when(
      p < 0.001 ~ "***",
      p < 0.01  ~ "**",
      p < 0.05  ~ "*",
      TRUE      ~ ""
    )
  )

# Generate ggplot2 heatmap
ggplot(plot_df, aes(x = Var1, y = Var2, fill = cor_sig)) +
  geom_tile(color = "grey90", na.rm = TRUE) +
  geom_text(aes(label = if_else(is.na(cor_sig), "", sprintf("%.2f", cor_sig))),
            size = 4, fontface = "bold", color = "white", vjust = 0.1) +
  # Add the stars slightly higher in the cell (adjust vjust as you need)
  geom_text(aes(label = stars), vjust = 1.3, color = "white", size = 6) +
  scale_fill_gradient2(low = "firebrick", mid = "white", high = "blue4", 
                       midpoint = 0, limits = c(-1, 1), na.value = "white") +
  labs(
    x = NULL,
    y = NULL,
    fill = "Spearman\nCorrelation",
    #title = "Significant Correlations Only (p < 0.05)"
  ) +
  theme_bw() +
  theme(legend.position = "none") +
  theme(axis.title.x = element_text(size = 18, face = "bold", vjust = 0, margin = margin(t = 0, r = 0, b = 0, l = 0)),
        axis.title.y = element_text(size = 18, face = "bold", vjust = 0, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.text.x = element_text(size = 16, face = 'bold', angle = 45, hjust = 1),
        axis.text.y = element_text(size = 16, face = 'bold'),
        title = element_text(size = 22, face = "bold"),
        strip.text = element_text(face = "bold", size = rel(2)),
        legend.position = "right",
        legend.spacing.y = unit(0.3, 'cm'),
        legend.text = element_text(size = 12, face = 'bold', color = "black"),
        legend.key.size = unit(0.85, "cm"),
        legend.key.width = unit(1, "cm"),
        legend.title.align = 0,
        legend.title = element_text(size = 16, face = "bold", margin = margin(t = 0, r = 0, b = 10, l = 0)),
        plot.margin = unit(c(1, 1, 1, 1), "cm"),
        legend.key.spacing.y = unit(0.3, "cm"))

#organic compounds----------
df_PCA2_orga <- df_PCA %>% 
  filter(state == "used") %>%
  dplyr::select("FN", "state", 
                
                # "tOP",  "acenaphtene",  "acenaphtylene",  "anthracene",  "ATBC",  "BBP",      "BDE_28",  "BDE_47",  "BDE_154",
                # "BDE_183",  "BDE_153", "BDE_100", "benzofluoranthene",  "dibenzoahanthracene",
                # "BDE_99",  "benzoghiperylee",  "benzoaanthracene",  "Dibenzothiophene", "fluoranthene", "benzoepyrene",  "benzothiophene",  "biphenyl",  "chrysene",  "DBP",  "DEHA",  "DEP",  "DEHP",  "DMP", ,    "fluorene",  "indeno123cdpyrene",  "naphtalene", "Phenanthrene",  "pyrene",
                
                "benzothiophene",
                "BDE_100",
                "DEHA",
                
                "Biolu_inhi", 
                "BLA_LOFF1", "VLMR",
                "BLA_LON", 
                "ASD_LOFF2", "TPZ", "Survival", "HR", "ROS", "Viability") %>% 
  mutate(FN_state = paste(FN, state, sep = "_")) %>% 
  dplyr::select(-FN, -state, -FN_state) 
df_PCA2_orga

df_PCA2_orga <- as.data.frame(df_PCA2_orga)
rownames(df_PCA2_orga) <- c("pa_a35_new", "pa_b33_new", "pa_b95_new", 
                       "pbs_d35_new", "pbs_d60_new",    "hppe_e425_new","pa_g33_new", "pa_g60_new")
df_PCA2_orga

## PCA quantitative variables
#Obtaining the final matrix with values
data_orga <- df_PCA2_orga %>% 
  cor(method = "spearman") %>% 
  round(2)
data_orga

summary(data_orga)

#Statistic of correlation
# mat : is a matrix of data
# ... : further arguments to pass to the native R cor.test function
cor.mtest <- function(mat, ...) {
    mat <- as.matrix(mat)
    n <- ncol(mat)
    p.mat<- matrix(NA, n, n)
    diag(p.mat) <- 0
    for (i in 1:(n - 1)) {
        for (j in (i + 1):n) {
            tmp <- cor.test(method = "spearman", mat[, i], mat[, j], ...)
            p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
        }
    }
  colnames(p.mat) <- rownames(p.mat) <- colnames(mat)
  p.mat
}
# matrix of the p-value of the correlation
p.mat <- cor.mtest(df_PCA2_orga)
p.mat

# Step 1: Convert the correlation matrix to a tidy tibble
cor_tibble <- data_orga %>%
  as.data.frame() %>%
  rownames_to_column("Var1") %>%
  pivot_longer(-Var1, names_to = "Var2", values_to = "cor") %>%
  mutate(Var1 = factor(Var1, levels = colnames(data_orga)),
         Var2 = factor(Var2, levels = colnames(data_orga)))

# Step 2: Convert the p-value matrix to a tidy tibble
pval_tibble <- p.mat %>%
  as.data.frame() %>%
  rownames_to_column("Var1") %>%
  pivot_longer(-Var1, names_to = "Var2", values_to = "p") %>%
  mutate(Var1 = factor(Var1, levels = colnames(p.mat)),
         Var2 = factor(Var2, levels = colnames(p.mat)))

# Step 3: Merge correlation and p-value tibbles
plot_df <- left_join(cor_tibble, pval_tibble, by = c("Var1", "Var2")) %>%
  # Step 4: Set correlation to NA if not significant
  mutate(cor_sig = if_else(p < 0.05, cor, NA_real_)) %>% 
  mutate(
    stars = case_when(
      p < 0.001 ~ "***",
      p < 0.01  ~ "**",
      p < 0.05  ~ "*",
      TRUE      ~ ""
    )
  )

# Generate ggplot2 heatmap
ggplot(plot_df, aes(x = Var1, y = Var2, fill = cor_sig)) +
  geom_tile(color = "grey90", na.rm = TRUE) +
  geom_text(aes(label = if_else(is.na(cor_sig), "", sprintf("%.2f", cor_sig))),
            size = 4, fontface = "bold", color = "white", vjust = 0.1) +
  # Add the stars slightly higher in the cell (adjust vjust as you need)
  geom_text(aes(label = stars), vjust = 1.3, color = "white", size = 6) +
  scale_fill_gradient2(low = "firebrick", mid = "white", high = "blue4", 
                       midpoint = 0, limits = c(-1, 1), na.value = "white") +
  labs(
    x = NULL,
    y = NULL,
    fill = "Spearman\nCorrelation",
    #title = "Significant Correlations Only (p < 0.05)"
  ) +
  theme_bw() +
  theme(legend.position = "none") +
  theme(axis.title.x = element_text(size = 18, face = "bold", vjust = 0, margin = margin(t = 0, r = 0, b = 0, l = 0)),
        axis.title.y = element_text(size = 18, face = "bold", vjust = 0, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.text.x = element_text(size = 16, face = 'bold', angle = 45, hjust = 1),
        axis.text.y = element_text(size = 16, face = 'bold'),
        title = element_text(size = 22, face = "bold"),
        strip.text = element_text(face = "bold", size = rel(2)),
        legend.position = "right",
        legend.spacing.y = unit(0.3, 'cm'),
        legend.text = element_text(size = 12, face = 'bold', color = "black"),
        legend.key.size = unit(0.85, "cm"),
        legend.key.width = unit(1, "cm"),
        legend.title.align = 0,
        legend.title = element_text(size = 16, face = "bold", margin = margin(t = 0, r = 0, b = 10, l = 0)),
        plot.margin = unit(c(1, 1, 1, 1), "cm"),
        legend.key.spacing.y = unit(0.3, "cm"))
  

```

correlation between organic compounds and toxicity variables 
benzothiophene
BDE 100
BBP
DEHA

# ============================================================================
#Perplexity approach

```{r}
library(tidyverse)
library(relaimpo)  # For relative importance
library(corrplot)
library(pheatmap)
library(viridis)
```

# ANALYSIS 1: TOP 5 EXPLANATORY CHEMICALS PER ENDPOINT
```{r tox vs. chemicals}

# Resolve conflicts
select <- dplyr::select

# Define chemical predictors
chemicals <- colnames(df_PCA)[!(colnames(df_PCA) %in% c("FN", "state",
                                              "Biolu_inhi", "BLA_OFF", "BLA_LON", "VLMR", "VLSR",
                                              "ASD_LOFF2", "TPZ_LOFF2", "TPZ_LOFF1", "TPZ_LON",
                                              "Survival", "HR", "ROS", "Viability", "Op_time"))]
chemicals

# Endpoints
endpoints <- c("Biolu_inhi", "BLA_OFF", "BLA_LON", "VLMR", "VLSR",
               "ASD_LOFF2", "TPZ_LOFF2",
               "Survival", "HR", "ROS", "Viability")

# SIMPLIFIED APPROACH: Use correlations + partial correlations
get_top5_predictors <- function(endpoint_name, data, predictors) {
  
  cat("  Analyzing", endpoint_name, "...\n")
  
  # Prepare data -----------------------------------------------------------
  df_analysis <- data %>%
    dplyr::select(all_of(c(predictors, endpoint_name))) %>%
    tidyr::drop_na()
  
  if (nrow(df_analysis) < 10) {
    cat("  Warning: Insufficient data\n")
    return(NULL)
  }
  
  # Spearman correlations + BH correction ---------------------------------
  correlations <- purrr::map_dfr(predictors, function(pred) {
    
    cor_test <- cor.test(
      df_analysis[[pred]],
      df_analysis[[endpoint_name]],
      method = "spearman",
      exact  = FALSE
    )
    
    tibble::tibble(
      chemical        = pred,
      correlation     = unname(cor_test$estimate),
      p_value         = cor_test$p.value,
      abs_correlation = abs(cor_test$estimate)
    )
  }) %>%
    dplyr::mutate(
      p_value_BH = p.adjust(p_value, method = "BH")  # BH / FDR
    )
  
  # Get top 5 by |rho|, report BH significance -----------------------------
  top5 <- correlations %>%
    dplyr::arrange(dplyr::desc(abs_correlation)) %>%
    dplyr::slice(1:5) %>%
    dplyr::mutate(
      endpoint   = endpoint_name,
      rank       = dplyr::row_number(),
      direction  = dplyr::if_else(correlation > 0, "Positive", "Negative"),
      signif_raw = dplyr::case_when(          # optional: keep raw stars
        p_value < 0.001 ~ "***",
        p_value < 0.01  ~ "**",
        p_value < 0.05  ~ "*",
        TRUE            ~ "ns"
      ),
      signif_BH  = dplyr::case_when(          # BH-adjusted stars (recommended)
        p_value_BH < 0.001 ~ "***",
        p_value_BH < 0.01  ~ "**",
        p_value_BH < 0.05  ~ "*",
        TRUE               ~ "ns"
      )
    )
  
  # Simple standardized LM for effect sizes --------------------------------
  top5_with_lm <- purrr::map_dfr(seq_len(nrow(top5)), function(i) {
    
    chem <- top5$chemical[i]
    
    x_scaled <- scale(df_analysis[[chem]])[, 1]
    y_scaled <- scale(df_analysis[[endpoint_name]])[, 1]
    
    lm_fit    <- lm(y_scaled ~ x_scaled)
    lm_sum    <- summary(lm_fit)
    
    top5[i, ] %>%
      dplyr::mutate(
        estimate   = coef(lm_fit)[2],
        std_error  = lm_sum$coefficients[2, "Std. Error"],
        t_value    = lm_sum$coefficients[2, "t value"],
        r_squared  = lm_sum$r.squared
      )
  })
  
  top5_with_lm
}


# Apply to all endpoints

top5_results <- list()

for(endpoint in endpoints) {
  cat("Processing:", endpoint, "\n")
  result <- get_top5_predictors(endpoint, df_PCA, chemicals)
  if(!is.null(result)) {
    top5_results[[endpoint]] <- result
  }
}

# Combine results
top5_df <- bind_rows(top5_results) %>%
  mutate(
    chemical_class = case_when(
      chemical %in% c("Ag", "Al", "As", "Cu", "Fe", "Mn", "Zn") ~ "Metals",
      chemical %in% c("BBP", "DBP","DEP", "DEHP", "DMP") ~ "Phthalates",
      chemical %in% c("ATBC", "DEHA") ~ "Non-phthalate plasticizers",
      str_detect(chemical, "BDE") ~ "Flame Retardants",
      chemical %in% c("tOP", "nonylphenols") ~ "Alkylphenols",
      TRUE ~ "PAHs"
    )
  )

# Display results

for(endpoint in endpoints) {
  endpoint_data <- top5_df %>% filter(endpoint == !!endpoint)
  
  if(nrow(endpoint_data) > 0) {
    cat(endpoint, "\n")
    cat(paste(rep("-", 70), collapse = ""), "\n")
    
    for(i in 1:nrow(endpoint_data)) {
      cat(sprintf(
        "  %d. %-20s [%s] ρ = %6.3f, β = %6.3f (p = %.4f) %s\n",
        endpoint_data$rank[i],
        endpoint_data$chemical[i],
        endpoint_data$chemical_class[i],
        endpoint_data$correlation[i],
        endpoint_data$estimate[i],
        endpoint_data$p_value[i],
        endpoint_data$significance[i]
      ))
    }
    cat("\n")
  }
}

# Display the dataframe
top5_df

CrossTable(top5_df$chemical)

#number of time the chemical appears in the top 5
rank_top5_chem <- top5_df %>%
  group_by(chemical_class) %>%
  summarise(
    appearances = n(),
    avg_pvalue = mean(p_value_BH),
    sd_pvalue = sd(p_value_BH)
  ) %>%
  #add proportion and percentages of apperance based on the number of chemicals by class
  mutate(
    proportion = case_when(
      chemical_class == "Metals" ~ appearances / 7,
      chemical_class == "Phthalates" ~ appearances / 5,
      chemical_class == "Non-phthalate plasticizers" ~ appearances / 2,
      chemical_class == "Flame Retardants" ~ appearances / 5,
      chemical_class == "Alkylphenols" ~ appearances / 2,
      chemical_class == "PAHs" ~ appearances / 11,
      TRUE ~ NA_real_),
    percentage = proportion*100 / sum(proportion)) %>% 
  arrange(desc(percentage)) 
rank_top5_chem
```

```{r Vizualisation}

# Create lollipop chart showing top drivers with significance

#manual order facets
top_5_df <- top5_df %>% 
  mutate(
  endpoint = case_when(
      endpoint == "Biolu_inhi" ~ "Bacteria biolu. inhi.",
      endpoint == "BLA_OFF" ~ "Fish BLA_LOFF",
      endpoint == "BLA_LON" ~ "Fish BLA_LON",
      endpoint == "VLSR" ~ "Fish VLSR",
      endpoint == "VLMR" ~ "Fish VLMR",
      endpoint == "ASD_LOFF2" ~ "Fish ASD",
      endpoint == "TPZ_LOFF2" ~ "Fish TPZ",
      endpoint == "Survival" ~ "Fish Mortality",
      endpoint == "HR" ~ "Fish heart rate",
      endpoint == "ROS" ~ "Cell ROS",
      endpoint == "Viability" ~ "Cell viability",
      endpoint == "Op_time" ~ "Operation time",
      TRUE ~ endpoint)) %>% 
  mutate(
  chemical = case_when(
    chemical == "acenaphtylene" ~ "Acenaphtylene",
      chemical == "benzofluoranthene" ~ "Benzofluoranthene",
    chemical == "benzothiophene" ~ "Benzothiophene",
    chemical == "biphenyl" ~ "Biphenyl",
      chemical == "indeno123cdpyrene" ~ "Indeno[1,2,3-cd]pyrene",
    chemical == "BDE_47" ~ "BDE 47",
      chemical == "BDE_99" ~ "BDE 99",
      chemical == "BDE_100" ~ "BDE 100",
      chemical == "BDE_153" ~ "BDE 153",
    chemical == "BDE_183" ~ "BDE 183",
    chemical == "nonylphenols" ~ "Nonylphenols",
    chemical == "anthracene" ~ "Anthracene",
    chemical == "chrysene" ~ "Chrysene",
    chemical == "fluorene" ~ "Fluorene",
    chemical == "benzoaaanthracene" ~ "Benzo[a]anthracene",
    chemical == "benzoepyrene" ~ "Benzo[e]pyrene",
    chemical == "benzoghiperylee" ~ "Benzo[ghi]perylee",
    chemical == "dibenzoahanthracene" ~ "Dibenzo[a,h]anthracene",
    chemical == "naphtalene" ~ "Naphtalene",
    chemical == "benzoaanthracene" ~ "Benzo[a]anthracene",
    TRUE ~ chemical)) %>% 
  mutate(chemical_class = case_when(
    chemical_class == "Metals" ~ "Trace metals",
    TRUE ~ chemical_class)) %>% 
  mutate(endpoint = factor(endpoint, levels = c(
    "Bacteria biolu. inhi.", "Cell viability", "Cell ROS",
    "Fish Mortality", "Fish heart rate",
    "Fish BLA_LOFF", "Fish BLA_LON", "Fish VLSR", "Fish VLMR", "Fish ASD", "Fish TPZ", "Operation time"))) %>% 
  mutate(chemical_class = factor(chemical_class, levels = c(
    "Alkylphenols", "Flame Retardants", "Non-phthalate plasticizers", "Phthalates", "PAHs", "Trace metals"))) #%>% 
  #keep only the correlation coeeficient > 0.5
  #filter(abs_correlation >= 0.4)

top_5_df

p_lollipop <- ggplot(
  top_5_df,
  aes(x = chemical,
      y = correlation,
      color = chemical_class)
) +
  geom_segment(
    aes(xend = chemical, y = 0, yend = correlation),
    linewidth = 2) +
  geom_point(aes(shape = signif_BH), size = 5) +
  scale_y_continuous(limits = c(-0.9, 0.9), breaks = seq(-0.9, 0.9, by = 0.2)) +
  
  coord_flip() +
  
  facet_wrap(~endpoint, ncol = 2, scales = "free_y") +
  scale_color_viridis_d(option = "turbo", 
                        begin     = 0.05,
                        end       = 0.95,
                        direction = 1, 
                        name = "Plastic chemical categories"
                        ) +
  
  scale_shape_manual(
    values = c("***" = 16, "**" = 17, "*" = 15, "ns" = 1),
    name = "Significance (BH's adjusted p-value)",
    labels = c("***" = "p < 0.001", "**" = "p < 0.01", 
               "*" = "p < 0.05", "ns" = "ns")
  ) +
  
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey30") +
  geom_hline(yintercept = c(0.5, -0.5), linetype = "dotdash", color = "red3", linewidth = 0.7) +
  
  labs(
    x = "Chemical compounds",
    y = "Spearman's correlation coefficient (ρ)",
    #title = "Top 5 Chemical Drivers per Ecotoxicological Endpoint",
    #subtitle = "Positive values = increased toxicity with chemical concentration"
  ) +
  
  theme_bw() +
  theme(
    axis.title.y = element_text(face = "bold", size = 20, vjust = -4),
    axis.title.x = element_text(face = "bold", size = 20, vjust = 0),
    axis.text.y = element_text(face = "bold", size = 18),
    axis.text.x = element_text(face = "bold", size = 18),
    strip.text = element_text(face = "bold", size = 18),
    strip.background = element_rect(fill = "grey95", color = "grey70"),
    legend.position = "right",
    #legend.box = "vertical",
    legend.spacing.y = unit(0.05, 'cm'),
    legend.box.spacing = unit(1, 'cm'),
    legend.title = element_text(size = 18, face = 'bold', color = "black"),
    legend.text = element_text(size = 18, face = 'bold', color = "black"),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(fill = NA, color = "grey70")
  ) +
  
  guides(
    size = "none",
    color = guide_legend(order = 1, nrow = 6),
    shape = guide_legend(order = 2, nrow = 3)
  )

p_lollipop

```


#---------------------

```{r operation time vs. chemicals}

# Resolve conflicts
select <- dplyr::select
filter <- dplyr::filter
mutate <- dplyr::mutate

# Define chemical predictors
chemicals <- colnames(df_PCA)[!(colnames(df_PCA) %in% c("FN", "state",
                                              "Biolu_inhi", "BLA_OFF", "BLA_LON", "VLMR", "VLSR",
                                              "ASD_LOFF2", "TPZ_LOFF2", "TPZ_LOFF1", "TPZ_LON",
                                              "Survival", "HR", "ROS", "Viability", "Op_time"))]
chemicals

# Endpoints
endpoints <- c("Op_time")

# SIMPLIFIED APPROACH: Use correlations + partial correlations
get_top5_predictors <- function(endpoint_name, data, predictors) {
  
  cat("  Analyzing", endpoint_name, "...\n")
  
  # Prepare data -----------------------------------------------------------
  df_analysis <- data %>%
    dplyr::select(all_of(c(predictors, endpoint_name))) %>%
    tidyr::drop_na()
  
  if (nrow(df_analysis) < 10) {
    cat("  Warning: Insufficient data\n")
    return(NULL)
  }
  
  # Spearman correlations + BH correction ---------------------------------
  correlations <- purrr::map_dfr(predictors, function(pred) {
    
    cor_test <- cor.test(
      df_analysis[[pred]],
      df_analysis[[endpoint_name]],
      method = "spearman",
      exact  = FALSE
    )
    
    tibble::tibble(
      chemical        = pred,
      correlation     = unname(cor_test$estimate),
      p_value         = cor_test$p.value,
      abs_correlation = abs(cor_test$estimate)
    )
  }) %>%
    dplyr::mutate(
      p_value_BH = p.adjust(p_value, method = "BH")  # BH / FDR
    )
  
  # Get top 5 by |rho|, report BH significance -----------------------------
  top5 <- correlations %>%
    dplyr::arrange(dplyr::desc(abs_correlation)) %>%
    dplyr::slice(1:8) %>%
    dplyr::mutate(
      endpoint   = endpoint_name,
      rank       = dplyr::row_number(),
      direction  = dplyr::if_else(correlation > 0, "Positive", "Negative"),
      signif_raw = dplyr::case_when(          # optional: keep raw stars
        p_value < 0.001 ~ "***",
        p_value < 0.01  ~ "**",
        p_value < 0.05  ~ "*",
        TRUE            ~ "ns"
      ),
      signif_BH  = dplyr::case_when(          # BH-adjusted stars (recommended)
        p_value_BH < 0.001 ~ "***",
        p_value_BH < 0.01  ~ "**",
        p_value_BH < 0.05  ~ "*",
        TRUE               ~ "ns"
      )
    )
  
  # Simple standardized LM for effect sizes --------------------------------
  top5_with_lm <- purrr::map_dfr(seq_len(nrow(top5)), function(i) {
    
    chem <- top5$chemical[i]
    
    x_scaled <- scale(df_analysis[[chem]])[, 1]
    y_scaled <- scale(df_analysis[[endpoint_name]])[, 1]
    
    lm_fit    <- lm(y_scaled ~ x_scaled)
    lm_sum    <- summary(lm_fit)
    
    top5[i, ] %>%
      dplyr::mutate(
        estimate   = coef(lm_fit)[2],
        std_error  = lm_sum$coefficients[2, "Std. Error"],
        t_value    = lm_sum$coefficients[2, "t value"],
        r_squared  = lm_sum$r.squared
      )
  })
  
  top5_with_lm
}


# Apply to all endpoints

top5_results <- list()

for(endpoint in endpoints) {
  cat("Processing:", endpoint, "\n")
  result <- get_top5_predictors(endpoint, df_PCA, chemicals)
  if(!is.null(result)) {
    top5_results[[endpoint]] <- result
  }
}

# Combine results
top5_df <- bind_rows(top5_results) %>%
  mutate(
    chemical_class = case_when(
      chemical %in% c("Ag", "Al", "As", "Cu", "Fe", "Mn", "Zn") ~ "Metals",
      chemical %in% c("BBP", "DBP","DEP", "DEHP", "DMP") ~ "Phthalates",
      chemical %in% c("ATBC", "DEHA") ~ "Non-phthalate plasticizers",
      str_detect(chemical, "BDE") ~ "Flame Retardants",
      chemical %in% c("tOP", "nonylphenols") ~ "Alkylphenols",
      TRUE ~ "PAHs"
    )
  )

# Display results

for(endpoint in endpoints) {
  endpoint_data <- top5_df %>% filter(endpoint == !!endpoint)
  
  if(nrow(endpoint_data) > 0) {
    cat(endpoint, "\n")
    cat(paste(rep("-", 70), collapse = ""), "\n")
    
    for(i in 1:nrow(endpoint_data)) {
      cat(sprintf(
        "  %d. %-20s [%s] ρ = %6.3f, β = %6.3f (p = %.4f) %s\n",
        endpoint_data$rank[i],
        endpoint_data$chemical[i],
        endpoint_data$chemical_class[i],
        endpoint_data$correlation[i],
        endpoint_data$estimate[i],
        endpoint_data$p_value[i],
        endpoint_data$significance[i]
      ))
    }
    cat("\n")
  }
}

# Display the dataframe
top5_df

```

```{r Vizualisation}

# Create lollipop chart showing top drivers with significance

#manual order facets
top_5_df <- top5_df %>% 
  mutate(
  endpoint = case_when(
      endpoint == "Op_time" ~ "Duration of use (fishing nets)",
      TRUE ~ endpoint)) %>% 
  mutate(
  chemical = case_when(
    chemical == "acenaphtylene" ~ "Acenaphtylene",
      chemical == "benzofluoranthene" ~ "Benzofluoranthene",
    chemical == "BDE_47" ~ "BDE 47",
      chemical == "BDE_99" ~ "BDE 99",
      chemical == "BDE_100" ~ "BDE 100",
      chemical == "BDE_153" ~ "BDE 153",
    chemical == "BDE_183" ~ "BDE 183",
    chemical == "benzoghiperylee" ~ "Benzo[ghi]perylene",
    TRUE ~ chemical)) 

p_lollipop <- ggplot(
  top_5_df,
  aes(x = chemical,
      y = correlation,
      color = chemical_class)
) +
  geom_segment(
    aes(xend = chemical, y = 0, yend = correlation),
    linewidth = 2) +
  geom_point(aes(shape = signif_BH), size = 5) +
  scale_y_continuous(limits = c(-0.9, 0.9), breaks = seq(-0.9, 0.9, by = 0.2)) +
  
  coord_flip() +
  
  facet_wrap(~endpoint, ncol = 4, scales = "free_y") +
  scale_color_viridis_d(option = "turbo", 
                        begin     = 0.05,
                        end       = 0.95,
                        direction = 1, 
                        name = "Plastic chemical categories"
                        ) +
  
  scale_shape_manual(
    values = c("***" = 16, "**" = 17, "*" = 15, "ns" = 1),
    name = "Significance (BH's adjusted p-value)",
    labels = c("***" = "p < 0.001", "**" = "p < 0.01", 
               "*" = "p < 0.05", "ns" = "ns")
  ) +
  
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey30") +
  geom_hline(yintercept = c(0.5, -0.5), linetype = "dotdash", color = "red3", linewidth = 0.7) +
  
  labs(
    x = "Chemical compounds",
    y = "Spearman correlation coefficient (ρ)",
    #title = "Top 5 Chemical Drivers per Ecotoxicological Endpoint",
    #subtitle = "Positive values = increased toxicity with chemical concentration"
  ) +
  
  theme_bw() +
  theme(
    axis.title.y = element_text(face = "bold", size = 18, vjust = 2.5),
    axis.title.x = element_text(face = "bold", size = 18, vjust = -4),
    axis.text.y = element_text(face = "bold", size = 16),
    axis.text.x = element_text(face = "bold", size = 16),
    strip.text = element_text(face = "bold", size = 18),
    strip.background = element_rect(fill = "grey95", color = "grey70"),
    legend.position = "bottom",
    legend.box = "vertical",
    legend.spacing.y = unit(0.05, 'cm'),
    legend.box.spacing = unit(1, 'cm'),
    legend.title = element_text(size = 18, face = 'bold', color = "black"),
    legend.text = element_text(size = 18, face = 'bold', color = "black"),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(fill = NA, color = "grey70")
  ) +
  
  guides(
    size = "none",
    color = guide_legend(order = 1, nrow = 1),
    shape = guide_legend(order = 2, nrow = 1)
  )

p_lollipop

```
