---
title: "Orga_DMSO"
author: "Edgar Dusacre"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---
```{r upload package}
library(ggplot2) 
library(forcats)
library(tidyr)
library(questionr)
library(deSolve)
library(tidyverse)
library(readxl)
library(skimr)
library(gmodels)
library(ggrepel)
library(lazyeval)
library(ggpubr)
library(multcompView)
library(readr)
library(scales)
library(knitr)
library(wesanderson)
library(dplyr) 
library(lubridate)
library(report)
library(ecotox)
library(stats)
library(dunn.test)
library(boot)
library(gridExtra)
library(multcompView)
library(rcompanion)
library(RColorBrewer)
library(car)
library(emmeans)
library(PMCMRplus)
library(multcomp)
library(kableExtra)
library(ggpattern)
```

```{r palette colors}
Plasfito_C <- c("#80CAD0", "#36A7A7", "#276573", "#054959","#E3CCC0", "#F7EAE1", "#A48A7B", "#C6AF8D", "#49BED3", "#256CB4", "#008163", "#44B494", "#7BC6B9")

Plasfito_color <- c("GreenP4" = "#80CAD0", "GreenP3" = "#36A7A7", "GreenP2" = "#276573", "GreenP1" = "#054959","Brown1" = "#E3CCC0", "Brown2" = "#F7EAE1", "Brown3" = "#A48A7B", "Brown4" = "#C6AF8D", "Turquoise1" = "#49BED3", "Blue1" = "#256CB4", "Green1" = "#008163", "Green2" = "#44B494", "Green3" = "#7BC6B9")

Color_FN <- c("pa_\u03B333"= "#054959", 
              "pa_\u03B360"= "#36A7A7", 
              "pbs_\u03B435"= "#49BED3", 
              "pbs_\u03B460"= "#256CB4")

Color_FN2 <- c("pa_g33_aa"= "#054959", 
              "pa_g60_aa"= "#36A7A7", 
              "pbs_d60_aa"= "aquamarine", 
              "pbs_d60_aa"= "#256CB4")

Color_FN3 <- c("pa_\u03B333"= "#054959", 
              "pa_\u03B360"= "#0096FC", 
              "pbs_\u03B435"= "#9beaa1", 
              "pbs_\u03B460"= "#77655C")

Color_FN4 <- c("pa_\u03B333"= "#80CAD0", 
              "pa_\u03B360"= "#0039D8", 
              "pbs_\u03B435"= "#0a7011", 
              "pbs_\u03B460"= "#C6AF8D")

color <- c("PBS 0.35 r1" = "#33aa3c", 
                               "PBS 0.35 r2" = "#0a7011",
                               "PBS 0.60 r1" = "#C6AF8D", 
                               "PBS 0.60 r2" = "#A48A7B",
                               "PA 6 0.33 r1" = "#80CAD0", 
                               "PA 6 0.33 r2" = "#054959",
                               "PA 6 0.60 r1" = "#0096FC",
                               "PA 6 0.60 r2" = "#0039D8",
                               "PBS 0.35 pHa" = "#9beaa1")

replicats <- c("1"= "#054959", 
              "2"= "#36A7A7", 
              "3"= "aquamarine", 
              "4"= "#256CB4")

time <- c("0"= "aquamarine", 
              "25"= "#054959")

time2 <- c("0"= "aquamarine", 
              "6"= "#33aa3c",
              "60" = "#36A7A7",
              "12"= "#256CB4", 
              "25"= "#054959")

Color_real_FN <- c("dmso" = "#A48A7B", "ctl H2O" = "#256CB4", "BLANK" = "#256CB4", "blc" = "#A48A7B", "pa_a35" = "#4fd355", "pa_b33" = "#ca98d3", "pa_b95" = "#6e217c", "pa_g33" = "#92b78f", "pa_g60" = "#bbb3bc", "pbs_d35" = "#d3ad4f","pbs_d60" = "#c68640", "hppe_e425" = "#36A7A7")

Color_real_FN3 <- c("dmso" = "#A48A7B", "ctl H2O" = "#256CB4", "BLANK" = "#256CB4", "pa_a35" = "#4fd355", "pa_b33" = "#ca98d3", "pa_b95" = "#6e217c", "pa_g33" = "#92b78f", "PA6" = "#4fd355", "pbs_d35" = "#d3ad4f","PBS-PBAT" = "#c68640", "PE-PP" = "#36A7A7")

Color_real_FN2 <- c("dmso" = "#A48A7B", "ctl H2O" = "#256CB4", "BLANK" = "#256CB4", "pa_a33_aa" = "#4fd355", "pa_b33_aa" = "#ca98d3", "pa_b95_aa" = "#6e217c", "pa_g33_aa" = "#92b78f", "pa_g60_aa" = "#bbb3bc", "pbs_d60_aa" = "#d3ad4f","pbs_d60_aa" = "#c68640", "hppe_e4.25_aa" = "#36A7A7")

Color_code_FN <- c("dmso" = "#A48A7B", "ctl H2O" = "#256CB4", "BLANK" = "#256CB4", "pa_\u03B135" = "#4fd355", "pa_\u03B233" = "#ca98d3", "pa_\u03B295" = "#6e217c", "pa_\u03B333" = "#92b78f", "pa_\u03B360" = "#bbb3bc", "pbs_\u03B435" = "#d3ad4f","pbs_\u03B460" = "#c68640", "pe_\u03B54.25" = "#36A7A7")

Color_real_FN5 <- c("Blank" = "#A48A7B", "blank" = "#A48A7B", "SW" = "#256CB4", "Seawater control" = "#256CB4", "PA α35" = "#4fd355", "PA β33" = "#ca98d3", "PA β95" = "#6e217c", "PA γ33" = "#92b78f", "PA γ60" = "#bbb3bc", "PBS δ35" = "#d3ad4f","PBS δ60" = "#c68640", "PE-PP ε4.25" = "#36A7A7")


```
5 categories of compounds are large categories in "Bilan_Analyses_EPOC_Edgar_Dusacre_CEDRE.xlsx" and tehre 6 in "Bilan_Analyses_EPOC_Edgar_Dusacre.xlsx":
```{r import data}
library(readxl)
data0 <- read_excel("Bilan_Analyses_EPOC_Edgar_Dusacre.xlsx", 
    sheet = "R") 
data0

#46 - 6 = 40 --> 40 compounds quantified

CrossTable(data0$compounds)

data_bis <- read_excel("Bilan_Analyses_EPOC_Edgar_Dusacre_CEDRE.xlsx", 
    sheet = "Bilan_R") 
data_bis

data1 <- left_join(data0, data_bis, by = c("LD_(ng_mL)", "LQ_(ng_mL)", "compounds")) %>% 
  filter(!(compounds %in% c(
    "1-methylnaphtalene",
    "2-methylfluoranthene",
    "2-methylnaphtalene",
    "perylene",
    "benzoapyrene",
    "4-NP")))
data1

data_metals <- read_excel("df_PhD_def.xlsx") %>% 
  mutate(state = if_else(state == "used", "EOL", state)) %>% 
  group_by(FN, state, rep) %>% 
  summarise(values_corr = sum(Conc_corr, na.rm = TRUE),
            values = sum(Concentration, na.rm = TRUE)) %>% 
  mutate(compounds = "Metals", LD = NA, LQ = NA, avg_blc = NA, sd_blc = NA) %>%  #to get the values of LD, LQ, avg_blc and sd_blc please go in the R script for metals
  dplyr::select(FN, state, rep, compounds, LD, LQ, values, avg_blc, sd_blc, values_corr) %>% 
  mutate(FN = case_when(
    FN == "pa_a35" ~ "PA α35",
    FN == "pa_b33" ~ "PA β33", 
    FN == "pa_b95" ~ "PA β95",
    FN == "pa_g33" ~ "PA γ33",
    FN == "pa_g60" ~ "PA γ60",
    FN == "pbd_d35" ~ "PBS δ35",
    FN == "pbd_d60" ~ "PBS δ60",
    FN == "hppe_e425" ~ "PE-PP ε4.25",
    TRUE ~ FN  # Garde les autres valeurs inchangées
  ))
data_metals

CrossTable(data_metals$FN)

data_metals_cp <- read_excel("df_PhD_def.xlsx") %>% 
  mutate(state = if_else(state == "used", "EOL", state)) %>% 
  rename(compounds = Metals, values =Concentration, avg_blc = Avg_blc, values_corr = Conc_corr) %>%
  mutate(LD = NA, LQ = NA, avg_blc = NA, sd_blc = NA) %>%  #to get the values of LD, LQ, avg_blc and sd_blc please go in the R script for metals
  dplyr::select(FN, state, rep, compounds, LD, LQ, values, avg_blc, sd_blc, values_corr) %>% 
  mutate(FN = case_when(
    FN == "pa_a35" ~ "PA α35",
    FN == "pa_b33" ~ "PA β33", 
    FN == "pa_b95" ~ "PA β95",
    FN == "pa_g33" ~ "PA γ33",
    FN == "pa_g60" ~ "PA γ60",
    FN == "pbd_d35" ~ "PBS δ35",
    FN == "pbd_d60" ~ "PBS δ60",
    FN == "hppe_e425" ~ "PE-PP ε4.25",
    TRUE ~ FN  # Garde les autres valeurs inchangées
  ))
data_metals_cp

data_metals_rep <- data_metals %>% 
  filter(rep == "3" | rep == "4" | rep == "5") %>% 
  group_by(FN, state, compounds) %>% 
  summarise(values_corr = mean(values_corr, na.rm = T)) %>% 
  mutate(rep = "3")
data_metals_rep

data_metal_short <- data_metals %>% 
  filter(rep == "1" | rep == "2") %>% 
  bind_rows(data_metals_rep) %>% 
  #change name FNs
  mutate(FN = case_when(
    FN == "pa_a35" ~ "PA α35",
    FN == "pa_b33" ~ "PA β33", 
    FN == "pa_b95" ~ "PA β95",
    FN == "pa_g33" ~ "PA γ33",
    FN == "pa_g60" ~ "PA γ60",
    FN == "pbd_d35" ~ "PBS δ35",
    FN == "pbd_d60" ~ "PBS δ60",
    FN == "hppe_e425" ~ "PE-PP ε4.25",
    TRUE ~ FN  # Garde les autres valeurs inchangées
  ))
data_metal_short

avg_metals_sum <- data_metal_short %>% 
  group_by(FN, state, compounds) %>% 
  summarise(n = n(),
            avg_corr = mean(values_corr, na.rm = T))
avg_metals_sum
```

When for a FN of a specific state the values of the 3 replicates are <LQ or <LD --> NA
When one or more values <LQ or <LD --> LQ/2 or LD/2


```{r tidydata}
compounds <- data1 %>% dplyr::select(compounds)

data2 <- data1 %>% 
  # mutate(across(
  #   .cols = where(is.character) & !c("compounds"), # Exclude metadata
  #   .fns = ~ case_when(
  #     .x == "<LQ" ~ as.character(`LQ_(ng_mL)`),
  #     .x == "<LD" ~ as.character(`LD_(ng_mL)`),
  #     TRUE ~ .x
  #   )
  # )) %>% 
  dplyr::select(-compounds) %>% 
  #mutate_if(is.character, as.double) %>%
  bind_cols(compounds) %>%
  pivot_longer(!c(`LD_(ng_mL)`, `LQ_(ng_mL)`, compounds), names_to = "FN", values_to = "values") %>% 
  #split the column FN in two columns with the first "_"
  separate(FN, into = c("rep", "FN"), sep = "_", extra = "merge") %>% 
  separate(FN, into = c("FN", "state"), sep = "_", extra = "merge") %>% 
  mutate(state = if_else(state == "n", "new",
                         if_else(state == "u", "EOL", NA))) %>% 
  rename(LD = `LD_(ng_mL)`, LQ = `LQ_(ng_mL)`) %>% 
  dplyr::select(FN, state, rep, compounds, LD, LQ, values) %>% 
  mutate(FN = case_when(
    FN %in% c("alpha", "PA α ø.35", "pa_a33", "α35") ~ "PA α35",
    FN %in% c("beta33", "PA β ø.33", "pa_b33", "β33") ~ "PA β33", 
    FN %in% c("beta95", "PA β ø.95", "pa_b95", "β95") ~ "PA β95",
    FN %in% c("gamma33", "PA γ ø.33", "pa_g33", "γ33") ~ "PA γ33",
    FN %in% c("gamma60", "PA γ ø.60", "pa_g60", "γ60") ~ "PA γ60",
    FN %in% c("delta35", "PBS δ ø.35", "pbs_d35", "δ35") ~ "PBS δ35",
    FN %in% c("delta60", "PBS δ ø.60", "pbs_d60", "δ60") ~ "PBS δ60",
    FN %in% c("epsi", "HPPE ε ø4.25", "pe_e4.25", "ε4,25") ~ "PE-PP ε4.25",
    TRUE ~ FN  # Garde les autres valeurs inchangées
  )) %>% 
  #LOD & LOQ transformations
  ##if for a same FN of same state and same compounds only <LD or/and <LQ values become NA
  # group_by(FN, state, compounds) %>%
  # mutate(
  #   # Is there at least one numeric value in this group?
  #   has_numeric = any(!values %in% c("<LD", "<LQ") & !is.na(values)),
  #   # If no numeric in the group and value is <LD or <LQ → NA
  #   values = if_else(
  #     !has_numeric & values %in% c("<LD", "<LQ"),
  #     NA_character_,
  #     values
  #   )
  # ) %>%
  # ungroup() %>%
  # dplyr::select(-has_numeric) %>% 
  ##if <LD or <lQ --> LQ/2 or LD/2
  mutate(values = if_else(values == "<LD", "-1", 
                          if_else(values == "<LQ", "-2", values))) %>% 
  mutate(values = as.numeric(values)) %>% 
  mutate(values = case_when(
    values == -2 ~ LQ/2,
    values == -1 ~ LD/2,
    TRUE ~ values
  ))
data2

data_no_LDLQ <- data2 %>% filter(LD != values & LQ != values)
data_no_LDLQ

Comp_cat <- data2 %>% filter(compounds %in% c("HAP", "PBDE", "Phtalates", "non_Phtalates", "AKP"))
Comp_cat

```

```{r avg}
data_avg <- data2 %>% 
  filter(!(compounds %in% c("HAP", "PBDE", "Phtalates", "non_Phtalates", "AKP", "AKP_NP"))) %>% 
   mutate(values = if_else(abs(values - LD) < 1e-6 | abs(values - LQ) < 1e-6, NA_real_, values)) %>% 
  group_by(FN, state, compounds) %>% 
  summarise( n = n(),
             avg = mean(values, na.rm = T),
             sd = sd(values, na.rm = T)) 
data_avg


data_sum_FN <- data_avg %>% 
  summarize(n_avg_gt0 = sum(avg > 0, na.rm = TRUE))
data_sum_FN

df <- data_avg %>%
  filter(avg > 0) 

data_avg_cat <- data2 %>% 
  filter((compounds %in% c("HAP", "PBDE", "Phtalates", "non_Phtalates", "AKP"))) %>% 
   #mutate(values = if_else(abs(values - LD) < 1e-6 | abs(values - LQ) < 1e-6, NA_real_, values)) %>% 
  group_by(FN, state, compounds) %>% 
  summarise( n = n(),
             avg = mean(values, na.rm = T),
             sd = sd(values, na.rm = T)) 
data_avg_cat

```


```{r corr blank substraction cat}
avg_blc_cat <- Comp_cat %>% 
  group_by(FN, state, compounds) %>% 
  summarise( n = n(),
             avg = mean(values, na.rm = T),
             sd = sd(values, na.rm = T)
             ) %>% 
  filter(FN == "blank") %>% 
  ungroup() %>% 
  dplyr::select(-state, -n) %>%
  rename(avg_blc = avg, sd_blc = sd)
avg_blc_cat

data_corr_cat <- Comp_cat %>% 
  left_join(avg_blc_cat, by = c("compounds")) %>% 
  mutate(values_corr = values - avg_blc) %>% 
  mutate(values_corr = if_else(values_corr < 0, 0, values_corr)) %>% 
  dplyr::select(-FN.y) %>% 
  rename(FN = FN.x) 
data_corr_cat

metal_orga <- data_corr_cat %>% 
  bind_rows(data_metals) %>% 
  mutate(compounds = case_when(
    compounds == "Phtalates" ~ "Phthalates",
    compounds == "non_Phtalates" ~ "Non phthalate plasticizers",
    TRUE ~ compounds
  ))
metal_orga

data_avg_corr_cat <- data_corr_cat %>% 
  filter(FN != "blank") %>% 
  group_by(state, compounds) %>% 
  summarise(n = n(),
             avg_corr = mean(values_corr, na.rm = T),
            sd_corr = sd(values_corr, na.rm = T)) %>% 
  mutate(avg_ng_gFN = avg_corr*0.003*1000,
         sd_ng_gFN = sd_corr*0.003*1000) #%>% 
#   filter(compounds == "HAP") %>% 
#   group_by(state, compounds) %>%
#   summarise(n = n(),
#              avg_corr = mean(avg_ng_gFN, na.rm = T),
#             sd_corr = sd(sd_ng_gFN, na.rm = T))
data_avg_corr_cat

#export excel
# library(writexl)
# write_xlsx(data_avg_corr_cat, "orga_dmso_avg_cat.xlsx")
```

```{r corr blank substraction compounds}
avg_blc <- data2 %>% 
  filter(!(compounds %in% c("HAP", "PBDE", "Phtalates", "non_Phtalates", "AKP", "AKP_NP"))) %>% 
  group_by(FN, state, compounds) %>% 
  summarise( n = n(),
             avg = mean(values, na.rm = T),
             sd = sd(values, na.rm = T)
             ) %>% 
  filter(FN == "blank") %>% 
  ungroup() %>% 
  dplyr::select(-state, -n) %>%
  rename(avg_blc = avg, sd_blc = sd)
avg_blc

data_corr <- data2 %>% 
  filter(!(compounds %in% c("HAP", "PBDE", "Phtalates", "non_Phtalates", "AKP", "AKP_NP"))) %>% 
  left_join(avg_blc, by = c("compounds")) %>% 
  rename(FN = FN.x) %>% 
  mutate(values_corr = if_else(FN != "blank", values - avg_blc, values)) %>% 
  mutate(values_corr = if_else(values_corr < 0, 0, values_corr)) %>% 
  dplyr::select(-FN.y)
data_corr

metal_orga_cp <- data_corr %>% 
  bind_rows(data_metals_cp) 
metal_orga_cp

data_avg_corr <- metal_orga_cp %>% 
  filter(!(compounds %in% c("HAP", "PBDE", "Phtalates", "non_Phtalates", "AKP", "AKP_NP"))) %>% 
  #filter(FN != "blank") %>% 
  filter(!(compounds %in% c(
    "1-methylnaphtalene",
    "2-methylfluoranthene",
    "2-methylnaphtalene",
    "perylene",
    "benzoapyrene",
    "4-NP"))) %>%
  group_by(FN, state, compounds) %>% 
  summarise(n = n(),
            avg = mean(values, na.rm = T),
             sd = sd(values, na.rm = T),
             avg_corr = mean(values_corr, na.rm = T),
             sd_corr = sd(values_corr, na.rm = T)) 
data_avg_corr

nb_compound_by_FN <- data_avg_corr %>% 
  mutate(cat = case_when(
    compounds %in% c("As", "Ag", "Al", "Cu", "Fe", "Zn", "Mn") ~ "metals",
    TRUE ~ "organic"
  )) %>% 
  filter(avg_corr >0 & sd_corr >0) %>% 
  #don't tale into account the trace metals
  #filter(cat != "metals") %>% 
  group_by(FN, state, cat) %>% 
  summarise(
    n_compounds = n_distinct(compounds),
    .groups = "drop"
  ) %>% 
  mutate(percentage = case_when(
    cat == "metals" ~ n_compounds *100 /7,
    cat == "organic" ~ n_compounds *100 /34))
nb_compound_by_FN


# #export excel
# library(writexl)
# write_xlsx(data_avg_corr, "orga_dmso_avg.xlsx")
```


Compounds with values below LD or LD:
1-methylnaphtalene
2-methylfluoranthene
2-methylnaphtalene
perylene
benzoapyrene

4-NP

Results of the nonylphenol seems wrong due to high strange values for the FNs:

##Statistics large categories
```{r Anova ou kruskal including blanks - new FNs}
# ANOVA or Kruskal-Wallis test including blanks
df_new <- metal_orga %>% 
  mutate(state = if_else(is.na(state), "blank", state)) %>%
  filter(state != "EOL") %>% 
  arrange(compounds) 
df_new

CrossTable(df_new$compounds)

res_aov <- df_new %>% 
  group_by(compounds) %>% 
  nest() %>% 
  mutate(
    aov_model = map(data, ~ aov(values ~ FN, data = .x)),
    aov_tidy  = map(aov_model, ~ broom::tidy(.x)),
    resid     = map(aov_model, residuals),
    shapiro   = map(resid, ~ shapiro.test(.x)),
    bartlett  = map(data, ~ bartlett.test(values ~ FN, data = .x))
  )

res_aov$shapiro

res_kw <- df_new %>% 
  group_by(compounds) %>% 
  nest() %>% 
  mutate(
    kw_test  = map(data, ~ kruskal.test(values ~ FN, data = .x)),
    kw_tidy  = map(kw_test, ~ broom::tidy(.x))
  )
res_kw$kw_tidy

# 2) Keep only compounds with p.value < 0.05
res_kw_sig <- res_kw %>% 
  mutate(p_value = map_dbl(kw_tidy, ~ .x$p.value)) %>% 
  filter(p_value < 0.05)
res_kw_sig

# 3) Dunn test for those significant compounds
res_dunn <- res_kw_sig %>% 
  mutate(
    dunn_raw = map(data, ~ FSA::dunnTest(values ~ FN, data = .x, method = "holm")),
    dunn_tbl = map(dunn_raw, ~ .x$res %>% as_tibble())
  )

# 4) Flat table of all post-hoc comparisons
dunn_table <- res_dunn %>% 
  dplyr::select(compounds, dunn_tbl) %>%   # use the real column name
  unnest(dunn_tbl)
dunn_table

# 3bis) Dunn test + letters for significant compounds only
res_letters <- res_kw_sig %>% 
  mutate(
    # Dunn all-pairs test per compound
    dunn_kw   = map(data, ~ kwAllPairsDunnTest(values ~ as.factor(FN),
                                               data = .x,
                                               p.adjust.method = "holm")),
    # matrix of adjusted p-values
    p_mat     = map(dunn_kw, ~ round(.x$p.value, digits = 3)),
    # full symmetric matrix required by multcompLetters
    p_full    = map(p_mat, fullPTable),
    # compact letter display
    letters   = map(p_full, ~ multcompLetters(.x)$Letters),
    # convert named vector of letters to tibble
    letters_df = map(letters, ~ tibble(
      FN = names(.x),
      label = as.vector(unlist(.x))
    ))
  )

letters_table_new <- res_letters %>% 
  dplyr::select(compounds, letters_df) %>% 
  unnest(letters_df)
letters_table_new
```

```{r Anova ou kruskal including blanks - EOL FNs}
# ANOVA or Kruskal-Wallis test including blanks
df_EOL <- metal_orga %>% 
  mutate(state = if_else(is.na(state), "blank", state)) %>%
  filter(state != "new") %>% 
  arrange(compounds)
df_EOL

res_aov <- df_EOL %>% 
  group_by(compounds) %>% 
  nest() %>% 
  mutate(
    aov_model = map(data, ~ aov(values ~ FN, data = .x)),
    aov_tidy  = map(aov_model, ~ broom::tidy(.x)),
    resid     = map(aov_model, residuals),
    shapiro   = map(resid, ~ shapiro.test(.x)),
    bartlett  = map(data, ~ bartlett.test(values ~ FN, data = .x))
  )

res_aov$shapiro

res_kw <- df_EOL %>% 
  group_by(compounds) %>% 
  nest() %>% 
  mutate(
    kw_test  = map(data, ~ kruskal.test(values ~ FN, data = .x)),
    kw_tidy  = map(kw_test, ~ broom::tidy(.x))
  )
res_kw$kw_tidy

# 2) Keep only compounds with p.value < 0.05
res_kw_sig <- res_kw %>% 
  mutate(p_value = map_dbl(kw_tidy, ~ .x$p.value)) %>% 
  filter(p_value < 0.05)
res_kw_sig

# 3) Dunn test for those significant compounds
res_dunn <- res_kw_sig %>% 
  mutate(
    dunn_raw = map(data, ~ FSA::dunnTest(values ~ FN, data = .x, method = "holm")),
    dunn_tbl = map(dunn_raw, ~ .x$res %>% as_tibble())
  )

# 4) Flat table of all post-hoc comparisons
dunn_table <- res_dunn %>% 
  dplyr::select(compounds, dunn_tbl) %>%   # use the real column name
  unnest(dunn_tbl)
dunn_table

# 3bis) Dunn test + letters for significant compounds only
res_letters <- res_kw_sig %>% 
  mutate(
    # Dunn all-pairs test per compound
    dunn_kw   = map(data, ~ kwAllPairsDunnTest(values ~ as.factor(FN),
                                               data = .x,
                                               p.adjust.method = "holm")),
    # matrix of adjusted p-values
    p_mat     = map(dunn_kw, ~ round(.x$p.value, digits = 3)),
    # full symmetric matrix required by multcompLetters
    p_full    = map(p_mat, fullPTable),
    # compact letter display
    letters   = map(p_full, ~ multcompLetters(.x)$Letters),
    # convert named vector of letters to tibble
    letters_df = map(letters, ~ tibble(
      FN = names(.x),
      label = as.vector(unlist(.x))
    ))
  )

letters_table_EOL <- res_letters %>% 
  dplyr::select(compounds, letters_df) %>% 
  unnest(letters_df)
letters_table_EOL
```

```{r df with all letters KW including blanks}
results_KW_blc <- bind_rows(
  letters_table_new %>% mutate(state = "new"),
  letters_table_EOL %>% mutate(state = "EOL")
) %>%
  #mutate(state = if_else(FN == "blank", "blank", state)) %>% 
  arrange(compounds, state, FN) %>% 
  #if state = new label in capital letters
  mutate(
    label = case_when(
      state == "new" ~ toupper(label),
      TRUE ~ label))
results_KW_blc 
```

```{r Anova ou kruskal excluding blanks - new FNs}
# ANOVA or Kruskal-Wallis test including blanks
df_new <- data_corr_cat %>% 
  mutate(state = if_else(is.na(state), "blank", state)) %>%
  filter(state != "EOL", FN != "blank") 
df_new

res_aov <- df_new %>% 
  group_by(compounds) %>% 
  nest() %>% 
  mutate(
    aov_model = map(data, ~ aov(values ~ FN, data = .x)),
    aov_tidy  = map(aov_model, ~ broom::tidy(.x)),
    resid     = map(aov_model, residuals),
    shapiro   = map(resid, ~ shapiro.test(.x)),
    bartlett  = map(data, ~ bartlett.test(values ~ FN, data = .x))
  )

res_aov$shapiro

res_kw <- df_new %>% 
  group_by(compounds) %>% 
  nest() %>% 
  mutate(
    kw_test  = map(data, ~ kruskal.test(values ~ FN, data = .x)),
    kw_tidy  = map(kw_test, ~ broom::tidy(.x))
  )
res_kw$kw_tidy

# 2) Keep only compounds with p.value < 0.05
res_kw_sig <- res_kw %>% 
  mutate(p_value = map_dbl(kw_tidy, ~ .x$p.value)) %>% 
  filter(p_value < 0.05)

# 3) Dunn test for those significant compounds
res_dunn <- res_kw_sig %>% 
  mutate(
    dunn_raw = map(data, ~ FSA::dunnTest(values ~ FN, data = .x, method = "holm")),
    dunn_tbl = map(dunn_raw, ~ .x$res %>% as_tibble())
  )

# 4) Flat table of all post-hoc comparisons
dunn_table <- res_dunn %>% 
  dplyr::select(compounds, dunn_tbl) %>%   # use the real column name
  unnest(dunn_tbl)
dunn_table

# 3bis) Dunn test + letters for significant compounds only
res_letters <- res_kw_sig %>% 
  mutate(
    # Dunn all-pairs test per compound
    dunn_kw   = map(data, ~ kwAllPairsDunnTest(values ~ as.factor(FN),
                                               data = .x,
                                               p.adjust.method = "holm")),
    # matrix of adjusted p-values
    p_mat     = map(dunn_kw, ~ round(.x$p.value, digits = 3)),
    # full symmetric matrix required by multcompLetters
    p_full    = map(p_mat, fullPTable),
    # compact letter display
    letters   = map(p_full, ~ multcompLetters(.x)$Letters),
    # convert named vector of letters to tibble
    letters_df = map(letters, ~ tibble(
      FN = names(.x),
      label = as.vector(unlist(.x))
    ))
  )

letters_table_new <- res_letters %>% 
  dplyr::select(compounds, letters_df) %>% 
  unnest(letters_df)
letters_table_new
```

```{r Anova ou kruskal excluding blanks - EOL FNs}
# ANOVA or Kruskal-Wallis test including blanks
df_EOL <- data_corr_cat %>% 
  mutate(state = if_else(is.na(state), "blank", state)) %>%
  filter(state != "new", FN != "blank") 
df_EOL

res_aov <- df_EOL %>% 
  group_by(compounds) %>% 
  nest() %>% 
  mutate(
    aov_model = map(data, ~ aov(values ~ FN, data = .x)),
    aov_tidy  = map(aov_model, ~ broom::tidy(.x)),
    resid     = map(aov_model, residuals),
    shapiro   = map(resid, ~ shapiro.test(.x)),
    bartlett  = map(data, ~ bartlett.test(values ~ FN, data = .x))
  )

res_aov$shapiro

res_kw <- df_EOL %>% 
  group_by(compounds) %>% 
  nest() %>% 
  mutate(
    kw_test  = map(data, ~ kruskal.test(values ~ FN, data = .x)),
    kw_tidy  = map(kw_test, ~ broom::tidy(.x))
  )
res_kw$kw_tidy

# 2) Keep only compounds with p.value < 0.05
res_kw_sig <- res_kw %>% 
  mutate(p_value = map_dbl(kw_tidy, ~ .x$p.value)) %>% 
  filter(p_value < 0.05)

# 3) Dunn test for those significant compounds
res_dunn <- res_kw_sig %>% 
  mutate(
    dunn_raw = map(data, ~ FSA::dunnTest(values ~ FN, data = .x, method = "holm")),
    dunn_tbl = map(dunn_raw, ~ .x$res %>% as_tibble())
  )

# 4) Flat table of all post-hoc comparisons
dunn_table <- res_dunn %>% 
  dplyr::select(compounds, dunn_tbl) %>%   # use the real column name
  unnest(dunn_tbl)
dunn_table

# 3bis) Dunn test + letters for significant compounds only
res_letters <- res_kw_sig %>% 
  mutate(
    # Dunn all-pairs test per compound
    dunn_kw   = map(data, ~ kwAllPairsDunnTest(values ~ as.factor(FN),
                                               data = .x,
                                               p.adjust.method = "holm")),
    # matrix of adjusted p-values
    p_mat     = map(dunn_kw, ~ round(.x$p.value, digits = 3)),
    # full symmetric matrix required by multcompLetters
    p_full    = map(p_mat, fullPTable),
    # compact letter display
    letters   = map(p_full, ~ multcompLetters(.x)$Letters),
    # convert named vector of letters to tibble
    letters_df = map(letters, ~ tibble(
      FN = names(.x),
      label = as.vector(unlist(.x))
    ))
  )

letters_table_EOL <- res_letters %>% 
  dplyr::select(compounds, letters_df) %>% 
  unnest(letters_df)
letters_table_EOL
```

```{r df with all letters KW excluding blanks}
results_KW_nblc <- bind_rows(
  letters_table_new %>% mutate(state = "new"),
  letters_table_EOL %>% mutate(state = "EOL")
) %>%
  #mutate(state = if_else(FN == "blank", "blank", state)) %>% 
  arrange(compounds, state, FN) %>% 
  #if state = new label in capital letters
  mutate(
    label = case_when(
      state == "new" ~ toupper(label),
      TRUE ~ label))
results_KW_nblc 
```


```{r Statistics new vs EOL}
df_new_EOL <- metal_orga %>% 
  filter(FN != "blank") 
df_new_EOL

#Eliminate the FN and state for which the values of the three replicates were = 0
df_counts <-
  df_new_EOL %>%
  group_by(FN, compounds, state) %>%
  summarise(
    n_zero = sum(!is.na(values_corr) & values_corr == 0),
    .groups = "drop"
  )

compounds_ok <-
  df_counts %>%
  group_by(FN, compounds) %>%
  filter(all(n_zero < 3)) %>%   # remove FN/compound with any state having 3 zeros
  ungroup() %>%
  distinct(FN, compounds)

df_new_EOL_ok <-
  df_new_EOL %>%
  semi_join(compounds_ok, by = c("FN", "compounds"))
df_new_EOL_ok

results_tests <-
  df_new_EOL_ok %>%
  group_by(compounds, FN) %>%
  group_modify(~{
    # simple one-way model: values_corr ~ state
    mod <- lm(values_corr ~ state, data = .x)
    
    # Shapiro–Wilk on residuals (normality)
    shapiro_p <- shapiro.test(residuals(mod))$p.value
    
    # Levene’s test (homogeneity of variance across states)
    lev_p <- leveneTest(values_corr ~ state, data = .x)$`Pr(>F)`[1]
    
    tibble(
      shapiro_p = shapiro_p,
      levene_p  = lev_p,
      n         = n_distinct(.x$state)
    )
  }) %>%
  ungroup()
results_tests

# One MWU test per FN × compounds, comparing new vs EOL
tt_results <- df_new_EOL_ok %>% 
  group_by(FN, compounds) %>% 
  summarise(
    tt = list(t.test(values_corr ~ state, var.equal = T)),  # t test
    .groups = "drop"
  ) %>% 
  mutate(
    tt_tidy = map(tt, broom::tidy)
  ) %>% 
  unnest(tt_tidy) %>% 
  mutate(
    diff = if_else(p.value < 0.0001, "****", 
                   if_else(p.value < 0.001, "***",
                           if_else(p.value < 0.01, "**",
                                   if_else(p.value < 0.05, "*", "ns"))))
  ) 
tt_results


```


```{r Statistics blank vs. FN and state}

#1) Prepare data

df <- metal_orga %>%
  filter(!is.na(values)) %>% 
  filter(!compounds %in% c("Metals"))


# blank replicated for each state so comparisons are "compound + state"
blank_states <- tibble(state = c("new", "EOL"))

df_blank <- df %>%
  filter(FN == "blank") %>%
  dplyr::select(FN, compounds, values) %>%
  crossing(blank_states)

df_test <- df %>%
  filter(FN != "blank", state %in% c("new", "EOL")) %>%
  dplyr::select(FN, state, compounds, values)

# 2) Run MWU test: FN vs blank
#    for each (FN, state, compounds)

results_vs_blank <- df_test %>%
  group_by(FN, state, compounds) %>%
  summarise(
    n_FN = sum(!is.na(values)),
    x = list(values),
    .groups = "drop"
  ) %>%
  left_join(
    df_blank %>%
      group_by(state, compounds) %>%
      summarise(
        n_blank = sum(!is.na(values)),
        y = list(values),
        .groups = "drop"
      ),
    by = c("state", "compounds")
  ) %>%
  mutate(
    # Welch t-test only if both groups have enough data + some variability
    p_value = pmap_dbl(
      list(x, y, n_FN, n_blank),
      ~{
        if (..3 < 2 || ..4 < 2) return(NA_real_)
        if (dplyr::n_distinct(..1) < 2 && dplyr::n_distinct(..2) < 2) return(NA_real_)
        suppressWarnings(wilcox.test(..1, ..2, paired = FALSE)$p.value)
      }
    ),
    stars = case_when(
      is.na(p_value)  ~ NA_character_,
      p_value < 0.001 ~ "###",
      p_value < 0.01  ~ "##",
      p_value < 0.05  ~ "#",
      TRUE            ~ "ns"
    )
  ) %>%
  dplyr::select(FN, state, compounds, n_FN, n_blank, p_value, stars) %>%
  arrange(compounds, state, FN) #%>% 
  #filter(stars != "ns")

results_vs_blank


```

```{r test homogeneity of the variance}

df <- metal_orga %>%
  filter(!is.na(values)) %>% 
  group_by(FN, state, compounds) %>%
  filter(n() >= 3) %>%                    # keep only groups with ≥ 3 rows
  ungroup() #%>% 
  #filter(compounds %in% c("Metals"))

# 1) store blanks once (they have FN == "blank", state == NA)
df_blanks <- df %>%
  filter(FN == "blank") %>%
  dplyr::select(FN, state, rep, compounds, LD, LQ, values, avg_blc, sd_blc, values_corr)

# 2) for each FN-state-compound (non-blank), bind the corresponding blank rows (same compound)
lst_FN_state_compound <- df %>%
  filter(FN != "blank") %>%
  group_by(FN, state, compounds) %>%
  group_split(.keep = TRUE) %>%                         # list of tibbles (one per FN-state-compound) [web:8]
  map(\(.x) bind_rows(
    .x,
    df_blanks %>% filter(compounds == .x$compounds[1])
  ))

# optional: name the list for easier access
keys <- df %>%
  filter(FN != "blank") %>%
  distinct(FN, state, compounds) %>%
  mutate(id = paste(FN, state, compounds, sep = "_"))

names(lst_FN_state_compound) <- keys$id

# lst_FN_state_compound[[1]]
# lst_FN_state_compound[["PA α35_new_HAP"]]

bartlett_by_df <- imap_dfr(
  lst_FN_state_compound,
  \(d, id) {
    # Bartlett needs >=2 observations in each FN level (here: blank vs your FN)
    n_by_FN <- d %>% count(FN)

    ok <- (n_distinct(d$FN) == 2) && all(n_by_FN$n >= 2)  # blank + sample, each >=2 [web:49]

    out <- if (ok) {
      broom::tidy(bartlett.test(values ~ FN, data = d))   # returns statistic/parameter/p.value/method [web:22]
    } else {
      tibble(
        statistic = NA_real_,
        parameter = NA_real_,
        p.value   = NA_real_,
        method    = "Bartlett test of homogeneity of variances"
      )
    }

    tibble(id = id, ok = ok) %>%
      bind_cols(out)
      
  }
)

bartlett_by_df

df_bartlett <- bartlett_by_df %>% 
  tidyr::separate(
    col  = id,
    into = c("FN", "state", "compounds"),
    sep  = "_",
    remove = TRUE
  ) %>% 
  dplyr::select(FN, state, compounds, p.value) %>% 
  mutate(res = case_when(
    p.value < 0.05 ~ "variances different",
    p.value >= 0.05 ~ "variances homogeneous",
    TRUE ~ NA_character_
  ))
df_bartlett 
```


students better for metals because normal distri + homogeneity of variance

```{r test statistics blc vs FN metals student}

#1) Prepare data

df <- metal_orga %>%
  filter(!is.na(values)) %>% 
  group_by(FN, state, compounds) %>%
  filter(n() >= 3) %>%                    # keep only groups with ≥ 3 rows
  ungroup() %>% 
  filter(compounds %in% c("Metals"))

# blank replicated for each state so comparisons are "compound + state"
blank_states <- tibble(state = c("new", "EOL"))

df_blank <- df %>%
  filter(FN == "blank") %>%
  dplyr::select(FN, compounds, values) %>%
  crossing(blank_states)

df_test <- df %>%
  filter(FN != "blank", state %in% c("new", "EOL")) %>%
  dplyr::select(FN, state, compounds, values)


# 1. Long data with group indicator
df_all <- bind_rows(
  df_test  %>% mutate(group = "FN"),
  df_blank %>% mutate(group = "blank")
)

# 2. Shapiro–Wilk normality per FN/state/compound and group
normality_results <- df_all %>%
  group_by(FN, state, compounds, group) %>%
  summarise(
    shapiro_p = if (sum(!is.na(values)) >= 3 && dplyr::n_distinct(values) > 1) {
      shapiro.test(values)$p.value
    } else {
      NA_real_
    },
    .groups = "drop"
  )

# 3. Levene test FN vs blank per state/compound
levene_results <- df_all %>%
  filter(!is.na(values)) %>%
  group_by(state, compounds) %>%
  summarise(
    levene_p = tryCatch(
      car::leveneTest(values, group)$`Pr(>F)`[1],
      error = function(e) NA_real_
    ),
    .groups = "drop"
  )

# 4. Combine and choose Student / Welch / Wilcoxon
results_vs_blank_auto <- df_test %>%
  group_by(FN, state, compounds) %>%
  summarise(
    n_FN = sum(!is.na(values)),
    x = list(values),
    .groups = "drop"
  ) %>%
  # keep an explicit copy of FN that will survive joins
  mutate(FN_source = FN) %>%
  left_join(
    df_blank %>%
      group_by(state, compounds) %>%
      summarise(
        n_blank = sum(!is.na(values)),
        y = list(values),
        .groups = "drop"
      ),
    by = c("state", "compounds")
  ) %>%
  left_join(
    normality_results %>%
      filter(group == "FN") %>%
      rename(shapiro_p_FN = shapiro_p) %>%
      dplyr::select(-group),
    by = c("FN" = "FN", "state", "compounds")
  ) %>%
  left_join(
    normality_results %>%
      filter(group == "blank") %>%
      rename(shapiro_p_blank = shapiro_p) %>%
      dplyr::select(-group),
    by = c("state", "compounds")
  ) %>%
  left_join(
    levene_results,
    by = c("state", "compounds")
  ) %>%
  mutate(
    test_type = case_when(
      is.na(shapiro_p_FN) | is.na(shapiro_p_blank) ~ "wilcox",
      shapiro_p_FN  > 0.03 &
        shapiro_p_blank > 0.03 &
        !is.na(levene_p) &
        levene_p > 0.05 ~ "student",
      shapiro_p_FN  > 0.03 &
        shapiro_p_blank > 0.05 &
        !is.na(levene_p) &
        levene_p <= 0.05 ~ "welch",
      TRUE ~ "wilcox"
    ),
    p_value = pmap_dbl(
      list(x, y, n_FN, n_blank, test_type),
      ~{
        if (..3 < 2 || ..4 < 2) return(NA_real_)
        if (dplyr::n_distinct(..1) < 2 && dplyr::n_distinct(..2) < 2) return(NA_real_)

        if (..5 == "student") {
          suppressWarnings(t.test(..1, ..2,
                                  var.equal = TRUE,
                                  paired = FALSE)$p.value)
        } else if (..5 == "welch") {
          suppressWarnings(t.test(..1, ..2,
                                  var.equal = FALSE,
                                  paired = FALSE)$p.value)
        } else {
          suppressWarnings(wilcox.test(..1, ..2,
                                       paired = FALSE)$p.value)
        }
      }
    ),
    stars = case_when(
      is.na(p_value)  ~ NA_character_,
      p_value < 0.001 ~ "###",
      p_value < 0.01  ~ "##",
      p_value < 0.05  ~ "#",
      TRUE            ~ "ns"
    )
  ) %>%
  # recreate FN from the preserved copy, then select
  mutate(FN = FN_source) %>%
  dplyr::select(
    FN, state, compounds,
    n_FN, n_blank,
    shapiro_p_FN, shapiro_p_blank, levene_p, test_type,
    p_value, stars
  ) %>%
  arrange(compounds, state, FN, test_type) #%>% 
  #replace results of wilcox test by ns because not meaningfull and useless to show it because very low power
  # mutate(stars_corr   = if_else(test_type == "wilcox", "ns", stars)
  # ) %>% 
  # filter(stars_corr != "ns") %>% 
  # dplyr::select(FN,          state, compounds,  n_FN, n_blank, p_value, stars)


results_vs_blank_auto

#compare tables
compare <- results_vs_blank_auto %>%
  left_join(results_vs_blank %>% mutate(test_type = "wilcox"),
            by = c("FN", "state", "compounds")) %>% 
  dplyr::select(FN, state, compounds, test_type.x, test_type.y, stars.x, stars.y) %>% 
  mutate(compare = if_else(grepl("#", stars.x) & grepl("#", stars.y) | stars.x == stars.y, "ok", "diff"))
compare

results_vs_blank_metals <- results_vs_blank_auto %>% 
  dplyr::select(FN, state, compounds, n_FN, n_blank, p_value, stars)

results_blc_FN <- results_vs_blank %>% 
  bind_rows(results_vs_blank_metals)
results_blc_FN
```


##Statistics individual compounds
```{r Anova ou kruskal including blanks - new FNs}
# ANOVA or Kruskal-Wallis test including blanks
df_new_cp <- metal_orga_cp %>% 
  mutate(state = if_else(is.na(state), "blank", state)) %>%
  filter(state != "EOL") 
df_new_cp

# res_aov <- df_new_cp %>% 
#   group_by(compounds) %>% 
#   nest() %>% 
#   mutate(
#     aov_model = map(data, ~ aov(values ~ FN, data = .x)),
#     aov_tidy  = map(aov_model, ~ broom::tidy(.x)),
#     resid     = map(aov_model, residuals),
#     shapiro   = map(resid, ~ shapiro.test(.x)),
#     bartlett  = map(data, ~ bartlett.test(values ~ FN, data = .x))
#   )
# 
# res_aov$shapiro

res_kw <- df_new_cp %>% 
  group_by(compounds) %>% 
  nest() %>% 
  mutate(
    kw_test  = map(data, ~ kruskal.test(values ~ FN, data = .x)),
    kw_tidy  = map(kw_test, ~ broom::tidy(.x))
  )
res_kw$kw_tidy

# 2) Keep only compounds with p.value < 0.05
res_kw_sig <- res_kw %>% 
  mutate(p_value = map_dbl(kw_tidy, ~ .x$p.value)) %>% 
  filter(p_value < 0.05)

# 3) Dunn test for those significant compounds
res_dunn <- res_kw_sig %>% 
  mutate(
    dunn_raw = map(data, ~ FSA::dunnTest(values ~ FN, data = .x, method = "holm")),
    dunn_tbl = map(dunn_raw, ~ .x$res %>% as_tibble())
  )

# 4) Flat table of all post-hoc comparisons
dunn_table <- res_dunn %>% 
  dplyr::select(compounds, dunn_tbl) %>%   # use the real column name
  unnest(dunn_tbl)
dunn_table

# 3bis) Dunn test + letters for significant compounds only
res_letters <- res_kw_sig %>% 
  mutate(
    # Dunn all-pairs test per compound
    dunn_kw   = map(data, ~ kwAllPairsDunnTest(values ~ as.factor(FN),
                                               data = .x,
                                               p.adjust.method = "holm")),
    # matrix of adjusted p-values
    p_mat     = map(dunn_kw, ~ round(.x$p.value, digits = 3)),
    # full symmetric matrix required by multcompLetters
    p_full    = map(p_mat, fullPTable),
    # compact letter display
    letters   = map(p_full, ~ multcompLetters(.x)$Letters),
    # convert named vector of letters to tibble
    letters_df = map(letters, ~ tibble(
      FN = names(.x),
      label = as.vector(unlist(.x))
    ))
  )

letters_table_new_cp <- res_letters %>% 
  dplyr::select(compounds, letters_df) %>% 
  unnest(letters_df) %>% 
  group_by(compounds) %>%
  filter(n_distinct(label) > 1) %>%   # keep compounds having ≥2 different labels
  ungroup()
  
letters_table_new_cp
```

```{r Anova ou kruskal including blanks - EOL FNs}
# ANOVA or Kruskal-Wallis test including blanks
df_EOL_cp <- metal_orga_cp %>% 
  mutate(state = if_else(is.na(state), "blank", state)) %>%
  filter(state != "new") 
df_EOL_cp

# res_aov <- df_EOL_cp %>% 
#   group_by(compounds) %>% 
#   nest() %>% 
#   mutate(
#     aov_model = map(data, ~ aov(values ~ FN, data = .x)),
#     aov_tidy  = map(aov_model, ~ broom::tidy(.x)),
#     resid     = map(aov_model, residuals),
#     shapiro   = map(resid, ~ shapiro.test(.x)),
#     bartlett  = map(data, ~ bartlett.test(values ~ FN, data = .x))
#   )
# 
# res_aov$shapiro

res_kw <- df_EOL_cp %>% 
  group_by(compounds) %>% 
  nest() %>% 
  mutate(
    kw_test  = map(data, ~ kruskal.test(values ~ FN, data = .x)),
    kw_tidy  = map(kw_test, ~ broom::tidy(.x))
  )
res_kw$kw_tidy

# 2) Keep only compounds with p.value < 0.05
res_kw_sig <- res_kw %>% 
  mutate(p_value = map_dbl(kw_tidy, ~ .x$p.value)) %>% 
  filter(p_value < 0.05)

# 3) Dunn test for those significant compounds
res_dunn <- res_kw_sig %>% 
  mutate(
    dunn_raw = map(data, ~ FSA::dunnTest(values ~ FN, data = .x, method = "holm")),
    dunn_tbl = map(dunn_raw, ~ .x$res %>% as_tibble())
  )

# 4) Flat table of all post-hoc comparisons
dunn_table <- res_dunn %>% 
  dplyr::select(compounds, dunn_tbl) %>%   # use the real column name
  unnest(dunn_tbl)
dunn_table

# 3bis) Dunn test + letters for significant compounds only
res_letters <- res_kw_sig %>% 
  mutate(
    # Dunn all-pairs test per compound
    dunn_kw   = map(data, ~ kwAllPairsDunnTest(values ~ as.factor(FN),
                                               data = .x,
                                               p.adjust.method = "holm")),
    # matrix of adjusted p-values
    p_mat     = map(dunn_kw, ~ round(.x$p.value, digits = 3)),
    # full symmetric matrix required by multcompLetters
    p_full    = map(p_mat, fullPTable),
    # compact letter display
    letters   = map(p_full, ~ multcompLetters(.x)$Letters),
    # convert named vector of letters to tibble
    letters_df = map(letters, ~ tibble(
      FN = names(.x),
      label = as.vector(unlist(.x))
    ))
  )

letters_table_EOL_cp <- res_letters %>% 
  dplyr::select(compounds, letters_df) %>% 
  unnest(letters_df) %>% 
  group_by(compounds) %>%
  filter(n_distinct(label) > 1) %>%   # keep compounds having ≥2 different labels
  ungroup()
  
letters_table_EOL_cp
```

```{r df with all letters KW including blanks}
results_KW_blc_cp <- bind_rows(
  letters_table_new_cp %>% mutate(state = "new"),
  letters_table_EOL_cp %>% mutate(state = "EOL")
) %>%
  #mutate(state = if_else(FN == "blank", "blank", state)) %>% 
  arrange(compounds, state, FN) %>% 
  #if state = new label in capital letters
  mutate(
    label = case_when(
      state == "new" ~ toupper(label),
      TRUE ~ label))
results_KW_blc_cp 
```

```{r Anova ou kruskal excluding blanks - new FNs}
# ANOVA or Kruskal-Wallis test including blanks
df_new_cp <- metal_orga_cp %>% 
  mutate(state = if_else(is.na(state), "blank", state)) %>%
  filter(state != "EOL", FN != "blank") 
df_new_cp

# res_aov <- df_new_cp %>% 
#   group_by(compounds) %>% 
#   nest() %>% 
#   mutate(
#     aov_model = map(data, ~ aov(values ~ FN, data = .x)),
#     aov_tidy  = map(aov_model, ~ broom::tidy(.x)),
#     resid     = map(aov_model, residuals),
#     shapiro   = map(resid, ~ shapiro.test(.x)),
#     bartlett  = map(data, ~ bartlett.test(values ~ FN, data = .x))
#   )
# 
# res_aov$shapiro

res_kw <- df_new_cp %>% 
  group_by(compounds) %>% 
  nest() %>% 
  mutate(
    kw_test  = map(data, ~ kruskal.test(values ~ FN, data = .x)),
    kw_tidy  = map(kw_test, ~ broom::tidy(.x))
  )
res_kw$kw_tidy

# 2) Keep only compounds with p.value < 0.05
res_kw_sig <- res_kw %>% 
  mutate(p_value = map_dbl(kw_tidy, ~ .x$p.value)) %>% 
  filter(p_value < 0.05)

# 3) Dunn test for those significant compounds
res_dunn <- res_kw_sig %>% 
  mutate(
    dunn_raw = map(data, ~ FSA::dunnTest(values ~ FN, data = .x, method = "holm")),
    dunn_tbl = map(dunn_raw, ~ .x$res %>% as_tibble())
  )

# 4) Flat table of all post-hoc comparisons
dunn_table <- res_dunn %>% 
  dplyr::select(compounds, dunn_tbl) %>%   # use the real column name
  unnest(dunn_tbl)
dunn_table

# 3bis) Dunn test + letters for significant compounds only
res_letters <- res_kw_sig %>% 
  mutate(
    # Dunn all-pairs test per compound
    dunn_kw   = map(data, ~ kwAllPairsDunnTest(values ~ as.factor(FN),
                                               data = .x,
                                               p.adjust.method = "holm")),
    # matrix of adjusted p-values
    p_mat     = map(dunn_kw, ~ round(.x$p.value, digits = 3)),
    # full symmetric matrix required by multcompLetters
    p_full    = map(p_mat, fullPTable),
    # compact letter display
    letters   = map(p_full, ~ multcompLetters(.x)$Letters),
    # convert named vector of letters to tibble
    letters_df = map(letters, ~ tibble(
      FN = names(.x),
      label = as.vector(unlist(.x))
    ))
  )

letters_table_new_cp <- res_letters %>% 
  dplyr::select(compounds, letters_df) %>% 
  unnest(letters_df) %>% 
  group_by(compounds) %>%
  filter(n_distinct(label) > 1) %>%   # keep compounds having ≥2 different labels
  ungroup()
  
letters_table_new_cp
```

```{r Anova ou kruskal including blanks - EOL FNs}
# ANOVA or Kruskal-Wallis test including blanks
df_EOL_cp <- metal_orga_cp %>% 
  mutate(state = if_else(is.na(state), "blank", state)) %>%
  filter(state != "new", FN != "blank") 
df_EOL_cp

# res_aov <- df_EOL_cp %>% 
#   group_by(compounds) %>% 
#   nest() %>% 
#   mutate(
#     aov_model = map(data, ~ aov(values ~ FN, data = .x)),
#     aov_tidy  = map(aov_model, ~ broom::tidy(.x)),
#     resid     = map(aov_model, residuals),
#     shapiro   = map(resid, ~ shapiro.test(.x)),
#     bartlett  = map(data, ~ bartlett.test(values ~ FN, data = .x))
#   )
# 
# res_aov$shapiro

res_kw <- df_EOL_cp %>% 
  group_by(compounds) %>% 
  nest() %>% 
  mutate(
    kw_test  = map(data, ~ kruskal.test(values ~ FN, data = .x)),
    kw_tidy  = map(kw_test, ~ broom::tidy(.x))
  )
res_kw$kw_tidy

# 2) Keep only compounds with p.value < 0.05
res_kw_sig <- res_kw %>% 
  mutate(p_value = map_dbl(kw_tidy, ~ .x$p.value)) %>% 
  filter(p_value < 0.05)

# 3) Dunn test for those significant compounds
res_dunn <- res_kw_sig %>% 
  mutate(
    dunn_raw = map(data, ~ FSA::dunnTest(values ~ FN, data = .x, method = "holm")),
    dunn_tbl = map(dunn_raw, ~ .x$res %>% as_tibble())
  )

# 4) Flat table of all post-hoc comparisons
dunn_table <- res_dunn %>% 
  dplyr::select(compounds, dunn_tbl) %>%   # use the real column name
  unnest(dunn_tbl)
dunn_table

# 3bis) Dunn test + letters for significant compounds only
res_letters <- res_kw_sig %>% 
  mutate(
    # Dunn all-pairs test per compound
    dunn_kw   = map(data, ~ kwAllPairsDunnTest(values ~ as.factor(FN),
                                               data = .x,
                                               p.adjust.method = "holm")),
    # matrix of adjusted p-values
    p_mat     = map(dunn_kw, ~ round(.x$p.value, digits = 3)),
    # full symmetric matrix required by multcompLetters
    p_full    = map(p_mat, fullPTable),
    # compact letter display
    letters   = map(p_full, ~ multcompLetters(.x)$Letters),
    # convert named vector of letters to tibble
    letters_df = map(letters, ~ tibble(
      FN = names(.x),
      label = as.vector(unlist(.x))
    ))
  )

letters_table_EOL_cp <- res_letters %>% 
  dplyr::select(compounds, letters_df) %>% 
  unnest(letters_df) %>% 
  group_by(compounds) %>%
  filter(n_distinct(label) > 1) %>%   # keep compounds having ≥2 different labels
  ungroup()
  
letters_table_EOL_cp
```

```{r df with all letters KW excluding blanks}
results_KW_nblc_cp <- bind_rows(
  letters_table_new_cp %>% mutate(state = "new"),
  letters_table_EOL_cp %>% mutate(state = "EOL")
) %>%
  #mutate(state = if_else(FN == "blank", "blank", state)) %>% 
  arrange(compounds, state, FN) %>% 
  #if state = new label in capital letters
  mutate(
    label = case_when(
      state == "new" ~ toupper(label),
      TRUE ~ label))
results_KW_nblc_cp 
```


```{r Statistics blank vs. FN and state}

#1) Prepare data

df <- metal_orga_cp %>%
  filter(!is.na(values))

# blank replicated for each state so comparisons are "compound + state"
blank_states <- tibble(state = c("new", "EOL"))

df_blank <- df %>%
  filter(FN == "blank") %>%
  dplyr::select(FN, compounds, values) %>%
  crossing(blank_states)

df_test <- df %>%
  filter(FN != "blank", state %in% c("new", "EOL")) %>%
  dplyr::select(FN, state, compounds, values)

# 2) Run MWU test: FN vs blank
#    for each (FN, state, compounds)

results_vs_blank <- df_test %>%
  group_by(FN, state, compounds) %>%
  summarise(
    n_FN = sum(!is.na(values)),
    x = list(values),
    .groups = "drop"
  ) %>%
  left_join(
    df_blank %>%
      group_by(state, compounds) %>%
      summarise(
        n_blank = sum(!is.na(values)),
        y = list(values),
        .groups = "drop"
      ),
    by = c("state", "compounds")
  ) %>%
  mutate(
    # MWU only if both groups have enough data + at least some variability
    p_value = pmap_dbl(
      list(x, y, n_FN, n_blank),
      ~{
        if (..3 < 2 || ..4 < 2) return(NA_real_)
        if (dplyr::n_distinct(..1) < 2 && dplyr::n_distinct(..2) < 2) return(NA_real_)
        suppressWarnings(wilcox.test(..1, ..2, paired = FALSE)$p.value)
      }
    ),
    stars = case_when(
      is.na(p_value)  ~ NA_character_,
      p_value < 0.001 ~ "###",
      p_value < 0.01  ~ "##",
      p_value < 0.05  ~ "#",
      TRUE            ~ "ns"
    )
  ) %>%
  dplyr::select(FN, state, compounds, n_FN, n_blank, p_value, stars) %>%
  arrange(compounds, state, FN)

results_vs_blank

```



```{r Statistics new vs EOL}
df_new_EOL_cp <- metal_orga_cp %>% 
  filter(FN != "blank") %>% 
  mutate(
    state     = as.factor(state),
    FN        = as.factor(FN),
    compounds = as.factor(compounds)
  ) 
df_new_EOL_cp

#Eliminate the FN and state for which the values of the three replicates were = 0
df_counts <-
  df_new_EOL_cp %>%
  group_by(FN, compounds, state) %>%
  summarise(
    n_zero = sum(!is.na(values_corr) & values_corr == 0),
    .groups = "drop"
  )

metals <- c("Ag", "As", "Al", "Fe", "Cu", "Mn", "Zn")

compounds_ok <- df_counts %>%
  group_by(FN, compounds) %>%
  filter(
    all(
      n_zero < if_else(first(compounds) %in% metals, 3L, 3L)
    )
  ) %>%
  ungroup() %>%
  distinct(FN, compounds)

compounds_ok

df_new_EOL_cp_ok <-
  df_new_EOL_cp %>%
  semi_join(compounds_ok, by = c("FN", "compounds"))
df_new_EOL_cp_ok

results_tests <-
  df_new_EOL_cp_ok %>%
  group_by(compounds, FN) %>%
  group_modify(~{
    # simple one-way model: values_corr ~ state
    mod <- lm(values_corr ~ state, data = .x)
    
    # Shapiro–Wilk on residuals (normality)
    shapiro_p <- shapiro.test(residuals(mod))$p.value
    
    # Levene’s test (homogeneity of variance across states)
    lev_p <- leveneTest(values_corr ~ state, data = .x)$`Pr(>F)`[1]
    
    tibble(
      shapiro_p = shapiro_p,
      levene_p  = lev_p,
      n         = n_distinct(.x$state)
    )
  }) %>%
  ungroup()
results_tests

# One MWU test per FN × compounds, comparing new vs EOL
tt_results_cp <- df_new_EOL_cp_ok %>% 
  group_by(FN, compounds) %>% 
  summarise(
    tt = list(t.test(values_corr ~ state, var.equal = T)),  # Mann-Whitney
    .groups = "drop"
  ) %>% 
  mutate(
    tt_tidy = map(tt, broom::tidy)
  ) %>% 
  unnest(tt_tidy) %>% 
  mutate(
    diff = if_else(p.value < 0.0001, "****", 
                   if_else(p.value < 0.001, "***",
                           if_else(p.value < 0.01, "**",
                                   if_else(p.value < 0.05, "*", "ns"))))
  ) 
tt_results_cp

```

#Visualizations
```{r First visualization}
G_comp_cat <- Comp_cat %>% ggplot(aes(x = rep, y = values, fill = state)) + 
  geom_col(position = position_dodge()) +
  facet_grid(compounds~FN, scales = "free")
G_comp_cat

# G_all <- data2 %>% ggplot(aes(x = rep, y = values, fill = state)) + 
#   geom_col(position = position_dodge()) +
#   facet_grid(compounds~FN, scales = "free")
# G_all

G_avg <- data_avg %>% 
  mutate(state = if_else(is.na(state), "blank", state)) %>% 
  mutate(state = factor(state, levels = c("blank", "new", "EOL"))) %>%
  ggplot(aes(x = state, y = avg, fill = FN)) + 
  geom_col(position = position_dodge()) +
  geom_errorbar(aes(ymin = avg, ymax = avg + sd), 
                position = position_dodge(width = 0.9), 
                width = 0.2) +
  scale_fill_viridis_d(option = "turbo") +
  facet_wrap(~compounds, scales = "free")
G_avg

G_avg_cat <- data_avg_cat %>% 
  mutate(state = if_else(is.na(state), "blank", state)) %>% 
  mutate(state = factor(state, levels = c("blank", "new", "EOL"))) %>%
  ggplot(aes(x = state, y = avg, fill = FN)) + 
  geom_col(position = position_dodge()) +
  geom_errorbar(aes(ymin = avg, ymax = avg + sd), 
                position = position_dodge(width = 0.9), 
                width = 0.2) +
  scale_fill_viridis_d(option = "turbo") +
  facet_wrap(~compounds, scales = "free")
G_avg_cat

G_avg_corr <- data_avg_corr %>% 
  mutate(compounds = case_when(
      compounds == "acenaphtene" ~ "Acenaphtene",
      compounds == "acenaphtylene" ~ "Acenaphtylene",
      compounds == "anthracene" ~ "Anthracene",
      compounds == "benzo(ghi)péryléne" ~ "Benzo(ghi)perylene",
      compounds == "benzo[b+k]fluoranthene" ~ "Benzo[b+k]fluoranthene",
      compounds == "benzoaanthracene" ~ "Benzo[a]anthracene",
      compounds == "benzoepyrene" ~ "Benzo[e]pyrene",
      compounds == "benzothiophene" ~ "Benzothiophene",
      compounds == "biphenyl" ~ "Biphenyl",
      compounds == "chrysene" ~ "Chrysene",
      compounds == "dibenzoahanthracene" ~ "Dibenzo[a,h]anthracene",
      compounds == "fluoranthene" ~ "Fluoranthene",
      compounds == "fluorene" ~ "Fluorene",
      compounds == "indeno123cdpyrene" ~ "Indeno[1,2,3-cd]pyrene",
      compounds == "naphtalene" ~ "Naphtalene",
      compounds == "pyrene" ~ "Pyrene",
      compounds == "4-tOP" ~ "4-tert-Octylphenol",
      compounds == "Nonylphénols" ~ "Nonylphenols",
      TRUE ~ compounds
      )) %>% 
  mutate(compounds = factor(compounds, levels = c(
      "Acenaphtene", "Acenaphtylene", "Anthracene", "Benzo[e]pyrene", "Benzo(ghi)perylene", "Benzo[b+k]fluoranthene", "Benzo[a]anthracene", "Benzothiophene", "Biphenyl", "Chrysene", "Dibenzo[a,h]anthracene", "Dibenzothiophene", "Fluoranthene", "Fluorene", "Indeno[1,2,3-cd]pyrene", "Phenanthrene", "Naphtalene", "Pyrene",
      "BDE 28", "BDE 47", "BDE 99", "BDE 100", "BDE 153", "BDE 154", "BDE 183",
      "ATBC", "BBP", "DBP", "DEHA", "DEHP", "DEP", "DMP",
      "4-tert-Octylphenol", "Nonylphenols"))) %>% 
  mutate(state = factor(state, levels = c("blank", "new", "EOL"))) %>%
  ggplot(aes(x = state, y = avg_corr, fill = FN)) + 
  geom_col(position = position_dodge()) +
  #scale_fill_viridis_d(option = "turbo") +
  geom_errorbar(aes(ymin = avg_corr, ymax = avg_corr + sd_corr), 
                position = position_dodge(width = 0.9), 
                width = 0.2) +
  scale_fill_manual(values = Color_real_FN5) +
  facet_wrap(~compounds, scales = "free") +
  labs(
    # title = "Concentrations of organic compounds in fishing net extracts",
    #    subtitle = "Values corrected by average blank (n = 4) subtraction\n",
       x = "State of the FNs", 
       y = "Average concentration (µg/L)", 
       fill = "Fishing net\nextracts") +
  theme_bw() +
  theme(
    axis.text.x = ggtext::element_markdown(size = 16, face = 'bold', angle = 0, hjust = 1),
    axis.text.y = ggtext::element_markdown(size = 16, face = 'bold'),
    axis.title.x = element_text(size = 15, face = "bold"),
    axis.title.y = element_text(size = 15, face = "bold"),
    title = element_text(size = 18, face = "bold"),
    strip.text = element_text(face = "bold", size = rel(1.2)),
    legend.position = "right",
    legend.spacing.y = unit(0.3, 'cm'),
    legend.text = element_text(size = 16, face = 'bold', color = "black"),
    legend.key.size = unit(0.85, "cm"),
    legend.key.width = unit(1, "cm"),
    legend.title.align = 0,
    legend.title = element_text(size = 16, face = "bold"),
    plot.margin = unit(c(1, 1, 1, 1), "cm"),
    legend.key.spacing.y = unit(0.3, "cm")
  ) 
G_avg_corr

G_avg_corr_cat <- metal_orga %>% 
  mutate(compounds = case_when(
      compounds == "AKP" ~ "Alkylphenols",
      compounds == "AKP_NP" ~ "Alkylphenols without Nonylphenols",
      compounds == "HAP" ~ "PAHs",
      compounds == "PBDE" ~ "PBDEs",
      compounds == "Phtalates" ~ "Phthalates",
      compounds == "metals" ~ "Trace metals",
      TRUE ~ compounds
      )) %>% 
  mutate(compounds = factor(compounds, levels = c(
      "PAHs", "PBDEs", "Phthalates", "Alkylphenols", "Alkylphenols without Nonylphenols", "Trace metals"))) %>%
  mutate(state = factor(state, levels = c("blank", "new", "EOL"))) %>%
  filter(compounds != "Alkylphenols", FN != "blank") %>%
  mutate(compounds = if_else(compounds == "Alkylphenols without Nonylphenols", "Alkylphenols", compounds)) %>%
  ggplot(aes(x = state, y = values_corr, color = compounds, shape = rep, group = compounds)) + 
  scale_y_log10(
    breaks = c(0.1, 1, 10, 100, 1000),          # Set your desired breaks
    labels = label_number(trim = TRUE)           # Remove scientific format
  ) +
  geom_point(position = position_dodge(width = 0.7), 
    size = 4) +
  scale_shape_manual(values = c(19, 18, 17)) + 
  #scale_color_viridis_d(option = "turbo") +
  scale_color_manual(
    values = c(
      "PAHs" = "#1ae4b6",              # Dark goldenrod
      "PBDEs" = "#4686fb",             # Steel blue
      "Phthalates" = "#faba39",        # Vivid red
      "Alkylphenols" = "#770000",      # Strong green
      "Trace metals" = "#B12090FF"      # Strong green
    )) +
  #scale_fill_manual(values = Color_real_FN5) +
  facet_wrap(~FN) +
  labs(#title = "Concentrations of organic compounds in fishing net extracts",
       #subtitle = "Values corrected by average blank (n = 4) subtraction\n",
       x = "State of the FNs", 
       y = "Average concentration (µg/L)", 
       fill = "Organic compounds") +
  theme_bw() +
  theme(axis.title.x = element_text(size = 18, face = "bold", vjust = -4, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.title.y = element_text(size = 18, face = "bold", vjust = 4, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.text.x = element_text(size = 15, face = "bold"),
        axis.text.y = element_text(size = 15, face = 'bold'),
        title = element_text(size = 18, face = "bold", margin = margin(t = 0, r = 0, b = 20, l = 0)),
        strip.text = element_text(face = "bold", size = rel(1.5)),
        strip.background = element_rect(fill = "grey", color = "grey", linewidth = 0.1),
        legend.title= element_text(size = 18, face = "bold", vjust = 1, margin = margin(t = 0, r = 5, b = 10, l = 0)),
        legend.text = element_text(size = 18),
        legend.spacing.x = unit(0.5, 'cm'),
        legend.spacing.y = unit(0.5, 'cm'),
        legend.key.spacing.y = unit(0.2, "cm"),
        legend.position="right",
        panel.spacing = unit(2, "lines"),
        plot.margin = unit(c(1, 1, 2, 1), "cm")) +
  guides(
    color = guide_legend(title = "Plastic chemical \ncategories", order = 1),
    shape = guide_legend(title = "Replicates", order = 2))
G_avg_corr_cat

G_avg_corr_cat2 <- metal_orga %>% 
  #avg and sd with reframe
  group_by(FN, state, compounds) %>%
  reframe(
    n = n(),
    avg_corr = mean(values_corr, na.rm = T),
    sd_corr = sd(values_corr, na.rm = T)) %>%
  mutate(avg_corr = if_else(avg_corr <1, avg_corr+1, avg_corr),
         sd_corr = if_else(sd_corr <1, sd_corr+1, sd_corr)) %>%
  mutate(avg_corr_log = log10(avg_corr),
         sd_corr_log = log10(sd_corr)) %>%
  mutate(compounds = case_when(
      compounds == "AKP" ~ "Alkylphenols",
      compounds == "AKP_NP" ~ "Alkylphenols without Nonylphenols",
      compounds == "HAP" ~ "PAHs",
      compounds == "PBDE" ~ "PBDEs",
      compounds == "Phtalates" ~ "Phthalates",
      compounds == "metals" ~ "Trace metals",
      TRUE ~ compounds
      )) %>% 
  mutate(compounds = factor(compounds, levels = c(
      "PAHs", "PBDEs", "Phthalates", "Alkylphenols", "Alkylphenols without Nonylphenols", "Trace metals"))) %>%
  mutate(state = factor(state, levels = c("blank", "new", "EOL"))) %>%
  filter(compounds != "Alkylphenols without Nonylphenols", FN != "blank") %>%
  #mutate(compounds = if_else(compounds == "Alkylphenols without Nonylphenols", "Alkylphenols", compounds)) %>%
  ggplot(aes(x = state, y = avg_corr, 
             fill = compounds 
             #shape = rep, 
             #group = compounds
             )) + 
  scale_y_log10(
    breaks = c(0.1, 1, 10, 100, 1000),          # Set your desired breaks
    labels = label_number(trim = TRUE)           # Remove scientific format
  ) +
  geom_col(position = position_dodge(width = 0.5), 
    width = 0.5) +
  geom_errorbar(aes(ymin = avg_corr, ymax = if_else(avg_corr > 1, avg_corr + sd_corr, avg_corr)), 
                position = position_dodge(width = 0.5), 
                width = 0.2) + 
  #scale_color_viridis_d(option = "turbo") +
  scale_color_manual(
    values = c(
      "PAHs" = "#1ae4b6",              # Dark goldenrod
      "PBDEs" = "#4686fb",             # Steel blue
      "Phthalates" = "#faba39",        # Vivid red
      "Alkylphenols" = "#770000",      # Strong green
      "Trace metals" = "#B12090FF"      # Strong green
    )) +
  #scale_fill_manual(values = Color_real_FN5) +
  facet_wrap(~FN) +
  labs(#title = "Concentrations of organic compounds in fishing net extracts",
       #subtitle = "Values corrected by average blank (n = 4) subtraction\n",
       x = "State of the FNs", 
       y = "Average concentration (µg/L)", 
       fill = "Organic compounds") +
  theme_bw() +
  theme(axis.title.x = element_text(size = 18, face = "bold", vjust = -4, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.title.y = element_text(size = 18, face = "bold", vjust = 4, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.text.x = element_text(size = 15, face = "bold"),
        axis.text.y = element_text(size = 15, face = 'bold'),
        title = element_text(size = 18, face = "bold", margin = margin(t = 0, r = 0, b = 20, l = 0)),
        strip.text = element_text(face = "bold", size = rel(1.5)),
        strip.background = element_rect(fill = "grey", color = "grey", linewidth = 0.1),
        legend.title= element_text(size = 18, face = "bold", vjust = 1, margin = margin(t = 0, r = 5, b = 10, l = 0)),
        legend.text = element_text(size = 18),
        legend.spacing.x = unit(0.5, 'cm'),
        legend.spacing.y = unit(0.5, 'cm'),
        legend.key.spacing.y = unit(0.2, "cm"),
        legend.position="right",
        panel.spacing = unit(2, "lines"),
        plot.margin = unit(c(1, 1, 2, 1), "cm")) +
  guides(
    color = guide_legend(title = "Plastic chemical \ncategories", order = 1),
    shape = guide_legend(title = "Replicates", order = 2))
G_avg_corr_cat2

```

```{r visualization by compounds orga}
df_prepa_raw <- data_avg_corr %>% 
  mutate(compounds = case_when(
      compounds == "acenaphtene" ~ "Acenaphtene",
      compounds == "acenaphtylene" ~ "Acenaphtylene",
      compounds == "anthracene" ~ "Anthracene",
      compounds == "benzo(ghi)péryléne" ~ "Benzo(ghi)perylene",
      compounds == "benzo[b+k]fluoranthene" ~ "Benzo[b+k]fluoranthene",
      compounds == "benzoaanthracene" ~ "Benzo[a]anthracene",
      compounds == "benzoepyrene" ~ "Benzo[e]pyrene",
      compounds == "benzothiophene" ~ "Benzothiophene",
      compounds == "biphenyl" ~ "Biphenyl",
      compounds == "chrysene" ~ "Chrysene",
      compounds == "dibenzoahanthracene" ~ "Dibenzo[a,h]anthracene",
      compounds == "fluoranthene" ~ "Fluoranthene",
      compounds == "fluorene" ~ "Fluorene",
      compounds == "indeno123cdpyrene" ~ "Indeno[1,2,3-cd]pyrene",
      compounds == "naphtalene" ~ "Naphthalene",
      compounds == "pyrene" ~ "Pyrene",
      compounds == "4-tOP" ~ "4-tert-Octylphenol",
      compounds == "Nonylphénols" ~ "Nonylphenols",
      TRUE ~ compounds
      )) %>% 
  mutate(compounds = factor(compounds, levels = c(
      "Acenaphtene", "Acenaphtylene", "Anthracene", "Benzo[e]pyrene", "Benzo(ghi)perylene", "Benzo[b+k]fluoranthene", "Benzo[a]anthracene", "Benzothiophene", "Biphenyl", "Chrysene", "Dibenzo[a,h]anthracene", "Dibenzothiophene", "Fluoranthene", "Fluorene", "Indeno[1,2,3-cd]pyrene", "Phenanthrene", "Naphthalene", "Pyrene",
      "BDE 28", "BDE 47", "BDE 99", "BDE 100", "BDE 153", "BDE 154", "BDE 183",
      "ATBC", "BBP", "DBP", "DEHA", "DEHP", "DEP", "DMP",
      "4-tert-Octylphenol", "Nonylphenols"))) %>% 
  mutate(state = if_else(is.na(state), "blank", state)) %>%
  mutate(state = factor(state, levels = c("blank", "new", "EOL")))  
df_prepa_raw

G_compounds <- df_prepa_raw %>% 
  filter(FN != "blank") %>%
  ggplot(aes(x = state, y = avg_corr, fill = FN)) +
  geom_col(
    width = 0.8,
    position = position_dodge(width = 0.8)
  ) +
  geom_errorbar(
    aes(ymin = avg_corr, ymax = avg_corr + sd_corr),
    position = position_dodge(width = 0.8),
    width = 0.2
  ) +
  scale_fill_viridis_d(option = "turbo") +
  facet_wrap(~compounds, scales = "free_y") +
  ## add some headroom above the tallest bar/errorbar
  #scale_y_continuous(expand = expansion(mult = c(0, 0.2))) +
  labs(
    x = "State of the FNs",
    y = "Average concentration (ng/L)",
    fill = "Fishing net\nextracts"
  ) +
  theme_bw() +
  theme(
    axis.title.x = element_text(size = 18, face = "bold", vjust = -4,
                                margin = margin(t = 0, r = 5, b = 0, l = 0)),
    axis.title.y = element_text(size = 18, face = "bold", vjust = 4,
                                margin = margin(t = 0, r = 5, b = 0, l = 0)),
    axis.text.x  = element_text(size = 15, face = "bold"),
    axis.text.y  = element_text(size = 15, face = "bold"),
    strip.text   = element_text(face = "bold", size = rel(1.3)),
    legend.title = element_text(size = 18, face = "bold", vjust = 1,
                                margin = margin(t = 0, r = 5, b = 10, l = 0)),
    legend.text  = element_text(size = 18),
    legend.spacing.x = unit(0.5, "cm"),
    legend.spacing.y = unit(0.5, "cm"),
    legend.key.spacing.y = unit(0.2, "cm"),
    legend.position = "right",
    plot.margin = unit(c(1, 1, 2, 1), "cm")
  ) 
G_compounds

#graph without blank correction
df_prepa_raw <- data_avg_corr %>% 
  mutate(compounds = case_when(
      compounds == "acenaphtene" ~ "Acenaphtene",
      compounds == "acenaphtylene" ~ "Acenaphtylene",
      compounds == "anthracene" ~ "Anthracene",
      compounds == "benzo(ghi)péryléne" ~ "Benzo(ghi)perylene",
      compounds == "benzo[b+k]fluoranthene" ~ "Benzo[b+k]fluoranthene",
      compounds == "benzoaanthracene" ~ "Benzo[a]anthracene",
      compounds == "benzoepyrene" ~ "Benzo[e]pyrene",
      compounds == "benzothiophene" ~ "Benzothiophene",
      compounds == "biphenyl" ~ "Biphenyl",
      compounds == "chrysene" ~ "Chrysene",
      compounds == "dibenzoahanthracene" ~ "Dibenzo[a,h]anthracene",
      compounds == "fluoranthene" ~ "Fluoranthene",
      compounds == "fluorene" ~ "Fluorene",
      compounds == "indeno123cdpyrene" ~ "Indeno[1,2,3-cd]pyrene",
      compounds == "naphtalene" ~ "Naphthalene",
      compounds == "pyrene" ~ "Pyrene",
      compounds == "4-tOP" ~ "4-tert-Octylphenol",
      compounds == "Nonylphénols" ~ "Nonylphenols",
      TRUE ~ compounds
      )) %>% 
  mutate(compounds = factor(compounds, levels = c(
      "Acenaphtene", "Acenaphtylene", "Anthracene", "Benzo[e]pyrene", "Benzo(ghi)perylene", "Benzo[b+k]fluoranthene", "Benzo[a]anthracene", "Benzothiophene", "Biphenyl", "Chrysene", "Dibenzo[a,h]anthracene", "Dibenzothiophene", "Fluoranthene", "Fluorene", "Indeno[1,2,3-cd]pyrene", "Phenanthrene", "Naphthalene", "Pyrene",
      "BDE 28", "BDE 47", "BDE 99", "BDE 100", "BDE 153", "BDE 154", "BDE 183",
      "ATBC", "BBP", "DBP", "DEHA", "DEHP", "DEP", "DMP",
      "4-tert-Octylphenol", "Nonylphenols"))) %>% 
  mutate(state = if_else(is.na(state), "blank", state)) %>%
  mutate(state = factor(state, levels = c("blank", "new", "EOL"))) 
df_prepa_raw

tt_results_Gcp <- tt_results_cp %>%  dplyr::select(FN, compounds, diff) %>% 
  # duplicate each row exactly 2 times
  slice(rep(row_number(), each = 2)) %>% 
  # create the new variable with values "new" and "EOL"
  mutate(state = rep(c("new", "EOL"), times = nrow(tt_results_cp))) %>% 
  #mutate(diff = if_else(state == "new", "ns", diff)) %>% 
  arrange(compounds) %>% 
  group_by(compounds) %>% 
  filter(any(diff != "ns")) %>%  # keep compounds with at least one non-"ns"
  ungroup() %>% 
  mutate(compounds = case_when(
      compounds == "acenaphtene" ~ "Acenaphtene",
      compounds == "acenaphtylene" ~ "Acenaphtylene",
      compounds == "anthracene" ~ "Anthracene",
      compounds == "benzo(ghi)péryléne" ~ "Benzo(ghi)perylene",
      compounds == "benzo[b+k]fluoranthene" ~ "Benzo[b+k]fluoranthene",
      compounds == "benzoaanthracene" ~ "Benzo[a]anthracene",
      compounds == "benzoepyrene" ~ "Benzo[e]pyrene",
      compounds == "benzothiophene" ~ "Benzothiophene",
      compounds == "biphenyl" ~ "Biphenyl",
      compounds == "chrysene" ~ "Chrysene",
      compounds == "dibenzoahanthracene" ~ "Dibenzo[a,h]anthracene",
      compounds == "fluoranthene" ~ "Fluoranthene",
      compounds == "fluorene" ~ "Fluorene",
      compounds == "indeno123cdpyrene" ~ "Indeno[1,2,3-cd]pyrene",
      compounds == "naphtalene" ~ "Naphthalene",
      compounds == "pyrene" ~ "Pyrene",
      compounds == "4-tOP" ~ "4-tert-Octylphenol",
      compounds == "Nonylphénols" ~ "Nonylphenols",
      TRUE ~ compounds
      )) %>% 
  mutate(state = factor(state, levels = c("new", "EOL")))
tt_results_Gcp

# match names and states between tables
results_KW_lab <- results_KW_blc_cp  %>% 
  mutate(compounds = case_when(
      compounds == "acenaphtene" ~ "Acenaphtene",
      compounds == "acenaphtylene" ~ "Acenaphtylene",
      compounds == "anthracene" ~ "Anthracene",
      compounds == "benzo(ghi)péryléne" ~ "Benzo(ghi)perylene",
      compounds == "benzo[b+k]fluoranthene" ~ "Benzo[b+k]fluoranthene",
      compounds == "benzoaanthracene" ~ "Benzo[a]anthracene",
      compounds == "benzoepyrene" ~ "Benzo[e]pyrene",
      compounds == "benzothiophene" ~ "Benzothiophene",
      compounds == "biphenyl" ~ "Biphenyl",
      compounds == "chrysene" ~ "Chrysene",
      compounds == "dibenzoahanthracene" ~ "Dibenzo[a,h]anthracene",
      compounds == "fluoranthene" ~ "Fluoranthene",
      compounds == "fluorene" ~ "Fluorene",
      compounds == "indeno123cdpyrene" ~ "Indeno[1,2,3-cd]pyrene",
      compounds == "naphtalene" ~ "Naphthalene",
      compounds == "pyrene" ~ "Pyrene",
      compounds == "4-tOP" ~ "4-tert-Octylphenol",
      compounds == "Nonylphénols" ~ "Nonylphenols",
      TRUE ~ compounds
      )) %>% 
  mutate(y_top = case_when(
      compounds == "Anthracene" ~ 3.2,
      compounds == "Benzo(ghi)perylene" ~ 6.2,
      compounds == "Benzo[b+k]fluoranthene" ~ 4.2,
      compounds == "Benzo[a]anthracene" ~ 7.5,
      compounds == "Biphenyl" ~ 17,
      compounds == "Chrysene" ~ 25,
      compounds == "Fluoranthene" ~ 35,
      compounds == "Phenanthrene" ~ 60,
      compounds == "Naphthalene" ~ 38,
      compounds == "Pyrene" ~ 36,
      compounds == "ATBC" ~ 42,
      compounds == "DEHA" ~ 190,
      compounds == "4-tert-Octylphenol" ~ 17,
      compounds == "Nonylphenols" ~ 5300,
      TRUE ~ NA_real_
  )) %>% 
  #change order state
  mutate(state = factor(state, levels = c("blank", "new", "EOL"))) %>% 
  mutate(label = if_else(compounds == "Phenanthrene" & state == "EOL", NA, label)) %>% 
  na.omit()

results_KW_lab

df_cp_stat <- df_prepa_raw %>% 
  filter(compounds %in% c("Anthracene", "Benzo(ghi)perylene", "Benzo[b+k]fluoranthene","Benzo[a]anthracene", "Biphenyl",
                          "Chrysene", "Fluoranthene", "Phenanthrene", "Naphthalene", "Pyrene",
                          "ATBC", "DEHA", 
                          "Nonylphenols", "4-tert-Octylphenol"))
df_cp_stat 

pos_dodge <- position_dodge(width = 0.5)

Gcp_no_corr <- df_cp_stat %>% 
  ggplot(aes(x = FN, y = avg, fill = FN, pattern = state, group = state)) +
  geom_bar_pattern(
    stat = "identity",
    width = 0.5,
    position = pos_dodge,
    pattern_density = 0.15,
    pattern_fill = "white",
    pattern_color = "white",
    pattern_spacing = 0.04,
    show.legend = TRUE
  ) +
  geom_errorbar(
    aes(ymin = avg, ymax = avg + sd),
    position = pos_dodge,
    width = 0.2
  ) +
  scale_pattern_discrete(
    na.value = "none",
    choices = c("new" = "none", "EOL" = "stripe", "blank" = "circle"),
    limits = c("new", "EOL", "blank")
  ) +
  #scale_fill_viridis_d(option = "turbo") +
  scale_fill_manual(values = Color_real_FN5) +
  facet_wrap(~compounds, scales = "free_y") +
  ## add some headroom above the tallest bar/errorbar
  #scale_y_continuous(expand = expansion(mult = c(0, 0.2))) +
  labs(
    x = "Fishing nets",
    y = "Average concentration (µg/L)",
    fill = "Fishing net",
    pattern = "State"
  ) +
  theme_bw() +
  theme(
    axis.title.x = element_text(size = 18, face = "bold"#, vjust = -4,
                                #margin = margin(t = 0, r = 5, b = 0, l = 0)
                                ),
    axis.title.y = element_text(size = 18, face = "bold"#, vjust = -4,
                                #margin = margin(t = 0, r = 5, b = 0, l = 0)
                                ),
    axis.text.x  = element_text(size = 15, face = "bold"),
    axis.text.y  = element_text(size = 15, face = "bold"),
    strip.text   = element_text(face = "bold", size = rel(1.5)),
    legend.title = element_text(size = 18, face = "bold"#, vjust = -4,
                                #margin = margin(t = 0, r = 5, b = 0, l = 0)
                                ),
    legend.text  = element_text(size = 18),
    legend.spacing.x = unit(0.5, "cm"),
    legend.spacing.y = unit(0.5, "cm"),
    legend.key.spacing.y = unit(0.2, "cm"),
    legend.position = "right"#,
    #aspect.ratio = 1/2,
    #plot.margin = grid::unit(c(0.3, 0, 0.7, 0.7), "cm")
  ) +
  rotate_x_text(40)

Gcp_no_corr +
  geom_text(
    data = results_KW_lab,
    aes(x = FN, y = y_top, label = label, group = state, hjust = if_else(state == "new", 0.7, 
                    if_else(state == "EOL", -0.3, 0))),
    position = pos_dodge,
    size = 4
    ) +
  ggpubr::geom_bracket(
    data = tibble(
      compounds  = "4-tert-Octylphenol",  # adapt to your facet name if needed
      xmin       = c(4.88, 6.88, 7.88),
      xmax       = c(5.12, 7.12, 8.12),
      y.position = c(6, 9.5, 14),
      label      = c("**", "***", "**")
    ),
    aes(xmin = xmin, xmax = xmax, y.position = y.position, label = label),
    size       = 1.06,
    label.size = 4,
    vjust      = 0.3,
    tip.length = c(0.03, 0.03),
    inherit.aes = FALSE
  ) +
  ggpubr::geom_bracket(
    data = tibble(
      compounds  = "Anthracene",  # adapt to your facet name if needed
      xmin       = c(2.88, 6.88),
      xmax       = c(3.12, 7.12),
      y.position = c(0.7, 2.8),
      label      = c("*", "****")
    ),
    aes(xmin = xmin, xmax = xmax, y.position = y.position, label = label),
    size       = 1.06,
    label.size = 4,
    vjust      = 0.3,
    tip.length = c(0.03, 0.03),
    inherit.aes = FALSE
  ) +
  ggpubr::geom_bracket(
    data = tibble(
      compounds  = "ATBC",  # adapt to your facet name if needed
      xmin       = c(4.88, 6.88),
      xmax       = c(5.12, 7.12),
      y.position = c(43, 39),
      label      = c("**", "**")
    ),
    aes(xmin = xmin, xmax = xmax, y.position = y.position, label = label),
    size       = 1.06,
    label.size = 4,
    vjust      = 0.3,
    tip.length = c(0.03, 0.03),
    inherit.aes = FALSE
  ) +
  ggpubr::geom_bracket(
    data = tibble(
      compounds  = "Benzo[a]anthracene",  # adapt to your facet name if needed
      xmin       = c(2.88, 6.88),
      xmax       = c(3.12, 7.12),
      y.position = c(1.5, 2.3),
      label      = c("*", "***")
    ),
    aes(xmin = xmin, xmax = xmax, y.position = y.position, label = label),
    size       = 1.06,
    label.size = 4,
    vjust      = 0.3,
    tip.length = c(0.03, 0.03),
    inherit.aes = FALSE
  ) +
  ggpubr::geom_bracket(
    data = tibble(
      compounds  = "Benzo[b+k]fluoranthene",  # adapt to your facet name if needed
      xmin       = c(6.88, 8.88),
      xmax       = c(7.12, 9.12),
      y.position = c(3.6, 2),
      label      = c("**", "**")
    ),
    aes(xmin = xmin, xmax = xmax, y.position = y.position, label = label),
    size       = 1.06,
    label.size = 4,
    vjust      = 0.3,
    tip.length = c(0.03, 0.03),
    inherit.aes = FALSE
  ) +
  ggpubr::geom_bracket(
    data = tibble(
      compounds  = "Biphenyl",  # adapt to your facet name if needed
      xmin       = c(5.88),
      xmax       = c(6.12),
      y.position = c(3.5),
      label      = c("**")
    ),
    aes(xmin = xmin, xmax = xmax, y.position = y.position, label = label),
    size       = 1.06,
    label.size = 4,
    vjust      = 0.3,
    tip.length = c(0.03, 0.03),
    inherit.aes = FALSE
  ) +
  ggpubr::geom_bracket(
    data = tibble(
      compounds  = "Chrysene",  # adapt to your facet name if needed
      xmin       = c(6.88),
      xmax       = c(7.12),
      y.position = c(9),
      label      = c("*")
    ),
    aes(xmin = xmin, xmax = xmax, y.position = y.position, label = label),
    size       = 1.06,
    label.size = 4,
    vjust      = 0.3,
    tip.length = c(0.03, 0.03),
    inherit.aes = FALSE
  ) +
  ggpubr::geom_bracket(
    data = tibble(
      compounds  = "DEHA",  # adapt to your facet name if needed
      xmin       = c(6.88),
      xmax       = c(7.12),
      y.position = c(163),
      label      = c("*")
    ),
    aes(xmin = xmin, xmax = xmax, y.position = y.position, label = label),
    size       = 1.06,
    label.size = 4,
    vjust      = 0.3,
    tip.length = c(0.03, 0.03),
    inherit.aes = FALSE
  ) +
  ggpubr::geom_bracket(
    data = tibble(
      compounds  = "Naphthalene",  # adapt to your facet name if needed
      xmin       = c(6.88, 7.88),
      xmax       = c(7.12, 8.12),
      y.position = c(41, 27),
      label      = c("****", "**")
    ),
    aes(xmin = xmin, xmax = xmax, y.position = y.position, label = label),
    size       = 1.06,
    label.size = 4,
    vjust      = 0.3,
    tip.length = c(0.03, 0.03),
    inherit.aes = FALSE
  ) +
  ggpubr::geom_bracket(
    data = tibble(
      compounds  = "Phenanthrene",  # adapt to your facet name if needed
      xmin       = c(3.88, 6.88),
      xmax       = c(4.12, 7.12),
      y.position = c(13, 50),
      label      = c("**", "**")
    ),
    aes(xmin = xmin, xmax = xmax, y.position = y.position, label = label),
    size       = 1.06,
    label.size = 4,
    vjust      = 0.3,
    tip.length = c(0.03, 0.03),
    inherit.aes = FALSE
  ) 

#-------------------Plot with blank correction-------------

results_KW_lab <- results_KW_nblc_cp  %>% 
  mutate(compounds = case_when(
      compounds == "acenaphtene" ~ "Acenaphtene",
      compounds == "acenaphtylene" ~ "Acenaphtylene",
      compounds == "anthracene" ~ "Anthracene",
      compounds == "benzo(ghi)péryléne" ~ "Benzo(ghi)perylene",
      compounds == "benzo[b+k]fluoranthene" ~ "Benzo[b+k]fluoranthene",
      compounds == "benzoaanthracene" ~ "Benzo[a]anthracene",
      compounds == "benzoepyrene" ~ "Benzo[e]pyrene",
      compounds == "benzothiophene" ~ "Benzothiophene",
      compounds == "biphenyl" ~ "Biphenyl",
      compounds == "chrysene" ~ "Chrysene",
      compounds == "dibenzoahanthracene" ~ "Dibenzo[a,h]anthracene",
      compounds == "fluoranthene" ~ "Fluoranthene",
      compounds == "fluorene" ~ "Fluorene",
      compounds == "indeno123cdpyrene" ~ "Indeno[1,2,3-cd]pyrene",
      compounds == "naphtalene" ~ "Naphthalene",
      compounds == "pyrene" ~ "Pyrene",
      compounds == "4-tOP" ~ "4-tert-Octylphenol",
      compounds == "Nonylphénols" ~ "Nonylphenols",
      TRUE ~ compounds
      )) %>% 
  mutate(y_top = case_when(
      compounds == "Anthracene" ~ 3.2,
      compounds == "Benzo(ghi)perylene" ~ 5.2,
      compounds == "Benzo[b+k]fluoranthene" ~ 3.8,
      compounds == "Benzo[a]anthracene" ~ 7.5,
      compounds == "Biphenyl" ~ 17,
      compounds == "Chrysene" ~ 25,
      compounds == "Fluoranthene" ~ 35,
      compounds == "Phenanthrene" ~ 60,
      compounds == "Naphthalene" ~ 70,
      compounds == "Pyrene" ~ 36,
      compounds == "ATBC" ~ 42,
      compounds == "DEHA" ~ 190,
      compounds == "4-tert-Octylphenol" ~ 16,
      compounds == "Nonylphenols" ~ 4900,
      TRUE ~ NA_real_
  )) %>% 
  #change order state
  mutate(state = factor(state, levels = c("blank", "new", "EOL"))) %>% 
  # mutate(label = if_else(compounds == "Phenanthrene" & state == "EOL", NA, label)) %>% 
  na.omit()

results_KW_lab

Gcp_no_corr <- df_cp_stat %>% 
  filter(FN != "blank") %>% 
  ggplot(aes(x = FN, y = avg_corr, fill = FN, pattern = state, group = state)) +
  geom_bar_pattern(
    stat = "identity",
    width = 0.5,
    position = pos_dodge,
    pattern_density = 0.15,
    pattern_fill = "white",
    pattern_color = "white",
    pattern_spacing = 0.04,
    show.legend = TRUE
  ) +
  geom_errorbar(
    aes(ymin = avg_corr, ymax = avg_corr + sd_corr),
    position = pos_dodge,
    width = 0.2
  ) +
  scale_pattern_discrete(
    na.value = "none",
    choices = c("new" = "none", "EOL" = "stripe"),
    limits = c("new", "EOL")
  ) +
  #scale_fill_viridis_d(option = "turbo") +
  scale_fill_manual(values = Color_real_FN5) +
  facet_wrap(~compounds, scales = "free_y") +
  ## add some headroom above the tallest bar/errorbar
  #scale_y_continuous(expand = expansion(mult = c(0, 0.2))) +
  labs(
    x = "Fishing nets",
    y = "Average concentration (µg/L)",
    fill = "Fishing net",
    pattern = "State"
  ) +
  theme_bw() +
  theme(
    axis.title.x = element_text(size = 20, face = "bold"#, vjust = -4,
                                #margin = margin(t = 0, r = 5, b = 0, l = 0)
                                ),
    axis.title.y = element_text(size = 20, face = "bold"#, vjust = -4,
                                #margin = margin(t = 0, r = 5, b = 0, l = 0)
                                ),
    axis.text.x  = element_text(size = 18, face = "bold"),
    axis.text.y  = element_text(size = 18, face = "bold"),
    strip.text   = element_text(face = "bold", size = rel(1.5)),
    legend.title = element_text(size = 18, face = "bold"#, vjust = -4,
                                #margin = margin(t = 0, r = 5, b = 0, l = 0)
                                ),
    legend.text  = element_text(size = 18),
    legend.spacing.x = unit(0.5, "cm"),
    legend.spacing.y = unit(0.5, "cm"),
    legend.key.spacing.y = unit(0.2, "cm"),
    legend.position = "right"#,
    #aspect.ratio = 1/2,
    #plot.margin = grid::unit(c(0.3, 0, 0.7, 0.7), "cm")
  ) +
  rotate_x_text(40)


Gcp_no_corr +
  geom_text(
    data = results_KW_lab,
    aes(x = FN, y = y_top, label = label, group = state, hjust = if_else(state == "new", 0.7, 
                    if_else(state == "EOL", -0.3, 0))),
    position = pos_dodge,
    size = 4
    ) +
  ggpubr::geom_bracket(
    data = tibble(
      compounds  = "4-tert-Octylphenol",  # adapt to your facet name if needed
      xmin       = c(3.88, 5.88, 6.88),
      xmax       = c(4.12, 6.12, 7.12),
      y.position = c(5, 8.5, 13),
      label      = c("**", "***", "**")
    ),
    aes(xmin = xmin, xmax = xmax, y.position = y.position, label = label),
    size       = 1.06,
    label.size = 4,
    vjust      = 0.3,
    tip.length = c(0.03, 0.03),
    inherit.aes = FALSE
  ) +
  ggpubr::geom_bracket(
    data = tibble(
      compounds  = "Anthracene",  # adapt to your facet name if needed
      xmin       = c(1.88, 5.88),
      xmax       = c(2.12, 6.12),
      y.position = c(0.5, 2.7),
      label      = c("*", "****")
    ),
    aes(xmin = xmin, xmax = xmax, y.position = y.position, label = label),
    size       = 1.06,
    label.size = 4,
    vjust      = 0.3,
    tip.length = c(0.03, 0.03),
    inherit.aes = FALSE
  ) +
  ggpubr::geom_bracket(
    data = tibble(
      compounds  = "ATBC",  # adapt to your facet name if needed
      xmin       = c(3.88, 5.88),
      xmax       = c(4.12, 6.12),
      y.position = c(30, 28),
      label      = c("**", "**")
    ),
    aes(xmin = xmin, xmax = xmax, y.position = y.position, label = label),
    size       = 1.06,
    label.size = 4,
    vjust      = 0.3,
    tip.length = c(0.03, 0.03),
    inherit.aes = FALSE
  ) +
  ggpubr::geom_bracket(
    data = tibble(
      compounds  = "Benzo[a]anthracene",  # adapt to your facet name if needed
      xmin       = c(1.88, 5.88),
      xmax       = c(2.12, 6.12),
      y.position = c(1.3, 2.1),
      label      = c("*", "***")
    ),
    aes(xmin = xmin, xmax = xmax, y.position = y.position, label = label),
    size       = 1.06,
    label.size = 4,
    vjust      = 0.3,
    tip.length = c(0.03, 0.03),
    inherit.aes = FALSE
  ) +
  ggpubr::geom_bracket(
    data = tibble(
      compounds  = "Benzo[b+k]fluoranthene",  # adapt to your facet name if needed
      xmin       = c(5.88, 7.88),
      xmax       = c(6.12, 8.12),
      y.position = c(3.3, 1.8),
      label      = c("**", "**")
    ),
    aes(xmin = xmin, xmax = xmax, y.position = y.position, label = label),
    size       = 1.06,
    label.size = 4,
    vjust      = 0.3,
    tip.length = c(0.03, 0.03),
    inherit.aes = FALSE
  ) +
  ggpubr::geom_bracket(
    data = tibble(
      compounds  = "Biphenyl",  # adapt to your facet name if needed
      xmin       = c(4.88),
      xmax       = c(5.12),
      y.position = c(2.5),
      label      = c("**")
    ),
    aes(xmin = xmin, xmax = xmax, y.position = y.position, label = label),
    size       = 1.06,
    label.size = 4,
    vjust      = 0.3,
    tip.length = c(0.03, 0.03),
    inherit.aes = FALSE
  ) +
  ggpubr::geom_bracket(
    data = tibble(
      compounds  = "Chrysene",  # adapt to your facet name if needed
      xmin       = c(5.88),
      xmax       = c(6.12),
      y.position = c(7),
      label      = c("*")
    ),
    aes(xmin = xmin, xmax = xmax, y.position = y.position, label = label),
    size       = 1.06,
    label.size = 4,
    vjust      = 0.3,
    tip.length = c(0.03, 0.03),
    inherit.aes = FALSE
  ) +
  ggpubr::geom_bracket(
    data = tibble(
      compounds  = "DEHA",  # adapt to your facet name if needed
      xmin       = c(5.88),
      xmax       = c(6.12),
      y.position = c(160),
      label      = c("*")
    ),
    aes(xmin = xmin, xmax = xmax, y.position = y.position, label = label),
    size       = 1.06,
    label.size = 4,
    vjust      = 0.3,
    tip.length = c(0.03, 0.03),
    inherit.aes = FALSE
  ) +
  ggpubr::geom_bracket(
    data = tibble(
      compounds  = "Naphthalene",  # adapt to your facet name if needed
      xmin       = c(5.88, 6.88),
      xmax       = c(6.12, 7.12),
      y.position = c(38, 24),
      label      = c("****", "**")
    ),
    aes(xmin = xmin, xmax = xmax, y.position = y.position, label = label),
    size       = 1.06,
    label.size = 4,
    vjust      = 0.3,
    tip.length = c(0.03, 0.03),
    inherit.aes = FALSE
  ) +
  ggpubr::geom_bracket(
    data = tibble(
      compounds  = "Phenanthrene",  # adapt to your facet name if needed
      xmin       = c(2.88, 5.88),
      xmax       = c(3.12, 6.12),
      y.position = c(13, 50),
      label      = c("**", "**")
    ),
    aes(xmin = xmin, xmax = xmax, y.position = y.position, label = label),
    size       = 1.06,
    label.size = 4,
    vjust      = 0.3,
    tip.length = c(0.03, 0.03),
    inherit.aes = FALSE
  ) 


```


```{r visualization by compounds metals}
df_prepa_raw <- data_avg_corr %>% 
  mutate(compounds = case_when(
      compounds == "acenaphtene" ~ "Acenaphtene",
      compounds == "acenaphtylene" ~ "Acenaphtylene",
      compounds == "anthracene" ~ "Anthracene",
      compounds == "benzo(ghi)péryléne" ~ "Benzo(ghi)perylene",
      compounds == "benzo[b+k]fluoranthene" ~ "Benzo[b+k]fluoranthene",
      compounds == "benzoaanthracene" ~ "Benzo[a]anthracene",
      compounds == "benzoepyrene" ~ "Benzo[e]pyrene",
      compounds == "benzothiophene" ~ "Benzothiophene",
      compounds == "biphenyl" ~ "Biphenyl",
      compounds == "chrysene" ~ "Chrysene",
      compounds == "dibenzoahanthracene" ~ "Dibenzo[a,h]anthracene",
      compounds == "fluoranthene" ~ "Fluoranthene",
      compounds == "fluorene" ~ "Fluorene",
      compounds == "indeno123cdpyrene" ~ "Indeno[1,2,3-cd]pyrene",
      compounds == "naphtalene" ~ "Naphtalene",
      compounds == "pyrene" ~ "Pyrene",
      compounds == "4-tOP" ~ "4-tert-Octylphenol",
      compounds == "Nonylphénols" ~ "Nonylphenols",
      TRUE ~ compounds
      )) %>% 
  mutate(compounds = factor(compounds, levels = c(
      "Acenaphtene", "Acenaphtylene", "Anthracene", "Benzo[e]pyrene", "Benzo(ghi)perylene", "Benzo[b+k]fluoranthene", "Benzo[a]anthracene", "Benzothiophene", "Biphenyl", "Chrysene", "Dibenzo[a,h]anthracene", "Dibenzothiophene", "Fluoranthene", "Fluorene", "Indeno[1,2,3-cd]pyrene", "Phenanthrene", "Naphtalene", "Pyrene",
      "BDE 28", "BDE 47", "BDE 99", "BDE 100", "BDE 153", "BDE 154", "BDE 183",
      "ATBC", "BBP", "DBP", "DEHA", "DEHP", "DEP", "DMP",
      "4-tert-Octylphenol", "Nonylphenols", "Ag", "As", "Al", "Fe", "Cu", "Mn", "Zn"))) %>% 
  mutate(state = if_else(is.na(state), "blank", state)) %>%
  mutate(state = factor(state, levels = c("blank", "new", "EOL")))  
df_prepa_raw

#graph without blank correction
df_prepa_raw <- data_avg_corr %>% 
  mutate(compounds = case_when(
      compounds == "acenaphtene" ~ "Acenaphtene",
      compounds == "acenaphtylene" ~ "Acenaphtylene",
      compounds == "anthracene" ~ "Anthracene",
      compounds == "benzo(ghi)péryléne" ~ "Benzo(ghi)perylene",
      compounds == "benzo[b+k]fluoranthene" ~ "Benzo[b+k]fluoranthene",
      compounds == "benzoaanthracene" ~ "Benzo[a]anthracene",
      compounds == "benzoepyrene" ~ "Benzo[e]pyrene",
      compounds == "benzothiophene" ~ "Benzothiophene",
      compounds == "biphenyl" ~ "Biphenyl",
      compounds == "chrysene" ~ "Chrysene",
      compounds == "dibenzoahanthracene" ~ "Dibenzo[a,h]anthracene",
      compounds == "fluoranthene" ~ "Fluoranthene",
      compounds == "fluorene" ~ "Fluorene",
      compounds == "indeno123cdpyrene" ~ "Indeno[1,2,3-cd]pyrene",
      compounds == "naphtalene" ~ "Naphtalene",
      compounds == "pyrene" ~ "Pyrene",
      compounds == "4-tOP" ~ "4-tert-Octylphenol",
      compounds == "Nonylphénols" ~ "Nonylphenols",
      TRUE ~ compounds
      )) %>% 
  mutate(compounds = factor(compounds, levels = c(
      "Acenaphtene", "Acenaphtylene", "Anthracene", "Benzo[e]pyrene", "Benzo(ghi)perylene", "Benzo[b+k]fluoranthene", "Benzo[a]anthracene", "Benzothiophene", "Biphenyl", "Chrysene", "Dibenzo[a,h]anthracene", "Dibenzothiophene", "Fluoranthene", "Fluorene", "Indeno[1,2,3-cd]pyrene", "Phenanthrene", "Naphtalene", "Pyrene",
      "BDE 28", "BDE 47", "BDE 99", "BDE 100", "BDE 153", "BDE 154", "BDE 183",
      "ATBC", "BBP", "DBP", "DEHA", "DEHP", "DEP", "DMP",
      "4-tert-Octylphenol", "Nonylphenols", "Ag", "As", "Al", "Fe", "Cu", "Mn", "Zn"))) %>% 
  mutate(state = if_else(is.na(state), "blank", state)) %>%
  mutate(state = factor(state, levels = c("blank", "new", "EOL"))) 
df_prepa_raw

tt_results_Gcp <- tt_results_cp %>%  dplyr::select(FN, compounds, diff) %>% 
  # duplicate each row exactly 2 times
  slice(rep(row_number(), each = 2)) %>% 
  # create the new variable with values "new" and "EOL"
  mutate(state = rep(c("new", "EOL"), times = nrow(tt_results_cp))) %>% 
  #mutate(diff = if_else(state == "new", "ns", diff)) %>% 
  arrange(compounds) %>% 
  group_by(compounds) %>% 
  filter(any(diff != "ns")) %>%  # keep compounds with at least one non-"ns"
  ungroup() %>% 
  mutate(compounds = case_when(
      compounds == "acenaphtene" ~ "Acenaphtene",
      compounds == "acenaphtylene" ~ "Acenaphtylene",
      compounds == "anthracene" ~ "Anthracene",
      compounds == "benzo(ghi)péryléne" ~ "Benzo(ghi)perylene",
      compounds == "benzo[b+k]fluoranthene" ~ "Benzo[b+k]fluoranthene",
      compounds == "benzoaanthracene" ~ "Benzo[a]anthracene",
      compounds == "benzoepyrene" ~ "Benzo[e]pyrene",
      compounds == "benzothiophene" ~ "Benzothiophene",
      compounds == "biphenyl" ~ "Biphenyl",
      compounds == "chrysene" ~ "Chrysene",
      compounds == "dibenzoahanthracene" ~ "Dibenzo[a,h]anthracene",
      compounds == "fluoranthene" ~ "Fluoranthene",
      compounds == "fluorene" ~ "Fluorene",
      compounds == "indeno123cdpyrene" ~ "Indeno[1,2,3-cd]pyrene",
      compounds == "naphtalene" ~ "Naphtalene",
      compounds == "pyrene" ~ "Pyrene",
      compounds == "4-tOP" ~ "4-tert-Octylphenol",
      compounds == "Nonylphénols" ~ "Nonylphenols",
      TRUE ~ compounds
      )) 
tt_results_Gcp


#-------------------Plot with blank correction-------------

results_KW_lab <- results_KW_nblc_cp  %>% 
  mutate(y_top = case_when(
      compounds == "Ag" & state == "new" ~ 50,
      compounds == "Ag" & state == "EOL" ~ 55,
      # compounds == "Al" & state == "new" ~ 300,
      # compounds == "Al" & state == "EOL" ~ 320,
      # compounds == "As" & state == "new" ~ 110,
      compounds == "As" & state == "EOL" ~ 130,
      compounds == "Cu" & state == "new" ~ 880,
      compounds == "Cu" & state == "EOL" ~ 1000,
      compounds == "Fe" & state == "new" ~ 360,
      compounds == "Fe" & state == "EOL" ~ 410,
      compounds == "Mn" & state == "new" ~ 155,
      compounds == "Mn" & state == "EOL" ~ 180,
      compounds == "Zn" & state == "new" ~ 1500,
      compounds == "Zn" & state == "EOL" ~ 1700,
      TRUE ~ NA_real_
  )) %>% 
  #change order state
  mutate(state = factor(state, levels = c("blank", "new", "EOL"))) %>% 
  na.omit()

results_KW_lab

Gcp_no_corr <- df_cp_stat %>% 
  filter(FN != "blank") %>% 
  ggplot(aes(x = FN, y = avg_corr, fill = FN, pattern = state, group = state)) +
  geom_bar_pattern(
    stat = "identity",
    width = 0.5,
    position = pos_dodge,
    pattern_density = 0.15,
    pattern_fill = "white",
    pattern_color = "white",
    pattern_spacing = 0.04,
    show.legend = TRUE
  ) +
  geom_errorbar(
    aes(ymin = avg_corr, ymax = avg_corr + sd_corr),
    position = pos_dodge,
    width = 0.2
  ) +
  scale_pattern_discrete(
    na.value = "none",
    choices = c("new" = "none", "EOL" = "stripe"),
    limits = c("new", "EOL")
  ) +
  #scale_fill_viridis_d(option = "turbo") +
  scale_fill_manual(values = Color_real_FN5) +
  facet_wrap(~compounds, scales = "free_y") +
  ## add some headroom above the tallest bar/errorbar
  #scale_y_continuous(expand = expansion(mult = c(0, 0.2))) +
  labs(
    x = "Fishing net",
    y = "Average concentration (µg/L)",
    fill = "Fishing net",
    pattern = "State"
  ) +
  theme_bw() +
  theme(
    axis.title.x = element_text(size = 18, face = "bold", vjust = -4,
                                margin = margin(t = 0, r = 5, b = 0, l = 0)),
    axis.title.y = element_text(size = 18, face = "bold", vjust = 4,
                                margin = margin(t = 0, r = 5, b = 0, l = 0)),
    axis.text.x  = element_text(size = 15, face = "bold"),
    axis.text.y  = element_text(size = 15, face = "bold"),
    strip.text   = element_text(face = "bold", size = rel(1.5)),
    legend.title = element_text(size = 18, face = "bold", vjust = 1,
                                margin = margin(t = 0, r = 5, b = 10, l = 0)),
    legend.text  = element_text(size = 18),
    legend.spacing.x = unit(0.5, "cm"),
    legend.spacing.y = unit(0.5, "cm"),
    legend.key.spacing.y = unit(0.2, "cm"),
    legend.position = "right",
    plot.margin = unit(c(1, 1, 1, 1), "cm")
  ) +
  rotate_x_text(30)

tt_results_cp_plot <- tt_results_cp %>% 
  filter(compounds %in% c("Ag", "As", "Al", "Fe", "Cu", "Mn", "Zn")) %>% 
  dplyr::select(FN, compounds, diff) %>% 
  filter(diff != "ns") %>% 
  arrange(compounds)
tt_results_cp_plot

Gcp_no_corr +
  geom_text(
    data = results_KW_lab,
    aes(x = FN, y = y_top, label = label, group = state, hjust = if_else(state == "new", 0.7, 
                    if_else(state == "EOL", 0, 0))),
    position = pos_dodge,
    size = 4
    ) +
  ggpubr::geom_bracket(
    data = tibble(
      compounds  = "Ag",  # adapt to your facet name if needed
      xmin       = c(5.88, 6.88),
      xmax       = c(6.12, 7.12),
      y.position = c(37, 14),
      label      = c("***", "**")
    ),
    aes(xmin = xmin, xmax = xmax, y.position = y.position, label = label),
    size       = 1.06,
    label.size = 4,
    vjust      = 0.3,
    tip.length = c(0.03, 0.03),
    inherit.aes = FALSE
  ) +
  ggpubr::geom_bracket(
    data = tibble(
      compounds  = "As",  # adapt to your facet name if needed
      xmin       = c(5.88),
      xmax       = c(6.12),
      y.position = c(30),
      label      = c("**")
    ),
    aes(xmin = xmin, xmax = xmax, y.position = y.position, label = label),
    size       = 1.06,
    label.size = 4,
    vjust      = 0.3,
    tip.length = c(0.03, 0.03),
    inherit.aes = FALSE
  ) +
  ggpubr::geom_bracket(
    data = tibble(
      compounds  = "Cu",  # adapt to your facet name if needed
      xmin       = c(5.88, 6.88),
      xmax       = c(6.12, 7.12),
      y.position = c(435, 500),
      label      = c("***", "**")
    ),
    aes(xmin = xmin, xmax = xmax, y.position = y.position, label = label),
    size       = 1.06,
    label.size = 4,
    vjust      = 0.3,
    tip.length = c(0.03, 0.03),
    inherit.aes = FALSE
  ) +
    ggpubr::geom_bracket(
    data = tibble(
      compounds  = "Mn",  # adapt to your facet name if needed
      xmin       = c(0.88, 5.88, 6.88),
      xmax       = c(1.12, 6.12, 7.12),
      y.position = c(125, 135, 75),
      label      = c("**", "****", "*")
    ),
    aes(xmin = xmin, xmax = xmax, y.position = y.position, label = label),
    size       = 1.06,
    label.size = 4,
    vjust      = 0.3,
    tip.length = c(0.03, 0.03),
    inherit.aes = FALSE
  ) +
    ggpubr::geom_bracket(
    data = tibble(
      compounds  = "Zn",  # adapt to your facet name if needed
      xmin       = c(5.88, 6.88),
      xmax       = c(6.12, 7.12),
      y.position = c(1250, 600),
      label      = c("****", "****")
    ),
    aes(xmin = xmin, xmax = xmax, y.position = y.position, label = label),
    size       = 1.06,
    label.size = 4,
    vjust      = 0.3,
    tip.length = c(0.03, 0.03),
    inherit.aes = FALSE
  ) 

```


```{r visualization by large categories orga + metals no publi}

G_avg_corr_cat <- metal_orga %>% 
  mutate(compounds = case_when(
      compounds == "AKP" ~ "Alkylphenols",
      compounds == "AKP_NP" ~ "Alkylphenols without Nonylphenols",
      compounds == "HAP" ~ "PAHs",
      compounds == "PBDE" ~ "PBDEs",
      compounds == "Phtalates" ~ "Phthalates",
      compounds == "metals" ~ "Trace metals",
      TRUE ~ compounds
      )) %>% 
  mutate(compounds = factor(compounds, levels = c(
      "PAHs", "PBDEs", "Phthalates", "Alkylphenols", "Alkylphenols without Nonylphenols", "Trace metals"))) %>%
  mutate(state = factor(state, levels = c("blank", "new", "EOL"))) %>%
  filter(compounds != "Alkylphenols", FN != "blank") %>%
  mutate(compounds = if_else(compounds == "Alkylphenols without Nonylphenols", "Alkylphenols", compounds)) %>%
  ggplot(aes(x = state, y = values_corr, color = compounds, shape = rep, group = compounds)) + 
  scale_y_log10(
    breaks = c(0.1, 1, 10, 100, 1000),          # Set your desired breaks
    labels = label_number(trim = TRUE)           # Remove scientific format
  ) +
  geom_point(position = position_dodge(width = 0.7), 
    size = 4) +
  scale_shape_manual(values = c(19, 18, 17)) + 
  #scale_color_viridis_d(option = "turbo") +
  scale_color_manual(
    values = c(
      "PAHs" = "#1ae4b6",              # Dark goldenrod
      "PBDEs" = "#4686fb",             # Steel blue
      "Phthalates" = "#faba39",        # Vivid red
      "Alkylphenols" = "#770000",      # Strong green
      "Trace metals" = "#B12090FF"      # Strong green
    )) +
  #scale_fill_manual(values = Color_real_FN5) +
  facet_wrap(~FN) +
  labs(#title = "Concentrations of organic compounds in fishing net extracts",
       #subtitle = "Values corrected by average blank (n = 4) subtraction\n",
       x = "State of the FNs", 
       y = "Average concentration (µg/L)", 
       fill = "Organic compounds") +
  theme_bw() +
  theme(axis.title.x = element_text(size = 18, face = "bold", vjust = -4, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.title.y = element_text(size = 18, face = "bold", vjust = 4, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.text.x = element_text(size = 15, face = "bold"),
        axis.text.y = element_text(size = 15, face = 'bold'),
        title = element_text(size = 18, face = "bold", margin = margin(t = 0, r = 0, b = 20, l = 0)),
        strip.text = element_text(face = "bold", size = rel(1.5)),
        strip.background = element_rect(fill = "grey", color = "grey", linewidth = 0.1),
        legend.title= element_text(size = 18, face = "bold", vjust = 1, margin = margin(t = 0, r = 5, b = 10, l = 0)),
        legend.text = element_text(size = 18),
        legend.spacing.x = unit(0.5, 'cm'),
        legend.spacing.y = unit(0.5, 'cm'),
        legend.key.spacing.y = unit(0.2, "cm"),
        legend.position="right",
        panel.spacing = unit(2, "lines"),
        plot.margin = unit(c(1, 1, 2, 1), "cm")) +
  guides(
    color = guide_legend(title = "Plastic chemical \ncategories", order = 1),
    shape = guide_legend(title = "Replicates", order = 2))
G_avg_corr_cat

G_avg_corr_cat2 <- metal_orga %>% 
  #avg and sd with reframe
  group_by(FN, state, compounds) %>%
  reframe(
    n = n(),
    avg_corr = mean(values_corr, na.rm = T),
    sd_corr = sd(values_corr, na.rm = T)) %>%
  mutate(avg_corr = if_else(avg_corr <1, avg_corr+1, avg_corr),
         sd_corr = if_else(sd_corr <1, sd_corr+1, sd_corr)) %>%
  mutate(avg_corr_log = log10(avg_corr),
         sd_corr_log = log10(sd_corr)) %>%
  mutate(compounds = case_when(
      compounds == "AKP" ~ "Alkylphenols",
      compounds == "AKP_NP" ~ "Alkylphenols without Nonylphenols",
      compounds == "HAP" ~ "PAHs",
      compounds == "PBDE" ~ "PBDEs",
      compounds == "Phtalates" ~ "Phthalates",
      compounds == "metals" ~ "Metallic elements",
      TRUE ~ compounds
      )) %>% 
  mutate(compounds = factor(compounds, levels = c(
      "PAHs", "PBDEs", "Phthalates", "Alkylphenols", "Alkylphenols without Nonylphenols", "Metallic elements"))) %>%
  mutate(state = factor(state, levels = c("blank", "new", "EOL"))) %>%
  filter(compounds != "Alkylphenols without Nonylphenols", 
         #FN != "blank"
         ) %>%
  #mutate(compounds = if_else(compounds == "Alkylphenols without Nonylphenols", "Alkylphenols", compounds)) %>%
  ggplot(aes(x = state, y = avg_corr, 
             fill = compounds 
             #shape = rep, 
             #group = compounds
             )) + 
  scale_y_log10(
    breaks = c(0.1, 1, 10, 100, 1000),          # Set your desired breaks
    labels = label_number(trim = TRUE)           # Remove scientific format
  ) +
  geom_col(position = position_dodge(width = 0.5), 
    width = 0.5) +
  geom_errorbar(aes(ymin = avg_corr, ymax = if_else(avg_corr > 1, avg_corr + sd_corr, avg_corr)), 
                position = position_dodge(width = 0.5), 
                width = 0.2) + 
  #scale_color_viridis_d(option = "turbo") +
  scale_color_manual(
    values = c(
      "PAHs" = "#1ae4b6",              # Dark goldenrod
      "PBDEs" = "#4686fb",             # Steel blue
      "Phthalates" = "#faba39",        # Vivid red
      "Alkylphenols" = "#770000",      # Strong green
      "Metallic elements" = "#B12090FF"      # Strong green
    )) +
  #scale_fill_manual(values = Color_real_FN5) +
  facet_wrap(~FN) +
  labs(#title = "Concentrations of organic compounds in fishing net extracts",
       #subtitle = "Values corrected by average blank (n = 4) subtraction\n",
       x = "State of the FNs", 
       y = "Average concentration (µg/L)", 
       fill = "Organic compounds") +
  theme_bw() +
  theme(axis.title.x = element_text(size = 18, face = "bold", vjust = -4, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.title.y = element_text(size = 18, face = "bold", vjust = 4, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.text.x = element_text(size = 15, face = "bold"),
        axis.text.y = element_text(size = 15, face = 'bold'),
        title = element_text(size = 18, face = "bold", margin = margin(t = 0, r = 0, b = 20, l = 0)),
        strip.text = element_text(face = "bold", size = rel(1.5)),
        strip.background = element_rect(fill = "grey", color = "grey", linewidth = 0.1),
        legend.title= element_text(size = 18, face = "bold", vjust = 1, margin = margin(t = 0, r = 5, b = 10, l = 0)),
        legend.text = element_text(size = 18),
        legend.spacing.x = unit(0.5, 'cm'),
        legend.spacing.y = unit(0.5, 'cm'),
        legend.key.spacing.y = unit(0.2, "cm"),
        legend.position="right",
        panel.spacing = unit(2, "lines"),
        plot.margin = unit(c(1, 1, 2, 1), "cm")) +
  guides(
    color = guide_legend(title = "Plastic chemical \ncategories", order = 1),
    shape = guide_legend(title = "Replicates", order = 2))
G_avg_corr_cat2

G_avg_corr_cat3 <- metal_orga %>% 
  #avg and sd with reframe
  group_by(FN, state, compounds) %>%
  reframe(
    n = n(),
    avg_corr = mean(values_corr, na.rm = T),
    sd_corr = sd(values_corr, na.rm = T)) %>%
  mutate(avg_corr = if_else(avg_corr <1, avg_corr+1, avg_corr),
         sd_corr = if_else(sd_corr <1, sd_corr+1, sd_corr)) %>%
  mutate(avg_corr_log = log10(avg_corr),
         sd_corr_log = log10(sd_corr)) %>%
  mutate(compounds = case_when(
      compounds == "AKP" ~ "Alkylphenols",
      compounds == "AKP_NP" ~ "Alkylphenols without Nonylphenols",
      compounds == "HAP" ~ "PAHs",
      compounds == "PBDE" ~ "PBDEs",
      compounds == "Phtalates" ~ "Phthalates",
      compounds == "Metals" ~ "Metallic elements",
      TRUE ~ compounds
      )) %>% 
  mutate(compounds = factor(compounds, levels = c(
      "PAHs", "PBDEs", "Phthalates", "Non phthalate plasticizers" ,"Alkylphenols", "Alkylphenols without Nonylphenols", "Metallic elements"))) %>%
  mutate(state = factor(state, levels = c("blank", "new", "EOL"))) %>%
  filter(compounds != "Alkylphenols without Nonylphenols", 
         #FN != "blank"
         ) %>%
  #mutate(compounds = if_else(compounds == "Alkylphenols without Nonylphenols", "Alkylphenols", compounds)) %>%
  ggplot(aes(x = FN, y = avg_corr, 
             fill = FN, 
             pattern = state, 
             #group = compounds
             )) + 
  # scale_y_log10(
  #   breaks = c(0.1, 1, 10, 100, 1000),          # Set your desired breaks
  #   labels = label_number(trim = TRUE)           # Remove scientific format
  # ) +
  geom_bar_pattern(stat = "identity", width = 0.5, position = position_dodge(width = 0.5), pattern_density = 0.1, 
                   pattern_fill = "white", pattern_color = "white", pattern_spacing = 0.015, show.legend = T) +
  scale_pattern_discrete(na.value = "none", 
                         choices = c("new" = "none", "EOL" = "stripe"), 
                         limits = c("new", "EOL")) +
  geom_errorbar(aes(ymin = avg_corr, ymax = if_else(avg_corr > 1, avg_corr + sd_corr, avg_corr)), 
                position = position_dodge(width = 0.5), linewidth = 1, width = 0.2) + 
  facet_wrap(~compounds, scales = "free_y") +
  #scale_fill_viridis_d(option = "turbo") +
  scale_fill_manual(values = Color_real_FN5) +
  labs(#title = "Concentrations of organic compounds in fishing net extracts",
       #subtitle = "Values corrected by average blank (n = 4) subtraction\n",
       x = "Fishing nets", 
       y = "Average concentration (µg/L)", 
       fill = "Fishing nets",
       pattern = "FN state") +
  theme_bw() +
  theme(axis.title.x = element_text(size = 18, face = "bold", vjust = -4, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.title.y = element_text(size = 18, face = "bold", vjust = 4, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.text.x = element_text(size = 15, face = "bold"),
        axis.text.y = element_text(size = 15, face = 'bold'),
        strip.text = element_text(face = "bold", size = rel(1.5)),
        #strip.background = element_rect(fill = "grey", color = "grey", linewidth = 0.1),
        legend.title= element_text(size = 18, face = "bold", vjust = 1, margin = margin(t = 0, r = 5, b = 10, l = 0)),
        legend.text = element_text(size = 18),
        legend.spacing.x = unit(0.5, 'cm'),
        legend.spacing.y = unit(0.5, 'cm'),
        legend.key.spacing.y = unit(0.2, "cm"),
        legend.position="right",
        #panel.spacing = unit(2, "lines"),
        plot.margin = unit(c(1, 1, 1, 1), "cm")) +
  rotate_x_text(angle = 30)
  #coord_flip()
G_avg_corr_cat3

tt_results_G <- tt_results %>%  dplyr::select(FN, compounds, diff) %>% 
  # duplicate each row exactly 2 times
  slice(rep(row_number(), each = 2)) %>% 
  # create the new variable with values "new" and "EOL"
  mutate(state = rep(c("new", "EOL"), times = nrow(tt_results))) %>% 
  mutate(diff = if_else(state == "new", "ns", diff)) %>% 
  mutate(compounds = case_when(
      compounds == "AKP" ~ "Alkylphenols",
      compounds == "AKP_NP" ~ "Alkylphenols without Nonylphenols",
      compounds == "HAP" ~ "PAHs",
      compounds == "PBDE" ~ "PBDEs",
      compounds == "Phtalates" ~ "Phthalates",
      compounds == "metals" ~ "Trace metals",
      TRUE ~ compounds
      ))
tt_results_G

results_vs_blank2 <- results_vs_blank %>%
mutate(stars = if_else(compounds == "AKP", "ns", stars)) %>%
  mutate(y_stars = case_when(
           compounds == "AKP" ~ 4900,
           compounds == "HAP" ~ 190,
           compounds == "PBDE" ~ 10,
           compounds == "Metals" ~ 2100,
           compounds == "Phthalates" ~ 3500,
           compounds == "Non phthalate plasticizers" ~ 200,
           TRUE ~ NA_real_)) %>% 
  mutate(compounds = case_when(
      compounds == "AKP" ~ "Alkylphenols",
      compounds == "AKP_NP" ~ "Alkylphenols without Nonylphenols",
      compounds == "HAP" ~ "PAHs",
      compounds == "PBDE" ~ "PBDEs",
      compounds == "Phtalates" ~ "Phthalates",
      compounds == "Metals" ~ "Metallic elements",
      TRUE ~ compounds
      )) %>% 
  mutate(stars = if_else(stars == "ns", NA, stars)) #%>% 
  #change order state
  mutate(state = factor(state, levels = c("blank", "new", "EOL")))

G_avg_corr_cat3 +
  #add letter stats with results_KW df
    geom_text(
    data = results_vs_blank2,
    aes(x = FN, y = y_stars, label = stars, color = state),
    position = position_dodge(width = 0.55),
    #hjust = -0.1,
    size = 5,
    color = "red4"
  ) +
  ggpubr::geom_bracket(
    data = tibble(
      compounds  = "PAHs",  # adapt to your facet name if needed
      xmin       = c(1.88, 2.88, 6.88),
      xmax       = c(2.12, 3.12, 7.12),
      y.position = c(35, 35, 170),
      label      = c("*", "*", "**")
    ),
    aes(xmin = xmin, xmax = xmax, y.position = y.position, label = label),
    size       = 1.06,
    label.size = 6,
    vjust      = 0.3,
    tip.length = c(0.02, 0.02),
    inherit.aes = FALSE
  ) +
  ggpubr::geom_bracket(
    data = tibble(
      compounds  = "Non phthalate plasticizers",  # adapt to your facet name if needed
      xmin       = c(6.88),
      xmax       = c(7.12),
      y.position = c(190),
      label      = c("*")
    ),
    aes(xmin = xmin, xmax = xmax, y.position = y.position, label = label),
    size       = 1.06,
    label.size = 6,
    vjust      = 0.3,
    tip.length = c(0.02, 0.02),
    inherit.aes = FALSE
  ) +
  ggpubr::geom_bracket(
    data = tibble(
      compounds  = "Metallic elements",  # adapt to your facet name if needed
      xmin       = c(6.88),
      xmax       = c(7.12),
      y.position = c(1850),
      label      = c("***")
    ),
    aes(xmin = xmin, xmax = xmax, y.position = y.position, label = label),
    size       = 1.06,
    label.size = 6,
    vjust      = 0.3,
    tip.length = c(0.02, 0.02),
    inherit.aes = FALSE
  ) 


```

```{r visualization by large categories orga + metals publi}

highlights <- metal_orga %>% 
  mutate(cat = if_else(compounds == "Metals", "Metals", "Organics")) %>%
  #avg and sd with reframe
  group_by(FN, state, cat) %>%
  reframe(
    n = n(),
    avg_corr = mean(values_corr, na.rm = T),
    sd_corr = sd(values_corr, na.rm = T)) %>%
  mutate(avg_corr = if_else(avg_corr <1, avg_corr+1, avg_corr),
         sd_corr = if_else(sd_corr <1, sd_corr+1, sd_corr))
highlights

G_avg_corr_cat3 <- metal_orga %>% 
  #avg and sd with reframe
  group_by(FN, state, compounds) %>%
  reframe(
    n = n(),
    avg_corr = mean(values_corr, na.rm = T),
    sd_corr = sd(values_corr, na.rm = T)) %>%
  mutate(avg_corr = if_else(avg_corr <1, avg_corr+1, avg_corr),
         sd_corr = if_else(sd_corr <1, sd_corr+1, sd_corr)) %>%
  mutate(avg_corr_log = log10(avg_corr),
         sd_corr_log = log10(sd_corr)) %>%
  mutate(compounds = case_when(
      compounds == "AKP" ~ "Alkylphenols",
      compounds == "AKP_NP" ~ "Alkylphenols without Nonylphenols",
      compounds == "HAP" ~ "PAHs",
      compounds == "PBDE" ~ "PBDEs",
      compounds == "Phtalates" ~ "Phthalates",
      compounds == "Metals" ~ "Metallic elements",
      TRUE ~ compounds
      )) %>% 
  mutate(compounds = factor(compounds, levels = c(
      "PAHs", "PBDEs", "Phthalates", "Non phthalate plasticizers" ,"Alkylphenols", "Alkylphenols without Nonylphenols", "Metallic elements"))) %>%
  mutate(state = factor(state, levels = c("blank", "new", "EOL"))) %>%
  filter(compounds != "Alkylphenols without Nonylphenols", 
         #FN != "blank"
         ) %>%
  #mutate(compounds = if_else(compounds == "Alkylphenols without Nonylphenols", "Alkylphenols", compounds)) %>%
  ggplot(aes(x = FN, y = avg_corr, 
             fill = FN, 
             pattern = state, 
             #group = compounds
             )) + 
  # scale_y_log10(
  #   breaks = c(0.1, 1, 10, 100, 1000),          # Set your desired breaks
  #   labels = label_number(trim = TRUE)           # Remove scientific format
  # ) +
  geom_bar_pattern(stat = "identity", width = 0.5, position = position_dodge(width = 0.5), pattern_density = 0.1, 
                   pattern_fill = "white", pattern_color = "white", pattern_spacing = 0.015, show.legend = T) +
  scale_pattern_discrete(na.value = "none", 
                         choices = c("new" = "none", "EOL" = "stripe"), 
                         limits = c("new", "EOL")) +
  geom_errorbar(aes(ymin = avg_corr, ymax = if_else(avg_corr > 1, avg_corr + sd_corr, avg_corr)), 
                position = position_dodge(width = 0.5), linewidth = 1, width = 0.2) + 
  facet_wrap(~compounds, scales = "free_y") +
  #scale_fill_viridis_d(option = "turbo") +
  scale_fill_manual(values = Color_real_FN5) +
  labs(#title = "Concentrations of organic compounds in fishing net extracts",
       #subtitle = "Values corrected by average blank (n = 4) subtraction\n",
       x = "Fishing nets", 
       y = "Average concentration (µg/L)", 
       fill = "Fishing nets",
       pattern = "FN state") +
  theme_bw() +
  theme(axis.title.x = element_text(size = 18, face = "bold", vjust = -4, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.title.y = element_text(size = 18, face = "bold", vjust = 4, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.text.x = element_text(size = 15, face = "bold"),
        axis.text.y = element_text(size = 15, face = 'bold'),
        strip.text = element_text(face = "bold", size = rel(1.5)),
        #strip.background = element_rect(fill = "grey", color = "grey", linewidth = 0.1),
        legend.title= element_text(size = 18, face = "bold", vjust = 1, margin = margin(t = 0, r = 5, b = 10, l = 0)),
        legend.text = element_text(size = 18),
        legend.spacing.x = unit(0.5, 'cm'),
        legend.spacing.y = unit(0.5, 'cm'),
        legend.key.spacing.y = unit(0.2, "cm"),
        legend.position="right",
        #panel.spacing = unit(2, "lines"),
        plot.margin = unit(c(1, 1, 1, 1), "cm")) +
  rotate_x_text(angle = 30)
  #coord_flip()
G_avg_corr_cat3

tt_results_G <- tt_results %>%  dplyr::select(FN, compounds, diff) %>% 
  # duplicate each row exactly 2 times
  slice(rep(row_number(), each = 2)) %>% 
  # create the new variable with values "new" and "EOL"
  mutate(state = rep(c("new", "EOL"), times = nrow(tt_results))) %>% 
  mutate(diff = if_else(state == "new", "ns", diff)) %>% 
  mutate(compounds = case_when(
      compounds == "AKP" ~ "Alkylphenols",
      compounds == "AKP_NP" ~ "Alkylphenols without Nonylphenols",
      compounds == "HAP" ~ "PAHs",
      compounds == "PBDE" ~ "PBDEs",
      compounds == "Phtalates" ~ "Phthalates",
      compounds == "metals" ~ "Metallic elements",
      TRUE ~ compounds
      )) %>% 
  filter(diff != "ns")
tt_results_G

results_vs_blank2 <- results_blc_FN %>%
  mutate(stars = if_else(compounds == "AKP", "ns", stars)) %>%
  mutate(stars = if_else(compounds == "Metals" & FN == "PBS δ60" & state == "EOL", "#", stars)) %>% #manual modif car results of wilcox
  mutate(y_stars = case_when(
           compounds == "AKP" ~ 4900,
           compounds == "HAP" ~ 190,
           compounds == "PBDE" ~ 10,
           compounds == "Metals" ~ 2100,
           compounds == "Phthalates" ~ 3500,
           compounds == "Non phthalate plasticizers" ~ 200,
           TRUE ~ NA_real_)) %>% 
  mutate(compounds = case_when(
      compounds == "AKP" ~ "Alkylphenols",
      compounds == "AKP_NP" ~ "Alkylphenols without Nonylphenols",
      compounds == "HAP" ~ "PAHs",
      compounds == "PBDE" ~ "PBDEs",
      compounds == "Phtalates" ~ "Phthalates",
      compounds == "Metals" ~ "Metallic elements",
      TRUE ~ compounds
      )) %>% 
  mutate(stars = if_else(stars == "ns", NA, stars)) %>% 
  #change order state
  mutate(state = factor(state, levels = c("blank", "new", "EOL")))
results_vs_blank2

G_avg_corr_cat3 +
  #add letter stats with results_KW df
    geom_text(
    data = results_vs_blank2,
    aes(x = FN, y = y_stars, label = stars, color = state),
    position = position_dodge(width = 0.8),
    #hjust = -0.1,
    size = 4,
    color = "red4"
  ) +
  ggpubr::geom_bracket(
    data = tibble(
      compounds  = "PAHs",  # adapt to your facet name if needed
      xmin       = c(3.88, 2.88, 6.88),
      xmax       = c(4.12, 3.12, 7.12),
      y.position = c(52, 35, 170),
      label      = c("*", "*", "**")
    ),
    aes(xmin = xmin, xmax = xmax, y.position = y.position, label = label),
    size       = 1.06,
    label.size = 6,
    vjust      = 0.3,
    tip.length = c(0.02, 0.02),
    inherit.aes = FALSE
  ) +
  ggpubr::geom_bracket(
    data = tibble(
      compounds  = "Non phthalate plasticizers",  # adapt to your facet name if needed
      xmin       = c(6.88),
      xmax       = c(7.12),
      y.position = c(190),
      label      = c("*")
    ),
    aes(xmin = xmin, xmax = xmax, y.position = y.position, label = label),
    size       = 1.06,
    label.size = 6,
    vjust      = 0.3,
    tip.length = c(0.02, 0.02),
    inherit.aes = FALSE
  ) +
  ggpubr::geom_bracket(
    data = tibble(
      compounds  = "Metallic elements",  # adapt to your facet name if needed
      xmin       = c(6.88),
      xmax       = c(7.12),
      y.position = c(1850),
      label      = c("***")
    ),
    aes(xmin = xmin, xmax = xmax, y.position = y.position, label = label),
    size       = 1.06,
    label.size = 6,
    vjust      = 0.3,
    tip.length = c(0.02, 0.02),
    inherit.aes = FALSE
  ) 


```


```{r visualization by large categories orga}

#orga alone without blank correction
df_no_corr <- data_corr_cat %>% 
  mutate(state = if_else(is.na(state), "blank", state)) %>%
  #avg and sd with reframe
  group_by(FN, state, compounds) %>%
  reframe(
    n = n(),
    avg_corr = mean(values, na.rm = T),
    sd_corr = sd(values, na.rm = T)) %>%
  mutate(avg_corr = if_else(avg_corr <1, avg_corr+1, avg_corr),
         sd_corr = if_else(sd_corr <1, sd_corr+1, sd_corr)) %>%
  mutate(avg_corr_log = log10(avg_corr),
         sd_corr_log = log10(sd_corr)) %>%
  mutate(compounds = case_when(
      compounds == "AKP" ~ "Alkylphenols",
      compounds == "AKP_NP" ~ "Alkylphenols without Nonylphenols",
      compounds == "HAP" ~ "PAHs",
      compounds == "PBDE" ~ "PBDEs",
      compounds == "Phtalates" ~ "Phthalates",
      compounds == "metals" ~ "Trace metals",
      TRUE ~ compounds
      )) %>% 
  mutate(compounds = factor(compounds, levels = c(
      "PAHs", "PBDEs", "Phthalates", "Alkylphenols", "Alkylphenols without Nonylphenols", "Trace metals"))) %>%
  mutate(state = factor(state, levels = c("blank", "new", "EOL"))) %>%
  filter(compounds != "Alkylphenols without Nonylphenols") 
df_no_corr

G_avg_corr_cat4 <- df_no_corr %>% ggplot(aes(x = FN, y = avg_corr, 
             fill = FN, 
             pattern = state, 
             #group = compounds
             )) + 
  # scale_y_log10(
  #   breaks = c(0.1, 1, 10, 100, 1000),          # Set your desired breaks
  #   labels = label_number(trim = TRUE)           # Remove scientific format
  # ) +
  geom_bar_pattern(stat = "identity", width = 0.5, position = position_dodge(width = 0.5), pattern_density = 0.1, 
                   pattern_fill = "white", pattern_color = "white", pattern_spacing = 0.015, show.legend = T) +
  scale_pattern_discrete(na.value = "none", 
                         choices = c("new" = "none", "EOL" = "stripe", "blank" = "circle"), 
                         limits = c("new", "EOL", "blank")) +
  geom_errorbar(aes(ymin = avg_corr, ymax = if_else(avg_corr > 1, avg_corr + sd_corr, avg_corr)), 
                position = position_dodge(width = 0.5), linewidth = 1, width = 0.2) + 
  facet_wrap(~compounds, scales = "free_y") +
  scale_fill_viridis_d(option = "turbo") +
  labs(#title = "Concentrations of organic compounds in fishing net extracts",
       #subtitle = "Values corrected by average blank (n = 4) subtraction\n",
       x = "Fishing nets", 
       y = "Average concentration (µg/L)", 
       fill = "Fishing nets", pattern = "Fishing net states") +
  theme_bw() +
  theme(axis.title.x = element_text(size = 18, face = "bold", vjust = -4, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.title.y = element_text(size = 18, face = "bold", vjust = 4, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.text.x = element_text(size = 15, face = "bold"),
        axis.text.y = element_text(size = 15, face = 'bold'),
        strip.text = element_text(face = "bold", size = rel(1.5)),
        #strip.background = element_rect(fill = "grey", color = "grey", linewidth = 0.1),
        legend.title= element_text(size = 18, face = "bold", vjust = 1, margin = margin(t = 0, r = 5, b = 10, l = 0)),
        legend.text = element_text(size = 18),
        legend.spacing.x = unit(0.5, 'cm'),
        legend.spacing.y = unit(0.5, 'cm'),
        legend.key.spacing.y = unit(0.2, "cm"),
        legend.position="right",
        #panel.spacing = unit(2, "lines"),
        plot.margin = unit(c(1, 1, 2, 1), "cm")) +
  rotate_x_text(angle = 30)
  #coord_flip()
G_avg_corr_cat4

# match names and states between tables
results_KW_lab <- results_KW_blc %>% 
  mutate(compounds = case_when(
      compounds == "AKP" ~ "Alkylphenols",
      compounds == "AKP_NP" ~ "Alkylphenols without Nonylphenols",
      compounds == "HAP" ~ "PAHs",
      compounds == "PBDE" ~ "PBDEs",
      compounds == "Phtalates" ~ "Phthalates",
      compounds == "metals" ~ "Trace metals",
      TRUE ~ compounds
      )) %>% 
  mutate(y_top = case_when(
      compounds == "PAHs" ~ 175,
      compounds == "PBDEs" ~ 11.5,
      compounds == "Phthalates" ~ 3700,
      compounds == "Alkylphenols" ~ 5000,
      compounds == "Trace metals" ~ 250,
      TRUE ~ NA_real_
  )) %>% 
  #delete lables all similar 
  mutate(label = case_when(
      compounds == "PBDEs" ~ NA,
      compounds == "Phthalates" ~ NA,
      TRUE ~ label
    )) %>% 
  mutate(label = case_when(
      compounds == "Alkylphenols" ~ NA,
      TRUE ~ label
    )) %>% 
  #change order state
  mutate(state = factor(state, levels = c("blank", "new", "EOL"))) %>% 
  na.omit()
  
results_KW_lab

tt_results_G <- tt_results %>%  dplyr::select(FN, compounds, diff) %>% 
  # duplicate each row exactly 2 times
  slice(rep(row_number(), each = 2)) %>% 
  # create the new variable with values "new" and "EOL"
  mutate(state = rep(c("new", "EOL"), times = nrow(tt_results))) %>% 
  mutate(diff = if_else(state == "new", "ns", diff)) %>% 
  mutate(compounds = case_when(
      compounds == "AKP" ~ "Alkylphenols",
      compounds == "AKP_NP" ~ "Alkylphenols without Nonylphenols",
      compounds == "HAP" ~ "PAHs",
      compounds == "PBDE" ~ "PBDEs",
      compounds == "Phtalates" ~ "Phthalates",
      compounds == "metals" ~ "Trace metals",
      TRUE ~ compounds
      ))
tt_results_G

G_avg_corr_cat4 +
  #add letter stats with results_KW df
    geom_text(
    data = results_KW_lab,
    aes(x = FN, y = y_top+30, label = label, color = state),
    position = position_dodge(width = 0.9),
    hjust = -0.1,
    size = 5,
  ) +
  scale_color_manual(values = c("black", "red4")) + 
  guides(color = "none") +
  geom_bracket(aes(xmin = 2.88 , xmax= 3.12,
                           y.position = 55,
                           label = "*"),
               size = 1.1,
               label.size = 7,
               vjust = 0.3,
               tip.length = c(0.03, 0.03),
               data = subset(tt_results_G, compounds == "PAHs"),
               inherit.aes = FALSE
               ) +
  geom_bracket(aes(xmin = 3.88 , xmax= 4.12,
                             y.position = 55,
                             label = "*"),
                 size = 1.1,
                 label.size = 7,
                 vjust = 0.3,
                 tip.length = c(0.03, 0.03),
                 data = subset(tt_results_G, compounds == "PAHs"),
                 inherit.aes = FALSE
                 ) +
    geom_bracket(aes(xmin = 6.88 , xmax= 7.12,
                           y.position = 177,
                           label = "**"),
               size = 1.1,
               label.size = 7,
               vjust = 0.3,
               tip.length = c(0.03, 0.03),
               data = subset(tt_results_G, compounds == "PAHs"),
               inherit.aes = FALSE
               )

#orga alone with blank correction
df_corr_graph <- data_corr_cat %>% 
  mutate(state = if_else(is.na(state), "blank", state)) %>%
  #avg and sd with reframe
  group_by(FN, state, compounds) %>%
  reframe(
    n = n(),
    avg_corr = mean(values_corr, na.rm = T),
    sd_corr = sd(values_corr, na.rm = T)) %>%
  mutate(avg_corr = if_else(avg_corr <1, avg_corr+1, avg_corr),
         sd_corr = if_else(sd_corr <1, sd_corr+1, sd_corr)) %>%
  mutate(avg_corr_log = log10(avg_corr),
         sd_corr_log = log10(sd_corr)) %>%
  mutate(compounds = case_when(
      compounds == "AKP" ~ "Alkylphenols",
      compounds == "AKP_NP" ~ "Alkylphenols without Nonylphenols",
      compounds == "HAP" ~ "PAHs",
      compounds == "PBDE" ~ "PBDEs",
      compounds == "Phtalates" ~ "Phthalates",
      compounds == "metals" ~ "Trace metals",
      TRUE ~ compounds
      )) %>% 
  mutate(compounds = factor(compounds, levels = c(
      "PAHs", "PBDEs", "Phthalates", "Alkylphenols", "Alkylphenols without Nonylphenols", "Trace metals"))) %>%
  mutate(state = factor(state, levels = c("blank", "new", "EOL"))) %>%
  filter(compounds != "Alkylphenols without Nonylphenols", FN != "blank")
df_corr_graph
 
G_avg_corr_cat5 <-  df_corr_graph %>% ggplot(aes(x = FN, y = avg_corr, 
             fill = FN, 
             pattern = state, 
             #group = compounds
             )) + 
  # scale_y_log10(
  #   breaks = c(0.1, 1, 10, 100, 1000),          # Set your desired breaks
  #   labels = label_number(trim = TRUE)           # Remove scientific format
  # ) +
  geom_bar_pattern(stat = "identity", width = 0.5, position = position_dodge(width = 0.5), pattern_density = 0.1, 
                   pattern_fill = "white", pattern_color = "white", pattern_spacing = 0.015, show.legend = T) +
  scale_pattern_discrete(na.value = "none", 
                         choices = c("new" = "none", "EOL" = "stripe"), 
                         limits = c("new", "EOL")) +
  geom_errorbar(aes(ymin = avg_corr, ymax = if_else(avg_corr > 1, avg_corr + sd_corr, avg_corr)), 
                position = position_dodge(width = 0.5), linewidth = 1, width = 0.2) + 
  facet_wrap(~compounds, scales = "free_y") +
  scale_fill_viridis_d(option = "turbo") +
  labs(#title = "Concentrations of organic compounds in fishing net extracts",
       #subtitle = "Values corrected by average blank (n = 4) subtraction\n",
       x = "Fishing nets", 
       y = "Average concentration (µg/L)", 
       fill = "Fishing nets",
       pattern = "Fishing net states") +
  theme_bw() +
  theme(axis.title.x = element_text(size = 18, face = "bold", vjust = -4, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.title.y = element_text(size = 18, face = "bold", vjust = 4, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.text.x = element_text(size = 15, face = "bold"),
        axis.text.y = element_text(size = 15, face = 'bold'),
        strip.text = element_text(face = "bold", size = rel(1.5)),
        #strip.background = element_rect(fill = "grey", color = "grey", linewidth = 0.1),
        legend.title= element_text(size = 18, face = "bold", vjust = 1, margin = margin(t = 0, r = 5, b = 10, l = 0)),
        legend.text = element_text(size = 18),
        legend.spacing.x = unit(0.5, 'cm'),
        legend.spacing.y = unit(0.5, 'cm'),
        legend.key.spacing.y = unit(0.2, "cm"),
        legend.position="right",
        #panel.spacing = unit(2, "lines"),
        plot.margin = unit(c(1, 1, 2, 1), "cm")) +
  rotate_x_text(angle = 30)
  #coord_flip()
G_avg_corr_cat5

# match names and states between tables
results_KW_lab <- results_KW_nblc %>% 
  mutate(compounds = case_when(
      compounds == "AKP" ~ "Alkylphenols",
      compounds == "AKP_NP" ~ "Alkylphenols without Nonylphenols",
      compounds == "HAP" ~ "PAHs",
      compounds == "PBDE" ~ "PBDEs",
      compounds == "Phtalates" ~ "Phthalates",
      compounds == "metals" ~ "Trace metals",
      TRUE ~ compounds
      )) %>% 
  mutate(y_top = case_when(
      compounds == "Alkylphenols" ~ 4700,
      TRUE ~ NA_real_
  )) %>% 
  #delete lables all similar
  mutate(label = case_when(
      compounds == "PAHs" ~ NA,
      TRUE ~ label
    )) %>%
  mutate(label = case_when(
      compounds == "Alkylphenols" & state == "new" ~ NA,
      TRUE ~ label
    )) %>%
  #change order state
  mutate(state = factor(state, levels = c("blank", "new", "EOL"))) %>% 
  na.omit()
  
results_KW_lab

tt_results_G <- tt_results %>%  dplyr::select(FN, compounds, diff) %>% 
  # duplicate each row exactly 2 times
  slice(rep(row_number(), each = 2)) %>% 
  # create the new variable with values "new" and "EOL"
  mutate(state = rep(c("new", "EOL"), times = nrow(tt_results))) %>% 
  mutate(diff = if_else(state == "new", "ns", diff)) %>% 
  mutate(compounds = case_when(
      compounds == "AKP" ~ "Alkylphenols",
      compounds == "AKP_NP" ~ "Alkylphenols without Nonylphenols",
      compounds == "HAP" ~ "PAHs",
      compounds == "PBDE" ~ "PBDEs",
      compounds == "Phtalates" ~ "Phthalates",
      compounds == "metals" ~ "Trace metals",
      TRUE ~ compounds
      ))
tt_results_G

G_avg_corr_cat5 +
  #add letter stats with results_KW df
  #   geom_text(
  #   data = results_KW_lab,
  #   aes(x = FN, y = y_top, label = label, color = state),
  #   position = position_dodge(width = 0.5),
  #   size = 5,
  # ) +
  scale_color_manual(values = c("black", "red4")) + 
  guides(color = "none") +
  geom_bracket(aes(xmin = 1.88 , xmax= 2.12,
                           y.position = 50,
                           label = "*"),
               size = 1.1,
               label.size = 7,
               vjust = 0.3,
               tip.length = c(0.03, 0.03),
               data = subset(tt_results_G, compounds == "PAHs"),
               inherit.aes = FALSE
               ) +
  geom_bracket(aes(xmin = 2.88 , xmax= 3.12,
                             y.position = 50,
                             label = "*"),
                 size = 1.1,
                 label.size = 7,
                 vjust = 0.3,
                 tip.length = c(0.03, 0.03),
                 data = subset(tt_results_G, compounds == "PAHs"),
                 inherit.aes = FALSE
                 ) +
    geom_bracket(aes(xmin = 5.88 , xmax= 6.12,
                           y.position = 167,
                           label = "**"),
               size = 1.1,
               label.size = 7,
               vjust = 0.3,
               tip.length = c(0.03, 0.03),
               data = subset(tt_results_G, compounds == "PAHs"),
               inherit.aes = FALSE
               )

```

Compounds also found in leachates:
ATBC
DEP


Compounds not in new FN extracts (5/34):
benzo[b+k]fluoranthene
dibenzoahanthracene
BDE 100
BDE 153
BDE 183


Compounds not in EOL FN extracts (5/34):
benzothiophene
fluorene
indeno123cdpyrene
dibenzoahanthracene
BDE 28

```{r compounds insides}
# Comprehensive table of plastic-related compounds
inside_compounds <- tibble(
  CompoundName = c(
    "Naphthalene", "Benzothiophene", "Biphenyl", "Acenaphthylene", "Acenaphthene",
    "Fluorene", "Dibenzothiophene", "Phenanthrene", "Anthracene", "Fluoranthene",
    "Pyrene", "Benzo[a]anthracene", "Chrysene", "Benzo[b+k]fluoranthene", "Benzo[a]pyrene",
    "Indeno[1,2,3-cd]pyrene", "Dibenzo[a,h]anthracene", "Benzo[ghi]perylene",
    "BDE 28", "BDE 47", "BDE 100", "BDE 99", "BDE 154", "BDE 153", "BDE 183",
    "DMP", "DEP", "DBP", "BBP", "DEHA", "DEHP", "ATBC", "4-tOP", "Nonylphenols"
  ),
  MainUse = c(
    rep("Contaminant from combustion processes, coal tar, petroleum products", 18),
    rep("Flame retardant additive in plastics, electronics, textiles, and furniture foam", 7),
    "Plasticizer for cellulose acetate, vinyl resins, and other polymers",
    "Plasticizer for cellulose acetate, PVC, and other polymer applications",
    "Plasticizer for PVC, cellulose esters, synthetic rubber, and adhesives",
    "Plasticizer for PVC, vinyl flooring, wall coverings, and consumer products",
    "Plasticizer for PVC and other polymers; alternative to phthalates",
    "Primary plasticizer for PVC; most widely used phthalate plasticizer",
    "Non-phthalate plasticizer for PVC; eco-friendly alternative",
    "Antioxidant and stabilizer in rubber and plastic manufacturing; surfactant",
    "Surfactant production; antioxidant in rubber and plastics; resin modifier"
  ),
  Classification = c(
    rep("Priority pollutant (US EPA); persistent organic pollutant; combustion/industrial origin", 6),
    "Environmental contaminant; petroleum and combustion origin",
    rep("Priority pollutant (US EPA); persistent organic pollutant; combustion/industrial origin", 11),
    rep("Stockholm Convention POP candidate; banned/restricted flame retardant; industrial origin", 7),
    "REACH Candidate List substance; reproductive toxin; industrial additive origin",
    "REACH Candidate List substance; reproductive toxin; industrial additive origin",
    "REACH Candidate List substance; reproductive toxin; banned in toys; industrial origin",
    "REACH Candidate List substance; reproductive toxin; banned in toys; industrial origin",
    "Environmental contaminant; industrial additive origin",
    "REACH Candidate List substance; reproductive toxin; banned in toys; industrial origin",
    "Non-classified; considered safer alternative plasticizer; industrial additive origin",
    "Priority substance (EU WFD); endocrine disruptor; industrial origin",
    "Priority hazardous substance; endocrine disruptor; restricted use; industrial origin"
  ),
  Hazard = c(
    "Carcinogenic; toxic to aquatic organisms; bioaccumulative; mutagenic",
    "Moderately toxic to aquatic organisms; potential carcinogen",
    "Toxic to aquatic organisms; endocrine disruptor; bioaccumulative",
    "Carcinogenic; toxic to aquatic organisms; bioaccumulative; mutagenic",
    "Moderately toxic to aquatic organisms; suspected carcinogen",
    "Toxic to aquatic organisms; suspected carcinogen; bioaccumulative",
    "Moderately toxic to aquatic organisms; potential endocrine disruptor",
    "Carcinogenic; toxic to aquatic organisms; bioaccumulative; mutagenic",
    "Carcinogenic; toxic to aquatic organisms; bioaccumulative; phototoxic",
    "Carcinogenic; highly toxic to aquatic organisms; bioaccumulative; mutagenic",
    "Carcinogenic; highly toxic to aquatic organisms; bioaccumulative; mutagenic",
    "Carcinogenic; highly toxic to aquatic organisms; bioaccumulative; mutagenic",
    "Carcinogenic; highly toxic to aquatic organisms; bioaccumulative; mutagenic",
    "Carcinogenic; highly toxic to aquatic organisms; bioaccumulative; mutagenic",
    "Highly carcinogenic; highly toxic to aquatic organisms; bioaccumulative; mutagenic",
    "Probable carcinogen; highly toxic to aquatic organisms; bioaccumulative; mutagenic",
    "Carcinogenic; highly toxic to aquatic organisms; bioaccumulative; mutagenic",
    "Probable carcinogen; highly toxic to aquatic organisms; bioaccumulative; mutagenic",
    rep("Endocrine disruptor; thyroid hormone disruptor; neurotoxic; bioaccumulative; persistent", 7),
    "Reproductive toxin; endocrine disruptor; developmental toxin; aquatic toxicity",
    "Reproductive toxin; endocrine disruptor; developmental toxin; aquatic toxicity",
    "Reproductive toxin; anti-androgenic; developmental toxin; aquatic toxicity; banned in toys",
    "Reproductive toxin; anti-androgenic; carcinogenic; developmental toxin; high aquatic toxicity; banned in toys",
    "Lower toxicity than phthalates; minimal reproductive effects; aquatic toxicity",
    "Reproductive toxin; anti-androgenic; carcinogenic; developmental toxin; high aquatic toxicity; banned in toys",
    "Lower toxicity profile; considered safer alternative; minimal reproductive effects",
    "Endocrine disruptor; estrogenic activity; toxic to aquatic organisms; bioaccumulative; restricted use",
    "Strong endocrine disruptor; estrogenic activity; highly toxic to aquatic organisms; bioaccumulative; priority hazardous substance"
  ))

inside_compounds

#export excel
# library(writexl)
# write_xlsx(inside_compounds, "inside_compounds.xlsx")
```

```{r leaching kinetics}
Op_time_FN <- rep(c(650, 2700, 2700, 624, 624, 624, 624, 12700, 
                       0, 0, 0, 0, 0, 0, 0, 0), each = 5)
Op_time_FN

avg_metal_orga_FN <- metal_orga %>% 
  group_by(FN, state, compounds) %>%
  reframe(
    n = n(),
    avg_corr = mean(values_corr, na.rm = T),
    sd_corr = sd(values_corr, na.rm = T)) %>% 
  filter(FN != "blank") %>% 
  arrange(state, FN) %>% 
  mutate(Op_time = Op_time_FN)
avg_metal_orga_FN

avg_metal_orga <- metal_orga %>% 
  filter(FN != "blank") %>% 
  mutate(Op_time = case_when(
    FN == "PA α35" & state == "EOL" ~ 650,
    FN == "PA β33" & state == "EOL" ~ 2700,
    FN == "PA β95" & state == "EOL" ~ 2700,
    FN == "PA γ33" & state == "EOL" ~ 624,
    FN == "PA γ60" & state == "EOL" ~ 624,
    FN == "PBS δ35" & state == "EOL" ~ 624,
    FN == "PBS δ60" & state == "EOL" ~ 624,
    FN == "PE-PP ε4.25" & state == "EOL" ~ 624,
    TRUE ~ 0
  )) %>% 
  group_by(state, Op_time, compounds) %>%
  reframe(
    n = n(),
    avg_corr = mean(values_corr, na.rm = T),
    sd_corr = sd(values_corr, na.rm = T))  
avg_metal_orga


G_leach_kinetics <- avg_metal_orga_FN %>%
  ggplot(aes(x = Op_time, y = avg_corr, 
             color = compounds, 
             group = interaction(compounds))) + 
  geom_point(size = 4) +
  geom_line(linewidth = 1) +
  # scale_y_log10(
  #   breaks = c(0.1, 1, 10, 100, 1000),          # Set your desired breaks
  #   labels = label_number(trim = TRUE)           # Remove scientific format
  # ) +
  facet_wrap(~FN, scales = "free") +
  labs(title = "Leaching kinetics of plastic-associated compounds from fishing nets",
       x = "State of the FNs", 
       y = "Average concentration (µg/L)", 
       color = "Plastic chemical categories",
       shape = "Fishing nets") +
  theme_bw() +
  theme(axis.title.x = element_text(size = 18, face = "bold", vjust = -4, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.title.y = element_text(size = 18, face = "bold", vjust = 4, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.text.x = element_text(size = 15, face = "bold"),
        axis.text.y = element_text(size = 15, face = 'bold'),
        title = element_text(size = 18, face = "bold", margin = margin(t = 0, r = 0, b = 20, l = 0)),
        legend.title= element_text(size = 18, face = "bold", vjust = 1, margin = margin(t = 0, r = 5, b = 10, l = 0)),
        legend.text = element_text(size = 18),
        legend.spacing.x = unit(0.5, 'cm'),
        legend.spacing.y = unit(0.5, 'cm'),
        legend.key.spacing.y = unit(0.2, "cm"),
        legend.position="right",
        panel.spacing = unit(2, "lines"),
        plot.margin = unit(c(1, 1, 2, 1), "cm"))
G_leach_kinetics  
  
```
