---
title: "Heart_Rate"
author: "Edgar Dusacre"
date: "2023-03-21"
output: html_document
editor_options: 
  chunk_output_type: console
---
```{r Insertion package, include=FALSE}
library(ggplot2) 
library(tidyr)
library(purrr)
library(tidyverse)
library(ggrepel)
library(ggpubr)
library(knitr)
library(yaml)
library(dplyr) 
library(matrixStats)
library(EnvStats)
library(stringr)
library(gtable)
library(grid)
library(FSA)
library(scales)
library(wbstats)
library(ggh4x)
library(multcompView)
library(report)
library(ecotox)
library(wesanderson)
library(RColorBrewer)
library(readr)
library(readxl)
library(gmodels)
library(ggpattern)
library(zoo)
library(forcats)
library(car)
library(dunn.test)


library(forcats)
library(binom)
library(lubridate)
library(ade4)
library(broom)
library(rstatix)
library(rcompanion)
library(chron)
library(PMCMRplus)

```



```{r Charger les palettes de couleurs, include=FALSE}
Plasfito_C <- c("#80CAD0", "#36A7A7", "#276573", "#054959","#E3CCC0", "#F7EAE1", "#A48A7B", "#C6AF8D", "#49BED3", "#256CB4", "#008163", "#44B494", "#7BC6B9")

Plasfito_color <- c("GreenP4" = "#80CAD0", "GreenP3" = "#36A7A7", "GreenP2" = "#276573", "GreenP1" = "#054959","Brown1" = "#E3CCC0", "Brown2" = "#F7EAE1", "Brown3" = "#A48A7B", "Brown4" = "#C6AF8D", "Turquoise1" = "#49BED3", "Blue1" = "#256CB4", "Green1" = "#008163", "Green2" = "#44B494", "Green3" = "#7BC6B9")

List_color_Fr <- c("Mimizan" = "#008163" , "Bayonne" = "#44B494", "Hendaye" = "#7BC6B9", 
                   "Capbretons"  = "#80CAD0", "Arcachon" = "#36A7A7", "St_Jean" = "#276573")

List_color <- c("Mimizan" = "#008163" , "Bayonne" = "#44B494", "Hendaye" = "#7BC6B9", 
                 "Capbretons"  = "#80CAD0", "Arcachon" = "#36A7A7", "St_Jean" = "#276573",
                 "Euskadi" = "#054959")

Plasfito_Tps <- c("5" = "#80CAD0", "15" = "#36A7A7", "30" = "#276573")


#A part si vous souhaitez changer les couleurs do not touch.
Ech_K2CR2O7<- c("K2CR2O7" = "#80CAD0")

Tps_color <- c("5" = "#80CAD0" , "15" = "#36A7A7", "30" = "#276573")

Dilu_color <- c("0.0125" = "#80CAD0" , "0.025" = "#36A7A7", "0.05" = "#276573", "0.1" = "#008163")

Conc_color <- c("0.4125" = "#80CAD0" , "0.825" = "#36A7A7", "1.65" = "#276573", "3.3" = "#008163")
Conc_color3 <- c("0.825" = "aquamarine", "1.65" = "#36A7A7", "3.3" = "#276573")

Color_biolu_Pasaia <- c("Ech1" = "aquamarine", "Ech2" = "#36A7A7" , "DMSO" = "#A48A7B")

Color_real_FN <- c("dmso" = "#A48A7B", "ctl H2O" = "#256CB4", "pa_a33" = "#4fd355", "pa_b33" = "#ca98d3", "pa_b95" = "#6e217c", "pa_g33" = "#92b78f", "pa_g60" = "#bbb3bc", "pbs_d35" = "#d3ad4f","pbs_d60" = "#c68640", "pe_e4.25" = "#36A7A7")

Color_state <- c("Solvent ctl" = "#A48A7B", "ctl H2O" = "#256CB4", "new" = "aquamarine", "used" = "#36A7A7")

Color_real_FN <- c("Solvent control" = "#A48A7B", "ctl H2O" = "#256CB4", "PA α ø.35" = "#4fd355", "PA β ø.33" = "#ca98d3", "PA β ø.95" = "#6e217c", "PA γ ø.33" = "#92b78f", "PA γ ø.60" = "#bbb3bc", "PBS δ ø.35" = "#d3ad4f","PBS δ ø.60" = "#c68640", "HPPE ε ø4.25" = "#36A7A7")

Color_real_FN4 <- c("Solvent control" = "#A48A7B", "ctl H2O" = "#256CB4", "PA6 α 35" = "#4fd355", "PA6 β 33" = "#ca98d3", "PA6 β 95" = "#6e217c", "PA6 γ 33" = "#92b78f", "PA6 γ 60" = "#bbb3bc", "PBS-PBAT δ 35" = "#d3ad4f","PBS-PBAT δ 60" = "#c68640", "HPPE-PP ε 4.25" = "#36A7A7")

Color_real_FN3 <- c("ctl" = "#A48A7B", "ctl H2O" = "#256CB4", "pa_a35" = "#4fd355", "pa_b33" = "#ca98d3", "pa_b95" = "#6e217c", "pa_g33" = "#92b78f", "pa_g60" = "#bbb3bc", "pbs_d35" = "#d3ad4f","pbs_d60" = "#c68640", "pe_e4.25" = "#36A7A7", "hppe_e425" = "#36A7A7")

Color_real_FN2 <- c("ctl" = "#A48A7B", "ctl H2O" = "#256CB4", "PA_a35" = "#4fd355", "PA_b33" = "#ca98d3", "PA_b95" = "#6e217c", "PA_g33" = "#92b78f", "PA_g60" = "#bbb3bc", "PBS_d35" = "#d3ad4f","PBS_d60" = "#c68640", "PE_e4.25" = "#36A7A7", "HPPE_e425" = "#36A7A7")

Color_real_FN5 <- c("DMSO\ncontrol" = "#A48A7B", "ctl H2O" = "#256CB4", "PA α35" = "#4fd355", "PA β33" = "#ca98d3", "PA β95" = "#6e217c", "PA γ33" = "#92b78f", "PA γ60" = "#bbb3bc", "PBS δ35" = "#d3ad4f","PBS δ60" = "#c68640", "PE-PP ε4.25" = "#36A7A7")
```


```{r fct n}
stat_box_data <- function(y, upper_limit = max(BPM_ajusted$ajusted_BPM) * 1.15) {
  return( 
    data.frame(
      y = 0.95 * upper_limit,
      label = paste('n =', length(y), '\n',
                    'mean =', round(mean(y), 1), '\n')
    )
  )
}

stat_box_data <- function(y, lower_limit = min(BPM_ajusted$ajusted_BPM) * 1.15) {
  return( 
    data.frame(
      y = 0.95 * lower_limit,
      label = paste('n =', length(y))
    )
  )
}
```

```{r data import}
HR_DMSO_n <- read_excel("Hearth rate/HR_analysis_122022_bis.xlsx") %>% 
  rename(N = BPS_n) %>% 
  select(-BPS_se, -BPM_se, -BPM_n) %>% 
  mutate(state = "new",
         ID = if_else(FN == "pbs_d60_n" & ID == "benzo", "l1", ID),
         FN = if_else(FN == "benzo" & ID == "m3", "pbs_d35", FN)) %>% 
  filter(FN != "dmso" | Hole != "1" | Subject != "S02",
         FN != "dmso" | Hole != "3" | Subject != "S03",
         FN != "dmso" | Hole != "4" | Subject != "S03",
         FN != "dmso" | Hole != "1" | Subject != "S01")
HR_DMSO_n

HR_DMSO_n$FN <- gsub("_n", "", HR_DMSO_n$FN)

HR_DMSO_u <- read_excel("Hearth rate/HR_analysis_bis.xlsx") %>% 
  rename(N = BPS_n) %>% 
  select(-BPS_se, -BPM_se, -BPM_n)%>% 
  mutate(state = "used") %>% 
  filter(FN != "blc", FN != "ph4_14", FN != "ph7_23")
HR_DMSO_u

HR_DMSO_u$FN <- gsub("_u", "", HR_DMSO_u$FN)

HR_dmso_tot <- rbind(HR_DMSO_n, HR_DMSO_u) 
HR_dmso_tot


```

```{r DMSO}
HR_dmso <-HR_dmso_tot  %>% filter(FN == "dmso")
HR_dmso

HR_dmso %>%
  ggplot(aes(x = FN, y = BPM, fill=state)) +
  geom_boxplot(notch = F)+
  theme_minimal()+
  labs(y = "Rythme cardiaque (BPM)",
       title = "Comparaison des dmso")+
  theme(axis.title.x = element_blank())+
  annotate(geom="text", x= "dmso", y=40, label="n=18        n=20",
           color="black", parse = F, size = 3)+
  annotate(geom="text", x="dmso", y=230, label="a                                                                                  a",
           color="black", parse = F, size = 3)

```

```{r Mean comparison  dmso}
dmso_avg <- HR_dmso %>% 
  group_by(state, FN) %>% 
  summarise(n = n(),
            mean = mean(BPM), 
            sd = sd(BPM),
            se = sd/sqrt(n))
dmso_avg

dmso_ctl_n <- dmso_avg %>% filter(state == "new")
dmso_ctl_u <- dmso_avg %>% filter(state == "used")

```

```{r Normalisation des données autour du CTL}

HR_aju <- HR_dmso_tot %>% 
  filter(FN != "benzo") %>% 
  mutate(aju_HR = if_else(state == "new", (BPM * 100) / dmso_ctl_n$mean, 
                              if_else(state == "used", (BPM * 100) / dmso_ctl_u$mean, NA)))
HR_aju

#export data
# library(writexl)
# write_xlsx(HR_aju, "HR_aju_ibr.xlsx")

df_avg_HR <- HR_aju %>% 
  group_by(FN, state) %>% 
  summarise(n = n(),
            avg_HR_adj = mean(aju_HR, na.rm = T), 
            sd_HR_adj = sd(aju_HR, na.rm = T),
            se_HR_adj = sd_HR_adj/sqrt(n)) 

df_avg_HR

#export as csv
#write.csv(df_avg_HR, "C:/Users/edusacre/ownCloud/PhD/SCIENCES/Manips/Tox/PCA_tables_dmso/Avg_HR.csv")

```

Here, we have 3 sets of hypotheses
▶ H0: The age of the fishing net has no effect on the Heart rates
(x n = x u = x ctl)
▶ HA: The age of the fishing net has an effect on the Heart rates
(x undergrad != x grad != x ctl)

▶ H0: The FN have no effect on the Heart rates
(x FN1 = x FN2 ...)
▶ HA: The FN have no effect on the Heart rates
(x FN1 = x FN2 ...)

▶ H0: The state has the same effect on the toxicity of the FN 
▶ HA: The state has not the same effect on the toxicity of the FN 

```{r toxicity score}

Tox_sco_HR <- df_avg_HR %>% 
  mutate(m_effect = if_else(FN == "pa_b33" & state == "used", abs(100-avg_HR_adj), 
                            if_else(FN == "pa_b95" & state == "used", abs(100-avg_HR_adj), 0)),
         score = m_effect/0.33*0.4) %>% 
  dplyr::select(FN, state, m_effect, score)
Tox_sco_HR

#export as csv
write.csv(Tox_sco_HR, "dmso_tox_score/Tox_sco_HR.csv")
  
IBR_HR <- HR_aju %>% 
  mutate(ID_IBR = paste(FN, state, sep = "_")) %>% 
  dplyr::select(FN, state, ID, ID_IBR, aju_HR)
IBR_HR

#export as csv
#windows: 
#write.csv(IBR_HR, "C:/Users/edusacre/ownCloud/PhD/SCIENCES/Manips/Tox/IBR_tables/IBR_HR.csv")

#mac
#write.csv(IBR_HR, "~/ownCloud/PhD/SCIENCES/Manips/Tox/IBR_tables/IBR_HR.csv")

```



```{r statistics General}
#test ANOVA
#H0= toute les moyennes sont égales
#H1= au moins une des moyennes est différente des autres

Aov <- HR_aju %>% filter(state == "n" | state == "Solvent ctl")

res <- aov(aju_HR ~ state * FN, data = HR_aju)
summary(res)

#H0 = distribution normale 
#H1 = pas de distribution normale
shapiro.test(res$residuals) #p-value > 0.05 donc H0 cannot be rejected 

#Homogeneite des variances
#H0 = les deux variances sont egales
#H1 = les deux variances ne sont pas egales
leveneTest(aju_HR ~ state * FN, data = HR_aju) 
#p-value < 0.05, HO est rejetee
```


```{r statistics New general}
New <- HR_aju %>% filter(state == "new" | state == "Solvent ctl", FN != "benzo") %>% mutate_if(is.character, as.factor)
New
#condition non respectee donc test de kruskal
KW <- kruskal.test(aju_HR~FN, New)
KW

MWU_res_n <- PMCMRplus::kwAllPairsDunnTest(aju_HR~FN, New, p.adjust.method = "holm")
MWU_res_n

#Letters

df_pval =  MWU_res_n$p.value
df_pval

df_pval2 = fullPTable(df_pval)
df_pval2

Lett <- multcompLetters(df_pval2)
Wlett <- as.vector(unlist(Lett$Letters))

label_n <- data.frame(label = Wlett)
label_n

max_values <- New %>%
  group_by(FN) %>%
  summarize(max_value = max(aju_HR, na.rm = F))
max_values

Star_dmso <- as_tibble(df_pval2, rownames = "FN") %>% 
  dplyr::select(FN, dmso) %>% 
  mutate(diff = if_else(dmso == 1 & FN == "dmso", NA,
                        if_else(dmso >= 0.05, "ns",
                                if_else(dmso < 0.0001, "####",
                                        if_else(dmso < 0.001, "###",
                                                if_else(dmso < 0.01, "##",
                                                      if_else(dmso < 0.05, "#", NA)))))))
Star_dmso

MWU_n_Lett_New <- cbind(max_values, label_n, diff = Star_dmso$diff, state = c("new")) %>% 
  mutate(FN = if_else(grepl("pa_g60", FN), "PA \u03B360",
                      if_else(grepl("pa_g33", FN), "PA \u03B333",
                                       if_else(grepl("pbs_d60", FN), "PBS \u03B460",
                                               if_else(grepl("pbs_d35", FN), "PBS \u03B435",
                                                       if_else(grepl("pe_e4.25", FN), "PE-PP \u03B54.25",
                                                               if_else(grepl("pa_b95", FN), "PA \u03B295",
                      if_else(grepl("pa_b33", FN), "PA \u03B233",
                              if_else(grepl("pa_a33", FN), "PA \u03B135", 
                                      if_else(grepl("dmso", FN), "Control", FN))))))))))
MWU_n_Lett_New
```


```{r statistics Used general}
Used <- HR_aju %>% filter(state == "used" | state == "Solvent ctl", FN != "benzo") %>% mutate_if(is.character, as.factor)
Used

#condition non respectee donc test de kruskal
KW <- kruskal.test(aju_HR~FN, Used)
KW

MWU_res_n <- PMCMRplus::kwAllPairsDunnTest(aju_HR~FN, Used, p.adjust.method = "holm")
MWU_res_n

#Letters

df_pval =  MWU_res_n$p.value
df_pval

df_pval2 = fullPTable(df_pval)
df_pval2

Lett <- multcompLetters(df_pval2)
Wlett <- as.vector(unlist(Lett$Letters))

label_n <- data.frame(label = Wlett)
label_n

max_values <- Used %>%
  group_by(FN) %>%
  summarize(max_value = max(aju_HR, na.rm = F))
max_values

Star_dmso <- as_tibble(df_pval2, rownames = "FN") %>% 
  dplyr::select(FN, dmso) %>% 
  mutate(diff = if_else(dmso == 1 & FN == "dmso", NA,
                        if_else(dmso >= 0.05, "ns",
                                if_else(dmso < 0.0001, "####",
                                        if_else(dmso < 0.001, "###",
                                                if_else(dmso < 0.01, "##",
                                                      if_else(dmso < 0.05, "#", NA)))))))
Star_dmso

MWU_n_Lett_Used <- cbind(max_values, label_n, diff = Star_dmso$diff, state = c("used")) %>% 
  mutate(FN = if_else(grepl("pa_g60", FN), "PA \u03B360",
                      if_else(grepl("pa_g33", FN), "PA \u03B333",
                                       if_else(grepl("pbs_d60", FN), "PBS \u03B460",
                                               if_else(grepl("pbs_d35", FN), "PBS \u03B435",
                                                       if_else(grepl("pe_e4.25", FN), "PE-PP \u03B54.25",
                                                               if_else(grepl("pa_b95", FN), "PA \u03B295",
                      if_else(grepl("pa_b33", FN), "PA \u03B233",
                              if_else(grepl("pa_a33", FN), "PA \u03B135", 
                                      if_else(grepl("dmso", FN), "Control", FN))))))))))
MWU_n_Lett_Used

MWU_n_Lett <- bind_rows(MWU_n_Lett_New, MWU_n_Lett_Used)
MWU_n_Lett

```


```{r statistic FN U vs N}
#MU test FN u vs n---------------

df_list <- HR_aju %>%
  group_split(FN)

results <- list()

for (i in seq_along(df_list)) {
  df_sub <- df_list[[i]]
  states <- unique(df_sub$state)
  for (j in 1:(length(states) - 1)) {
    for (k in (j + 1):length(states)) {
      sample1 <- df_sub[df_sub$state == states[j], "BPM"]$BPM
      sample2 <- df_sub[df_sub$state == states[k], "BPM"]$BPM
      test_result <- wilcox.test(sample1, sample2, paired = FALSE)
      result <- tibble(
        FN = df_sub$FN[1],
        vs = paste(states[j], states[k], sep = "_vs_"),
        p_value = test_result$p.value,
        W = test_result$statistic)
      results <- c(results, list(result))}}}

results_MU <- bind_rows(results) %>% 
  mutate(p_value = if_else(is.na(p_value), 0, p_value)) %>%  
  na.omit() %>% 
  separate(vs, into = c("state1", "state2"), sep = "_vs_", remove = T) %>% 
  mutate(diff = if_else(p_value < 0.0001, "****", 
                        if_else(p_value < 0.001, "***",
                                if_else(p_value < 0.01, "**",
                                        if_else(p_value < 0.05, "*", "ns"))))) %>% 
  mutate(FN = if_else(grepl("pa_g60", FN), "PA \u03B360",
                      if_else(grepl("pa_g33", FN), "PA \u03B333",
                                       if_else(grepl("pbs_d60", FN), "PBS \u03B460",
                                               if_else(grepl("pbs_d35", FN), "PBS \u03B435",
                                                       if_else(grepl("pe_e4.25", FN), "HPPE \u03B54.25",
                                                               if_else(grepl("pa_b95", FN), "PA \u03B295",
                      if_else(grepl("pa_b33", FN), "PA \u03B233",
                              if_else(grepl("pa_a33", FN), "PA \u03B135", 
                                      if_else(grepl("dmso", FN), "DMSO\ncontrol", FN))))))))))
results_MU

r1 <- results_MU %>% dplyr::select(FN, state1, p_value, W, diff) %>% rename(state = state1)
r2 <- results_MU %>% dplyr::select(FN, state2, p_value, W, diff) %>% rename(state = state2)

res_sign <- bind_rows(r1, r2) %>% 
  arrange(FN) 
res_sign



```

```{r plot publi}
Dead_1 <- HR_aju %>% 
  mutate(FN = if_else(grepl("pa_g60", FN), "PA \u03B360",
                      if_else(grepl("pa_g33", FN), "PA \u03B333",
                                       if_else(grepl("pbs_d60", FN), "PBS \u03B460",
                                               if_else(grepl("pbs_d35", FN), "PBS \u03B435",
                                                       if_else(grepl("pe_e4.25", FN), "PE-PP \u03B54.25",
                                                               if_else(grepl("pa_b95", FN), "PA \u03B295",
                      if_else(grepl("pa_b33", FN), "PA \u03B233",
                              if_else(grepl("pa_a33", FN), "PA \u03B135", 
                                      if_else(grepl("dmso", FN), "DMSO\ncontrol", FN)))))))))) %>% 
  mutate(state = if_else(state == "used", "EOL", state)) %>% 
  mutate(state = factor(state, levels = c("new", "EOL"))) %>% 
  ggplot(aes(FN, aju_HR, fill = FN, pattern = state)) +
  geom_boxplot_pattern(width = 0.5, position = "dodge", pattern_density = 0.1, 
                   pattern_fill = "white", pattern_color = "white", pattern_spacing = 0.015, show.legend = T) +
  scale_pattern_discrete(na.value = "none", choices = c("new" = "none", "EOL" = "stripe"), 
                         limits = c("new", "EOL")) +
  scale_fill_manual(values = Color_real_FN5, guide = "none")+
  scale_y_continuous(limits = c(70, 155), breaks = seq(70, 155, by = 10)) +
  stat_summary(fun = mean, 
               geom = "point", 
               size = 2, 
               color = "red3", 
               position = position_dodge(width = 0.6)) +
  geom_hline(yintercept = 100, colour = "black", linetype = "dashed") +
  labs(x = "Fishing nets",
       y = "Heart rate (% of the DMSO control)",
       # title = expression(paste("Effect of FN extracts on the cardiac rhythm of ", italic("Oryzias latipes"), " larvae")),
       # subtitle = "Exposure time 48 hours \nMesoplastic eq. concentration 0.33 mg/ml\nDMSO dilution 1/1000",
       pattern = "FN State") +
  theme_bw() +
  theme(legend.position = "none") +
  theme(axis.title.x = element_text(size = 18, face = "bold", vjust = 0.5, margin = margin(t = 10, r = 20, b = 0, l = 0)),
        axis.title.y = element_text(size = 18, face = "bold", vjust = 3, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.text.x = element_text(size = 16, face = 'bold'),
        axis.text.y = element_text(size = 16, face = 'bold'),
        title = element_text(size = 22, face = "bold"),
        strip.text = element_text(face = "bold", size = rel(2)),
        legend.position = "right",
        legend.spacing.y = unit(0.3, 'cm'),
        legend.key.spacing.y = unit(0.3, 'cm'),
        legend.text = element_text(size = 12, face = 'bold', color = "black"),
        legend.key.size = unit(0.85, "cm"),
        legend.key.width = unit(1, "cm"),
        legend.title.align = 0,
        plot.margin = unit(c(1, 1, 1, 1), "cm")) +
  guides(pattern = guide_legend(byrow = TRUE))
Dead_1

Dead_1 + 
  geom_text(data = MWU_n_Lett %>% mutate(diff = if_else(diff == "ns", NA, diff)) %>% filter(FN != "Control"), aes(x = FN, y = 155, label = diff),
            size = 5, vjust = 0, color="red3", fontface = "bold",
            position = position_dodge(width=0.6),
            show.legend = FALSE,
            na.rm = F) +
  geom_bracket(aes(xmin = 8.88 , xmax= 9.12, 
                           y.position = 125,
                           label = "***"),
                       size = 1.2,
               label.size = 7,
                       data = subset(res_sign, FN == "HPPE ε4.25"),
               inherit.aes = FALSE) +
  geom_bracket(aes(xmin = 1.88 , xmax= 2.12, 
                           y.position = 135,
                           label = "*"),
                       size = 1.2,
               label.size = 7,
                       data = subset(res_sign, FN == "PA α35"),
               inherit.aes = FALSE) +
  geom_bracket(aes(xmin = 2.88 , xmax= 3.12, 
                           y.position = 146,
                           label = "***"),
                       size = 1.2,
               label.size = 7,
                       data = subset(res_sign, FN == "PA β33"),
               inherit.aes = FALSE) +
  geom_bracket(aes(xmin = 3.88 , xmax= 4.12, 
                           y.position = 147,
                           label = "**"),
                       size = 1.2,
               label.size = 7,
                       data = subset(res_sign, FN == "PA β95"),
               inherit.aes = FALSE) +
  geom_bracket(aes(xmin = 6.88 , xmax= 7.12, 
                           y.position = 130,
                           label = "**"),
                       size = 1.2,
               label.size = 7,
                       data = subset(res_sign, FN == "PBS δ35"),
               inherit.aes = FALSE) +
  geom_bracket(aes(xmin = 7.88 , xmax= 8.12, 
                           y.position = 132,
                           label = "*"),
                       size = 1.2,
               label.size = 7,
                       data = subset(res_sign, FN == "PBS δ60"),
               inherit.aes = FALSE) +
  geom_bracket(aes(xmin = 5.88 , xmax= 6.12, 
                           y.position = 132,
                           label = "****"),
                       size = 1.2,
               label.size = 7,
                       data = subset(res_sign, FN == "PA γ60"),
               inherit.aes = FALSE) #+
  # labs(caption = "STATISTICS: \nMann-Whitney U-test:\n# = Control vs. FN\n* = New vs. Used\nn = 16") + 
  # theme(plot.caption = element_text(family = "serif", 
  #              face = "bold", 
  #              color = 1, 
  #              size = 12, 
  #              hjust = 0.99, 
  #              vjust = 263, 
  #              angle = 0, 
  #              lineheight = 1)) 
```


```{r General plot with statistics, eval=FALSE, include=FALSE}

MWU_Lett_all <- bind_rows(MWU_n_Lett_Used, MWU_n_Lett_New) %>% mutate(label = if_else(state == "new", NA, label)) %>% 
  mutate(FN = if_else(grepl("pa_g60", FN), "PA6 \u03B3 60",
                      if_else(grepl("pa_g33", FN), "PA6 \u03B3 33",
                                       if_else(grepl("pbs_d60", FN), "PBS-PBAT \u03B4 60",
                                               if_else(grepl("pbs_d35", FN), "PBS-PBAT \u03B4 35",
                                                       if_else(grepl("pe_e4.25", FN), "PE-PP \u03B5 4.25",
                                                               if_else(grepl("pa_b95", FN), "PA6 \u03B2 95",
                      if_else(grepl("pa_b33", FN), "PA6 \u03B2 33",
                              if_else(grepl("pa_a33", FN), "PA6 \u03B1 35", 
                                      if_else(grepl("dmso", FN), "Solvent control", FN))))))))))
MWU_Lett_all

BoxBPM_all <- HR_aju %>% filter(FN != "benzo", !(aju_HR <75)) %>%
  mutate(FN = if_else(grepl("pa_g60", FN), "PA6 \u03B3 60",
                      if_else(grepl("pa_g33", FN), "PA6 \u03B3 33",
                                       if_else(grepl("pbs_d60", FN), "PBS-PBAT \u03B4 60",
                                               if_else(grepl("pbs_d35", FN), "PBS-PBAT \u03B4 35",
                                                       if_else(grepl("pe_e4.25", FN), "PE-PP \u03B5 4.25",
                                                               if_else(grepl("pa_b95", FN), "PA6 \u03B2 95",
                      if_else(grepl("pa_b33", FN), "PA6 \u03B2 33",
                              if_else(grepl("pa_a33", FN), "PA6 \u03B1 35", 
                                      if_else(grepl("dmso", FN), "Solvent control", FN)))))))))) %>% 
  mutate(state = if_else(state == "used", "EOL", state)) %>% 
  mutate(state = factor(state, levels = c("new", "EOL"))) %>% 
  ggplot(aes(x = FN, y = aju_HR, fill = FN)) +
  geom_boxplot(width = 0.2, position = position_dodge(width = 0.6)) +
  stat_summary(fun = mean, 
               geom = "point", 
               size = 2, 
               color = "red3", 
               position = position_dodge(width = 0.6)) +
  # stat_summary( 
  #   fun.data = stat_box_data, 
  #   geom = "text", 
  #   hjust = 0.5,
  #   vjust = 0.9, 
  #   position = position_dodge(width = 0.85)) +
  facet_grid(~state) +
  scale_y_continuous(limits = c(70, 145), breaks = seq(70, 145, by = 10)) +
  geom_hline(yintercept = 100, colour = "black", linetype = "dashed") +
  theme_bw() +
  labs(x = "Fishing nets",
       y = "Heart rate (% of the control)",
       title = expression(paste("Effect of dmso extracts on the cardiac rhythm of ", italic("Oryzias latipes"), " larvae")),
       subtitle = "Exposure time 48 hours \nMesoplastic eq. concentration 330 µg/ml\nDMSO dilution 1/1000",
       fill = "Treatment" ) +
  scale_fill_manual(values = Color_real_FN4) +
  theme(axis.title.x = element_text(size = 20, face = "bold", vjust = -4, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.title.y = element_text(size = 20, face = "bold", vjust = 4, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 18, face = 'bold'),
        title = element_text(size = 18, face = "bold", margin = margin(t = 0, r = 0, b = 20, l = 0)),
        strip.text = element_text(face = "bold", size = rel(2)),
        strip.background = element_rect(fill = "grey", color = "grey", size = 0.1),
        legend.title= element_text(size = 18, face = "bold", vjust = 1, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        legend.text = element_text(size = 18),
        legend.spacing.x = unit(0.5, 'cm'),
        legend.spacing.y = unit(0.2, 'cm'),
        legend.position = "right",
        plot.margin = unit(c(1, 1, 2, 1), "cm")) +
  guides(fill = guide_legend(byrow = TRUE))
BoxBPM_all

BoxBPM_all + 
  geom_text(data = MWU_Lett_all, aes(x = FN, y = max_value -1, label = label),
            size = 5, vjust = -1, color="black", 
            position = position_dodge(width=0.6),
            show.legend = FALSE,
            na.rm = F) +
  labs(caption = "Kruskal Wallis test with holm correction: \nnew: p > 0.05 \nused: p < 0.05\nPostHoc test: Dunn test\nn = 16") + 
  theme(plot.caption = element_text(family = "serif", 
               face = "bold", 
               color = 1, 
               size = 12, 
               hjust = 0.99, 
               vjust = 225, 
               angle = 0, 
               lineheight = 1))

#-----------------

BoxBPM_n_vs_u <- HR_aju %>% filter(FN != "benzo", FN != "dmso", !(aju_HR <75)) %>%
  mutate(FN = if_else(grepl("pa_g60", FN), "PA6 \u03B3 60",
                      if_else(grepl("pa_g33", FN), "PA6 \u03B3 33",
                                       if_else(grepl("pbs_d60", FN), "PBS-PBAT \u03B4 60",
                                               if_else(grepl("pbs_d35", FN), "PBS-PBAT \u03B4 35",
                                                       if_else(grepl("pe_e4.25", FN), "HPPE-PP \u03B5 4.25",
                                                               if_else(grepl("pa_b95", FN), "PA6 \u03B2 95",
                      if_else(grepl("pa_b33", FN), "PA6 \u03B2 33",
                              if_else(grepl("pa_a33", FN), "PA6 \u03B1 35", FN))))))))) %>% 
  ggplot(aes(x = state, y = aju_HR, fill = FN)) +
  geom_boxplot(width = 0.2, position = position_dodge(width = 0.6)) +
  stat_summary(fun = mean, 
               geom = "point", 
               size = 2, 
               color = "red3", 
               position = position_dodge(width = 0.6)) +
  # stat_summary( 
  #   fun.data = stat_box_data, 
  #   geom = "text", 
  #   hjust = 0.5,
  #   vjust = 0.9, 
  #   position = position_dodge(width = 0.85)) +
  facet_grid(~FN, scales = "free_x") +
  scale_y_continuous(limits = c(70, 145), breaks = seq(70, 145, by = 10)) +
  geom_hline(yintercept = 100, colour = "black", linetype = "dashed") +
  theme_bw() +
  labs(x = "Fishing nets",
       y = "Heart rate (% of the control)",
       title = expression(paste("Effect of dmso extracts on the cardiac rhythm of ", italic("Oryzias latipes"), " larvae")),
       subtitle = "Exposure time 48 hours \nMesoplastic eq. concentration 330 µg/ml\nDMSO dilution 1/1000",
       fill = "Treatment" ) +
  scale_fill_manual(values = Color_real_FN4) +
  theme(axis.title.x = element_text(size = 20, face = "bold", vjust = -4, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.title.y = element_text(size = 20, face = "bold", vjust = 4, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        axis.text.x = element_text(size = 18, face = 'bold'),
        axis.text.y = element_text(size = 18, face = 'bold'),
        title = element_text(size = 18, face = "bold", margin = margin(t = 0, r = 0, b = 20, l = 0)),
        strip.text = element_text(face = "bold", size = rel(2)),
        strip.background = element_rect(fill = "grey", color = "grey", size = 0.1),
        legend.title= element_text(size = 18, face = "bold", vjust = 1, margin = margin(t = 0, r = 5, b = 0, l = 0)),
        legend.text = element_text(size = 18),
        legend.spacing.x = unit(0.5, 'cm'),
        legend.spacing.y = unit(0.2, 'cm'),
        legend.position = "none",
        plot.margin = unit(c(1, 1, 2, 1), "cm")) +
  guides(fill = guide_legend(byrow = TRUE))
BoxBPM_n_vs_u

BoxBPM_n_vs_u + 
   geom_bracket(aes(xmin = 1 , xmax= 2, 
                           y.position = 130,
                           label = "***"),
                       size = 1,
                       data = subset(res_sign, FN == "HPPE-PP \u03B5 4.25"),
               inherit.aes = FALSE) +
  geom_bracket(aes(xmin = 1 , xmax= 2, 
                           y.position = 130,
                           label = "*"),
                       size = 1,
                       data = subset(res_sign, FN == "PA6 α 35"),
               inherit.aes = FALSE) +
  geom_bracket(aes(xmin = 1 , xmax= 2, 
                           y.position = 143,
                           label = "***"),
                       size = 1,
                       data = subset(res_sign, FN == "PA6 β 33"),
               inherit.aes = FALSE) +
  geom_bracket(aes(xmin = 1 , xmax= 2, 
                           y.position = 145,
                           label = "**"),
                       size = 1,
                       data = subset(res_sign, FN == "PA6 β 95"),
               inherit.aes = FALSE) +
  geom_bracket(aes(xmin = 1 , xmax= 2, 
                           y.position = 130,
                           label = "****"),
                       size = 1,
                       data = subset(res_sign, FN == "PA6 γ 60"),
               inherit.aes = FALSE) +
  geom_bracket(aes(xmin = 1 , xmax= 2, 
                           y.position = 130,
                           label = "**"),
                       size = 1,
                       data = subset(res_sign, FN == "PBS-PBAT δ 35"),
               inherit.aes = FALSE) +
  geom_bracket(aes(xmin = 1 , xmax= 2, 
                           y.position = 130,
                           label = "**"),
                       size = 1,
                       data = subset(res_sign, FN == "PBS-PBAT δ 60"),
               inherit.aes = FALSE) +
  labs(caption = "Statistics:\nMann-Whitney U-test\n* = p-value < 0.05\n** = p-value < 0.01\n*** = p-value < 0.001\n**** = p-value < 0.0001\nn = 16") + 
  theme(plot.caption = element_text(family = "serif", 
               face = "bold", 
               color = 1, 
               size = 12, 
               hjust = 0.99, 
               vjust = 225, 
               angle = 0, 
               lineheight = 1))



```


```{r Correlation using time}

df_used_time <- df_avg_HR %>% 
  filter(state == "used") %>% 
  mutate(U_time = if_else(FN == "pa_g60", 624,
                          if_else(FN == "pa_g33", 624,
                                  if_else(FN == "pbs_d60", 624,
                                          if_else(FN == "pbs_d35", 624,
                                                  if_else(FN == "hppe_e4.25", 8280,
                                                          if_else(FN == "pa_b95", 2700,
                                                                  if_else(FN == "pa_b33", 2700,
                                                                          if_else(FN == "pa_a33", 640, NA))))))))) 

df_used_time

correlation <- cor.test(df_used_time$mean, df_used_time$U_time, method = "spearman")
correlation

# Créer le graphique avec ggplot2
ggplot(df_used_time, aes(x = U_time, y = mean)) +
  geom_point(color = "blue") + # Points en bleu
  geom_smooth(method = "lm", color = "red", fill = "red", alpha = 0.2) + # Régression linéaire avec intervalle de confiance
  labs(title = "Correlation between per_Inhni and U_time",
       x = "U_time (hours)",
       y = "per_Inhi") +
  theme_bw() 

```

No correlation between the bioluminescence inhibition and the time for which the Fn were used for.

```{r Correlation surface exchanges}

df_S_Ex <- df_avg %>% 
  filter(FN != "dmso", state != "used+", state == "used") %>% 
  mutate(S_Ex = if_else(FN == "pa_g60", 34.1,
                          if_else(FN == "pa_g33", 52.1,
                                  if_else(FN == "pbs_d60", 26.8,
                                          if_else(FN == "pbs_d35", 40.4,
                                                  if_else(FN == "hppe_e425", 11.7,
                                                          if_else(FN == "pa_b95", 95.3,
                                                                  if_else(FN == "pa_b33", 53.0,
                                                                          if_else(FN == "pa_a35", 66.6, NA))))))))) 

df_S_Ex

correlation <- cor.test(df_S_Ex$mean, df_S_Ex$S_Ex, method = "spearman")
correlation

# Créer le graphique avec ggplot2
ggplot(df_S_Ex, aes(x = S_Ex, y = mean)) +
  geom_point(color = "blue") + # Points en bleu
  geom_smooth(method = "lm", color = "red", fill = "red", alpha = 0.2) + # Régression linéaire avec intervalle de confiance
  labs(title = "Correlation between per_Inhni and U_time",
       x = "U_time (hours)",
       y = "per_Inhi") +
  theme_bw() 

```


```{r Correlation using time}

df_used_time <- df_avg_HR %>% 
  filter(state == "used", FN != "dmso") %>% 
  mutate(U_time = if_else(FN == "pa_g60", 624,
                          if_else(FN == "pa_g33", 624,
                                  if_else(FN == "pbs_d60", 624,
                                          if_else(FN == "pbs_d35", 624,
                                                  if_else(FN == "pe_e4.25", 8280,
                                                          if_else(FN == "pa_b95", 2700,
                                                                  if_else(FN == "pa_b33", 2700,
                                                                          if_else(FN == "pa_a33", 640, NA))))))))) 

df_used_time

correlation <- cor.test(df_used_time$avg_HR_adj, df_used_time$U_time, method = "spearman")
correlation

# Créer le graphique avec ggplot2
ggplot(df_used_time, aes(x = U_time, y = avg_HR_adj)) +
  geom_point(color = "blue") + # Points en bleu
  geom_smooth(method = "lm", color = "red", fill = "red", alpha = 0.2) + # Régression linéaire avec intervalle de confiance
  labs(title = "Correlation between per_Inhni and U_time",
       x = "U_time (hours)",
       y = "per_Inhi") +
  theme_bw() 

```

No correlation between the bioluminescence inhibition and the time for which the Fn were used for.

```{r Correlation surface exchanges}

df_S_Ex <- df_avg_HR %>% 
  filter(FN != "dmso", state != "used+", FN != "dmso") %>% 
  mutate(S_Ex = if_else(FN == "pa_g60", 34.1,
                          if_else(FN == "pa_g33", 52.1,
                                  if_else(FN == "pbs_d60", 26.8,
                                          if_else(FN == "pbs_d35", 40.4,
                                                  if_else(FN == "pe_e4.25", 11.7,
                                                          if_else(FN == "pa_b95", 95.3,
                                                                  if_else(FN == "pa_b33", 53.0,
                                                                          if_else(FN == "pa_a33", 66.6, NA))))))))) 

df_S_Ex

correlation <- cor.test(df_S_Ex$avg_HR_adj, df_S_Ex$S_Ex, method = "spearman")
correlation

# Créer le graphique avec ggplot2
ggplot(df_S_Ex, aes(x = S_Ex, y = avg_HR_adj)) +
  geom_point(color = "blue") + # Points en bleu
  geom_smooth(method = "lm", color = "red", fill = "red", alpha = 0.2) + # Régression linéaire avec intervalle de confiance
  labs(title = "Correlation between per_Inhni and U_time",
       x = "U_time (hours)",
       y = "per_Inhi") +
  theme_bw() 

```

No correlation between the bioluminescence inhibition and the FN's surface exchanges.

No correlation between the bioluminescence inhibition and the time for which the Fn were used for.

```{r Correlation surface exchanges}

df_S_Ex <- df_avg %>% 
  filter(FN != "dmso", state != "used+", state == "used") %>% 
  mutate(S_Ex = if_else(FN == "pa_g60", 34.1,
                          if_else(FN == "pa_g33", 52.1,
                                  if_else(FN == "pbs_d60", 26.8,
                                          if_else(FN == "pbs_d35", 40.4,
                                                  if_else(FN == "hppe_e425", 11.7,
                                                          if_else(FN == "pa_b95", 95.3,
                                                                  if_else(FN == "pa_b33", 53.0,
                                                                          if_else(FN == "pa_a35", 66.6, NA))))))))) 

df_S_Ex

correlation <- cor.test(df_S_Ex$mean, df_S_Ex$S_Ex, method = "spearman")
correlation

# Créer le graphique avec ggplot2
ggplot(df_S_Ex, aes(x = S_Ex, y = mean)) +
  geom_point(color = "blue") + # Points en bleu
  geom_smooth(method = "lm", color = "red", fill = "red", alpha = 0.2) + # Régression linéaire avec intervalle de confiance
  labs(title = "Correlation between per_Inhni and U_time",
       x = "U_time (hours)",
       y = "per_Inhi") +
  theme_bw() 

```

No correlation between the bioluminescence inhibition and the FN's surface exchanges.

